### 2017-04-05 paperMVVB_backup_2017-03-30/sections/content.tex
Folder paperMVVB_backup_2017-03-30 added.

\section{Introduction}

With his theoretical solar wind model \citet{Parker1958} laid the foundations...\\

Several space missions flew away from Earth's orbit to measure in situ solar wind at different heliocentric distances (e.g. the probes Helios, Voyager, Ulysses...). Voyager~1 is the farthest probe out of the solar system, covering more than 137~au (time? cite?). Ulysses was the single probe orbiting the Sun outside the ecliptic and retrieving solar wind measurements from the poles of the Sun. So far, Helios~2 made the nearest in situ solar wind measurements with \SI{0.29}{\au}, followed closely by Helios~1 with \SI{0.31}{\au}. The new mission Solar~Probe~Plus~(SPP), whose planned launch date is in mid 2018, aims to reach further down into the Sun's atmosphere.

%Solar Probe Plus
The main part of the SPP mission's goals is to gain insight into the coronal heating and solar wind acceleration processes. As these processes occur in the near-Sun region of the corona, SPP will have its closest perihelion at 9.86~solar radii (0.0459~au) \citep{Fox2015}. It will be the first spacecraft flying and measuring in situ solar wind this close to the Sun. Its planned observations range from the perihelion up to \SI{0.25}{\au}, leaving the outer part for data transfer, as \citet{Fox2015} state in their description of SPP's mission design.\\

white light imager WISPR... \citep{Vourlidas2016}\\

There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites...). They examine average values, additionally distinguishing between slow and fast wind. In this paper we instead look at the variations of the whole frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\

%definition of sw environment
\section{Solar wind environment}

%solar wind parameters
The goal of this paper is to estimate the solar wind environment SPP will probe during its orbits. We regard the solar wind primarily as a proton plasma, because protons make up most of it. The average helium abundance is only about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}. Neglecting heavier ions, the electron and mass density can be derived accordingly.

Generally, the characteristic behavior of a plasma is determined by its \textit{density}, \textit{temperature} and \textit{magnetic field strength}. Furthermore, the bulk \textit{velocity} is the parameter which makes the plasma a 'wind'. For our study we define the solar wind environment as the four major solar wind parameters. Quantities like flux densities, mass flux and plasma beta can directly be derived from those four parameters.

In addition, the velocity is the defining parameter of the two types of solar wind. Solar wind mostly consists of and switches between slow and fast wind, whose ratio highly depends on solar activity. These types have different characteristics and their interactions lead to phenomena such as interaction regions. Additionally there also are coronal mass ejections (CMEs) embedded, whose occurrence rate follows solar activity too. Their share varies between almost zero in cycle minimum up to a half in maximum. This study averages over these internal solar wind structures.

%frequency distribution data
One cannot know which specific solar wind type or structure SPP will encounter at a given point in time, so we extrapolate the parameters' probability distributions from existing solar wind measurements.

Our approach is to get an analytical representation of the frequency distributions' shapes, their solar activity dependence and their solar distance scaling. We get the parameters' frequency distributions and solar activity dependence from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles and their distance dependency from solar wind measurements of more than half a solar cycle covering more than two third of the distance to the Sun (\SIrange{0.29}{0.98}{\au}).%0.68~au\\

From the combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions we build a general model representing the solar activity and distance behavior of all four solar wind parameter frequencies.

This general model is then fed with a SSN prediction and extrapolated to SPP's planned orbital positions.\\
% 
% \begin{itemize}
% % 	\item We determine the fit function type for the parameters' frequency distributions with OMNI data.
% %	\item We determine the fit function type for the parameters' solar cycle dependency with OMNI and SSN data.
% % 	\item We determine the fit function type for the parameters' distance dependency with Helios data.
% 	\item Time dependent (yearly) distribution magnitudes versus solar activity. for OMNI
% % 	\item The function's behavior in direction of Sun down to \SI{0.0459}{\au} is evaluated.
% % 	\item We fit exponential (double) lognormal functions to (distance-binned) Helios data (Helios solar wind model).
% % 	\item We combine the obtained distance dependencies with the obtained solar activity relations (dynamical solar wind model).
% 	\item resulting dynamical model dependencies (distance, SSN)
% 	\item use extrapolated SSN (SILSO) of SPP mission for solar wind extrapolation (SPP solar wind estimation model).
% \end{itemize}
%

%lognormal fitting
%%%%%%%%%%%%%%%%%%
\section{Frequency distributions}
\label{sec:frequency_distribution}
This section looks at the solar wind parameters' frequency distributions which we extract from the in situ OMNI data set. We determine adequate fit function types and evaluate if they are suitable to represent the frequencies' shapes.

\subsection{OMNI frequency data}
\label{sec:omni_frequency_data}
The solar wind parameters are highly variable, due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on solar activity. Hence, for deriving general frequency distributions of the solar wind parameters, averaging over long-time solar wind variations is needed. This requires a distance-independent data set covering multiple solar cycles. The abundance of near-Earth hourly OMNI data is well suited for this task, because it spans almost five solar cycles.

%about OMNI data
This OMNI~2 data set \citep{King2005} combines solar wind plasma and magnetic field data and for this study not important energetic proton fluxes, geomagnetic and solar indices. Because it covers decades, the near-Earth solar wind data is composed of intercalibrated multi-spacecraft data which is time-shifted to the nose of the Earth's bow shock.

%data source
The data is obtained from the OMNIWeb interface\footnote{\url{http://omniweb.gsfc.nasa.gov/}} at NASA's Space Physics Data Facility (SPDF), Goddard Space Flight Center (GSFC).
%OMNIWeb Data Documentation: http://omniweb.gsfc.nasa.gov/html/ow_data.html
% Acknowledgement to the SPDF OMNIWeb database as the source of data used in publications is requested: "The OMNI data were obtained from the GSFC/SPDF OMNIWeb interface at http://omniweb.gsfc.nasa.gov". Further, for recent years when few sources (IMP 8, Wind, ACE, Geotail) contributed to OMNI, it would be appropriate to also cite the PI's who provided the data to OMNI. Copies of preprints or reprints of OMNI-based publications sent to Natalia Papitashvili (address below) would be appreciated for tracking purposes.
% The best citable reference to OMNI data is J.H. King and N.E. Papitashvili, Solar wind spatial scales in and comparisons of hourly Wind and ACE plasma and magnetic field data, J. Geophys. Res., Vol. 110, No. A2, A02209, 10.1029/2004JA010804.
%
%data time range
The hourly data of the whole time range (\textgreater50~years) up to \mbox{2016-12-31} is the basis for the frequency fits. The data starts in \mbox{1963-11-27}, but the temperature data not before \mbox{1965-07-26}. The data coverage of the parameters is between \SIrange{67}{74}{\percent}, which adds up to about 36--40~years in total. This plethora of data is well suited for our task.
%OMNI 1963-01-01 data
%B 1963-11-27 14:30
%V 1963-11-27 12:30
%N 1963-11-27 12:30
%T 1965-07-26 00:30
%1963-01-01~00:00--2016-12-31~23:30 all
%19724 d; 54 y\\
% B: 73.91 \%		39.91 y\\
% V: 73.07 \%		39.46 y\\
% N: 70.29 \%		37.96 y\\
% T: 66.73 \%		36.03 y\\

%data binning
We specify bin sizes considering the individual maximal parameter ranges and the OMNI data precision. Especially for the density and temperature we choose their bin sizes such small that their distributions' peaks can be resolved (the peaks are at their lower end). We set the individual bin sizes to \SI{0.5}{nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.

Next, we look for a suitable fit function for the resulting histogram shape of the solar wind parameters' frequency distributions.
% $B$: bin size 0.5~nT\\
% $v$: bin size 10~km/s\\
% $n$: bin size 1~cm$^{-3}$\\
% $T$: bin size 10\,000~K\\

\subsection{Lognormal fitting}
%choice of distribution function?/why lognormal function?
Obviously all possible values for the four parameters are positive. This hints to the supposition that they are lognormally distributed, as many positive natural quantities conform to a lognormal distribution. This distribution is described by a lognormal function.
%fitting method
Therefore we use a lognormal function as the fit function in the process of the least squares regression fitting.
%fit function
The lognormal function
\begin{align}
	W(x) &= \frac{1}{\sigma \sqrt{2 \pi} x} \, \exp\left(- \frac{\left(\ln x - \mu\right)^2}{2 \sigma^2}\right)	\label{eq:lognormal_function}
\end{align}
depends on the location $\mu$ and the shape parameter $\sigma$. Changes in $\mu$ affect both the horizontal and vertical scaling of the function whereas $\sigma$ influences its shape. The distribution's median $x_\text{med}$ and mean $x_\text{avg}$ (average) positions are easier to interprete and can directly be calculated from $\mu$ and $\sigma$:
\begin{align}
	x_\text{med} &= \exp\left(\mu\right)	&	&\Longleftrightarrow	&	\mu &= \ln\left(x_\text{med}\right)\,,	\label{eq:lognormal_median}\\
	x_\text{avg} &= \exp\left(\mu + \frac{\sigma^2}{2}\right)	&	&\Longleftrightarrow	&	\sigma &= \sqrt{2 \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)}\,.	\label{eq:lognormal_mean}
\end{align}
It is apparent that the mean is always larger than the median. Replacing the variables $\mu$ and $\sigma$ with these relations, the lognormal function~(\ref{eq:lognormal_function}) becomes
\begin{align}
	W(x) = \frac{1}{2 \sqrt{\pi \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)} \, x} \, \exp\left(- \frac{\ln^2\left(\frac{x}{x_\text{med}}\right)}{4 \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)}\right)\,.	\label{eq:single_lognormal_fit_function}
\end{align}
The values of $x_\text{med}$ and $x_\text{avg}$ obtained from fitting the solar wind frequency distributions are listed in Table~\ref{tab:lognormal_fit_parameters}.
\begin{table*}
	\caption{The resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au}. For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit. The sums of absolute residuals are shown as well. The values in brackets are the estimated standard deviation of each fit parameter.}
	\label{tab:lognormal_fit_parameters}
	\centering
	\sisetup{table-figures-integer=1, table-figures-decimal=4, table-figures-exponent=0}
	\begin{tabular}{l@{} c
		S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
		S[table-format = 2.3(2), table-space-text-post = a, table-align-text-post = false]
		@{}c@{}
		S[table-format = 2.1]
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{SAR}\\
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[\%]}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&6.83\\
		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&18.69\\
		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&6.48\\
		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&5.78\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
		\cline{2-6}
			&\multicolumn{1}{c}{$W_\text{II}$}	&4.12(14)\tablefootmark{b}	&4.38(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&4.20\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
	}
\end{table*}
% Vdbl fit:
% ('medians = ', 489.31184203751639, 368.3008016238619)
% ('means = ', 500.432137424129, 371.82451161611743)
% mean = 437.7390999905267
% median = 412.4937999968638

% fit data difference (normed area):\\
% B: 0.0682978\\
% v: 0.186874 -> 0.0419676 (double fit)\\
% n: 0.0648273\\
% T: 0.0578349\\

From visual inspection, the resulting curves match well with the shape of the magnetic field strength, density and temperature distributions (Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}). However, for the velocity the fit function seems insufficient in describing its more complex shape, especially at its peak position and the faster end of the distribution. Its sum of absolute residuals (SAR) between data and fit is almost three times larger than those from the other parameters (Table~\ref{tab:lognormal_fit_parameters}). They can be compared, because the area of probability distributions is unity.
\begin{figure*}
	\includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits. The histograms have bins of 0.5~nT, 10~km/s, 1~cm$^{-3}$ and 10\,000~K and are based on the hourly OMNI data set. The fit's median and mean values are indicated as well. The insets only have zoomed-in frequency axes, their x-axes stay the same.}
	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
\end{figure*}
% From the normed stdfit values (Table~\ref{tab:single_lognormal_fit_parameters}) we see that the velocity fit is not that good... \\
% While by visual inspection it is obvious, but also fit stdfit is an indication for a bad fit...\\
% What we see at visual inspection is the area difference between the fit and the data. This area is for the velocity almost three times larger than the other's.\\

%double lognormal fitting
%%%%%%%%%%%%%%%%%%%%%%%%%
%justification for compositional lognormal fit
To reach a better fit result for the velocity we change the fit function. We do not want to abandon the well-founded application of the lognormal function. However, it is reasonable to assume that the velocity distribution is composed of at least two branches (slow and fast). Therefore a compositional approach promises better fit results, which is why we combine two lognormal functions (\ref{eq:single_lognormal_fit_function}), bearing the disadvantage of more fit variables:
\begin{align}
	W_\text{II}(x) &= c \cdot W_1(x) + (1 -c) \cdot W_2(x)\,.	\label{eq:double_lognormal_fit_function}
\end{align}
The balancing parameter $c$ ensures that the resulting function remains normalized as it represents a probability distribution.

The fitting of $W_\text{II}(x)$ to the velocity's frequency distribution gives the values of the now five fit parameters ($c$, $x_\text{med,1}$, $x_\text{avg,1}$, $x_\text{med,2}$ and $x_\text{avg,2}$), which are also listed in Table~\ref{tab:lognormal_fit_parameters} together with the median and mean of the composed distribution, which can be derived via solving
\begin{align}
	\int W_\text{II}(x)\,\text{d}x = 0	&	&\text{and}	&	&\int x\,W_\text{II}(x)\,\text{d}x = 0
\end{align}
respectively.\\
As anticipated, this more complex fit function is more accurate in describing the velocity's frequency distribution (see Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/histogram_fits_V_a_zoom_dbl_paper_pdfplot.pdf}}
	\caption{Plot of the velocity's frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit. The fit's median and mean values and its two fit parts are indicated as well. The inset only has a zoomed-in frequency axis, its x-axis stays the same.}
	\label{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}
\end{figure}
In this model the slow and fast part contribute almost equally.\\

In solar cycle maximun (minimum) CMEs contribute with a fraction of \SI{5}{\percent} (half \SI{50}{\percent}) \citep{Richardson2012}.\\

In the following sections we keep using the double lognormal ansatz for the velocity frequency fits...\\

%transition
For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well (the deviation from the fitted functions is less than \SI{7}{\percent}). This is different for the extreme values (which may come from CMEs). The simple lognormal fit models of the magnetic field strength, the velocity and the density underestimate their frequency at the high value tails, whereas the temperature's tail is overestimated (see insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}). The velocity's compositional lognormal fit only slightly overestimates its tail (inset in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).\\

Short-term variations in the solar wind cannot be predicted, but their occurrence rate can. It depends on solar activity, which changes cyclically and thus can be forecasted to a certain degree---at least within a solar cycle.\\

\section{Solar activity variations}
\label{sec:solar_activity_variations}
This section aims to relate changes in the four solar wind parameters to general solar activity. For this we examine their correlations to the yearly sunspot number and determine the lag times with the highest coefficients. Next, we fit lognormal functions to the frequency distributions like before, but implement linear relations to the yearly SSN to shift the distributions. Only for the velocity the approach is different in that its two components are kept fixed and instead their balance is modified with changing SSN.

\subsection{SSN data}
Solar activity is commonly measured via the sunspot number.\\

activity -- cycle -- forecast -- yearly SSN\\

The international sunspot number is retrieved from the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
\citet{sidc}\\

why use only yearly SSN data?\\
because OMNI in situ measurements are from Earth orbit (causing variations in solar latitude and distance)\\
seasonal influence contained within yearly frequency distributions\\
yearly OMNI data\\

\subsection{SSN correlation}
We are interested in the correlation of the median, because it defines the position of the lognormal function.\\
yearly parameter medians and yearly SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot})\\

Deriving the correlation coefficients for different time lags between solar wind parameters and SSN (see also Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}).\\

The highest correlation coefficient for the magnetic field strength is 0.728. It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the solar surface magnetic flux (cite?).\\
Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540). The density even 6~years (0.468).\\
% maximal correlation coefficients and their lag times:\\
% magnetic field strength: lag 0, 0.728\\
% velocity: lag -3, 0.453\\
% density: lag -6, 0.468\\
% temperature: lag -3, 0.540\\

cause: direct/indirect correlation\\
cite literature to lag time...\\

\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_b_plot.pdf}}
	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} (top). Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
	\label{fig:OMNI_yearly_ssn_correlation_b_plot}
\end{figure}

\subsection{SSN fitting}
\label{sec:ssn_fitting}
yearly SSN sw model to sw data fits -> SSN dependency (figs)\\

To shift the distributions with SSN, we fit a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. The two values median and mean are sufficient to fully describe lognormal functions, so we relate the mean with a scaling factor to the median to keep the dependency on SSN: (why can we do that? mean proportional to median)
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new fit function $W'(x,ssn)$ is then fitted to the data. The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.\\
\begin{table*}
	\caption{The resulting fit coefficients from the data fitting with SSN. For the velocity the fit parameters from the double lognormal fit and their balancing function are given. The values in brackets are the estimated standard deviation of each fit parameter.}
	\label{tab:ssn_fit_parameters}
	\centering
%	\sisetup{table-figures-integer=1, table-figures-decimal=4, table-figures-exponent=1}
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Baseline $b_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
			&\multicolumn{1}{c}{$W_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

In comparison with the data the fit models roughly match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVNTSSN_fit_b_plot}).\\
\begin{figure*}
	\includegraphics[width=18cm]{figures/OMNI_yearly_BVNTSSN_fit_b_plot.pdf}
	\caption{Solar wind parameter frequencies, lognormal fit models and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016. The for the model shifted SSN is indicated by a black line.}
	\label{fig:OMNI_yearly_BVNTSSN_fit_b_plot}
\end{figure*}

Again, the velocity gets a special treatment with the double lognormal distribution (see Eq.~\ref{eq:double_lognormal_fit_function}), this time keeping its two components' positions constant and variing instead their balance with the SSN:	(discuss why...)
\begin{align}
	c(ssn) &= c_a \cdot ssn + c_b\,.
\end{align}
The fit result is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_b_plot.pdf}}
	\caption{Ratio of slow to fast solar wind depending on the by 3~years lagged SSN. The relation results from the velocity's double lognormal fit.}
	\label{fig:Vdbl_SSN_ratio_b_plot}
\end{figure}

All fit coefficients are given in Table~\ref{tab:ssn_fit_parameters}).\\

In comparison with the data the fit model roughly matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_VSSN_dblfit_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_VSSN_dblfit_plot.pdf}}
	\caption{Velocity frequency, double lognormal fit model and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016. The for the model shifted SSN is indicated by a black line.}
	\label{fig:OMNI_yearly_VSSN_dblfit_plot}
\end{figure}
3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
...compare with data\\

density modulation with SSN \citep{Schwenn1983} p.~499\\
density anticorrelation with SSN \citep{Bougeret1984} p.~406\\

%exponential fitting
%%%%%%%%%%%%%%%%%%%%
\section{Solar distance dependency}
\label{sec:solar_distance_dependency}

In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and evaluate the fits' extrapolation behavior in direction to the Sun.

To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data. This results in solar wind models comprising of exponentially with distance shifted lognormal functions.

%Helios data
\subsection{Helios distance data}
\label{sec:helios_distance_data}

The Helios probes were the only spacecraft measuring in situ solar wind over large solar distance ranges in the inner heliosphere. We use the combined data from both Helios~1 and Helios~2 probes. Helios~1's (Helios~2's) highly elliptical orbit in the ecliptic covered a solar distance range of \SIrange{0.31}{0.98}{\au} (\SIrange{0.29}{0.98}{\au}). Launched during solar cycle minimum, the data of both probes cover the rise to the maximum of cycle 21 ($\sim$6.5~years at varying distances).

Helios~1's (Helios~2's) merged hourly data set from the magnetometer and plasma instruments \citep{Rosenbauer1977} includes $\sim$12.5~orbits ($\sim$8~orbits) in the time range \mbox{1974-12-10} to \mbox{1981-06-14} (\mbox{1976-01-01} to \mbox{1980-03-04}).
%Helios plasma instrument (E1); Helios magnetometer instrument (E2)
% Helios data ranges:\\
% - time range Helios~1 [1974-12-10--1981-06-14] (12.5~orbits), Helios~2 [1976-01-01--1980-03-04] (8~orbits)\\
% - solar distance range Helios~1 0.31--0.98~au, Helios~2 0.29--0.98~au\\
%data sources
The Helios data was retrieved from the Coordinated~Data~Analysis~Web (CDAWeb) interface at NASA's GSFC/SPDF\footnote{\url{http://spdf.gsfc.nasa.gov/}}.

The Helios~1 (Helios~2) magnetometer data coverage is about 43~\% (54~\%) and amounts to 2.8~years (2.3~years) in total. The plasma data coverage is 76~\% (92~\%) and amounts to 5.0~years (3.9~years) in total.
% temporal coverage of merged data\\
% Helios 1: 1974-12-10--1981-06-14; 6y6m15d = 2388~d = 6.538~y\\
% Mag data coverage: 42.6~\%; 2.785~years\\
% Plasma data coverage: 76.4~\%; 4.995~years\\
% Helios 2: 1976-01-01--1980-03-04; 4y3m4d = 1557~d = 4.263~y\\
% Mag data coverage: 54.4~\%; 2.319~years (83~\% of H1)\\
% Plasma data coverage: 91.8~\%; 3.913~years (78~\% of H1)\\
Thus, the Helios data cover only fractions of a solar cycle and cannot be used for deriving representative time-independent solar wind multi-cycle conditions like the OMNI data can.

%Helios data biased towards solar minimum
Using this data, we also have to keep in mind that its time coverage is unequally distributed over the solar cycle. Dividing the data by the transition from cycle minimum to maximum (mid 1977) and considering the data gap distributions, the Helios data covers about \SI{68}{\percent} during cycle minimum whereas during maximum only \SI{38}{\percent}.\\

% data gaps -> uneven coverage -> solar cycle minimum dominates; ratio of max vs min cycle data coverage; for OMNI data negligible\\
% 13~months smoothed sunspot number \citep{sidc}: divide June~1977 (include figure)\\
% put link on sidc webpage: http://sidc.be/sunspot-data/SIDCpub.php
% begin: 1974-12 36.1\\
% minimum: May/June 1976 18.3/17.9 (cite?)\\
% divide 30~June~1977 37.7 from SIDC data (nearly same SSN as at Helios~1 beginning)\\
% cycle 21 maximum: Dec 1979 232.9 (cite?)\\
% end: 1981-06 200.9\\
% 
% data gap hours and percentages:\\
% % H1 minimum 22416 h\\
% % H1 maximum 34681 h\\
% % H2 minimum 13128 h\\
% % H2 maximum 23472 h\\
% % sum 93697 h\\
% solar minimum: 35\,544~h, 37.94~\%\\
% solar maximum: 58\,153~h, 62.06~\%\\

% 1974 11 1974.874   39.3   4.2    30  
% 1974 12 1974.958   36.1   4.0    31  
% 1975 01 1975.042   33.0   3.9    31  
% 1975 02 1975.123   31.8   3.8    28  
% 1975 03 1975.204   30.6   3.7    31  
% 1975 04 1975.288   26.8   3.5    30  
% 1975 05 1975.371   24.2   3.3    31  
% 1975 06 1975.455   23.2   3.3    30  
% 1975 07 1975.538   21.8   3.2    31  
% 1975 08 1975.623   20.7   3.1    31  
% 1975 09 1975.707   20.9   3.1    30  
% 1975 10 1975.790   22.3   3.2    31  
% 1975 11 1975.874   23.3   3.3    30  
% 1975 12 1975.958   23.6   3.3    31  
% 1976 01 1976.042   22.1   3.2    31  
% 1976 02 1976.124   19.2   3.0    29  
% 1976 03 1976.206   17.8   2.9    31  
% 1976 04 1976.290   18.4   2.9    30  
% 1976 05 1976.373   18.3   2.9    31  
% 1976 06 1976.456   17.9   2.9    30  
% 1976 07 1976.540   18.8   2.9    31  
% 1976 08 1976.624   20.5   3.1    31  
% 1976 09 1976.708   20.8   3.1    30  
% 1976 10 1976.791   19.7   3.0    31  
% 1976 11 1976.874   19.7   3.0    30  
% 1976 12 1976.958   21.6   3.2    31  
% 1977 01 1977.042   24.3   3.3    31  
% 1977 02 1977.123   26.3   3.5    28  
% 1977 03 1977.204   28.8   3.6    31  
% 1977 04 1977.288   31.9   3.8    30  
% 1977 05 1977.371   34.7   4.0    31  
% 1977 06 1977.455   37.7   4.1    30  
% 1977 07 1977.538   41.4   4.3    31  
% 1977 08 1977.623   47.6   4.6    31  
% 1977 09 1977.707   55.8   5.0    30  
% 1977 10 1977.790   64.8   5.4    31  
% 1977 11 1977.874   73.7   5.7    30  
% 1977 12 1977.958   80.7   6.0    31  
% 1978 01 1978.042   86.9   6.2    31  
% 1978 02 1978.123   91.5   6.4    28  
% 1978 03 1978.204   98.7   6.6    31  
% 1978 04 1978.288  109.0   7.0    30  
% 1978 05 1978.371  117.8   7.2    31  
% 1978 06 1978.455  126.6   7.5    30  
% 1978 07 1978.538  138.0   7.8    31  
% 1978 08 1978.623  147.3   8.1    31  
% 1978 09 1978.707  153.6   8.3    30  
% 1978 10 1978.790  157.3   8.4    31  
% 1978 11 1978.874  160.4   8.5    30  
% 1978 12 1978.958  166.7   8.6    31  
% 1979 01 1979.042  175.2   8.8    31  
% 1979 02 1979.123  185.4   9.1    28  
% 1979 03 1979.204  193.3   9.3    31  
% 1979 04 1979.288  199.9   9.4    30  
% 1979 05 1979.371  208.5   9.6    31  
% 1979 06 1979.455  216.7   9.8    30  
% 1979 07 1979.538  219.5   9.9    31  
% 1979 08 1979.623  220.1   9.9    31  
% 1979 09 1979.707  220.4   9.9    30  
% 1979 10 1979.790  223.4  10.0    31  
% 1979 11 1979.874  229.8  10.1    30  
% 1979 12 1979.958  232.9  10.2    31  
% 1980 01 1980.042  232.0  10.2    31  
% 1980 02 1980.124  230.2  10.2    29  
% 1980 03 1980.206  227.9  10.1    31  
% 1980 04 1980.290  224.6  10.0    30  
% 1980 05 1980.373  221.3  10.0    31  
% 1980 06 1980.456  219.1   9.9    30  
% 1980 07 1980.540  216.1   9.9    31  
% 1980 08 1980.624  212.0  10.0    31  
% 1980 09 1980.708  211.5  10.2    30  
% 1980 10 1980.791  211.9  10.5    31  
% 1980 11 1980.874  209.1  10.9    30  
% 1980 12 1980.958  202.8  11.0    31  
% 1981 01 1981.042  199.6  11.1   271  
% 1981 02 1981.123  202.2  11.5   229  
% 1981 03 1981.204  205.4  12.1   244  
% 1981 04 1981.288  205.7  12.6   254  
% 1981 05 1981.371  204.1  12.8   268  
% 1981 06 1981.455  200.9  13.1   227  
% 1981 07 1981.538  198.5  13.1   268

For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.

\subsection{Exponential fitting}
%why exponential function?
An exponential distance behavior is expected from all four parameters (cites?). Therefore we use the exponential function
\begin{align}
	x(r) = a\,r^b	\label{eq:exponential_function}
\end{align}
with the solar distance $r$ for the regression fit of the median and mean. The fits are weighted by data counts per bin.
%fit result table and figure
With $r$ in astronomical units we get the fit coefficients ($a_\text{med}$, $a_\text{avg}$, $b_\text{med}$ and $b_\text{avg}$) as given in Table~\ref{tab:mean_median_fit_parameter}.\\
\begin{table*}
	\caption{These are the fit coefficients for the median and mean solar distance dependencies of the four parameters from the combined Helios data set. The errors in brackets are the estimated standard deviations of each fit parameter. The crossing distance is the point where median and mean intersect.}
	\label{tab:mean_median_fit_parameter}
	\centering
	\begin{tabular}{l
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	@{}c
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	S[table-format = 1.1(2)e1]}
		\hline\hline
		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}\\
		\cline{2-3}	\cline{5-6}
			&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b_\text{med}$}	&	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}\\
		\hline
		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)\\
		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3\\
		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)\\
		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

%crossing distances
The next step is to fit the bulk of the solar wind parameters with lognormal functions. At all considered solar distances the mean of the three plasma parameters is larger than their median (Fig.~\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}).
\begin{figure*}
	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_skip_pdfcairo_plot.pdf}
	\caption{Helios hourly data plots of the four solar wind parameters over solar distance. The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well. The Helios data has a native distance resolution of \SI{0.01}{\au}. To make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.}
	\label{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}
\end{figure*}
However, the magnetic field strength's mean crosses the median at \SI{0.339}{\au} (Table~\ref{tab:mean_median_fit_parameter}) and is lower at smaller distances. But at the crossing point and below the magnetic field strength can therefore not be described anymore with a lognormal function. For an extrapolation to the SPP perihelion the same happens for the temperature at \SI{0.082}{\au}.

The large velocity's crossing distance and its large error indicate that the median's and mean's distance behavior could be identical and so the frequency's shape distance independent.

Those crossings limit the possible extrapolation distances with lognormal functions. To circumvent these limitations we set the exponents $b_\text{med}$ and $b_\text{avg}$ to be identical, avoiding crossing of median and mean. Then the distribution's width is constant and scales only exponentially with solar distance. Applying this approximation, we have to accept larger fit errors. It also limits the extrapolation accuracy.

\subsection{Exponential lognormal fitting}
To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:omni_frequency_data}).\\
% Helios histogram bin sizes for mean of frequency distribution (at specific solar distance):\\
% $B$: bin size 0.5~nT, min 337, mean precision: 0.000545\\
% $v$: bin size 1~cm$^{-3}$, min 497, mean precision: 0.00449\\
% $n$: bin size 10~km/s, min 497, mean precision:  0.00449\\
% $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\

As mentioned before, we set the exponents of median and average to be identical. Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function \ref{eq:single_lognormal_fit_function}, we have three fit parameters $a_\text{med}$, $a_\text{avg}$ and the common exponent $b$. (change variable naming...)

Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c$ and from the second lognormal part $a_\text{med,2}$ and $a_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
\begin{table*}
	\caption{These are the resulting fit coefficients with the single lognormal exponential function, respectively double lognormal for the velocity. The errors in brackets are the estimated standard deviations of each fit parameter.}
	\label{tab:extrapolation_model_fit_parameters}
	\centering
	\sisetup{table-figures-integer=1, table-figures-decimal=3, table-figures-exponent=0}
	\begin{tabular}{l c
	S[table-format = 1.3(2)]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = +1.4(2)]}
		\hline\hline
		\multicolumn{2}{l}{Parameter}	&$c$	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&\multicolumn{1}{c}{--}	&5.358(25)	&5.705(28)	&-1.662(11)\\
		\multicolumn{2}{l}{Density}	&\multicolumn{1}{c}{--}	&5.424(33)	&6.845(47)	&-2.114(20)\\
		\multicolumn{2}{l}{Temperature}	&\multicolumn{1}{c}{--}	&6.357(64)	&10.72(14)	&-1.100(20)\\
		\hline
		\multirow{1}{*}{Velocity}	&$W''_1$	&\multirow{2}{*}{0.557(45)}	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}\\
			&$W''_2$	&	&5.26(13)	&5.42(11)	&\\
		\cline{2-6}
		\multicolumn{2}{r}{$W''_\text{II}$}	&\multicolumn{1}{c}{--}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
	}
\end{table*}

With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (vgl.Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}). derive value...\\

The fit models seem to resemble the data quite well (Fig.~\ref{fig:mixed_fit_fixed_4_paper_d_plot}). The magnetic field strength frequency is more focused (around \SI{40}{nT}) at the lower distance boundary than the model's is. This is expected because of our fixed distance independent shape approximation.\\
\begin{figure*}
	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_d_plot.pdf}
	\caption{Solar wind parameter's frequency distributions over solar distance. Plotted are the binned Helios data and the exponential lognormal fit model (double lognormal for the velocity). choose normed color scale for b/w plot...}
	\label{fig:mixed_fit_fixed_4_paper_d_plot}
\end{figure*}

model errors, maximum errors; see Fig.~XX (data - model, fit errors)\\
The extreme values of the velocity and temperature seem to be too high (adjust color scale...)\\
L-> high value plots... (refer to histogram zoom)\\

This model represents the Helios time frame around the rise of solar cycle~21.

\section{General solar wind model}
\label{sec:general_solar_wind_model}

Finally we combine the obtained solar activity and distance dependencies for shifting the frequency distributions. The result will be an empirical solar wind model for the inner heliosphere.\\

%are the exponents time-independent?
Under the assumption that the exponential falloff laws do not change with time/solar activity, they can be used in general (indications for that: fig. + theory + studies/papers...).\\
assuming the distance scaling laws are time independent, which we deduced...? which is an approximation.\\

We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the exponential distance dependency (\ref{eq:exponential_function}):
\begin{align}
	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^b\,.
\end{align}

the combined model function $W''(x,ssn,r)$\\

...and double lognormal function for the velocity\\

%model errors
give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$

\section{Model extrapolation to SPP orbital time and position}
To estimate the solar wind environment at SPP's planned orbital positions during its mission time, SSN predictions and extrapolations to the SPP perihelion region are included into the general solar wind model.\\

SPP orbit description, Venus flybys, ecliptic, \citep{Fox2015}, see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot}\\
choosing SSN prediction source as input (SIDC + SWPC + previous cycle), (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_b_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. 13-month smoothed monthly actual SSN and SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24.}
	\label{fig:SPP_orbit_predicted_SSN_overview_b_plot}
\end{figure}

plot of SPP's estimated solar wind environment from predicted SSN (Fig.~\ref{fig:SPP_orbit_sw_forecast_BVNT_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_sw_forecast_BVNT_plot.png}}
	\caption{Estimated B-field median and frequency distribution during the mission time period 2024--2025.}
	\label{fig:SPP_orbit_sw_forecast_BVNT_plot}
\end{figure}
zoom into first perihelion (new figure...)\\

% The extrapolation of the general solar wind model of the SPP orbit range is plotted in Fig.~\ref{fig:sw_model_extrapolation_4_paper_plot}.\\
% \begin{figure*}
% 	{\includegraphics[width=17cm]{figures/sw_model_extrapolation_4_paper_plot.pdf}}
% 	\caption{Extrapolated solar wind parameters in the SPP observation range (\SIrange{0.0459}{0.25}{\au}). The median, mean and \SI{95.45}{\percent} range are extrapolated from the general solar wind model. use color scaled plot?}
% 	\label{fig:sw_model_extrapolation_4_paper_plot}
% \end{figure*}

\subsection{Near-Sun extrapolation behavior/effects}

The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\

extrapolation errors...\\

velocity:\\
%critical surfaces
in direction to the Sun is at $\sim$2.5~Rs the source surface (Schatten1969)\\

sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\

approaching these regions, acceleration plays a role\\

The near-Sun (SPP perihelion) solar wind velocity is expected to be slower than our model estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\

density:\\
\citet{Leblanc1998} -> electron density model derived from type~III radio burst observations\\
The density distance dependency scales with $r^{-2}$, but steepens below 10~Rs with $r^{-6}$ \citep{Leblanc1998}.\\

magnetic field and temperature:\\
crossing distance effect\\

\subsection{Model requirements and limits}

model requirements:\\
- modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
- modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
- possibility to extrapolate model down to 0.0459~au\\

%model boundaries
model boundaries (spherical coordinates):\\
- mean solar wind of the Helios time range -> error size (determine deviation from average)\\
- heliocentric distance range 0.29--0.98~au\\
- rotational symmetry\\
- confined to ecliptic\\
model constrictions:\\
- solar distance dependency function\\
- frequency distribution function\\
- neglected influence from heliolatitude variation\\

\subsection{Model validity and error sources}
\label{sec:model_validity_and_errors}

validity and estimation of error size outside of valid model range...\\
derive heliocentric distance depending error...\\

list simplifications/approximations...\\

error sources:\\
- extrapolation\\
- model\\

all estimates outside these boundaries are extrapolations with large uncertainties. see Sect.~\ref{sec:model_validity_and_errors}\\

discuss high value zoom figures\\

Generally, the use of hourly data instead of higher resolution data (less than 1~min) should not have significant influence on the results. The minutely OMNI~2 data's frequency distributions are almost congruent and differ only slightly at their extreme ends (we tested that...).\\

The many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions \citep[p.~491]{Schwenn1983}.\\

The OMNI~2 data is time-shifted to the nose of the Earth's bow shock. This leads to yearly solar distance variations of \SI{>2}{\percent} (cite?) as the Earth orbits the Sun. Furthermore, its orbit within the ecliptic leads to a yearly variation of \SI{+-7.2}{\degree} in heliospheric latitude.\\
The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS) (cite?).\\
The HCS's position in latitude is highly variable around the solar equator \citep[p.~127~ff.?]{Schwenn1990}.\\

- over year (seasonal/monthly) -> expect them to be less than 5~\%\\

%monthly seasonal variation
Sun-Earth distance over the course of the year.\\
In the year 2017 Earth's perihelion was on 5~January with a distance of \SI{-1.67}{\percent} from \SI{1}{\au} (Horizons On-Line Ephemeris System\footnote{\url{http://ssd.jpl.nasa.gov/horizons.cgi}}, Solar System Dynamics Group, Jet~Propulsion Laboratory).\\
The cosine approximation
\begin{align}
	r_\text{E}(t) = 1 - 0.0167 \cdot \cos\left(2 \pi \left(t - 2017 - \frac{5}{365}\right)\right)\,,
\end{align}
with $t$ in years, suffices for our accuracy requirements.\\
% HORIZONS Web-Interface
% http://ssd.jpl.nasa.gov/horizons.cgi
% Ephemeris Type:	VECTORS
% Target Body:		Earth [Geocenter] [399]
% Coordinate Origin:	Sun (body center) [500@10]
% Time Span:		Start=2017-01-01, Stop=2017-12-31, Step=1 d
% Table Settings:	CSV format=YES
% Display/Output:	download/save (plain text file)
%-> distance:	9.833098226363186E-01
%-> diff. to 1 au:	0.166901774
%-> change to day before:	4.4e-6	-> 0.1669018(44)

seasonal variation function:\\
$X_\text{avg}(t) = a\,r_\text{E}(t)^b$\\
% B_avg = 5.969(29)~nT\\
% B_med = 5.435(24)~nT\\
% N_avg = 6.329(85)~cm-3\\
% N_med = 4.858(60)~cm-3\\
% T_avg = 1.198(16)e5~K\\
% T_med = 7.17(12)e4~K\\
% V1_avg = 4.132(22)e2~km/s\\
% V1_med = 4.034(21)e2~km/s\\
% V2_avg = 4.132(22)e2~km/s\\
% V2_med = 4.034(21)e2~km/s\\

% Heliographic Inertial (HGI) coordinates\\
% HGI coordinates are Sun-centered with the z-axis directed along the solar rotation axis and directed northward of the solar equator. The solar equator plane is inclined \SI{7.25}{\degree} from the ecliptic.\\

HGI coordinates; latitude range -7.25\degr{}~to~7.25\degr{}\\
latitude variation (see Schwenn1990 p.~127)\\

OMNI data is not corrected for solar distace. only available for 1-/5-min data\\

%[limited parameter ranges... (minV: 171~km/s; Schwenn1983)]\\

\section{Results and discussion}

list of results:\\
- low velocity at 0.0459~au\\
- empirical solar wind model for inner heliosphere\\
- application validity of lognormal distributions\\
--> B inversion of frequency distribution\\
---> magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\

%discussion
Comparison with existing near-Sun models (renew extrapolation figure to 1-column)\\

\citet{Wang2000}, sources of slow solar wind + IMF regulation mechanism + blobs; compare with our slow V lognormal part\\

% comparison with other Helios studies (Schwenn, Bougeret)
\citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately ($v_\text{H1}(r) \propto r^{0.083}$ and $v_\text{H2}(r) \propto r^{0.036}$), average or median? fits well...\\
Helios results, radial gradients see \citet{Schwenn1990} p.~155\\

The electron density distance function, which \citet{Bougeret1984} derived from Helios data and normed to the 1976 1~au density ($n(r) = 6.14\,r^{-2.10(4)}\,\text{cm}^{-3}$) also fits well...\\

\citet{Sheeley1997} -> LASCO coronagraph observed speed profile of coronal features tracing the slow solar wind, 2--30~Rs\\
- parabolic eq.~(2) and exponential eq.~(3)\\
- sonic point 5--6~Rs\\
- slow solar wind origin 3--4~Rs\\

The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\

%solar wind -> structures\\
\citet{Balogh1999} p.~162~ff (origin and formation of CIRs in inner heliosphere with Helios data; latitude V dependence)\\
Balogh2009 (HMF review + inner heliosheath)\\
Patsourakos2016 (near-Sun B-field of CMEs)\\
Aschwanden2004, p.~29\\

Parker1963\\
%https://babel.hathitrust.org/cgi/pt?id=uc1.b4264142;view=1up;seq=12

individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
\citet{Sanchez-Diaz2016} (very slow solar wind)\\
Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\

The ratio of both varies with solar activity, e.g. 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use \citet{Bougeret1984} p.~498...\\

larger influx from higher latitudes (see figure b))\\

varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\

In most studies the density distance dependence is assumed to scale with $r^{-2}$ (cites), assuming a constant velocity.\\

\section{Conclusions}

Further investigations should be done into structure extrapolations...\\

Further questions:\\
nearer to the Sun (at and below the source surface) the solar wind expansion in the ecliptic should be less spherical but more circular due to the influx from higher latitudes. => density exponent > -2\\
see Li2011 Fig.~1\\
% n	v
% -2.05	0.05
% -2	0
% -1.8	-0.2
% -1.5	-0.5

### 2017-04-05 paperMVVB_backup_2017-03-31/sections/abstract.tex
new date version

\title{Solar wind prediction for the Solar Probe Plus orbit}
\subtitle{Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations}

\author{M.~S.~Venzmer
\and V.~Bothmer}

\institute{University of Goettingen, Institute for Astrophysics, Friedrich-Hund-Platz~1, 37077~Göttingen, Germany}

\date{First draft 9 August 2016; received date; accepted date }

\abstract
{In view of the planned near-Sun spacecraft mission Solar~Probe~Plus (SPP) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data. This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data. The space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}. This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters SPP will encounter on its mission.}	%aims
{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
Their individual frequency distributions are represented with lognormal functions. In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part. The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions. We compile functional relations to the solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data. Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies. Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time.}	%results
{}	%conclusions
%\SI{0.0459}{\au}

\keywords{solar wind -- sun: heliosphere -- sun: corona}

\maketitle

%\titlerunning{Solar wind extrapolation to SPP orbit}
%\authorrunning{Venzmer \& Bothmer}

%extrapolated ranges \SI{95.45}{\percent} of the solar wind parameter values lie within. The ranges are for the magnetic field strength \SIrange{522}{2725}{nT}, for the velocity \SIrange{209.4}{506}{\km\per\s}, for the density \SIrange[scientific-notation=fixed, fixed-exponent=3, range-units=brackets]{1.319e3}{1.72e4}{\per\cm\cubed} and for the temperature \SIrange[scientific-notation=fixed, fixed-exponent=6, range-units=brackets]{4.18e5}{1.59e7}{\K}.
%These ranges are consistent with... and differ with...

### 2017-04-05 paperMVVB_backup_2017-03-31/sections/acknowledgments.tex
new date version

\begin{acknowledgements}
	This work was done within the scope of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS), funded by the German Aerospace Center (DLR) (grant number...).\\
	The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data. The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive (NSSDCA) and the Space Physics Data Facility (SPDF) at NASA's Goddard Space Flight Center (GSFC).\\
	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
%	We thank the referees for /very important comments and suggestions. /careful review of this paper.

%	facilities/persons which made available the Helios and OMNI data\\
% 	``Ian Richardson and Hilary Cane for making their Interplanetary Coronal Mass Ejection list readily available''\\
% 	``Joseph King and Natalia Papitashvili for creating the combined OMNI data set''\\
% 	``We thank the reviewers for the careful review of this paper''\\
% 	The Authors extend their thanks to the referee for important comments and suggestions.\\
% 	We would like to thank XX for reading drafts of this manuscript...\\
% 	We would like to thank the Helios team and NASA's SPDF for supplying the plasma and magnetic field data (url)\\
\end{acknowledgements}

### 2017-04-05 paperMVVB_backup_2017-03-31/sections/content.tex
new date version

--- 2017-04-05 paperMVVB_backup_2017-03-30/sections/content.tex
@@
 
-plot of SPP's estimated solar wind environment from predicted SSN (Fig.~\ref{fig:SPP_orbit_sw_forecast_BVNT_plot})\\
+plot of SPP's estimated solar wind environment from predicted SSN; zoom into first and nearest perihelion (Fig.~\ref{fig:SPP_perihelia_prediction_plot})\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_sw_forecast_BVNT_plot.png}}
-	\caption{Estimated B-field median and frequency distribution during the mission time period 2024--2025.}
-	\label{fig:SPP_orbit_sw_forecast_BVNT_plot}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_plot.pdf}}
+	\caption{Estimated B-field median during the first and nearest perihelia in 2018 and 2024.}
+	\label{fig:SPP_perihelia_prediction_plot}
 \end{figure}
-zoom into first perihelion (new figure...)\\
-
-% The extrapolation of the general solar wind model of the SPP orbit range is plotted in Fig.~\ref{fig:sw_model_extrapolation_4_paper_plot}.\\
-% \begin{figure*}
-% 	{\includegraphics[width=17cm]{figures/sw_model_extrapolation_4_paper_plot.pdf}}
-% 	\caption{Extrapolated solar wind parameters in the SPP observation range (\SIrange{0.0459}{0.25}{\au}).
-The median, mean and \SI{95.45}{\percent} range are extrapolated from the general solar wind model.
-use color scaled plot?}
-% 	\label{fig:sw_model_extrapolation_4_paper_plot}
-% \end{figure*}
 
 \subsection{Near-Sun extrapolation behavior/effects}
-
 The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\

### 2017-04-05 paperMVVB/sections/content.tex
new date version

--- 2017-04-05 paperMVVB_backup_2017-03-31/sections/content.tex
@@
 For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit.
-The sums of absolute residuals are shown as well.
+The mean absolute errors and sums of absolute residuals are shown as well.
 The values in brackets are the estimated standard deviation of each fit parameter.}
@@
 		@{}c@{}
-		S[table-format = 2.1]
+		S[table-format = 1.2e+2]
+		S[table-format = 2.2]
 		}
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{SAR}\\
-		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[\%]}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{MAE}	&\multicolumn{1}{c}{SAR}\\
+		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{}	&\multicolumn{1}{c}{[\%]}\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&6.83\\
-		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&18.69\\
-		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&6.48\\
-		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&5.78\\
+		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&5.51e-4	&6.83\\
+		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&1.80e-3	&18.69\\
+		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&5.49e-4	&6.48\\
+		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&8.71e-5	&5.78\\
 		\hline
-		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
-			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
-		\cline{2-6}
-			&\multicolumn{1}{c}{$W_\text{II}$}	&4.12(14)\tablefootmark{b}	&4.38(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&4.20\\
+		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+		\cline{2-7}
+			&\multicolumn{1}{c}{$W_\text{II}$}	&4.12(14)\tablefootmark{b}	&4.38(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98e-4	&4.20\\
 		\hline
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_b_plot.pdf}}
-	\caption{Ratio of slow to fast solar wind depending on the by 3~years lagged SSN. The relation results from the velocity's double lognormal fit.}
+	\caption{Yearly ratio between slow to fast solar wind (threshold \SI{400}{\km\per\s} over SSN (+).
+Fit model ratio depending on the by 3~years lagged SSN (black line).
+The relation results from the velocity's double lognormal fit.}
 	\label{fig:Vdbl_SSN_ratio_b_plot}
@@
 
-With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (vgl.Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}). derive value...\\
+With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, vgl.Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
 
@@
 
+error estimation for general model and extreme value tendencies\\
+
 error sources:\\
 - extrapolation\\
-- model\\
+- lognormal model\\
+- SSN variance\\
 

### 2017-04-06 paperMVVB/sections/content.tex
implemented cubehelix color scheme for 1 plot

@@
 
-In comparison with the data the fit models roughly match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVNTSSN_fit_b_plot}).\\
+In comparison with the data the fit models roughly match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVNTSSN_fit_c_plot}).\\
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/OMNI_yearly_BVNTSSN_fit_b_plot.pdf}
-	\caption{Solar wind parameter frequencies, lognormal fit models and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
+	\includegraphics[width=18cm]{figures/OMNI_yearly_BVNTSSN_fit_c_plot.pdf}
+	\caption{Solar wind parameter frequencies, lognormal fit models, their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
 The for the model shifted SSN is indicated by a black line.}
-	\label{fig:OMNI_yearly_BVNTSSN_fit_b_plot}
+	\label{fig:OMNI_yearly_BVNTSSN_fit_c_plot}
 \end{figure*}

### 2017-04-07 paperMVVB/sections/abstract.tex
implemented cubehelix color scheme for fig. 8 and worked in my offline comments

--- 2017-04-05 paperMVVB_backup_2017-03-31/sections/abstract.tex
@@
 The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions.
-We compile functional relations to the solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
+We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
 Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies.

### 2017-04-07 paperMVVB/sections/content.tex
implemented cubehelix color scheme for fig. 8 and worked in my offline comments

--- 2017-04-05 paperMVVB/sections/content.tex
@@
 
+%solar wind models; theoretical and empirical
 With his theoretical solar wind model \citet{Parker1958} laid the foundations...\\
 
+%in situ spacecraft
 Several space missions flew away from Earth's orbit to measure in situ solar wind at different heliocentric distances (e.g.
 the probes Helios, Voyager, Ulysses...).
-Voyager~1 is the farthest probe out of the solar system, covering more than 137~au (time?
-cite?).
+Voyager~1 is the farthest probe out of the solar system, now covering more than 137~au (cite?).
 Ulysses was the single probe orbiting the Sun outside the ecliptic and retrieving solar wind measurements from the poles of the Sun.
@@
 
-%Solar Probe Plus
+%Solar Probe Plus mission
 The main part of the SPP mission's goals is to gain insight into the coronal heating and solar wind acceleration processes.
@@
 
+%WISPR
 white light imager WISPR... \citep{Vourlidas2016}\\
 
+%difference to other models
 There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites...).
@@
 Additionally there also are coronal mass ejections (CMEs) embedded, whose occurrence rate follows solar activity too.
-Their share varies between almost zero in cycle minimum up to a half in maximum.
+Their share varies between almost zero in cycle minimum up to a half in maximum \citep{Richardson2012}.
 This study averages over these internal solar wind structures.
@@
 Our approach is to get an analytical representation of the frequency distributions' shapes, their solar activity dependence and their solar distance scaling.
-We get the parameters' frequency distributions and solar activity dependence from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles and their distance dependency from solar wind measurements of more than half a solar cycle covering more than two third of the distance to the Sun (\SIrange{0.29}{0.98}{\au}).%0.68~au\\
+We get the parameters' frequency distributions and solar activity dependence from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles and their distance dependency from solar wind measurements of more than half a solar cycle, covering more than two third of the distance to the Sun (\SIrange{0.29}{0.98}{\au}).%0.68~au\\
 
@@
 This section looks at the solar wind parameters' frequency distributions which we extract from the in situ OMNI data set.
-We determine adequate fit function types and evaluate if they are suitable to represent the frequencies' shapes.
+We determine adequate fit function types and evaluate how suitable they are to represent the frequencies' shapes.
 
@@
 The solar wind parameters are highly variable, due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on solar activity.
-Hence, for deriving general frequency distributions of the solar wind parameters, averaging over long-time solar wind variations is needed.
+Hence, for deriving general frequency distributions of the solar wind parameters, averaging over long-term solar wind variations is needed.
 This requires a distance-independent data set covering multiple solar cycles.
@@
 %data time range
-The hourly data of the whole time range (\textgreater50~years) up to \mbox{2016-12-31} is the basis for the frequency fits.
+The hourly data of the whole time range up to \mbox{2016-12-31} is the basis for the frequency fits.
 The data starts in \mbox{1963-11-27}, but the temperature data not before \mbox{1965-07-26}.
@@
 Obviously all possible values for the four parameters are positive.
-This hints to the supposition that they are lognormally distributed, as many positive natural quantities conform to a lognormal distribution.
-This distribution is described by a lognormal function.
+This hints to the supposition that they are lognormally distributed, as many positive natural quantities conform to lognormal distributions.
+Its probability density function is described by a lognormal function.
 %fitting method
@@
 \begin{table*}
-	\caption{The resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au}.
+	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au}.
 For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit.
@@
 		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
-		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
+		\tablefoottext{b}{Error estimates derived from the individual fit part errors.}
 	}
@@
 Its sum of absolute residuals (SAR) between data and fit is almost three times larger than those from the other parameters (Table~\ref{tab:lognormal_fit_parameters}).
-They can be compared, because the area of probability distributions is unity.
+They can be compared, because the area of probability density functions is unity.
 \begin{figure*}
@@
 respectively.\\
-As anticipated, this more complex fit function is more accurate in describing the velocity's frequency distribution (see Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).\\
+As anticipated, this more complex fit function is more accurate in describing the velocity's frequency distribution (see Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).
 \begin{figure}
@@
 \end{figure}
-In this model the slow and fast part contribute almost equally.\\
-
-In solar cycle maximun (minimum) CMEs contribute with a fraction of \SI{5}{\percent} (half \SI{50}{\percent}) \citep{Richardson2012}.\\
-
-In the following sections we keep using the double lognormal ansatz for the velocity frequency fits...\\
+That is why we keep using the double lognormal ansatz for the velocity frequency fits in the following sections.\\
+In this static model the slow and fast part contribute almost equally ($c \approx 0.5$), which of course is only valid for this kind of long-term average.
+At different times in a solar cycle their contributions vary strongly.\\
 
 %transition
-For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well (the deviation from the fitted functions is less than \SI{7}{\percent}).
-This is different for the extreme values (which may come from CMEs).
+For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well.
+This is different for the extreme values (which may also stem from CMEs).
 The simple lognormal fit models of the magnetic field strength, the velocity and the density underestimate their frequency at the high value tails, whereas the temperature's tail is overestimated (see insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).
@@
 \subsection{SSN data}
-Solar activity is commonly measured via the sunspot number.\\
+Solar activity is commonly measured via the sunspot number.
+We want to correlate OMNI in situ measurements with the SSN, but OMNI data are from Earth orbit, causing variations in solar latitude and distance.
+To dodge these variations we use yearly OMNI and SSN data.\\
 
-activity -- cycle -- forecast -- yearly SSN\\
+The international sunspot number (\citeyear{sidc}) is retrieved from the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
 
-The international sunspot number is retrieved from the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
-\citet{sidc}\\
+seasonal influence contained within yearly frequency distributions\\
 
-why use only yearly SSN data?\\
-because OMNI in situ measurements are from Earth orbit (causing variations in solar latitude and distance)\\
-seasonal influence contained within yearly frequency distributions\\
-yearly OMNI data\\
+SIDC and SWPC provide limited SSN forecast (a few months)\\
 
 \subsection{SSN correlation}
-We are interested in the correlation of the median, because it defines the position of the lognormal function.\\
-yearly parameter medians and yearly SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot})\\
+Our current interest lies in the correlation of the SSN to the solar wind median value, because it defines the position of the lognormal function.
+The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}.\\
 
-Deriving the correlation coefficients for different time lags between solar wind parameters and SSN (see also Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}).\\
+solar activity = SSN $\neq$ solar cycle\\
+The solar wind velocity (and its close friends N \& T) is known to depend on the state of the solar cycle (cite?), which is why it follows the SSN only indirectly (with time lag).
+Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}).\\
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_b_plot.pdf}}
+	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top).
+Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
+	\label{fig:OMNI_yearly_ssn_correlation_b_plot}
+\end{figure}
 
@@
 
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_b_plot.pdf}}
-	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} (top).
-Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
-	\label{fig:OMNI_yearly_ssn_correlation_b_plot}
-\end{figure}
+yearly SSN sw model to sw data fits -> SSN dependency (figs)\\
 
@@
 \label{sec:ssn_fitting}
-yearly SSN sw model to sw data fits -> SSN dependency (figs)\\
-
-To shift the distributions with SSN, we fit a linear SSN dependency to the median
+To be able to shift the distributions with SSN, add fit a linear SSN dependency to the median
 \begin{align}
@@
 \end{align}
-using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$.
-The two values median and mean are sufficient to fully describe lognormal functions, so we relate the mean with a scaling factor to the median to keep the dependency on SSN: (why can we do that?
-mean proportional to median)
+using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to keep the new SSN dependency:
 \begin{align}
@@
 \end{align}
-With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new fit function $W'(x,ssn)$ is then fitted to the data.
+With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data.
 The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.\\
 \begin{table*}
-	\caption{The resulting fit coefficients from the data fitting with SSN.
+	\caption{Resulting fit coefficients from the data fitting with SSN.
 For the velocity the fit parameters from the double lognormal fit and their balancing function are given.
@@
 		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
-		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
+%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
 		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
@@
 
-In comparison with the data the fit models roughly match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVNTSSN_fit_b_plot}).\\
+In comparison with the data the fit models seem to match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/OMNI_yearly_BVNTSSN_fit_b_plot.pdf}
-	\caption{Solar wind parameter frequencies, lognormal fit models and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
-The for the model shifted SSN is indicated by a black line.}
-	\label{fig:OMNI_yearly_BVNTSSN_fit_b_plot}
+	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_d_plot.pdf}
+	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
+The for the models shifted SSN is indicated by a black line.
+The constant medians of both velocity's lognormal parts are marked with white dots.}
+	\label{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}
 \end{figure*}
 
-Again, the velocity gets a special treatment with the double lognormal distribution (see Eq.~\ref{eq:double_lognormal_fit_function}), this time keeping its two components' positions constant and variing instead their balance with the SSN:	(discuss why...)
+Again, the velocity gets a special treatment with the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
+It is known that slow and fast solar wind stream occurrence rates follow the solar cycle, but their magnitudes stay fairly stable (cite?).
+This time we keep the two velocity components' positions constant and vary instead their balance with the SSN:
 \begin{align}
@@
 \end{align}
-The fit result is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
 \begin{figure}
@@
 \end{figure}
+% 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
+...compare with data\\
+=> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
 
-All fit coefficients are given in Table~\ref{tab:ssn_fit_parameters}).\\
-
-In comparison with the data the fit model roughly matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_VSSN_dblfit_plot}).\\
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_VSSN_dblfit_plot.pdf}}
-	\caption{Velocity frequency, double lognormal fit model and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016. The for the model shifted SSN is indicated by a black line.}
-	\label{fig:OMNI_yearly_VSSN_dblfit_plot}
-\end{figure}
-3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
-...compare with data\\
+In comparison with the data the fit model roughly matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
 
@@
 In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and evaluate the fits' extrapolation behavior in direction to the Sun.
-
 To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data.
-This results in solar wind models comprising of exponentially with distance shifted lognormal functions.
+This results in models comprising of exponentially with distance shifted lognormal functions.
 
@@
 However, the magnetic field strength's mean crosses the median at \SI{0.339}{\au} (Table~\ref{tab:mean_median_fit_parameter}) and is lower at smaller distances.
-But at the crossing point and below the magnetic field strength can therefore not be described anymore with a lognormal function.
+At the crossing point and below the magnetic field strength can therefore not be described anymore with a lognormal function.
 For an extrapolation to the SPP perihelion the same happens for the temperature at \SI{0.082}{\au}.
 
-The large velocity's crossing distance and its large error indicate that the median's and mean's distance behavior could be identical and so the frequency's shape distance independent.
+The large velocity's crossing distance and its large error indicate that the median's and mean's distance behavior can be kept identical and so the frequency's shape distance independent.
 
 Those crossings limit the possible extrapolation distances with lognormal functions.
-To circumvent these limitations we set the exponents $b_\text{med}$ and $b_\text{avg}$ to be identical, avoiding crossing of median and mean.
+To circumvent these limitations for all four solar wind parameters we set the exponents $b_\text{med}$ and $b_\text{avg}$ to be identical, avoiding crossing of median and mean.
 Then the distribution's width is constant and scales only exponentially with solar distance.
-Applying this approximation, we have to accept larger fit errors.
+Applying this approximation, we have to accept larger model errors, especially for the magnetic field strength.
 It also limits the extrapolation accuracy.
@@
 As mentioned before, we set the exponents of median and average to be identical.
-Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function \ref{eq:single_lognormal_fit_function}, we have three fit parameters $a_\text{med}$, $a_\text{avg}$ and the common exponent $b$.
-(change variable naming...)
+Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($a_\text{med}$, $a_\text{avg}$ and the common exponent $b$).
 
@@
 
-With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, vgl.Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
+With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
 
-The fit models seem to resemble the data quite well (Fig.~\ref{fig:mixed_fit_fixed_4_paper_d_plot}).
+The fit models seem to resemble the data quite well (Fig.~\ref{fig:mixed_fit_fixed_4_paper_e_plot}).
 The magnetic field strength frequency is more focused (around \SI{40}{nT}) at the lower distance boundary than the model's is.
@@
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_d_plot.pdf}
+	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_e_plot.pdf}
 	\caption{Solar wind parameter's frequency distributions over solar distance.
-Plotted are the binned Helios data and the exponential lognormal fit model (double lognormal for the velocity).
-choose normed color scale for b/w plot...}
-	\label{fig:mixed_fit_fixed_4_paper_d_plot}
+Plotted are the binned Helios data and the exponential lognormal fit model (double lognormal for the velocity) with their median values (white).}
+	\label{fig:mixed_fit_fixed_4_paper_e_plot}
 \end{figure*}
 
-model errors, maximum errors; see Fig.~XX (data - model, fit errors)\\
+model errors, maximum errors\\
 The extreme values of the velocity and temperature seem to be too high (adjust color scale...)\\
-L-> high value plots... (refer to histogram zoom)\\
+L-> high value plots... (refer to histogram zoom in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot})\\
 
-This model represents the Helios time frame around the rise of solar cycle~21.
+This model represents the Helios time frame around the rise of solar cycle~21.\\
+
+study time/cycle variations\\
 
@@
 
-Finally we combine the obtained solar activity and distance dependencies for shifting the frequency distributions. The result will be an empirical solar wind model for the inner heliosphere.\\
+Finally, we combine the obtained solar activity and distance dependencies for shifting the frequency distributions. The result will be an empirical solar wind model for the inner heliosphere.\\
 

### 2017-04-08 paperMVVB/sections/content.tex
worked in 2nd part of my offline comments

@@
 The errors in brackets are the estimated standard deviations of each fit parameter.
-The crossing distance is the point where median and mean intersect.}
+The crossing distance is the point where the fitted median and mean intersect.}
 	\label{tab:mean_median_fit_parameter}
@@
 study time/cycle variations\\
+indications for that: fig. + theory + studies/papers...\\
+assuming the distance scaling laws are time independent, which we deduced...? which is an approximation.\\
 
@@
 
-Finally, we combine the obtained solar activity and distance dependencies for shifting the frequency distributions. The result will be an empirical solar wind model for the inner heliosphere.\\
+Finally, we combine the obtained solar activity and distance dependencies for shifting the frequency distributions. The result is an empirical solar wind model for the inner heliosphere.\\
 
 %are the exponents time-independent?
-Under the assumption that the exponential falloff laws do not change with time/solar activity, they can be used in general (indications for that: fig. + theory + studies/papers...).\\
-assuming the distance scaling laws are time independent, which we deduced...? which is an approximation.\\
+Under the assumption that the exponential falloff laws do not change with time/solar activity (as shown above...), they can be used in general.\\
 
-We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the exponential distance dependency (\ref{eq:exponential_function}):
+We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the exponential distance dependence (\ref{eq:exponential_function})
 \begin{align}
-	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^b\,.
+	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^b
 \end{align}
 
-the combined model function $W''(x,ssn,r)$\\
-
-...and double lognormal function for the velocity\\
+to get the combined model function $W''(x,ssn,r)$. And for the velocity $W_{II}''(x,ssn,r)$ with the double lognormal function.\\
 
 %model errors
-give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$
+give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$
 
@@
 
-SPP orbit description, Venus flybys, ecliptic, \citep{Fox2015}, see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot}\\
+%SPP orbit
+SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
+
+%SSN prediction
 choosing SSN prediction source as input (SIDC + SWPC + previous cycle), (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
@@
 Actual and predicted SSN (bottom), i.e.
-13-month smoothed monthly actual SSN and SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24.}
+SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
 	\label{fig:SPP_orbit_predicted_SSN_overview_b_plot}
@@
 
-plot of SPP's estimated solar wind environment from predicted SSN; zoom into first and nearest perihelion (Fig.~\ref{fig:SPP_perihelia_prediction_plot})\\
+Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
+A zoom into the first and the nearest perihelia shows... (Fig.~\ref{fig:SPP_perihelia_prediction_plot}).\\
 \begin{figure}
@@
 %critical surfaces
+Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
 in direction to the Sun is at $\sim$2.5~Rs the source surface (Schatten1969)\\
-
 sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
-Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
-
+sonic point and slow solar wind origin \citep{Sheeley1997}\\
 approaching these regions, acceleration plays a role\\
@@
 
-\subsection{Model requirements and limits}
-
-model requirements:\\
-- modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
-- modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
-- possibility to extrapolate model down to 0.0459~au\\
-
-%model boundaries
-model boundaries (spherical coordinates):\\
-- mean solar wind of the Helios time range -> error size (determine deviation from average)\\
-- heliocentric distance range 0.29--0.98~au\\
-- rotational symmetry\\
-- confined to ecliptic\\
-model constrictions:\\
-- solar distance dependency function\\
-- frequency distribution function\\
-- neglected influence from heliolatitude variation\\
-
-\subsection{Model validity and error sources}
-\label{sec:model_validity_and_errors}
-
-validity and estimation of error size outside of valid model range...\\
-derive heliocentric distance depending error...\\
-
-list simplifications/approximations...\\
-
-error estimation for general model and extreme value tendencies\\
-
-error sources:\\
-- extrapolation\\
-- lognormal model\\
-- SSN variance\\
-
-all estimates outside these boundaries are extrapolations with large uncertainties. see Sect.~\ref{sec:model_validity_and_errors}\\
-
-discuss high value zoom figures\\
-
-Generally, the use of hourly data instead of higher resolution data (less than 1~min) should not have significant influence on the results.
-The minutely OMNI~2 data's frequency distributions are almost congruent and differ only slightly at their extreme ends (we tested that...).\\
-
-The many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions \citep[p.~491]{Schwenn1983}.\\
-
-The OMNI~2 data is time-shifted to the nose of the Earth's bow shock.
-This leads to yearly solar distance variations of \SI{>2}{\percent} (cite?) as the Earth orbits the Sun.
-Furthermore, its orbit within the ecliptic leads to a yearly variation of \SI{+-7.2}{\degree} in heliospheric latitude.\\
-The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS) (cite?).\\
-The HCS's position in latitude is highly variable around the solar equator \citep[p.~127~ff.?]{Schwenn1990}.\\
-
-- over year (seasonal/monthly) -> expect them to be less than 5~\%\\
-
-%monthly seasonal variation
-Sun-Earth distance over the course of the year.\\
-In the year 2017 Earth's perihelion was on 5~January with a distance of \SI{-1.67}{\percent} from \SI{1}{\au} (Horizons On-Line Ephemeris System\footnote{\url{http://ssd.jpl.nasa.gov/horizons.cgi}}, Solar System Dynamics Group, Jet~Propulsion Laboratory).\\
-The cosine approximation
-\begin{align}
-	r_\text{E}(t) = 1 - 0.0167 \cdot \cos\left(2 \pi \left(t - 2017 - \frac{5}{365}\right)\right)\,,
-\end{align}
-with $t$ in years, suffices for our accuracy requirements.\\
-% HORIZONS Web-Interface
-% http://ssd.jpl.nasa.gov/horizons.cgi
-% Ephemeris Type:	VECTORS
-% Target Body:		Earth [Geocenter] [399]
-% Coordinate Origin:	Sun (body center) [500@10]
-% Time Span:		Start=2017-01-01, Stop=2017-12-31, Step=1 d
-% Table Settings:	CSV format=YES
-% Display/Output:	download/save (plain text file)
-%-> distance:	9.833098226363186E-01
-%-> diff. to 1 au:	0.166901774
-%-> change to day before:	4.4e-6	-> 0.1669018(44)
-
-seasonal variation function:\\
-$X_\text{avg}(t) = a\,r_\text{E}(t)^b$\\
-% B_avg = 5.969(29)~nT\\
-% B_med = 5.435(24)~nT\\
-% N_avg = 6.329(85)~cm-3\\
-% N_med = 4.858(60)~cm-3\\
-% T_avg = 1.198(16)e5~K\\
-% T_med = 7.17(12)e4~K\\
-% V1_avg = 4.132(22)e2~km/s\\
-% V1_med = 4.034(21)e2~km/s\\
-% V2_avg = 4.132(22)e2~km/s\\
-% V2_med = 4.034(21)e2~km/s\\
-
-% Heliographic Inertial (HGI) coordinates\\
-% HGI coordinates are Sun-centered with the z-axis directed along the solar rotation axis and directed northward of the solar equator.
-The solar equator plane is inclined \SI{7.25}{\degree} from the ecliptic.\\
-
-HGI coordinates; latitude range -7.25\degr{}~to~7.25\degr{}\\
-latitude variation (see Schwenn1990 p.~127)\\
-
-OMNI data is not corrected for solar distace. only available for 1-/5-min data\\
-
-%[limited parameter ranges... (minV: 171~km/s; Schwenn1983)]\\
-
-\section{Results and discussion}
-
-list of results:\\
-- low velocity at 0.0459~au\\
-- empirical solar wind model for inner heliosphere\\
-- application validity of lognormal distributions\\
---> B inversion of frequency distribution\\
----> magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
-
-%discussion
-Comparison with existing near-Sun models (renew extrapolation figure to 1-column)\\
+Comparison with existing near-Sun models (renew extrapolation figure to 1-column):\\
 
@@
 
+\subsection{Model requirements and limits}
+
+model requirements:\\
+- modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
+- modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
+- possibility to extrapolate model down to 0.0459~au\\
+
+%model limits
+model limits (spherical coordinates):\\
+- heliocentric distance range 0.29--0.98~au\\
+- rotational symmetry\\
+- confined to ecliptic +-7.2 degrees\\
+model constrictions:\\
+- solar distance dependency function\\
+- frequency distribution functions\\
+- neglected influence from heliolatitude variation\\
+
+\subsection{Model validity and error sources}
+\label{sec:model_validity_and_errors}
+
+validity and estimation of error size outside of valid model range...\\
+derive heliocentric distance depending error...\\
+
+list simplifications/approximations...\\
+
+error estimation for general model and extreme value tendencies\\
+
+error sources:\\
+- extrapolation\\
+- lognormal model\\
+- SSN variance\\
+
+all estimates outside these boundaries are extrapolations with large uncertainties.\\
+
+discuss high value zoom figures\\
+
+The use of hourly data instead of higher resolution data (less than 1~min) has no significant influence on the bulk results.
+The minutely OMNI data frequency distributions are almost congruent and differ only slightly at their extreme ends.\\
+The many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions \citep[p.~491]{Schwenn1983}.\\
+
+The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS).\\
+The OMNI data is time-shifted to the nose of the Earth's bow shock.
+This leads to yearly solar distance variations of \SI{>2}{\percent} (cite?) as the Earth orbits the Sun.
+Furthermore, its orbit within the ecliptic leads to a yearly variation of \SI{+-7.2}{\degree} in heliospheric latitude.\\
+The HCS's position in latitude is highly variable around the solar equator \citep[p.~127~ff.?]{Schwenn1990}.\\
+
+Error estimation over the year (seasonal/monthly) -> we expect variations to be less than 5~\%\\
+
+OMNI data is not corrected for solar distace. only available for 1-/5-min data\\
+
+%[limited parameter ranges... (minV: 171~km/s; Schwenn1983)]\\
+
+\section{Results and discussion}
+
+list of results:\\
+- empirical solar wind model for inner heliosphere within ecliptic\\
+- low velocity at 0.0459~au\\
+- slow/fast ratio SSN dependency\\
+- application validity of lognormal distributions\\
+--> B inversion of frequency distribution\\
+---> magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
+varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
+
 %solar wind -> structures\\
@@
 
-varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
-
 In most studies the density distance dependence is assumed to scale with $r^{-2}$ (cites), assuming a constant velocity.\\
@@
 
-Further investigations should be done into structure extrapolations...\\
+Further investigations should be done into structure extrapolations, outward extension of model to Mars...\\
 

### 2017-04-08 paperMVVB/sections/abstract.tex
removed some in-tex comments, table1 error fixed, table4 layout changed

@@
 Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
-{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time.}	%results
+{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time.
+The estimated solar wind values at SPP's nearest perihelion vary up to +-XX~\%, arising only from differing next solar cycle amplitude assumptions.}	%results
 {}	%conclusions
-%\SI{0.0459}{\au}
 
@@
 
+%\SI{0.0459}{\au}
 %extrapolated ranges \SI{95.45}{\percent} of the solar wind parameter values lie within.

### 2017-04-08 paperMVVB/sections/content.tex
removed some in-tex comments, table1 error fixed, table4 layout changed

@@
 This general model is then fed with a SSN prediction and extrapolated to SPP's planned orbital positions.\\
-% 
-% \begin{itemize}
-% % 	\item We determine the fit function type for the parameters' frequency distributions with OMNI data.
-% %	\item We determine the fit function type for the parameters' solar cycle dependency with OMNI and SSN data.
-% % 	\item We determine the fit function type for the parameters' distance dependency with Helios data.
-% 	\item Time dependent (yearly) distribution magnitudes versus solar activity. for OMNI
-% % 	\item The function's behavior in direction of Sun down to \SI{0.0459}{\au} is evaluated.
-% % 	\item We fit exponential (double) lognormal functions to (distance-binned) Helios data (Helios solar wind model).
-% % 	\item We combine the obtained distance dependencies with the obtained solar activity relations (dynamical solar wind model).
-% 	\item resulting dynamical model dependencies (distance, SSN)
-% 	\item use extrapolated SSN (SILSO) of SPP mission for solar wind extrapolation (SPP solar wind estimation model).
-% \end{itemize}
-%
 
 %lognormal fitting
-%%%%%%%%%%%%%%%%%%
 \section{Frequency distributions}
 \label{sec:frequency_distribution}
+
 This section looks at the solar wind parameters' frequency distributions which we extract from the in situ OMNI data set.
@@
 Next, we look for a suitable fit function for the resulting histogram shape of the solar wind parameters' frequency distributions.
-% $B$: bin size 0.5~nT\\
-% $v$: bin size 10~km/s\\
-% $n$: bin size 1~cm$^{-3}$\\
-% $T$: bin size 10\,000~K\\
 
 \subsection{Lognormal fitting}
-%choice of distribution function?/why lognormal function?
+%choice of distribution function---why lognormal function?
 Obviously all possible values for the four parameters are positive.
@@
 		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
-			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+			&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
 		\cline{2-7}
@@
 % median = 412.4937999968638
-
 % fit data difference (normed area):\\
@@
 \end{figure*}
-% From the normed stdfit values (Table~\ref{tab:single_lognormal_fit_parameters}) we see that the velocity fit is not that good... \\
-% While by visual inspection it is obvious, but also fit stdfit is an indication for a bad fit...\\
-% What we see at visual inspection is the area difference between the fit and the data. This area is for the velocity almost three times larger than the other's.\\
 
@@
 
-yearly SSN sw model to sw data fits -> SSN dependency (figs)\\
+yearly SSN sw model to sw data fits -> SSN dependency (new figs)\\
 
@@
 	\centering
-%	\sisetup{table-figures-integer=1, table-figures-decimal=4, table-figures-exponent=1}
 	\begin{tabular}{l@{} c@{}
@@
 
-For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.
+For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.\\
 
@@
 	\begin{tabular}{l c
-	S[table-format = 1.3(2)]
 	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
 	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
-	S[table-format = +1.4(2)]}
+	S[table-format = +1.4(2)]
+	S[table-format = 1.3(2)]}
 		\hline\hline
-		\multicolumn{2}{l}{Parameter}	&$c$	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}\\
+		\multicolumn{2}{l}{Parameter}	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&\multicolumn{1}{c}{--}	&5.358(25)	&5.705(28)	&-1.662(11)\\
-		\multicolumn{2}{l}{Density}	&\multicolumn{1}{c}{--}	&5.424(33)	&6.845(47)	&-2.114(20)\\
-		\multicolumn{2}{l}{Temperature}	&\multicolumn{1}{c}{--}	&6.357(64)	&10.72(14)	&-1.100(20)\\
+		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}\\
+		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}\\
+		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}\\
 		\hline
-		\multirow{1}{*}{Velocity}	&$W''_1$	&\multirow{2}{*}{0.557(45)}	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}\\
-			&$W''_2$	&	&5.26(13)	&5.42(11)	&\\
+		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}\\
+			&$W''_2$	&5.26(13)	&5.42(11)	&	&\\
 		\cline{2-6}
-		\multicolumn{2}{r}{$W''_\text{II}$}	&\multicolumn{1}{c}{--}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}\\
+		\multicolumn{2}{r}{$W''_\text{II}$}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
 		\hline
@@
 %SSN prediction
-choosing SSN prediction source as input (SIDC + SWPC + previous cycle), (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
+choosing SSN prediction sources as input:\\
+SIDC prediction---12-month forecast (Kalman fiter combined method)\\
+The SWPC prediction (until end of current cycle/end of 2019) follows a consensus of the Solar~Cycle~24 Prediction~Panel.\\
+For the prediction of the next solar cycle we simply assume a course similar to the last and thus we simply shift the last cycle by 11~years.
+Additionally we consider the two alternatives of half and twice the amplitude.\\
+SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
 \begin{figure}

### 2017-04-10 paperMVVB/sections/content.tex
optimized figs 3+8; build fig 9; drafted fig 10

@@
 Our current interest lies in the correlation of the SSN to the solar wind median value, because it defines the position of the lognormal function.
-The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}.\\
+The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.\\
 
@@
 The solar wind velocity (and its close friends N \& T) is known to depend on the state of the solar cycle (cite?), which is why it follows the SSN only indirectly (with time lag).
-Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}).\\
+Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_b_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
 	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top).
 Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
-	\label{fig:OMNI_yearly_ssn_correlation_b_plot}
+	\label{fig:OMNI_yearly_ssn_correlation_c_plot}
 \end{figure}
@@
 %SPP orbit
-SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
+SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\
 
@@
 Additionally we consider the two alternatives of half and twice the amplitude.\\
-SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
+SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_b_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_c_plot.pdf}}
 	\caption{SPP's solar distance during its mission time (top).
@@
 SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
-	\label{fig:SPP_orbit_predicted_SSN_overview_b_plot}
+	\label{fig:SPP_orbit_predicted_SSN_overview_c_plot}
 \end{figure}
@@
 Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
-A zoom into the first and the nearest perihelia shows... (Fig.~\ref{fig:SPP_perihelia_prediction_plot}).\\
+A zoom into the first and the nearest perihelia shows... (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_plot.pdf}}
-	\caption{Estimated B-field median during the first and nearest perihelia in 2018 and 2024.}
-	\label{fig:SPP_perihelia_prediction_plot}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity slow and fast part are plotted.}
+	\label{fig:SPP_perihelia_prediction_c_plot}
 \end{figure}
-
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity slow and fast part are plotted.}
+	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
+\end{figure}
 \subsection{Near-Sun extrapolation behavior/effects}

### 2017-04-24 paperMVVB/sections/content.tex
finished fig 10; adjusted fig 9; upgraded fig 5

@@
 \end{align}
-The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_d_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_b_plot.pdf}}
-	\caption{Yearly ratio between slow to fast solar wind (threshold \SI{400}{\km\per\s} over SSN (+).
-Fit model ratio depending on the by 3~years lagged SSN (black line).
-The relation results from the velocity's double lognormal fit.}
-	\label{fig:Vdbl_SSN_ratio_b_plot}
+	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_d_plot.pdf}}
+	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN.
+The yearly ratios (+) and their weighted linear fit (solid) are obtained from OMNI data with a threshold of \SI{400}{\km\per\s}.
+The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
+The model's balance is obtained without a threshold (dashed).}
+	\label{fig:Vdbl_SSN_ratio_d_plot}
 \end{figure}
 % 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
-...compare with data\\
-=> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
+The ratio of slow to fast wind obtained from yearly OMNI data via simply applying the commonly used constant velocity threshold of \SI{400}{\km\per\s} (cite?) has a flatter SSN dependence than the model's balance.
+Why?\\
+Both should not necessary be identical, because there is no specific velocity threshold between slow and fast solar wind types, as the velocity ranges of both types overlap (cite?).\\
 
@@
 
-With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
+With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_d_plot}).\\
 
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity slow and fast part are plotted.}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity the SSN independent slow and fast parts are plotted.}
 	\label{fig:SPP_perihelia_prediction_c_plot}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity slow and fast part are plotted.}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity the SSN independent slow and fast parts are plotted.}
 	\label{fig:SPP_perihelia_prediction_nearest_c_plot}

### 2017-04-29 paperMVVB/sections/content.tex
created figure 5; adjusted figs. 3,4 and 6; table 4 header; subsections §7 reorganized

@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{MAE}	&\multicolumn{1}{c}{SAR}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{2}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
 		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{}	&\multicolumn{1}{c}{[\%]}\\
@@
 \label{sec:ssn_fitting}
-To be able to shift the distributions with SSN, add fit a linear SSN dependency to the median
+To be able to shift the distributions with SSN, we add a linear SSN dependency to the median
 \begin{align}
@@
 \begin{table*}
-	\caption{Resulting fit coefficients from the data fitting with SSN.
+	\caption{Resulting fit coefficients from the data fitting with lagged SSN.
 For the velocity the fit parameters from the double lognormal fit and their balancing function are given.
@@
 
+The comparison with the yearly data median values shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN}).\\
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN.pdf}}
+	\caption{Solar wind parameter median over lagged SSN.
+The yearly data medians (+) with their weighted linear fit (solid) are obtained from OMNI data.
+The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
+The SSN dependent median (\ref{eq:median_with_ssn}) is from the lognormal model fit (dashed).
+For the velocity the SSN independent slow and fast model parts are plotted instead (dotted).}
+	\label{fig:OMNI_yearly_BVNTvsSSN}
+\end{figure}
+
 Again, the velocity gets a special treatment with the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
@@
 \begin{align}
-	c(ssn) &= c_a \cdot ssn + c_b\,.
+	c(ssn) &= c_a \cdot ssn + c_b\,.	\label{eq:balance_with_ssn}
 \end{align}
-The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_d_plot}).\\
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_d_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_e_plot.pdf}}
 	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN.
@@
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
-The model's balance is obtained without a threshold (dashed).}
-	\label{fig:Vdbl_SSN_ratio_d_plot}
+The model's balance (\ref{eq:balance_with_ssn}) is obtained without a threshold (dashed).}
+	\label{fig:Vdbl_SSN_ratio_e_plot}
 \end{figure}
@@
 
-In comparison with the data the fit model roughly matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
+In comparison with the data the velocity fit model also matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
 
@@
 		\hline\hline
-		\multicolumn{2}{l}{Parameter}	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
+		\multicolumn{2}{c}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
+			&	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
 		\hline
@@
 
-With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_d_plot}).\\
+With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
 
@@
 
-study time/cycle variations\\
-indications for that: fig. + theory + studies/papers...\\
-assuming the distance scaling laws are time independent, which we deduced...? which is an approximation.\\
+study cycle variation of exponent\\
+indications for that: figure! + theory + studies/papers...\\
+assuming the distance scaling laws are time independent, which we reason from that; it is an approximation\\
 
@@
 
+model requirements:\\
+- modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
+- modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
+- possibility to extrapolate model down to 0.0459~au\\
+
+%model limits
+model limits (spherical coordinates):\\
+- heliocentric distance range 0.29--0.98~au\\
+- rotational symmetry\\
+- confined to ecliptic +-7.2 degrees\\
+model constrictions:\\
+- solar distance dependency function\\
+- frequency distribution functions\\
+- neglected influence from heliolatitude variation\\
+
 \section{Model extrapolation to SPP orbital time and position}
@@
 
+\subsection{SPP mission time frame/SSN prediction}
 %SSN prediction
@@
 
-Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
-A zoom into the first and the nearest perihelia shows... (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity the SSN independent slow and fast parts are plotted.}
-	\label{fig:SPP_perihelia_prediction_c_plot}
-\end{figure}
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity the SSN independent slow and fast parts are plotted.}
-	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
-\end{figure}
-\subsection{Near-Sun extrapolation behavior/effects}
+=> Implications for the mission...\\
+
+SPP orbit data source\\
+
+\subsection{SPP orbit/near-Sun extrapolation}
 The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\
@@
 
-\subsection{Model requirements and limits}
-
-model requirements:\\
-- modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
-- modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
-- possibility to extrapolate model down to 0.0459~au\\
-
-%model limits
-model limits (spherical coordinates):\\
-- heliocentric distance range 0.29--0.98~au\\
-- rotational symmetry\\
-- confined to ecliptic +-7.2 degrees\\
-model constrictions:\\
-- solar distance dependency function\\
-- frequency distribution functions\\
-- neglected influence from heliolatitude variation\\
+\subsection{SPP solar wind model}
+Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
+A zoom into the first and the nearest perihelia shows... (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity the SSN independent slow and fast parts are plotted.}
+	\label{fig:SPP_perihelia_prediction_c_plot}
+\end{figure}
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity the SSN independent slow and fast parts are plotted.}
+	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
+\end{figure}
 

### 2017-05-07 paperMVVB/sections/abstract.tex
some minor changes to text and figures 1,2,3,5and 9; additions to §7

@@
 {The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time.
-The estimated solar wind values at SPP's nearest perihelion vary up to +-XX~\%, arising only from differing next solar cycle amplitude assumptions.}	%results
+The estimated solar wind values at SPP's nearest perihelion vary up to +-XX~\%, arising only from differing amplitude assumptions for the next solar cycle.}	%results
 {}	%conclusions

### 2017-05-07 paperMVVB/sections/content.tex
some minor changes to text and figures 1,2,3,5and 9; additions to §7

@@
 %difference to other models
-There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites...).
+There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites?).
 They examine average values, additionally distinguishing between slow and fast wind.
@@
 % T: 66.73 \%		36.03 y\\
+
+%hourly data
+We note that the use of higher time resolution instead, would not significantly change our results.
+The frequency distributions of the also available minutely OMNI data set are almost congruent with the hourly---they only differ slightly at their extreme ends.
 
@@
 	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN.
-The yearly ratios (+) and their weighted linear fit (solid) are obtained from OMNI data with a threshold of \SI{400}{\km\per\s}.
+The yearly ratios (+) and their weighted linear fit (solid) are obtained from OMNI data with a threshold velocity of $v_\text{th} = \SI{400}{\km\per\s}$.
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
@@
 % 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
-The ratio of slow to fast wind obtained from yearly OMNI data via simply applying the commonly used constant velocity threshold of \SI{400}{\km\per\s} (cite?) has a flatter SSN dependence than the model's balance.
+The ratio of slow to fast wind obtained from yearly OMNI data via simply applying the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (cite?) has a flatter SSN dependence than the model's balance.
 Why?\\
@@
 \label{sec:solar_distance_dependency}
-
-In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and evaluate the fits' extrapolation behavior in direction to the Sun.
+In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and also evaluate the fits' extrapolation behavior in direction to the Sun.
 To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data.
@@
 \label{sec:helios_distance_data}
-
 The Helios probes were the only spacecraft measuring in situ solar wind over large solar distance ranges in the inner heliosphere.
@@
 Launched during solar cycle minimum, the data of both probes cover the rise to the maximum of cycle 21 ($\sim$6.5~years at varying distances).
+
+%hourly data
+Again we choose data with hourly resolution to allow its use along with the hourly OMNI data.
+As \citet{Schwenn1983} pointed out, the many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions, nevertheless their effect is insignificant in the treatment of the bulk data.	%\citet[p.~491]{Schwenn1983}
 
@@
 		\hline\hline
-		\multicolumn{2}{c}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
 			&	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
@@
 model errors, maximum errors\\
-The extreme values of the velocity and temperature seem to be too high (adjust color scale...)\\
+The extreme values of the velocity and temperature seem to be too high\\
 L-> high value plots... (refer to histogram zoom in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot})\\
@@
 
-to get the combined model function $W''(x,ssn,r)$. And for the velocity $W_{II}''(x,ssn,r)$ with the double lognormal function.\\
+to get the combined model function $W''(x,ssn,r)$. And for the velocity $W_\text{II}''(x,ssn,r)$ with the double lognormal function.\\
 
 %model errors
-give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$
+give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\
 
@@
 \section{Model extrapolation to SPP orbital time and position}
-To estimate the solar wind environment at SPP's planned orbital positions during its mission time, SSN predictions and extrapolations to the SPP perihelion region are included into the general solar wind model.\\
+To estimate the solar wind environment at SPP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the SPP perihelion region are performed.\\
 
-%SPP orbit
-SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\
+\subsection{SSN prediction for SPP mission time}
+%SSN prediction
+For the SSN prediction there are several sources available.
+The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g.
+Kalman filter combined method) (use cite...).
+The Space Weather Prediction Center's (SWPC) prediction follows a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://legacy-www.swpc.noaa.gov/SolarCycle/}} (until end of 2019) (use cite...).
 
-\subsection{SPP mission time frame/SSN prediction}
-%SSN prediction
-choosing SSN prediction sources as input:\\
-SIDC prediction---12-month forecast (Kalman fiter combined method)\\
-The SWPC prediction (until end of current cycle/end of 2019) follows a consensus of the Solar~Cycle~24 Prediction~Panel.\\
-For the prediction of the next solar cycle we simply assume a course similar to the last and thus we simply shift the last cycle by 11~years.
-Additionally we consider the two alternatives of half and twice the amplitude.\\
-SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\
+For the prediction of the next solar cycle~25 we simply assume a course similar to the last and thus we shift the last cycle by 11~years.
+Additionally we consider the two alternatives of half and twice its amplitude.
+The SSN for SPP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_c_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_d_plot.pdf}}
 	\caption{SPP's solar distance during its mission time (top).
@@
 Actual and predicted SSN (bottom), i.e.
-SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
-	\label{fig:SPP_orbit_predicted_SSN_overview_c_plot}
+SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+	\label{fig:SPP_orbit_predicted_SSN_overview_d_plot}
 \end{figure}
 
-=> Implications for the mission...\\
+[=> Implications for the mission...]\\
+
+prediction errors...\\
+
+\subsection{Near-Sun extrapolation for SPP orbit}
+
+%SPP orbit
+SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
 
@@
 
-\subsection{SPP orbit/near-Sun extrapolation}
 The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\
@@
 
-The near-Sun (SPP perihelion) solar wind velocity is expected to be slower than our model estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
+The near-Sun (SPP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
 
@@
 
-Comparison with existing near-Sun models (renew extrapolation figure to 1-column):\\
+Comparison with existing near-Sun models (renew extrapolation figure to 1-column; with half/twice SSN)\\
+calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
 
@@
 
-\subsection{SPP solar wind model}
+\subsection{SPP solar wind environment estimation}
 Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
-A zoom into the first and the nearest perihelia shows... (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
+The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity the SSN independent slow and fast parts are plotted.}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018 at ?\SI{0.16}{\au}.
+For the velocity the SSN independent slow and fast parts are plotted.}
 	\label{fig:SPP_perihelia_prediction_c_plot}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity the SSN independent slow and fast parts are plotted.}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024 at \SI{0.0459}{\au}.
+For the velocity the SSN independent slow and fast parts are plotted.}
 	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
@@
 
-The use of hourly data instead of higher resolution data (less than 1~min) has no significant influence on the bulk results.
-The minutely OMNI data frequency distributions are almost congruent and differ only slightly at their extreme ends.\\
-The many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions \citep[p.~491]{Schwenn1983}.\\
-
 The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS).\\
@@
 
-OMNI data is not corrected for solar distace. only available for 1-/5-min data\\
+%OMNI data is not corrected for solar distace. only available for 1-/5-min data\\
 
@@
 
-Further investigations should be done into structure extrapolations, outward extension of model to Mars...\\
+Further investigations should be done into structure extrapolations; outward extension of model to Mars seems feasable...\\
 

### 2017-05-28 paperMVVB/sections/acknowledgments.tex
consistent variable naming; streamlined some sentences

--- 2017-04-05 paperMVVB_backup_2017-03-31/sections/acknowledgments.tex
@@
 	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
+	The SPP SPICE kernel was kindly provided by Angelos~Vourlidas.\\
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.

### 2017-05-28 paperMVVB/sections/content.tex
consistent variable naming; streamlined some sentences

@@
 %WISPR
-white light imager WISPR... \citep{Vourlidas2016}\\
+[white light imager WISPR... \citep{Vourlidas2016}]\\
 
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{2}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
-		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{}	&\multicolumn{1}{c}{[\%]}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{2}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
+		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{}	&\multicolumn{1}{c}{[\%]}\\
 		\hline
@@
 In this static model the slow and fast part contribute almost equally ($c \approx 0.5$), which of course is only valid for this kind of long-term average.
-At different times in a solar cycle their contributions vary strongly.\\
+At different times in a solar cycle their contributions vary strongly.
 
@@
 The simple lognormal fit models of the magnetic field strength, the velocity and the density underestimate their frequency at the high value tails, whereas the temperature's tail is overestimated (see insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).
-The velocity's compositional lognormal fit only slightly overestimates its tail (inset in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).\\
+The velocity's compositional lognormal fit only slightly overestimates its tail (inset in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).
 
 Short-term variations in the solar wind cannot be predicted, but their occurrence rate can.
-It depends on solar activity, which changes cyclically and thus can be forecasted to a certain degree---at least within a solar cycle.\\
+It depends on solar activity, which changes cyclically and thus can be forecasted to a certain degree---at least within a solar cycle.
 
@@
 Solar activity is commonly measured via the sunspot number.
-We want to correlate OMNI in situ measurements with the SSN, but OMNI data are from Earth orbit, causing variations in solar latitude and distance.
-To dodge these variations we use yearly OMNI and SSN data.\\
+We want to correlate OMNI in situ measurements with the SSN, yet OMNI data are from Earth orbit, causing variations in solar latitude and distance.
+To dodge these seasonal variations we use yearly OMNI and SSN data.
 
@@
 
-seasonal influence contained within yearly frequency distributions\\
-
-SIDC and SWPC provide limited SSN forecast (a few months)\\
+%seasonal influence contained within yearly frequency distributions\\
 
 \subsection{SSN correlation}
-Our current interest lies in the correlation of the SSN to the solar wind median value, because it defines the position of the lognormal function.
-The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.\\
+Our current interest lies in the correlation of the SSN to the solar wind median values, because the median defines the position of a lognormal function.
+The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.
 
-solar activity = SSN $\neq$ solar cycle\\
-The solar wind velocity (and its close friends N \& T) is known to depend on the state of the solar cycle (cite?), which is why it follows the SSN only indirectly (with time lag).
-Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}).\\
+%solar activity = SSN $\neq$ solar cycle\\
+The solar wind velocity and its close friends density and temperature are known to depend on the state of the solar cycle (cite?), which is why they follow the SSN indirectly (with time lag).
+Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}).
 \begin{figure}
@@
 It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the solar surface magnetic flux (cite?).\\
-Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540). The density even 6~years (0.468).\\
+Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540) and the density even 6~years (0.468).\\
 % maximal correlation coefficients and their lag times:\\
@@
 % temperature: lag -3, 0.540\\
-
-cause: direct/indirect correlation\\
+For all parameters their correlation coefficients' amplitudes decline with increasing lag time and, as expected, show a frequency of about 11~years.
 cite literature to lag time...\\
-
-yearly SSN sw model to sw data fits -> SSN dependency (new figs)\\
 
@@
 \end{align}
-using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to keep the new SSN dependency:
+using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to transfer its SSN dependency:
 \begin{align}
@@
 \end{align}
-With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data.
-The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.\\
+With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data (Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).
+\begin{figure*}
+	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_d_plot.pdf}
+	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
+The for the models shifted SSN is indicated by a black line.
+The constant medians of both velocity's lognormal parts are marked with white dots.}
+	\label{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}
+\end{figure*}
+
+The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
 \begin{table*}
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{2}{c}{Balance}\\
 		\cline{3-4}\cline{6-7}
-		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Baseline $b_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
+		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
 		\hline
@@
 		\hline
-		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
-			&\multicolumn{1}{c}{$W_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
+		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
+			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
 		\hline
@@
 
-In comparison with the data the fit models seem to match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
-\begin{figure*}
-	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_d_plot.pdf}
-	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
-The for the models shifted SSN is indicated by a black line.
-The constant medians of both velocity's lognormal parts are marked with white dots.}
-	\label{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}
-\end{figure*}
+Naturally, the fit models match with the general data trends, though single year variations are not able to be replicated by the model (e.g.
+the high velocity and temperature values in 1974, 1994 and 2003).\\
 
-The comparison with the yearly data median values shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN}).\\
+The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope and also show the expected(??) lower magnitude (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN}).\\
 \begin{figure}
@@
 \end{figure}
+
+density modulation with SSN \citep{Schwenn1983} p.~499\\
+density anticorrelation with SSN \citep{Bougeret1984} p.~406\\
 
@@
 In comparison with the data the velocity fit model also matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
-
-density modulation with SSN \citep{Schwenn1983} p.~499\\
-density anticorrelation with SSN \citep{Bougeret1984} p.~406\\
 
@@
 \begin{align}
-	x(r) = a\,r^b	\label{eq:exponential_function}
+	x(r) = d\,r^e	\label{eq:exponential_function}
 \end{align}
@@
 %fit result table and figure
-With $r$ in astronomical units we get the fit coefficients ($a_\text{med}$, $a_\text{avg}$, $b_\text{med}$ and $b_\text{avg}$) as given in Table~\ref{tab:mean_median_fit_parameter}.\\
+With $r$ in astronomical units we get the fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) as given in Table~\ref{tab:mean_median_fit_parameter}.\\
 \begin{table*}
@@
 		\cline{2-3}	\cline{5-6}
-			&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b_\text{med}$}	&	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}\\
+			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}\\
 		\hline
@@
 Those crossings limit the possible extrapolation distances with lognormal functions.
-To circumvent these limitations for all four solar wind parameters we set the exponents $b_\text{med}$ and $b_\text{avg}$ to be identical, avoiding crossing of median and mean.
+To circumvent these limitations for all four solar wind parameters we set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical, avoiding crossing of median and mean.
 Then the distribution's width is constant and scales only exponentially with solar distance.
@@
 \subsection{Exponential lognormal fitting}
-To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:omni_frequency_data}).\\
+To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:omni_frequency_data}).
 % Helios histogram bin sizes for mean of frequency distribution (at specific solar distance):\\
@@
 As mentioned before, we set the exponents of median and average to be identical.
-Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($a_\text{med}$, $a_\text{avg}$ and the common exponent $b$).
+Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
 
 Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
-The additional fit parameters are the balancing parameter $c$ and from the second lognormal part $a_\text{med,2}$ and $a_\text{avg,2}$.
+The additional fit parameters are the balancing parameter $c'$ and from the second lognormal part $d'_\text{med,2}$ and $d'_\text{avg,2}$.
 The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
-			&	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
+			&	&\multicolumn{1}{c}{$d'_\text{med}$}	&\multicolumn{1}{c}{$d'_\text{avg}$}	&\multicolumn{1}{c}{$e'$}	&$c'$\\
 		\hline
@@
 
-With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
+With $c' = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
 
@@
 
+The velocity and temperature models' upper values have a higher frequency than the data shows.
+This is due to the systematic fit discrepancy of the lognormal distribution's high value tails (see zoom box in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).\\
+
 model errors, maximum errors\\
-The extreme values of the velocity and temperature seem to be too high\\
-L-> high value plots... (refer to histogram zoom in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot})\\
 
@@
 %are the exponents time-independent?
-Under the assumption that the exponential falloff laws do not change with time/solar activity (as shown above...), they can be used in general.\\
+Under the assumption that the exponential fall-off laws do not change with time/solar activity (as shown above...), they can be used in general.\\
 
-We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the exponential distance dependence (\ref{eq:exponential_function})
+We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the exponential distance dependence (previous section)
 \begin{align}
-	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^b
+	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^{e'}
 \end{align}
 
-to get the combined model function $W''(x,ssn,r)$. And for the velocity $W_\text{II}''(x,ssn,r)$ with the double lognormal function.\\
+to get the combined model function $W'''(x,ssn,r)$. And for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function.\\
 
 %model errors
-give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\
+give model errors sizes/uncertainties (sigmas); $W'''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\
 
@@
 
-SPP orbit data source\\
-
 The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\
@@
 extrapolation errors...\\
+Comparison with existing near-Sun models (renew extrapolation figure to 1-column; with half/twice SSN)\\
+calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
 
@@
 crossing distance effect\\
-
-Comparison with existing near-Sun models (renew extrapolation figure to 1-column; with half/twice SSN)\\
-calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
 

### 2017-05-29 paperMVVB/sections/acknowledgments.tex
added model ratio line to figure 6; some minor text changes

--- 2017-04-05 paperMVVB_backup_2017-03-31/sections/acknowledgments.tex
@@
 	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
+	The SPP SPICE kernel was kindly provided by Angelos~Vourlidas (check...).\\
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.

### 2017-05-29 paperMVVB/sections/content.tex
added model ratio line to figure 6; some minor text changes

@@
 
-The international sunspot number (\citeyear{sidc}) is retrieved from the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
+The international sunspot number (\citeyear{sidc}) is retrieved from the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
 
@@
 %solar activity = SSN $\neq$ solar cycle\\
-The solar wind velocity and its close friends density and temperature are known to depend on the state of the solar cycle (cite?), which is why they follow the SSN indirectly (with time lag).
+The solar wind velocity and its close friends density and temperature are known to depend on the state of the solar cycle \citep{Schwenn1983}, which is why they follow the SSN indirectly (with time lag).
+%density modulation with SSN \citep{Schwenn1983} p.~499\\
 Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}).
@@
 It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the solar surface magnetic flux (cite?).\\
-Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540) and the density even 6~years (0.468).\\
+Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540).
+The density has a lag time of 6~years (0.468), which is in agreement with the by \citet{Bougeret1984} documented density anticorrelation with SSN.\\	%p.~406\\
+
 % maximal correlation coefficients and their lag times:\\
@@
 \end{align}
-With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data (Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).
-\begin{figure*}
-	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_d_plot.pdf}
-	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
-The for the models shifted SSN is indicated by a black line.
-The constant medians of both velocity's lognormal parts are marked with white dots.}
-	\label{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}
-\end{figure*}
-
+With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data.
 The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
@@
 Naturally, the fit models match with the general data trends, though single year variations are not able to be replicated by the model (e.g.
-the high velocity and temperature values in 1974, 1994 and 2003).\\
-
-The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope and also show the expected(??) lower magnitude (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN}).\\
+the high velocity and temperature values in 1974, 1994 and 2003) (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).
+\begin{figure*}
+	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_d_plot.pdf}
+	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
+The for the models shifted SSN is indicated by a black line.
+The constant medians of both velocity's lognormal parts are marked with white dots.}
+	\label{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}
+\end{figure*}
+The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN}).\\
 \begin{figure}
@@
 
-density modulation with SSN \citep{Schwenn1983} p.~499\\
-density anticorrelation with SSN \citep{Bougeret1984} p.~406\\
-
 Again, the velocity gets a special treatment with the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-It is known that slow and fast solar wind stream occurrence rates follow the solar cycle, but their magnitudes stay fairly stable (cite?).
-This time we keep the two velocity components' positions constant and vary instead their balance with the SSN:
+It is known that slow and fast solar wind stream occurrence rates follow the solar cycle, yet their magnitudes stay fairly stable (cite?).
+Thus we keep the two velocity components' positions constant and vary instead their balance with the SSN:
 \begin{align}
@@
 \end{align}
-The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_e_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_f_plot.pdf}}
 	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN.
@@
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
-The model's balance (\ref{eq:balance_with_ssn}) is obtained without a threshold (dashed).}
-	\label{fig:Vdbl_SSN_ratio_e_plot}
+The model's balance parameter (\ref{eq:balance_with_ssn}) and derived ratio (same threshold) are plotted as dashed and dotted lines.}
+	\label{fig:Vdbl_SSN_ratio_f_plot}
 \end{figure}
 % 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
-The ratio of slow to fast wind obtained from yearly OMNI data via simply applying the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (cite?) has a flatter SSN dependence than the model's balance.
-Why?\\
-Both should not necessary be identical, because there is no specific velocity threshold between slow and fast solar wind types, as the velocity ranges of both types overlap (cite?).\\
+To compare the ratios of slow to fast wind between model and data, we simply apply the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (cite?).
+The linear fit to the yearly data ratio and the derived model ratio are quite similar (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
+Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the somewhat steeper balance parameter of this model.
+The model's balance may represent the actual ratios of the solar wind types in a more realistic way than a specific velocity threshold does, as the velocity ranges of both types overlap (cites?
+- there exists slow sw with properties of fast wind and vice versa...).
 
@@
 
-With $c' = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
+With $c' = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).\\
 
@@
 %are the exponents time-independent?
-Under the assumption that the exponential fall-off laws do not change with time/solar activity (as shown above...), they can be used in general.\\
+Under the assumption that the exponential fall-off laws do not change with time/solar activity (as shown above...), they can be used in general.
 
@@
 The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g.
-Kalman filter combined method) (use cite...).
-The Space Weather Prediction Center's (SWPC) prediction follows a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://legacy-www.swpc.noaa.gov/SolarCycle/}} (until end of 2019) (use cite...).
+Kalman filter combined method).
+The Space Weather Prediction Center's (SWPC) prediction follows a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}} (until end of 2019).
 
@@
 
-prediction errors...\\
-
 \subsection{Near-Sun extrapolation for SPP orbit}
@@
 %SPP orbit
-SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
+SPP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
 
@@
 \subsection{SPP solar wind environment estimation}
-Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
+Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment $W'''(x,ssn,r)$.\\
 The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018 at ?\SI{0.16}{\au}.
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018 at about \SI{0.16}{\au}.
 For the velocity the SSN independent slow and fast parts are plotted.}

### 2017-05-30 paperMVVB/sections/content.tex
updated SSN in fig 9; corrected error band in figs 10+11

@@
 Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment $W'''(x,ssn,r)$.\\
-The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
+The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_d_plot} and \ref{fig:SPP_perihelia_prediction_nearest_d_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_d_plot.pdf}}
 	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018 at about \SI{0.16}{\au}.
 For the velocity the SSN independent slow and fast parts are plotted.}
-	\label{fig:SPP_perihelia_prediction_c_plot}
+	\label{fig:SPP_perihelia_prediction_d_plot}
 \end{figure}
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_d_plot.pdf}}
 	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024 at \SI{0.0459}{\au}.
 For the velocity the SSN independent slow and fast parts are plotted.}
-	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
+	\label{fig:SPP_perihelia_prediction_nearest_d_plot}
 \end{figure}

### 2017-06-01 paperMVVB/sections/abstract.tex
introduced Parker Solar Probe, PSP

--- 2017-04-07 paperMVVB/sections/abstract.tex
@@
-\title{Solar wind prediction for the Solar Probe Plus orbit}
+\title{Solar wind prediction for the Parker Solar Probe orbit}
 \subtitle{Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations}
@@
 \abstract
-{In view of the planned near-Sun spacecraft mission Solar~Probe~Plus (SPP) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
+{In view of the planned near-Sun spacecraft mission Parker~Solar~Probe (PSP) (formerly Solar~Probe~Plus) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
 This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
@@
 The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}.
-This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters SPP will encounter on its mission.}	%aims
+This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters PSP will encounter on its mission.}	%aims
 {The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
@@
 Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
-{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time.}	%results
+{The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment at PSP's planned orbital positions during its mission time.
+The estimated solar wind values at PSP's nearest perihelion vary up to +-XX~\%, arising only from differing amplitude assumptions for the next solar cycle.}	%results
 {}	%conclusions
-%\SI{0.0459}{\au}
 
@@
 
-%\titlerunning{Solar wind extrapolation to SPP orbit}
+%\titlerunning{Solar wind extrapolation to PSP orbit}
 %\authorrunning{Venzmer \& Bothmer}
 
+%\SI{0.0459}{\au}
 %extrapolated ranges \SI{95.45}{\percent} of the solar wind parameter values lie within.

### 2017-06-01 paperMVVB/sections/content.tex
introduced Parker Solar Probe, PSP

@@
 So far, Helios~2 made the nearest in situ solar wind measurements with \SI{0.29}{\au}, followed closely by Helios~1 with \SI{0.31}{\au}.
-The new mission Solar~Probe~Plus~(SPP), whose planned launch date is in mid 2018, aims to reach further down into the Sun's atmosphere.
+The new mission Parker~Solar~Probe (PSP), whose planned launch date is in mid 2018, aims to reach further down into the Sun's atmosphere.
 
 %Solar Probe Plus mission
-The main part of the SPP mission's goals is to gain insight into the coronal heating and solar wind acceleration processes.
-As these processes occur in the near-Sun region of the corona, SPP will have its closest perihelion at 9.86~solar radii (0.0459~au) \citep{Fox2015}.
+The main part of the PSP mission's goals is to gain insight into the coronal heating and solar wind acceleration processes.
+As these processes occur in the near-Sun region of the corona, PSP will have its closest perihelion at 9.86~solar radii (0.0459~au) \citep{Fox2015}.
 It will be the first spacecraft flying and measuring in situ solar wind this close to the Sun.
-Its planned observations range from the perihelion up to \SI{0.25}{\au}, leaving the outer part for data transfer, as \citet{Fox2015} state in their description of SPP's mission design.\\
+Its planned observations range from the perihelion up to \SI{0.25}{\au}, leaving the outer part for data transfer, as \citet{Fox2015} state in their description of PSP's mission design.\\
 
@@
 %solar wind parameters
-The goal of this paper is to estimate the solar wind environment SPP will probe during its orbits.
+The goal of this paper is to estimate the solar wind environment PSP will probe during its orbits.
 We regard the solar wind primarily as a proton plasma, because protons make up most of it.
@@
 %frequency distribution data
-One cannot know which specific solar wind type or structure SPP will encounter at a given point in time, so we extrapolate the parameters' probability distributions from existing solar wind measurements.
+One cannot know which specific solar wind type or structure PSP will encounter at a given point in time, so we extrapolate the parameters' probability distributions from existing solar wind measurements.
 
@@
 
-This general model is then fed with a SSN prediction and extrapolated to SPP's planned orbital positions.\\
+This general model is then fed with a SSN prediction and extrapolated to PSP's planned orbital positions.\\
 
@@
 At the crossing point and below the magnetic field strength can therefore not be described anymore with a lognormal function.
-For an extrapolation to the SPP perihelion the same happens for the temperature at \SI{0.082}{\au}.
+For an extrapolation to the PSP perihelion the same happens for the temperature at \SI{0.082}{\au}.
 
@@
 
-\section{Model extrapolation to SPP orbital time and position}
-To estimate the solar wind environment at SPP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the SPP perihelion region are performed.\\
+\section{Model extrapolation to PSP orbital time and position}
+To estimate the solar wind environment at PSP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the PSP perihelion region are performed.\\
 
-\subsection{SSN prediction for SPP mission time}
+\subsection{SSN prediction for PSP mission time}
 %SSN prediction
@@
 Additionally we consider the two alternatives of half and twice its amplitude.
-The SSN for SPP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_d_plot.pdf}}
-	\caption{SPP's solar distance during its mission time (top).
+	\caption{PSP's solar distance during its mission time (top).
 Consecutive Venus flybys bring its perihelia nearer to the Sun.
@@
 
-\subsection{Near-Sun extrapolation for SPP orbit}
+\subsection{Near-Sun extrapolation for PSP orbit}
 
-%SPP orbit
-SPP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
+%PSP orbit
+PSP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
 
@@
 
-The near-Sun (SPP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
+The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
 
@@
 
-\subsection{SPP solar wind environment estimation}
-Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment $W'''(x,ssn,r)$.\\
+\subsection{PSP solar wind environment estimation}
+Implementing the orbital distance data and predicted SSN for the mission time we get PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
 The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_d_plot} and \ref{fig:SPP_perihelia_prediction_nearest_d_plot}).\\
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_d_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018 at about \SI{0.16}{\au}.
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during PSP's first perihelion in 2018 at about \SI{0.16}{\au}.
 For the velocity the SSN independent slow and fast parts are plotted.}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_d_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024 at \SI{0.0459}{\au}.
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during PSP's nearest perihelion in 2024 at \SI{0.0459}{\au}.
 For the velocity the SSN independent slow and fast parts are plotted.}

### 2017-06-01 paperMVVB/sections/content.tex
added extrapolation figure draft; added some cites

@@
 %difference to other models
-There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites?).
+There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}).
 They examine average values, additionally distinguishing between slow and fast wind.
@@
 In addition, the velocity is the defining parameter of the two types of solar wind.
-Solar wind mostly consists of and switches between slow and fast wind, whose ratio highly depends on solar activity.
-These types have different characteristics and their interactions lead to phenomena such as interaction regions.
+Solar wind mostly consists of and switches between slow and fast wind, whose different compositions and characteristics also indicate different sources and generation processes \citep{McGregor2011a} (better cites?).
+Their ratio highly depends on solar activity (cite?) and their interactions lead to phenomena such as interaction regions.
+
 Additionally there also are coronal mass ejections (CMEs) embedded, whose occurrence rate follows solar activity too.
@@
 We do not want to abandon the well-founded application of the lognormal function.
-However, it is reasonable to assume that the velocity distribution is composed of at least two branches (slow and fast).
+However, it is reasonable to assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
 Therefore a compositional approach promises better fit results, which is why we combine two lognormal functions (\ref{eq:single_lognormal_fit_function}), bearing the disadvantage of more fit variables:
@@
 The highest correlation coefficient for the magnetic field strength is 0.728.
-It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the solar surface magnetic flux (cite?).\\
+It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the magnetic flux \citep{Smith2003}.\\
 Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540).
@@
 
+Comparison with existing near-Sun models (Fig.~\ref{fig:sw_extrapolation_ssn_plot}); with half/twice SSN)\\
+calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
+\begin{figure*}
+	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_plot.pdf}
+	\caption{Solar wind model extrapolations to the PSP orbit region.
+The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the case of solar minimum (maximum) with a SSN of 0 (200).
+For comparison other near-Sun models are also shown...
+to 1-column...?}
+	\label{fig:sw_extrapolation_ssn_plot}
+\end{figure*}
+
 extrapolation errors...\\
-Comparison with existing near-Sun models (renew extrapolation figure to 1-column; with half/twice SSN)\\
-calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
+
+\citep{Banaszkiewicz1998}, analytical magnetic field model, DQCS model\\
 

### 2017-06-05 paperMVVB/sections/abstract.tex
Parker solution into fig 10; changes to sect. 7.2; other minor text changes

@@
 Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies.
-Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
+Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic region.}	%methods
 {The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment at PSP's planned orbital positions during its mission time.

### 2017-06-05 paperMVVB/sections/acknowledgments.tex
Parker solution into fig 10; changes to sect. 7.2; other minor text changes

--- 2017-04-05 paperMVVB_backup_2017-03-31/sections/acknowledgments.tex
@@
 	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
+	The PSP SPICE kernel was kindly provided by Angelos~Vourlidas (check...).\\
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.

### 2017-06-05 paperMVVB/sections/content.tex
Parker solution into fig 10; changes to sect. 7.2; other minor text changes

@@
 Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540).
-The density has a lag time of 6~years (0.468), which is in agreement with the by \citet{Bougeret1984} documented density anticorrelation with SSN.\\	%p.~406\\
+The density has a lag time of 6~years (0.468), which is in agreement with the by \citet{Bougeret1984} documented density anticorrelation with SSN.	%p.~406\\
 
@@
 % temperature: lag -3, 0.540\\
-For all parameters their correlation coefficients' amplitudes decline with increasing lag time and, as expected, show a frequency of about 11~years.
-cite literature to lag time...\\
+For all parameters their correlation coefficients' amplitudes decline with increasing lag time and, as also expected, show a frequency of about 11~years.
 
@@
 \label{sec:ssn_fitting}
-To be able to shift the distributions with SSN, we add a linear SSN dependency to the median
+To be able to shift the frequency distributions with SSN, we add a linear SSN dependency to the median
 \begin{align}
@@
 Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the somewhat steeper balance parameter of this model.
-The model's balance may represent the actual ratios of the solar wind types in a more realistic way than a specific velocity threshold does, as the velocity ranges of both types overlap (cites?
-- there exists slow sw with properties of fast wind and vice versa...).
-
-In comparison with the data the velocity fit model also matches with the general trend (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).\\
+The model's balance may represent the actual ratios of the solar wind types in a more realistic way than a specific velocity threshold does, since the velocity ranges of both types overlap \citep{McGregor2011b}.
+%(i.e. there exists slow wind with properties of fast wind and vice versa)
 
@@
 \subsection{Exponential fitting}
+\label{sec:exponential_fitting}
 %why exponential function?
@@
 %fit result table and figure
-With $r$ in astronomical units we get the fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) as given in Table~\ref{tab:mean_median_fit_parameter}.\\
+With $r$ in astronomical units we get the fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) as given in Table~\ref{tab:mean_median_fit_parameter}.
 \begin{table*}
@@
 \end{figure*}
-However, the magnetic field strength's mean crosses the median at \SI{0.339}{\au} (Table~\ref{tab:mean_median_fit_parameter}) and is lower at smaller distances.
+
+The large velocity's crossing distance and its large error indicate that the median's and mean's distance behavior can be kept identical and so the frequency's shape distance independent.
+
+However, the magnetic field strength's mean crosses the median at \SI{0.339}{\au} and is lower at smaller distances (Table~\ref{tab:mean_median_fit_parameter}).
 At the crossing point and below the magnetic field strength can therefore not be described anymore with a lognormal function.
@@
 
-The large velocity's crossing distance and its large error indicate that the median's and mean's distance behavior can be kept identical and so the frequency's shape distance independent.
-
 Those crossings limit the possible extrapolation distances with lognormal functions.
 To circumvent these limitations for all four solar wind parameters we set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical, avoiding crossing of median and mean.
-Then the distribution's width is constant and scales only exponentially with solar distance.
+Then the distribution's width scales exponentially with solar distance.
 Applying this approximation, we have to accept larger model errors, especially for the magnetic field strength.
-It also limits the extrapolation accuracy.
+It also limits the extrapolation accuracy, however it keeps the model simpler.
 
@@
 
-With $c' = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to $c(59) = 0.53$, see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).\\
+With $c' = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to $c(59) = 0.53$; see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
 
@@
 The magnetic field strength frequency is more focused (around \SI{40}{nT}) at the lower distance boundary than the model's is.
-This is expected because of our fixed distance independent shape approximation.\\
+This is expected because of our fixed distance independent shape approximation.
 \begin{figure*}
@@
 
-model errors, maximum errors\\
+Possible differing scaling laws at smaller heliocentric distances are discussed in Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}.\\
 
-This model represents the Helios time frame around the rise of solar cycle~21.\\
+This radial solar wind model represents the Helios time frame around the rise of solar cycle~21.\\
 
@@
 - modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
-- possibility to extrapolate model down to 0.0459~au\\
+- possibility to extrapolate model down to \SI{0.0459}{\au}\\
 
@@
 \section{Model extrapolation to PSP orbital time and position}
+\label{sec:model_extrapolation_to_psp_orbital_time_and_position}
 To estimate the solar wind environment at PSP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the PSP perihelion region are performed.\\
@@
 %SSN prediction
-For the SSN prediction there are several sources available.
+For the SSN short-term prediction are several sources available.
 The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g.
@@
 
-[=> Implications for the mission...]\\
+[=> Implications for the sw estimation...]\\
 
@@
 PSP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
-
-The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\
 
@@
 
-\citep{Banaszkiewicz1998}, analytical magnetic field model, DQCS model\\
+%magnetic field:
+The magnetic field magnitude from our extrapolation is flatter than the analytical magnetic field model from \citet{Banaszkiewicz1998}, who constructed a dipole plus quadrupole plus current sheet (DQCS) model.
+We attribute this effect to the from a lognormal shape deviating distribution (see Sect.~\ref{sec:exponential_fitting}).\\
 
-velocity:\\
+%velocity:
 %critical surfaces
 Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
-in direction to the Sun is at $\sim$2.5~Rs the source surface (Schatten1969)\\
+in direction to the Sun is at about \SI{2.5}{R_s} the source surface (Schatten1969)\\
 sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
@@
 
+\citet{Wang2000}, sources of slow solar wind + IMF regulation mechanism + blobs; compare with our slow V lognormal part; Parker solution\\
+
+\citet{Sheeley1997} -> LASCO coronagraph observed speed profile of coronal features tracing the slow solar wind, 2--30~Rs\\
+- parabolic eq.~(2) and exponential eq.~(3)\\
+- sonic point 5--6~Rs\\
+- slow solar wind origin 3--4~Rs\\
+
 The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
+The \citet{Parker1958} model of an isothermal expanding corona with a temperature of \SI{e6}{\K} and a critical radius of \SI{5.8}{R_s}.\\
 
-density:\\
-\citet{Leblanc1998} -> electron density model derived from type~III radio burst observations\\
-The density distance dependency scales with $r^{-2}$, but steepens below 10~Rs with $r^{-6}$ \citep{Leblanc1998}.\\
+%density:
+We expect that even our Sun-nearest extrapolated density at PSP perihelion agrees well with the actual, since \citet{Leblanc1998} derived an electron density model from type~III radio burst observations.
+Their model shows that the density distance dependency scales with $r^{-2}$ and steepens not until below \SI{10}{R_s} with $r^{-6}$ (see Fig.~\ref{fig:sw_extrapolation_ssn_plot}).\\
 
@@
 crossing distance effect\\
-
-\citet{Wang2000}, sources of slow solar wind + IMF regulation mechanism + blobs; compare with our slow V lognormal part\\
 
@@
 
-\citet{Sheeley1997} -> LASCO coronagraph observed speed profile of coronal features tracing the slow solar wind, 2--30~Rs\\
-- parabolic eq.~(2) and exponential eq.~(3)\\
-- sonic point 5--6~Rs\\
-- slow solar wind origin 3--4~Rs\\
-
-The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
-L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
+% The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
+% L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
 
 \subsection{PSP solar wind environment estimation}
-Implementing the orbital distance data and predicted SSN for the mission time we get PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
+Implementing the orbital distance data and predicted SSN for the mission time we can derive PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
 The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_d_plot} and \ref{fig:SPP_perihelia_prediction_nearest_d_plot}).\\
@@
 Balogh2009 (HMF review + inner heliosheath)\\
-Patsourakos2016 (near-Sun B-field of CMEs)\\
 Aschwanden2004, p.~29\\
 
-Parker1963\\
-%https://babel.hathitrust.org/cgi/pt?id=uc1.b4264142;view=1up;seq=12
-
 individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
-\citet{Sanchez-Diaz2016} (very slow solar wind)\\
+\citet{Sanchez-Diaz2016} (very slow solar wind; continuation of slow sw)\\
 Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\

### 2017-06-07 paperMVVB/sections/content.tex
corrected combined median speeds in tab 1, 4 and fig 2; derived composed median velocity for fig 5, 4, 8 and 10; included perihelia into fig 9; reworked fig 10

@@
 \begin{table*}
-	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au}.
+	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au} (OMNI hourly data).
 For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit.
@@
 		\cline{2-7}
-			&\multicolumn{1}{c}{$W_\text{II}$}	&4.12(14)\tablefootmark{b}	&4.38(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98e-4	&4.20\\
+			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{b}	&4.42(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98e-4	&4.20\\
 		\hline
@@
 % Vdbl fit:
-% ('medians = ', 489.31184203751639, 368.3008016238619)
-% ('means = ', 500.432137424129, 371.82451161611743)
-% mean = 437.7390999905267
-% median = 412.4937999968638
+% medians = 489, 368
+% means = 500, 372
+% c = 0.504
+% via calculate_twolognormal_median.py:
+% mean = 442.38
+% median = 416.05
 % fit data difference (normed area):\\
@@
 \begin{table*}
-	\caption{Resulting fit coefficients from the data fitting with lagged SSN.
+	\caption{Resulting fit coefficients from the OMNI data fitting with lagged SSN.
 For the velocity the fit parameters from the double lognormal fit and their balancing function are given.
@@
 Naturally, the fit models match with the general data trends, though single year variations are not able to be replicated by the model (e.g.
-the high velocity and temperature values in 1974, 1994 and 2003) (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}).
+the high velocity and temperature values in 1974, 1994 and 2003) (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}).
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_d_plot.pdf}
+	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_e_plot.pdf}
 	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
 The for the models shifted SSN is indicated by a black line.
-The constant medians of both velocity's lognormal parts are marked with white dots.}
-	\label{fig:OMNI_yearly_BVdblNTSSN_fit_d_plot}
+The velocity median is derived from the SSN weighted constant lognormal parts (dotted).}
+	\label{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}
 \end{figure*}
-The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN}).\\
+The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN_a.pdf}}
 	\caption{Solar wind parameter median over lagged SSN.
@@
 The SSN dependent median (\ref{eq:median_with_ssn}) is from the lognormal model fit (dashed).
-For the velocity the SSN independent slow and fast model parts are plotted instead (dotted).}
-	\label{fig:OMNI_yearly_BVNTvsSSN}
+For the velocity the median is derived from the SSN weighting of the slow and fast model parts, whose magnitudes are SSN independent (dotted).}
+	\label{fig:OMNI_yearly_BVNTvsSSN_a}
 \end{figure}
@@
 \begin{table*}
-	\caption{These are the fit coefficients for the median and mean solar distance dependencies of the four parameters from the combined Helios data set.
+	\caption{Fit coefficients for the median and mean solar distance dependencies of the four parameters from the combined Helios data set.
 The errors in brackets are the estimated standard deviations of each fit parameter.
@@
 \begin{table*}
-	\caption{These are the resulting fit coefficients with the single lognormal exponential function, respectively double lognormal for the velocity.
+	\caption{Fit coefficients from the single lognormal exponential function, respectively double lognormal for the velocity (combined Helios data).
 The errors in brackets are the estimated standard deviations of each fit parameter.}
@@
 		\cline{2-6}
-		\multicolumn{2}{r}{$W''_\text{II}$}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+		\multicolumn{2}{r}{$W''_\text{II}$}	&4.13(13)\tablefootmark{b}	&4.47(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
 		\hline
@@
 \end{table*}
+% Vdbl fit:
+% medians = 370.7, 526
+% means = 374.8, 542
+% c = 0.557
+% via calculate_twolognormal_median.py:
+% mean = 446.64
+% median = 413.33
 
@@
 
-The fit models seem to resemble the data quite well (Fig.~\ref{fig:mixed_fit_fixed_4_paper_e_plot}).
+The fit models seem to resemble the data quite well (Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}).
 The magnetic field strength frequency is more focused (around \SI{40}{nT}) at the lower distance boundary than the model's is.
@@
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_e_plot.pdf}
+	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_f_plot.pdf}
 	\caption{Solar wind parameter's frequency distributions over solar distance.
 Plotted are the binned Helios data and the exponential lognormal fit model (double lognormal for the velocity) with their median values (white).}
-	\label{fig:mixed_fit_fixed_4_paper_e_plot}
+	\label{fig:mixed_fit_fixed_4_paper_f_plot}
 \end{figure*}
@@
 Additionally we consider the two alternatives of half and twice its amplitude.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot})\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_d_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_e_plot.pdf}}
 	\caption{PSP's solar distance during its mission time (top).
@@
 SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
-	\label{fig:SPP_orbit_predicted_SSN_overview_d_plot}
+	\label{fig:SPP_orbit_predicted_SSN_overview_e_plot}
 \end{figure}
@@
 %PSP orbit
-PSP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
+PSP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot})\\
 
-Comparison with existing near-Sun models (Fig.~\ref{fig:sw_extrapolation_ssn_plot}); with half/twice SSN)\\
+Comparison with existing near-Sun models (Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}); with half/twice SSN)\\
 calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_plot.pdf}
-	\caption{Solar wind model extrapolations to the PSP orbit region.
-The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the case of solar minimum (maximum) with a SSN of 0 (200).
-For comparison other near-Sun models are also shown...
+	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_b_plot.pdf}
+	\caption{Radial extrapolation of the solar wind parameters to the PSP orbit region.
+The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the extreme cases of solar minimum (SSN = 0) and maximum (SSN = 200).
+Note that there is a time lag to the SSN depending on the solar wind parameter.
+The magnetic field radial dependence is slightly flatter than the analytic DQCS model for solar minimum which \citet{Banaszkiewicz1998} derived.
+Below \SI{20}{R_s} the slow wind velocity is overestimated in comparison to the measurements from \citet{Wang2000}) and \citep{Sheeley1997}.
+They derived temperature and sonic point values for slow solar wind with the isothermal expansion model \citep{Parker1958}.
+Down to PSP's perihelion the density is in good agreement with the model from \citet{Leblanc1998}.
 to 1-column...?}
-	\label{fig:sw_extrapolation_ssn_plot}
+	\label{fig:sw_extrapolation_ssn_b_plot}
 \end{figure*}
@@
 We expect that even our Sun-nearest extrapolated density at PSP perihelion agrees well with the actual, since \citet{Leblanc1998} derived an electron density model from type~III radio burst observations.
-Their model shows that the density distance dependency scales with $r^{-2}$ and steepens not until below \SI{10}{R_s} with $r^{-6}$ (see Fig.~\ref{fig:sw_extrapolation_ssn_plot}).\\
+Their model shows that the density distance dependency scales with $r^{-2}$ and steepens not until below \SI{10}{R_s} with $r^{-6}$ (see Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}).\\
 

### 2017-06-09 paperMVVB/sections/content.tex
derived median perihelia speed for figs 11 and 12

@@
 Implementing the orbital distance data and predicted SSN for the mission time we can derive PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
-The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_d_plot} and \ref{fig:SPP_perihelia_prediction_nearest_d_plot}).\\
+The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot}).\\
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_d_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during PSP's first perihelion in 2018 at about \SI{0.16}{\au}.
-For the velocity the SSN independent slow and fast parts are plotted.}
-	\label{fig:SPP_perihelia_prediction_d_plot}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_e_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during 12 days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
+For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted).}
+	\label{fig:SPP_perihelia_prediction_e_plot}
 \end{figure}
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_d_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during PSP's nearest perihelion in 2024 at \SI{0.0459}{\au}.
-For the velocity the SSN independent slow and fast parts are plotted.}
-	\label{fig:SPP_perihelia_prediction_nearest_d_plot}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_e_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during during 12 days in 2024 with PSP's nearest perihelion at \SI{0.0459}{\au}.
+For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted).}
+	\label{fig:SPP_perihelia_prediction_nearest_e_plot}
 \end{figure}

### 2017-06-17 paperMVVB/sections/abstract.tex
included figure yearly exponents; sect. 7.2 beginning modified; text: some wording changed

@@
 {The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment at PSP's planned orbital positions during its mission time.
-The estimated solar wind values at PSP's nearest perihelion vary up to +-XX~\%, arising only from differing amplitude assumptions for the next solar cycle.}	%results
+The estimated solar wind values at PSP's nearest perihelion are: ...
+Their value vary up to \SI{+-0.0000}{\percent}, arising only from differing amplitude assumptions for the next solar cycle.}	%results
 {}	%conclusions

### 2017-06-17 paperMVVB/sections/content.tex
included figure yearly exponents; sect. 7.2 beginning modified; text: some wording changed

@@
 \end{figure}
-That is why we keep using the double lognormal ansatz for the velocity frequency fits in the following sections.\\
+For this reason we keep using the double lognormal ansatz for the velocity frequency fits in the following sections.\\
 In this static model the slow and fast part contribute almost equally ($c \approx 0.5$), which of course is only valid for this kind of long-term average.
@@
 	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top).
-Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
+Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
 	\label{fig:OMNI_yearly_ssn_correlation_c_plot}
@@
 
-The highest correlation coefficient for the magnetic field strength is 0.728.
-It is without lag time and the highest of all solar wind parameters, which is expected because the SSN is directly proportional to the magnetic flux \citep{Smith2003}.\\
+The highest correlation coefficient for the magnetic field strength is 0.728, which is without lag time and the highest of all solar wind parameters.
+This is anticipated because the SSN is directly proportional to the magnetic flux \citep{Smith2003}.\\
 Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540).
@@
 % temperature: lag -3, 0.540\\
-For all parameters their correlation coefficients' amplitudes decline with increasing lag time and, as also expected, show a frequency of about 11~years.
+As expected, the correlation coefficients' amplitudes of all parameters decline with increasing lag time and show a frequency of about 11~years.
 
@@
 \end{figure*}
-The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}).\\
+The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}).
 \begin{figure}
@@
 The linear fit to the yearly data ratio and the derived model ratio are quite similar (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
-Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the somewhat steeper balance parameter of this model.
+Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the to some degree steeper balance parameter of this model.
 The model's balance may represent the actual ratios of the solar wind types in a more realistic way than a specific velocity threshold does, since the velocity ranges of both types overlap \citep{McGregor2011b}.
@@
 Using this data, we also have to keep in mind that its time coverage is unequally distributed over the solar cycle.
-Dividing the data by the transition from cycle minimum to maximum (mid 1977) and considering the data gap distributions, the Helios data covers about \SI{68}{\percent} during cycle minimum whereas during maximum only \SI{38}{\percent}.\\
+Dividing the data by the transition from cycle minimum to maximum (mid 1977) and considering the data gap distributions, the Helios data covers about \SI{68}{\percent} during cycle minimum whereas during maximum only \SI{38}{\percent}.
 
@@
 
-For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.\\
+For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.
 
@@
 The errors in brackets are the estimated standard deviations of each fit parameter.
-The crossing distance is the point where the fitted median and mean intersect.}
+The crossing distance is the point where the fitted median and mean intersect.
+The year variation is the weighted standard deviation from all yearly fitted exponents.}
 	\label{tab:mean_median_fit_parameter}
@@
 	S[table-format = +1.3(2)]
-	S[table-format = 1.1(2)e1]}
+	S[table-format = 1.1(2)e1]
+	S[table-format = 1.3]}
 		\hline\hline
-		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}\\
+		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Year variation}\\
 		\cline{2-3}	\cline{5-6}
-			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}\\
+			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
 		\hline
-		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)\\
-		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3\\
-		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)\\
-		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)\\
+		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
+		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
+		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
+		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.005\\
 		\hline
@@
 \end{table*}
+% source year variation: fit_out_yearly_gradients_table_b_stats.txt
+
+% comparison with other Helios studies (Schwenn, Bougeret)
+As expected, the velocity exponents match with those from \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately ($v_\text{H1}(r) \propto r^{0.083}$ and $v_\text{H2}(r) \propto r^{0.036}$).
+%Helios results, radial gradients see \citet{Schwenn1990} p.~155\\
+Likewise, the density exponents agree well with the Helios plasma density model, which \citet{Bougeret1984} derived from Helios data and normed to the 1976 \SI{1}{\au} density ($n(r) = 6.14\,r^{-2.10}\,\text{cm}^{-3}$).
 
@@
 Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
-
 Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
@@
 \end{figure*}
+The velocity and temperature models' upper values have a higher frequency than the data shows.
+This is due to the systematic fit discrepancy of the lognormal distribution's high value tails (see zoom box in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).
 
-The velocity and temperature models' upper values have a higher frequency than the data shows.
-This is due to the systematic fit discrepancy of the lognormal distribution's high value tails (see zoom box in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).\\
+\subsection{Distance scaling law variations}
+\label{sec:distance_scaling_law_variations}
 
-Possible differing scaling laws at smaller heliocentric distances are discussed in Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}.\\
+relocate section to 5.3?\\
 
-This radial solar wind model represents the Helios time frame around the rise of solar cycle~21.\\
+This radial solar wind model represents the Helios time frame around the rise of solar cycle~21.
+It is known that the solar wind parameters' magnitudes vary with solar activity.
+Looking at the variation of the yearly distance scaling laws (Fig.~\ref{fig:yearly_gradients_b}), there is no systematic variation for the magnetic field.
+The exponents of velocity and temperature seem to follow the SSN and the density not...
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_b.pdf}}
+	\caption{Helios year variation of the solar wind parameters' fit exponents and SIDC 13-month smoothed monthly SSN. In this plot the year 1974 is omitted because the 21 days covered only }
+	\label{fig:yearly_gradients_b}
+\end{figure}
 
-study cycle variation of exponent\\
-indications for that: figure! + theory + studies/papers...\\
-assuming the distance scaling laws are time independent, which we reason from that; it is an approximation\\
+For simplicity we assume that the distance scaling laws are time independent and account for this approximation with including the calculated exponents' yearly variations (Table~\ref{tab:mean_median_fit_parameter}) as uncertainities.\\
+
+make remark about influence of unequal solar cycle coverage... (sect.~5.1)\\
+
+Possible differing scaling laws at smaller heliocentric distances are discussed in Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}.
 
@@
 
-to get the combined model function $W'''(x,ssn,r)$. And for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function.\\
+to get the combined model function $W'''(x,ssn,r)$. And for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).\\
 
 %model errors
-give model errors sizes/uncertainties (sigmas); $W'''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\
+%give model errors sizes/uncertainties (sigmas); $W'''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\
 
-model requirements:\\
-- modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
-- modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
-- possibility to extrapolate model down to \SI{0.0459}{\au}\\
+% model requirements:\\
+% - modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
+% - modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
+% - possibility to extrapolate model down to \SI{0.0459}{\au}\\
 
 %model limits
-model limits (spherical coordinates):\\
-- heliocentric distance range 0.29--0.98~au\\
+empirical model limits (spherical coordinates):\\
+- heliocentric distance range \SIrange{0.29}{0.98}{\au}\\
 - rotational symmetry\\
-- confined to ecliptic +-7.2 degrees\\
+- confined to ecliptic (\SI{+-7.2}{\degree} HGI)\\
 model constrictions:\\
@@
 \label{sec:model_extrapolation_to_psp_orbital_time_and_position}
-To estimate the solar wind environment at PSP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the PSP perihelion region are performed.\\
+To estimate the solar wind environment at PSP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the PSP perihelion region are performed.
 
@@
 Additionally we consider the two alternatives of half and twice its amplitude.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot})\\
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).
 \begin{figure}
@@
 
-[=> Implications for the sw estimation...]\\
+\subsection{Near-Sun extrapolation for PSP orbit}
+%PSP orbit
+Parker Solar Probe is planned to launch in mid 2018.
+With its first Venus flyby it will swing into Venus' orbital plane(?) (\SI{3.86}{\degree} to Sun's equator), which allows for additional seven flybys to finally reduce its perihelion distance to a minimum of less than \SI{10}{R_s} \citep{Fox2015} (Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).\\
 
-\subsection{Near-Sun extrapolation for PSP orbit}
-
-%PSP orbit
-PSP orbit description, seven Venus flybys, within Venus' orbital plane? (\SI{3.86}{\degree} to Sun's equator), \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot})\\
-
-Comparison with existing near-Sun models (Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}); with half/twice SSN)\\
-calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\
+For the extrapolation to PSP's orbital range we just assume that our derived distance scaling laws do not change.
+The comparison with existing near-Sun models reveals that this is not entirely true (Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}).\\
 \begin{figure*}
@@
 \end{figure*}
-
-extrapolation errors...\\
 
@@
 \citet{Wang2000}, sources of slow solar wind + IMF regulation mechanism + blobs; compare with our slow V lognormal part; Parker solution\\
+-> below 20~Rs PSP will fly well into sw acceleration region\\
 
 \citet{Sheeley1997} -> LASCO coronagraph observed speed profile of coronal features tracing the slow solar wind, 2--30~Rs\\
-- parabolic eq.~(2) and exponential eq.~(3)\\
+%- parabolic eq.~(2) and exponential eq.~(3)\\
 - sonic point 5--6~Rs\\
@@
 crossing distance effect\\
-
-% comparison with other Helios studies (Schwenn, Bougeret)
-\citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately ($v_\text{H1}(r) \propto r^{0.083}$ and $v_\text{H2}(r) \propto r^{0.036}$), average or median?
-fits well...\\
-Helios results, radial gradients see \citet{Schwenn1990} p.~155\\
-
-The electron density distance function, which \citet{Bougeret1984} derived from Helios data and normed to the 1976 1~au density ($n(r) = 6.14\,r^{-2.10(4)}\,\text{cm}^{-3}$) also fits well...\\
 
@@
 individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
-\citet{Sanchez-Diaz2016} (very slow solar wind; continuation of slow sw)\\
 Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\

### 2017-06-24 paperMVVB/sections/content.tex
minor

@@
 the probes Helios, Voyager, Ulysses...).
-Voyager~1 is the farthest probe out of the solar system, now covering more than 137~au (cite?).
-Ulysses was the single probe orbiting the Sun outside the ecliptic and retrieving solar wind measurements from the poles of the Sun.
+Voyager~1 is the farthest probe out of the solar system, now covering more than \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}}.
+Ulysses was the singular probe orbiting the Sun outside the ecliptic and retrieving solar wind measurements from the poles of the Sun.
 So far, Helios~2 made the nearest in situ solar wind measurements with \SI{0.29}{\au}, followed closely by Helios~1 with \SI{0.31}{\au}.
@@
 The main part of the PSP mission's goals is to gain insight into the coronal heating and solar wind acceleration processes.
-As these processes occur in the near-Sun region of the corona, PSP will have its closest perihelion at 9.86~solar radii (0.0459~au) \citep{Fox2015}.
+As these processes occur in the near-Sun region of the corona, PSP will have its closest perihelion at 9.86~solar radii (\SI{0.0459}{\au}) \citep{Fox2015}.
 It will be the first spacecraft flying and measuring in situ solar wind this close to the Sun.
@@
 They examine average values, additionally distinguishing between slow and fast wind.
-In this paper we instead look at the variations of the whole frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\
+In this paper we instead look at the variations of the bulk frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\
 
@@
 
-Our approach is to get an analytical representation of the frequency distributions' shapes, their solar activity dependence and their solar distance scaling.
+Our approach is to get an analytical representation of the frequency distributions' shapes (Sect.~\ref{sec:frequency_distribution}), their solar activity dependence (Sect.~\ref{sec:solar_activity_variations}) and their solar distance scaling (Sect.~\ref{sec:solar_distance_dependency}).
 We get the parameters' frequency distributions and solar activity dependence from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles and their distance dependency from solar wind measurements of more than half a solar cycle, covering more than two third of the distance to the Sun (\SIrange{0.29}{0.98}{\au}).%0.68~au\\
 
-From the combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions we build a general model representing the solar activity and distance behavior of all four solar wind parameter frequencies.
+From the combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions we build a general model representing the solar activity and distance behavior of all four solar wind parameter frequencies (Sect.~\ref{sec:general_solar_wind_model}).
 
-This general model is then fed with a SSN prediction and extrapolated to PSP's planned orbital positions.\\
+This general model is then fed with a SSN prediction and extrapolated to PSP's planned orbital positions (Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}).\\
 
@@
 Parker Solar Probe is planned to launch in mid 2018.
-With its first Venus flyby it will swing into Venus' orbital plane(?) (\SI{3.86}{\degree} to Sun's equator), which allows for additional seven flybys to finally reduce its perihelion distance to a minimum of less than \SI{10}{R_s} \citep{Fox2015} (Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).\\
+With its first Venus flyby it will swing into Venus' orbital plane (\SI{3.86}{\degree} to Sun's equator/\SI{3.39}{\degree} to ecliptic), which allows for additional seven flybys to finally reduce its perihelion distance to a minimum of less than \SI{10}{R_s} \citep{Fox2015} (Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).\\
 

### 2017-06-24 paperMVVB/sections/content.tex
minor change

@@
 
-%difference to other models
-There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}).
-They examine average values, additionally distinguishing between slow and fast wind.
-In this paper we instead look at the variations of the bulk frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\
+This paper examines the variations of the bulk solar wind frequency distributions, considers solar activity and extrapolates these distributions to the near-Sun region.\\
 

### 2017-06-24 paperMVVB/sections/abstract.tex
VB edit #1 integrated

--- 2017-06-01 paperMVVB/sections/abstract.tex
@@
 
-\date{First draft 9 August 2016; received date; accepted date }
+\date{First draft 9 August 2016; first changes 21 June 2017; received date; accepted date }
 
 \abstract
-{In view of the planned near-Sun spacecraft mission Parker~Solar~Probe (PSP) (formerly Solar~Probe~Plus) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
-This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
-{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data.
-The space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
-The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}.
-This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters PSP will encounter on its mission.}	%aims
-{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
+{\color{Green4} In view of the planned near-Sun spacecraft mission Parker~Solar~Probe (PSP) (formerly Solar~Probe~Plus) the solar wind environment for its prime mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
+The PSP mission will be humanity's first in situ exploration of the solar corona.
+Visiting this yet uncharted region is of special interest, because it will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
+The solar wind extrapolation of this study is performed within the project CGAUSS (Coronagraphic German And US Solar~Probe Survey) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
+{\color{Green4} We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data.
+The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
+The OMNI database at NASA's Space Physics Data Facility (SPDF) consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au}.
+The solar wind model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters PSP will encounter during its mission.}	%aims
+{\color{Green4} The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
 Their individual frequency distributions are represented with lognormal functions.
 In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part.
-The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions.
-We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
-Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies.
-Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
-{The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment at PSP's planned orbital positions during its mission time.
-The estimated solar wind values at PSP's nearest perihelion vary up to +-XX~\%, arising only from differing amplitude assumptions for the next solar cycle.}	%results
+The model accounts for solar activity and for solar distance dependency \hl{by shifting of these lognormal distributions.} We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
+Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted with respect to solar distance to obtain exponential dependencies.
+Finally, by combining the found solar cycle and solar distance relations, we obtain a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic region.}	%methods
+{\textcolor{Green4}{ The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its prime mission duration 2018--2025.} \hl{The estimated solar wind values at PSP's nearest perihelion are: ...
+Their value vary up to} \SI{+-0.0000}{\percent}, \hl{arising only from differing amplitude assumptions for the next solar cycle.}}	%results
 {}	%conclusions

### 2017-06-24 paperMVVB/sections/content.tex
VB edit #1 integrated

@@
 
-%solar wind models; theoretical and empirical
-With his theoretical solar wind model \citet{Parker1958} laid the foundations...\\
+\color{Green4}
+%solar wind beginnings
+From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun.
+With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1962 \citep{Neugebauer1966}.
 
 %in situ spacecraft
-Several space missions flew away from Earth's orbit to measure in situ solar wind at different heliocentric distances (e.g.
-the probes Helios, Voyager, Ulysses...).
-Voyager~1 is the farthest probe out of the solar system, now covering more than \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}}.
-Ulysses was the singular probe orbiting the Sun outside the ecliptic and retrieving solar wind measurements from the poles of the Sun.
-So far, Helios~2 made the nearest in situ solar wind measurements with \SI{0.29}{\au}, followed closely by Helios~1 with \SI{0.31}{\au}.
-The new mission Parker~Solar~Probe (PSP), whose planned launch date is in mid 2018, aims to reach further down into the Sun's atmosphere.
+The idea of a space mission flying through the solar corona \hl{dates back to the founding year of NASA in 1958 (ref.).} Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in the case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}}, having even left the heliospause into interstellar space \citep{Gurnett2013}.
+Ulysses was the unique probe that orbited the Sun out of the ecliptic plane and thus could retrieve solar wind measurements from the poles of the Sun \hl{(ref.)}.
+So far, Helios~2 made the nearest in situ solar wind measurements ever at a distance as close to the Sun as \SI{0.29}{\au}, closely followed by Helios~1 with \SI{0.31}{\au}.
 
 %Solar Probe Plus mission
-The main part of the PSP mission's goals is to gain insight into the coronal heating and solar wind acceleration processes.
-As these processes occur in the near-Sun region of the corona, PSP will have its closest perihelion at 9.86~solar radii (\SI{0.0459}{\au}) \citep{Fox2015}.
-It will be the first spacecraft flying and measuring in situ solar wind this close to the Sun.
-Its planned observations range from the perihelion up to \SI{0.25}{\au}, leaving the outer part for data transfer, as \citet{Fox2015} state in their description of PSP's mission design.\\
+The Parker~Solar~Probe, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia with 9.86~solar radii, i.e.
+\SI{0.0459}{\au}.
+This distance will be achieved through seven Venus gravity assists with orbital periods of 88--168~days.
+In its prime mission time 2018--2025 PSP provides 24 orbits with perihela inside \SI{0.25}{\au} \citep{Fox2015}.
+
+\color{Red2}
+%PSP objectives and instruments
+The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” (ref.
+NASA STDT report, \citet{Fox2015}).
+To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields, SWEAP for the measurements of flux of electrons, protons and alphas, IS\sun{}IS for the measurement of solar energetic particles and WISPR for the measurement of coronal structures (ref.
+to each instrument paper).\\
 
 %WISPR
-[white light imager WISPR... \citep{Vourlidas2016}]\\
+The Wide field Imager for Solar Probe (WISPR) will contribute to the science goals by deriving the 3D structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
+It will provide density power spectra over a wide range of structures, e.g., streamers and pseudostreamers, equatorial coronal holes, for determining the roles of turbulence, waves, and pressure-balanced structures in the solar wind.
+It will also measure the physical properties, such as speed and density jumps, of SEP-producing shocks and their CME drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.\\
 
-This paper examines the variations of the bulk solar wind frequency distributions, considers solar activity and extrapolates these distributions to the near-Sun region.\\
+%CGAUSS
+CGAUSS (Coronagraphic German And US Solar Probe Survey) is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).
+One of the objectives of the CGAUSS project is to extrapolate the solar wind environment down to the closest perihelion of \SI{9.86}{R_s} distance to the Sun in order to optimize the WISPR and PSP science operations.
+To achieve that goal this study uses in situ solar wind data from the US-German Helios~1 and 2 space probes and \SI{1}{\au} data from various satellites compiled in the NASA/GSFC OMNI solar wind database.\\
 
+\color{Green4}
+This paper examines the variations of the bulk solar wind frequency distributions, considers solar activity and extrapolates these distributions to the near-Sun region.
+
+\color{black}
 %definition of sw environment
@@
 
+\color{Green4}
 %solar wind parameters
-The goal of this paper is to estimate the solar wind environment PSP will probe during its orbits.
-We regard the solar wind primarily as a proton plasma, because protons make up most of it.
-The average helium abundance is only about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
-Neglecting heavier ions, the electron and mass density can be derived accordingly.
+As a baseline we treat the solar wind primarily as a proton plasma, because the average helium abundance is only about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
+Neglecting heavier ions, the electron and mass density can then \hl{be derived accordingly.}
 
-Generally, the characteristic behavior of a plasma is determined by its \textit{density}, \textit{temperature} and \textit{magnetic field strength}.
-Furthermore, the bulk \textit{velocity} is the parameter which makes the plasma a 'wind'.
-For our study we define the solar wind environment as the four major solar wind parameters.
+The characteristic behavior of a magnetized plasma is determined by its \textit{density}, \textit{temperature} and \textit{magnetic field strength}.
+Furthermore, the bulk flow \textit{velocity} is the parameter which makes the plasma a 'wind'.
+For this study we define the solar wind environment through these four major solar wind parameters.
 Quantities like flux densities, mass flux and plasma beta can directly be derived from those four parameters.
 
-In addition, the velocity is the defining parameter of the two types of solar wind.
-Solar wind mostly consists of and switches between slow and fast wind, whose different compositions and characteristics also indicate different sources and generation processes \citep{McGregor2011a} (better cites?).
-Their ratio highly depends on solar activity (cite?) and their interactions lead to phenomena such as interaction regions.
+Generally, two types of solar wind are observed in the heliosphere, slow and fast streams \citep{Neugebauer1966}\hl{, Schwenn (19xx), McComas et al.
+(19xx)).} Fast streams are found to originate from coronal holes as Ulysses polar measurements revealed \hl{(ref.).
+The origin of slow wind is a subject of controversial discussions because several sources are closed magnetic structures in the solar corona, such as Schwenn (19xx) has even reported the possibility of four types of solar wind depending on the phase of the solar cycle/activity.}
 
-Additionally there also are coronal mass ejections (CMEs) embedded, whose occurrence rate follows solar activity too.
-Their share varies between almost zero in cycle minimum up to a half in maximum \citep{Richardson2012}.
-This study averages over these internal solar wind structures.
+The solar wind velocity is the defining parameter of the two types of solar wind.
+Slow solar wind has typical speeds \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[see][p.~144]{Schwenn1990}.
+Their different compositions and characteristics indicate different sources and generation processes \citep{McGregor2011a}.
 
+Their occurrence frequency varies strongly with solar activity and their interactions lead to phenomena such as \color{red}
+stream interaction regions (SIRs) and for quasi-stationary coronal source regions to co-rotating interaction regions (CIRs, ref. Buch über CIRs).
+
+\color{Green4}
+Embedded in the slow and fast solar wind streams are coronal mass ejections (CMEs) \hl{(ref.)}.
+Their frequency in near \SI{1}{\au} measurements varies between almost zero during solar cycle minima \hl{up to a daily rate of about 0.5 during times of solar maximum} \citep{Richardson2012}.
+
+%frequency distribution data
+Since one cannot know which specific solar wind type or structure PSP will encounter at a given point in time during its mission, we extrapolate the parameters’ probability distributions from existing solar wind measurements.
+
+\color{black}
 %frequency distribution data

### 2017-07-16 paperMVVB/sections/abstract.tex
replaced 'exponential' with 'power law'

@@
 The model accounts for solar activity and for solar distance dependency \hl{by shifting of these lognormal distributions.} We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
-Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted with respect to solar distance to obtain exponential dependencies.
+Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
 Finally, by combining the found solar cycle and solar distance relations, we obtain a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic region.}	%methods

### 2017-07-16 paperMVVB/sections/content.tex
replaced 'exponential' with 'power law'

@@
 Ulysses was the unique probe that orbited the Sun out of the ecliptic plane and thus could retrieve solar wind measurements from the poles of the Sun \hl{(ref.)}.
-So far, Helios~2 made the nearest in situ solar wind measurements ever at a distance as close to the Sun as \SI{0.29}{\au}, closely followed by Helios~1 with \SI{0.31}{\au}.
+So far, Helios~2 made the nearest in situ solar wind measurements ever at a distance as close to the Sun as \SI{0.29}{\au}, closely followed by Helios~1 with \SI{0.31}{\au} \citep{Rosenbauer1977}.
 
@@
 \color{black}
-%frequency distribution data
-One cannot know which specific solar wind type or structure PSP will encounter at a given point in time, so we extrapolate the parameters' probability distributions from existing solar wind measurements.
-
 Our approach is to get an analytical representation of the frequency distributions' shapes (Sect.~\ref{sec:frequency_distribution}), their solar activity dependence (Sect.~\ref{sec:solar_activity_variations}) and their solar distance scaling (Sect.~\ref{sec:solar_distance_dependency}).
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/histogram_fits_V_a_zoom_dbl_paper_pdfplot.pdf}}
-	\caption{Plot of the velocity's frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
+	\caption{The velocity's frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
 The fit's median and mean values and its two fit parts are indicated as well.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
-	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top).
+	\caption{The solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top).
 Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
@@
 \label{sec:solar_distance_dependency}
-In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and also evaluate the fits' extrapolation behavior in direction to the Sun.
+In this section we use Helios data to obtain power law fit functions for the heliocentric distance dependency and also evaluate the fits' extrapolation behavior in direction to the Sun.
 To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data.
-This results in models comprising of exponentially with distance shifted lognormal functions.
+This results in models comprising of with distance shifted lognormal functions.
 
@@
 
-\subsection{Exponential fitting}
-\label{sec:exponential_fitting}
-%why exponential function?
-An exponential distance behavior is expected from all four parameters (cites?). Therefore we use the exponential function
+\subsection{Power law fitting}
+\label{sec:power_law_fitting}
+%why power law function?
+A power law scaling distance behavior is expected from all four parameters (cites?). Therefore we use the power function
 \begin{align}
-	x(r) = d\,r^e	\label{eq:exponential_function}
+	x(r) = d\,r^e	\label{eq:power_function}
 \end{align}
@@
 To circumvent these limitations for all four solar wind parameters we set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical, avoiding crossing of median and mean.
-Then the distribution's width scales exponentially with solar distance.
+Then the distribution's width has a power law scaling with solar distance.
 Applying this approximation, we have to accept larger model errors, especially for the magnetic field strength.
@@
 
-\subsection{Exponential lognormal fitting}
+\subsection{Power law lognormal fitting}
 To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:omni_frequency_data}).
@@
 As mentioned before, we set the exponents of median and average to be identical.
-Implementing the exponential distance dependency~(\ref{eq:exponential_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
+Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
 Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
@@
 \begin{table*}
-	\caption{Fit coefficients from the single lognormal exponential function, respectively double lognormal for the velocity (combined Helios data).
+	\caption{Fit coefficients from the single lognormal power function, respectively double lognormal for the velocity (combined Helios data).
 The errors in brackets are the estimated standard deviations of each fit parameter.}
@@
 	\caption{Solar wind parameter's frequency distributions over solar distance.
-Plotted are the binned Helios data and the exponential lognormal fit model (double lognormal for the velocity) with their median values (white).}
+Plotted are the binned Helios data and the power law lognormal fit model (double lognormal for the velocity) with their median values (white).}
 	\label{fig:mixed_fit_fixed_4_paper_f_plot}
@@
 %are the exponents time-independent?
-Under the assumption that the exponential fall-off laws do not change with time/solar activity (as shown above...), they can be used in general.
+Under the assumption that the fall-off laws do not change with time/solar activity (as shown above...), they can be used in general.
 
-We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the exponential distance dependence (previous section)
+We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the power law distance dependence (previous section)
 \begin{align}
@@
 The magnetic field magnitude from our extrapolation is flatter than the analytical magnetic field model from \citet{Banaszkiewicz1998}, who constructed a dipole plus quadrupole plus current sheet (DQCS) model.
-We attribute this effect to the from a lognormal shape deviating distribution (see Sect.~\ref{sec:exponential_fitting}).\\
+We attribute this effect to the from a lognormal shape deviating distribution (see Sect.~\ref{sec:power_law_fitting}).\\
 

### 2017-08-10 paperMVVB/sections/abstract.tex
implementing VBedits

@@
-\title{Solar wind prediction for the Parker Solar Probe orbit}
+\title{Solar wind predictions for the Parker Solar Probe orbit}
 \subtitle{Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations}
@@
 \abstract
-{\color{Green4} In view of the planned near-Sun spacecraft mission Parker~Solar~Probe (PSP) (formerly Solar~Probe~Plus) the solar wind environment for its prime mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
+{In view of the planned near-Sun spacecraft mission Parker~Solar~Probe (PSP) (formerly Solar~Probe~Plus) the solar wind environment for its prime mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
 The PSP mission will be humanity's first in situ exploration of the solar corona.
@@
 The solar wind extrapolation of this study is performed within the project CGAUSS (Coronagraphic German And US Solar~Probe Survey) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
-{\color{Green4} We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data.
+{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data.
 The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
@@
 The solar wind model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters PSP will encounter during its mission.}	%aims
-{\color{Green4} The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
+{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
 Their individual frequency distributions are represented with lognormal functions.
 In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part.
-The model accounts for solar activity and for solar distance dependency \hl{by shifting of these lognormal distributions.} We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
+The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions.
+We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
 Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
 Finally, by combining the found solar cycle and solar distance relations, we obtain a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic region.}	%methods
-{\textcolor{Green4}{ The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its prime mission duration 2018--2025.} \hl{The estimated solar wind values at PSP's nearest perihelion are: ...
-Their value vary up to} \SI{+-0.0000}{\percent}, \hl{arising only from differing amplitude assumptions for the next solar cycle.}}	%results
-{}	%conclusions
+{The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its prime mission duration 2018--2025.
+The estimated solar wind median values during PSP's first perihelion \hl{are} \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
+The modeled values for PSP’s closest perihelia \hl{are} \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}, where these velocity and temperature values are clearly overestimated in comparison with existing observations.}	%results
+{This empirical model shows that solar wind acceleration and heating processes \hl{below 20}~solar radii limit a simple back-extrapolation from existing in situ measurements.}	%conclusions
 

### 2017-08-10 paperMVVB/sections/content.tex
implementing VBedits

@@
 
-\color{Green4}
 %solar wind beginnings
 From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun.
-With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1962 \citep{Neugebauer1966}.
-
+With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1962 \citep{Neugebauer1966} \hl{+ ref.
+to Russian measurements}.
 %in situ spacecraft
-The idea of a space mission flying through the solar corona \hl{dates back to the founding year of NASA in 1958 (ref.).} Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in the case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}}, having even left the heliospause into interstellar space \citep{Gurnett2013}.
-Ulysses was the unique probe that orbited the Sun out of the ecliptic plane and thus could retrieve solar wind measurements from the poles of the Sun \hl{(ref.)}.
-So far, Helios~2 made the nearest in situ solar wind measurements ever at a distance as close to the Sun as \SI{0.29}{\au}, closely followed by Helios~1 with \SI{0.31}{\au} \citep{Rosenbauer1977}.
+The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in the case of Voyager~1 as far away as \SI{138}{\au} in July 2017\footnote{\url{https://voyager.jpl.nasa.gov/}}, having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with Wind \hl{(ref.)}, ACE \hl{(ref.)} and DSCOVR \hl{(ref.)} still orbiting around the L1 point \SI{1.5}{million \km} ahead of Earth in the sunward direction.
+Additional measurements at other distances were provided by planetary missions to Venus and Mercury, such as PVO \hl{(ref.)} or MESSENGER \hl{(ref.)}.
+Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind at polar latitudes \citep{McComas1998}.
+The nearest in situ solar wind measurements to date were obtained by the Helios mission.
+The in 1974 launched Helios~1 spacecraft reached distances of \SI{0.31}{\au}, Helios~2 launched two years later and approached the Sun up to \SI{0.29}{\au} \citep{Rosenbauer1977}.
 
 %Solar Probe Plus mission
-The Parker~Solar~Probe, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia with 9.86~solar radii, i.e.
-\SI{0.0459}{\au}.
+The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rsun), that is, \SI{0.0459}{\au} \citep{Fox2015}.
 This distance will be achieved through seven Venus gravity assists with orbital periods of 88--168~days.
-In its prime mission time 2018--2025 PSP provides 24 orbits with perihela inside \SI{0.25}{\au} \citep{Fox2015}.
+In its prime mission time 2018--2025 PSP provides 24~orbits with perihelia inside \SI{0.25}{\au} \citep{Fox2015}.
+Even its first perihelion, 93~days after launch in 2018, will take PSP to an unprecedented distance of \SI{0.16}{\au} (\SI{35.7}{\Rs}).
+{\color{Red2} In comparison, the ESA Solar Orbiter mission with a planned launch in 2019 will have a closest perihelion of \SI{0.289}{\au} \hl{(ref.)}.}
 
-\color{Red2}
 %PSP objectives and instruments
-The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” (ref.
-NASA STDT report, \citet{Fox2015}).
-To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields, SWEAP for the measurements of flux of electrons, protons and alphas, IS\sun{}IS for the measurement of solar energetic particles and WISPR for the measurement of coronal structures (ref.
-to each instrument paper).\\
+The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” as stated in \citet{Fox2015}.
+To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurements of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
 
-%WISPR
-The Wide field Imager for Solar Probe (WISPR) will contribute to the science goals by deriving the 3D structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
-It will provide density power spectra over a wide range of structures, e.g., streamers and pseudostreamers, equatorial coronal holes, for determining the roles of turbulence, waves, and pressure-balanced structures in the solar wind.
-It will also measure the physical properties, such as speed and density jumps, of SEP-producing shocks and their CME drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.\\
+%CGAUSS and WISPR
+The study presented in this paper is undertaken in the Coronagraphic German And US Solar Probe Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).
+WISPR will contribute to the PSP science goals by deriving the 3D structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
+It will provide density power spectra over a wide range of structures (e.g., streamers, pseudostreamers and equatorial coronal holes) for determining the roles of turbulence, waves and pressure-balanced structures in the solar wind.
+It will also measure the physical properties, such as speed and density jumps of SEP-producing shocks and their CME drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.
 
-%CGAUSS
-CGAUSS (Coronagraphic German And US Solar Probe Survey) is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).
-One of the objectives of the CGAUSS project is to extrapolate the solar wind environment down to the closest perihelion of \SI{9.86}{R_s} distance to the Sun in order to optimize the WISPR and PSP science operations.
-To achieve that goal this study uses in situ solar wind data from the US-German Helios~1 and 2 space probes and \SI{1}{\au} data from various satellites compiled in the NASA/GSFC OMNI solar wind database.\\
+In order to help optimize the WISPR and PSP preplanning of the science operations knowledge of the expected solar wind environment is needed.
+For this purpose the solar wind environment is extrapolated down to the closest perihelion of \SI{9.86}{R_s} distance to the Sun using in situ solar wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the NASA/GSFC OMNI solar wind database.\\
 
-\color{Green4}
-This paper examines the variations of the bulk solar wind frequency distributions, considers solar activity and extrapolates these distributions to the near-Sun region.
+%definition of sw environment
+%section{Solar wind}
 
-\color{black}
-%definition of sw environment
-\section{Solar wind environment}
+Generally, two types of solar wind are observed in the heliosphere, slow and fast streams \citep{Neugebauer1966}\hl{, Schwenn (19xx)}.
+Slow solar wind has typical speeds \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[p.~144]{Schwenn1990}.
+Their different compositions and characteristics indicate different sources and generation processes \citep{McGregor2011a}.
+Fast streams are found to originate from coronal holes as confirmed by Ulysses out-of-ecliptic measurements \citep{McComas1998}.
+The source of slow wind and its eventually different types (\hl{Schwenn19xx}), is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, {\color{red} such as ...intermittent reconnection at the top of streamers and pseudostreamers, coronal hole boundaries, ...
+(\hl{ref.}).} The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
 
-\color{Green4}
+Embedded in the slow and fast solar wind streams are transient flows of coronal mass ejections (CMEs), the faster ones driving shock waves ahead \hl{(ref.)}.
+Their rate follows the activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
+
+It is not known which specific solar wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar wind parameters from existing solar wind measurements and take solar cycle dependencies into account.
+
 %solar wind parameters
-As a baseline we treat the solar wind primarily as a proton plasma, because the average helium abundance is only about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
-Neglecting heavier ions, the electron and mass density can then \hl{be derived accordingly.}
+As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \textit{density}, \textit{temperature} and \textit{magnetic field strength}.
+Furthermore, the bulk flow \textit{velocity} is the defining parameter of the two types of solar wind.
+Solar wind quantities, like flux densities, mass flux and plasma beta, can directly be derived from these four parameters.
 
-The characteristic behavior of a magnetized plasma is determined by its \textit{density}, \textit{temperature} and \textit{magnetic field strength}.
-Furthermore, the bulk flow \textit{velocity} is the parameter which makes the plasma a 'wind'.
-For this study we define the solar wind environment through these four major solar wind parameters.
-Quantities like flux densities, mass flux and plasma beta can directly be derived from those four parameters.
-
-Generally, two types of solar wind are observed in the heliosphere, slow and fast streams \citep{Neugebauer1966}\hl{, Schwenn (19xx), McComas et al.
-(19xx)).} Fast streams are found to originate from coronal holes as Ulysses polar measurements revealed \hl{(ref.).
-The origin of slow wind is a subject of controversial discussions because several sources are closed magnetic structures in the solar corona, such as Schwenn (19xx) has even reported the possibility of four types of solar wind depending on the phase of the solar cycle/activity.}
-
-The solar wind velocity is the defining parameter of the two types of solar wind.
-Slow solar wind has typical speeds \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[see][p.~144]{Schwenn1990}.
-Their different compositions and characteristics indicate different sources and generation processes \citep{McGregor2011a}.
-
-Their occurrence frequency varies strongly with solar activity and their interactions lead to phenomena such as \color{red}
-stream interaction regions (SIRs) and for quasi-stationary coronal source regions to co-rotating interaction regions (CIRs, ref. Buch über CIRs).
-
-\color{Green4}
-Embedded in the slow and fast solar wind streams are coronal mass ejections (CMEs) \hl{(ref.)}.
-Their frequency in near \SI{1}{\au} measurements varies between almost zero during solar cycle minima \hl{up to a daily rate of about 0.5 during times of solar maximum} \citep{Richardson2012}.
-
-%frequency distribution data
-Since one cannot know which specific solar wind type or structure PSP will encounter at a given point in time during its mission, we extrapolate the parameters’ probability distributions from existing solar wind measurements.
-
-\color{black}
-Our approach is to get an analytical representation of the frequency distributions' shapes (Sect.~\ref{sec:frequency_distribution}), their solar activity dependence (Sect.~\ref{sec:solar_activity_variations}) and their solar distance scaling (Sect.~\ref{sec:solar_distance_dependency}).
-We get the parameters' frequency distributions and solar activity dependence from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles and their distance dependency from solar wind measurements of more than half a solar cycle, covering more than two third of the distance to the Sun (\SIrange{0.29}{0.98}{\au}).%0.68~au\\
-
-From the combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions we build a general model representing the solar activity and distance behavior of all four solar wind parameter frequencies (Sect.~\ref{sec:general_solar_wind_model}).
-
-This general model is then fed with a SSN prediction and extrapolated to PSP's planned orbital positions (Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}).\\
+Our approach is to obtain analytical representations of the shapes of the solar wind parameter’s frequency distributions in Sect.~\ref{sec:frequency_distribution}, of their solar activity dependence in Sect.~\ref{sec:solar_activity_variations} and of their solar distance scaling in Sect.~\ref{sec:solar_distance_dependency}.
+The solar wind parameters’ frequency distributions and solar activity dependence is derived from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles.
+Their distance dependency is derived from Helios solar wind measurements covering more than two third of the distance to the Sun and more than half a solar cycle.
+From combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions a general solar wind model is build in Sect.~\ref{sec:general_solar_wind_model}, representing the solar activity and distance behavior.
+Finally, this empirical model is fed with a SSN prediction and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}.
 
 %lognormal fitting
-\section{Frequency distributions}
+\section{Frequency distributions of the solar wind parameters}
 \label{sec:frequency_distribution}
 
-This section looks at the solar wind parameters' frequency distributions which we extract from the in situ OMNI data set.
-We determine adequate fit function types and evaluate how suitable they are to represent the frequencies' shapes.
-
-\subsection{OMNI frequency data}
-\label{sec:omni_frequency_data}
-The solar wind parameters are highly variable, due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on solar activity.
-Hence, for deriving general frequency distributions of the solar wind parameters, averaging over long-term solar wind variations is needed.
-This requires a distance-independent data set covering multiple solar cycles.
-The abundance of near-Earth hourly OMNI data is well suited for this task, because it spans almost five solar cycles.
+The solar wind parameters are highly variable, due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on the phase of the solar activity cycle.
+Hence, for deriving characteristic frequency distributions for the solar wind parameters, measurements over long-term time spans are needed.
+The abundance of the near-Earth hourly OMNI data set is ideally suited for this purpose, because it spans to date almost five solar cycles.
 
 %about OMNI data
-This OMNI~2 data set \citep{King2005} combines solar wind plasma and magnetic field data and for this study not important energetic proton fluxes, geomagnetic and solar indices.
-Because it covers decades, the near-Earth solar wind data is composed of intercalibrated multi-spacecraft data which is time-shifted to the nose of the Earth's bow shock.
-
-%data source
+The OMNI~2 data set \citep{King2005} combines solar wind plasma and magnetic field data collected by various satellites since 1963.
+This intercalibrated multi-spacecraft data is time-shifted to the nose of the Earth’s bow shock.
 The data is obtained from the OMNIWeb interface\footnote{\url{http://omniweb.gsfc.nasa.gov/}} at NASA's Space Physics Data Facility (SPDF), Goddard Space Flight Center (GSFC).
@@
 %data time range
-The hourly data of the whole time range up to \mbox{2016-12-31} is the basis for the frequency fits.
-The data starts in \mbox{1963-11-27}, but the temperature data not before \mbox{1965-07-26}.
-The data coverage of the parameters is between \SIrange{67}{74}{\percent}, which adds up to about 36--40~years in total.
-This plethora of data is well suited for our task.
+In this study the whole hourly data until 31 December 2016 is used, starting from 27 November 1963 (for the temperature from 26 July 1965).
+The data coverage of the parameters is in the range \SIrange{67}{74}{\percent},  corresponding to a total duration of 36--40~years.
 %OMNI 1963-01-01 data
@@
 % T: 66.73 \%		36.03 y\\
-
+%
 %hourly data
-We note that the use of higher time resolution instead, would not significantly change our results.
-The frequency distributions of the also available minutely OMNI data set are almost congruent with the hourly---they only differ slightly at their extreme ends.
+It should be noted that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016, did not show significant differences in our results.
 
 %data binning
-We specify bin sizes considering the individual maximal parameter ranges and the OMNI data precision.
-Especially for the density and temperature we choose their bin sizes such small that their distributions' peaks can be resolved (the peaks are at their lower end).
-We set the individual bin sizes to \SI{0.5}{nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
+The frequency distributions of the solar wind magnetic field strength, proton velocity, density and temperature are shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+According to the OMNI data precision and maximal parameter ranges we specify the bin sizes to \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
 
-Next, we look for a suitable fit function for the resulting histogram shape of the solar wind parameters' frequency distributions.
+The solar wind magnetic field strength is in the range \SIrange{0.4}{62}{nT}, the velocity in the range \SIrange{156}{1189}{\km\per\s}, the density in the range \SIrange{0}{117}{\per\cm\cubed}, and the temperature in the range \SIrange{3450}{6.63e6}{\K}, the mean values are at \SI{6.28}{\nT}, \SI{436}{\km\per\s}, \SI{6.8}{\per\cm\cubed} and \SI{1.05e5}{\K}.
+These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
 
-\subsection{Lognormal fitting}
-%choice of distribution function---why lognormal function?
-Obviously all possible values for the four parameters are positive.
-This hints to the supposition that they are lognormally distributed, as many positive natural quantities conform to lognormal distributions.
-Its probability density function is described by a lognormal function.
-%fitting method
-Therefore we use a lognormal function as the fit function in the process of the least squares regression fitting.
-%fit function
+Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 ICME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.\\
+
+%subsection{Lognormal fitting}
+%choice of distribution function
+The frequency distributions of the solar wind parameters magnetic field strength, proton density and temperature can
+well be approximated by lognormal distributions, whereas the proton velocity’s frequency has a differing shape, as shown in \citet{Veselovsky2010}.
+We investigate how well all four solar wind parameters’ frequency distributions can be represented by lognormal functions, which we use in the process of a least squares regression fitting.
 The lognormal function
@@
 Changes in $\mu$ affect both the horizontal and vertical scaling of the function whereas $\sigma$ influences its shape.
-The distribution's median $x_\text{med}$ and mean $x_\text{avg}$ (average) positions are easier to interprete and can directly be calculated from $\mu$ and $\sigma$:
+The distribution's median $x_\text{med}$ and mean $x_\text{avg}$ (average) positions are straightforward to interprete and are directly calculated from $\mu$ and $\sigma$:
 \begin{align}
@@
 \end{align}
-The values of $x_\text{med}$ and $x_\text{avg}$ obtained from fitting the solar wind frequency distributions are listed in Table~\ref{tab:lognormal_fit_parameters}.
+The values of $x_\text{med}$ and $x_\text{avg}$ obtained from fitting the individual solar wind frequency distributions are listed in Table~\ref{tab:lognormal_fit_parameters}.
 \begin{table*}
@@
 
-From visual inspection, the resulting curves match well with the shape of the magnetic field strength, density and temperature distributions (Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).
-However, for the velocity the fit function seems insufficient in describing its more complex shape, especially at its peak position and the faster end of the distribution.
-Its sum of absolute residuals (SAR) between data and fit is almost three times larger than those from the other parameters (Table~\ref{tab:lognormal_fit_parameters}).
-They can be compared, because the area of probability density functions is unity.
+From visual inspection, the resulting curves describe the shape of the magnetic field strength, density and temperature distributions well as shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its maximum and in the higher velocity range.
+This also can be inferred from the sum of absolute residuals (SAR) between data and fit listed in Table~\ref{tab:lognormal_fit_parameters}, being almost three times larger than those from the other parameters.
 \begin{figure*}
@@
 %justification for compositional lognormal fit
-To reach a better fit result for the velocity we change the fit function.
-We do not want to abandon the well-founded application of the lognormal function.
-However, it is reasonable to assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
-Therefore a compositional approach promises better fit results, which is why we combine two lognormal functions (\ref{eq:single_lognormal_fit_function}), bearing the disadvantage of more fit variables:
+In order to find a better fit result for the velocity distribution we assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
+Therefore a compositional approach  is chosen by combining two lognormal functions (\ref{eq:single_lognormal_fit_function}), involving more fit variables:
 \begin{align}
@@
 
-The fitting of $W_\text{II}(x)$ to the velocity's frequency distribution gives the values of the now five fit parameters ($c$, $x_\text{med,1}$, $x_\text{avg,1}$, $x_\text{med,2}$ and $x_\text{avg,2}$), which are also listed in Table~\ref{tab:lognormal_fit_parameters} together with the median and mean of the composed distribution, which can be derived via solving
+The fitting of $W_\text{II}(x)$ to the velocity's frequency distribution yields the values of the now five fit parameters ($c$, $x_\text{med,1}$, $x_\text{avg,1}$, $x_\text{med,2}$ and $x_\text{avg,2}$) as listed in Table~\ref{tab:lognormal_fit_parameters} together with the median and mean values of the composed distribution, which can be derived via solving
 \begin{align}
-	\int W_\text{II}(x)\,\text{d}x = 0	&	&\text{and}	&	&\int x\,W_\text{II}(x)\,\text{d}x = 0
+	\int W_\text{II}(x)\,\text{d}x = 0	&	&\text{and}	&	&\int x\,W_\text{II}(x)\,\text{d}x = 0	\,.
 \end{align}
-respectively.\\
+\hl{XXXXXXXXXXXXXXXXXXXXX}\\
 As anticipated, this more complex fit function is more accurate in describing the velocity's frequency distribution (see Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).
@@
 \subsection{Power law lognormal fitting}
-To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:omni_frequency_data}).
+To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:frequency_distribution}).
 % Helios histogram bin sizes for mean of frequency distribution (at specific solar distance):\\

### 2017-08-11 paperMVVB/sections/content.tex
mvvb edits worked in..

@@
 The in 1974 launched Helios~1 spacecraft reached distances of \SI{0.31}{\au}, Helios~2 launched two years later and approached the Sun up to \SI{0.29}{\au} \citep{Rosenbauer1977}.
-
 %Solar Probe Plus mission
-The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rsun), that is, \SI{0.0459}{\au} \citep{Fox2015}.
+The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rs), that is, \SI{0.0459}{\au} \citep{Fox2015}.
 This distance will be achieved through seven Venus gravity assists with orbital periods of 88--168~days.
@@
 \begin{table*}
-	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au} (OMNI hourly data).
-For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit.
-The mean absolute errors and sums of absolute residuals are shown as well.
-The values in brackets are the estimated standard deviation of each fit parameter.}
+	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions from near \SI{1}{\au} OMNI hourly data.
+For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
+The mean absolute errors and sums of absolute residuals are also listed.
+The values in brackets are the estimated standard deviations of each fit parameter.}
 	\label{tab:lognormal_fit_parameters}
@@
 	\includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
-	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits.
-The histograms have bins of 0.5~nT, 10~km/s, 1~cm$^{-3}$ and 10\,000~K and are based on the hourly OMNI data set.
+	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits derived from the hourly OMNI data set.
+The histograms have bins of \SI{0.5}{\nT}, \SI{10}{\km\per\s}, \SI{1}{\per\cm\cubed} and \SI{10000}{\K}.
 The fit's median and mean values are indicated as well.
-The insets only have zoomed-in frequency axes, their x-axes stay the same.}
+The insets show zoomed-in frequency axes.}
 	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
@@
 \end{align}
-\hl{XXXXXXXXXXXXXXXXXXXXX}\\
-As anticipated, this more complex fit function is more accurate in describing the velocity's frequency distribution (see Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).
+This more complex fit function is more accurately in describing the velocity's frequency distribution as shown in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 \begin{figure}
@@
 \end{figure}
-For this reason we keep using the double lognormal ansatz for the velocity frequency fits in the following sections.\\
-In this static model the slow and fast part contribute almost equally ($c \approx 0.5$), which of course is only valid for this kind of long-term average.
-At different times in a solar cycle their contributions vary strongly.
+Thus in the following sections we keep the double lognormal ansatz for all velocity frequency fits.
+
+The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
 
 %transition
-For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well.
-This is different for the extreme values (which may also stem from CMEs).
-The simple lognormal fit models of the magnetic field strength, the velocity and the density underestimate their frequency at the high value tails, whereas the temperature's tail is overestimated (see insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).
-The velocity's compositional lognormal fit only slightly overestimates its tail (inset in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}).
+For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, but differ for the extreme values, mainly caused by CME events.
 
-Short-term variations in the solar wind cannot be predicted, but their occurrence rate can.
-It depends on solar activity, which changes cyclically and thus can be forecasted to a certain degree---at least within a solar cycle.
+The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is overestimated as seen by the insets in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 
-\section{Solar activity variations}
+\section{Solar activity dependence of the solar wind frequency distributions}
 \label{sec:solar_activity_variations}
-This section aims to relate changes in the four solar wind parameters to general solar activity.
-For this we examine their correlations to the yearly sunspot number and determine the lag times with the highest coefficients.
-Next, we fit lognormal functions to the frequency distributions like before, but implement linear relations to the yearly SSN to shift the distributions.
-Only for the velocity the approach is different in that its two components are kept fixed and instead their balance is modified with changing SSN.
 
-\subsection{SSN data}
-Solar activity is commonly measured via the sunspot number.
-We want to correlate OMNI in situ measurements with the SSN, yet OMNI data are from Earth orbit, causing variations in solar latitude and distance.
-To dodge these seasonal variations we use yearly OMNI and SSN data.
+In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity.
+Therefore we examine their correlation with the sunspot number, being a commonly used long-term solar activity index and determine the time lags with the highest correlation coefficients.
 
-The international sunspot number (\citeyear{sidc}) is retrieved from the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
+%\subsection{SSN data}
+The international sunspot number (\citeyear{sidc}) is provided by the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
 
-%seasonal influence contained within yearly frequency distributions\\
+%\subsection{SSN correlation}
+For the correlations we fit lognormal functions to the frequency distributions as in Sect.~\ref{sec:frequency_distribution}, but implement linear relations to the yearly SSN, allowing shifting of the distribution functions with SSN.
+For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN.
 
-\subsection{SSN correlation}
-Our current interest lies in the correlation of the SSN to the solar wind median values, because the median defines the position of a lognormal function.
-The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.
-
-%solar activity = SSN $\neq$ solar cycle\\
-The solar wind velocity and its close friends density and temperature are known to depend on the state of the solar cycle \citep{Schwenn1983}, which is why they follow the SSN indirectly (with time lag).
-%density modulation with SSN \citep{Schwenn1983} p.~499\\
-Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}).
+Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} shows yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number.
+The reason for correlating the SSN to the solar wind median values is, because the position of a lognormal function is defined by its median.
+The data are averaged to yearly values to avoid seasonal effects during the Earth’s orbit around the Sun caused by its variations in solar latitude and distance.
+The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
-	\caption{The solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top).
+	\caption{The solar wind parameter yearly medians derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
 Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
@@
 
-The highest correlation coefficient for the magnetic field strength is 0.728, which is without lag time and the highest of all solar wind parameters.
-This is anticipated because the SSN is directly proportional to the magnetic flux \citep{Smith2003}.\\
-Velocity and temperature have a lag time of 3~years with their maximal correlation coefficients (0.453 and 0.540).
-The density has a lag time of 6~years (0.468), which is in agreement with the by \citet{Bougeret1984} documented density anticorrelation with SSN.	%p.~406\\
+The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}, \hl{ref. zu Korrelationen}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
+For instance the fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by \citet[\hl{Figure~XX, p.~XX}]{Bothmer2007}.
+Therefore the solar wind velocity, density and temperature maxima exhibit time-lags to the SSN maxima.
 
+The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength which has no time lag.
+This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
+
+Velocity and temperature show a lag time of 3~years with peak correlation coefficients of 0.453 and 0.540.
+The density with a correlation coefficient of 0.468 has a lag time of 6~years, which is in agreement with the by \citet{Bougeret1984} reported density anticorrelation to the SSN.	%p.~406\\
 % maximal correlation coefficients and their lag times:\\
@@
 As expected, the correlation coefficients' amplitudes of all parameters decline with increasing lag time and show a frequency of about 11~years.
+
+\hl{XXXXXXXXXXXXXX}\\
 

### 2017-08-13 paperMVVB/sections/acknowledgments.tex
mvvb edits implementation done

--- 2017-05-28 paperMVVB/sections/acknowledgments.tex
@@
 \begin{acknowledgements}
-	This work was done within the scope of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS), funded by the German Aerospace Center (DLR) (grant number...).\\
+	This work was done within the scope of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS), funded by the German Aerospace Center (DLR) under grant 50~OL~1601.\\
 	The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data.
@@
 	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
-	The SPP SPICE kernel was kindly provided by Angelos~Vourlidas.\\
+	The PSP SPICE kernel was kindly provided by Angelos~Vourlidas.\\
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.

### 2017-08-13 paperMVVB/sections/content.tex
mvvb edits implementation done

@@
 Their distance dependency is derived from Helios solar wind measurements covering more than two third of the distance to the Sun and more than half a solar cycle.
-From combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions a general solar wind model is build in Sect.~\ref{sec:general_solar_wind_model}, representing the solar activity and distance behavior.
-Finally, this empirical model is fed with a SSN prediction and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}.
+From combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions a general solar wind model is build in Sect.~\ref{sec:empirical_solar_wind_model}, representing the solar activity and distance behavior.
+Finally, this empirical model is fed with a SSN prediction and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
@@
 	\tablefoot{
-		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
+		\tablefoottext{a}{In units of \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
 		\tablefoottext{b}{Error estimates derived from the individual fit part errors.}
@@
 
-\hl{XXXXXXXXXXXXXX}\\
-
-\subsection{SSN fitting}
-\label{sec:ssn_fitting}
-To be able to shift the frequency distributions with SSN, we add a linear SSN dependency to the median
+%\subsection{SSN fitting}
+To enable to shifts of the solar wind frequency distributions with the SSN, we add a linear SSN dependency to the median
 \begin{align}
@@
 	\tablefoot{
-		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
+		\tablefoottext{a}{In units of \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
 	}
@@
 
-Naturally, the fit models match with the general data trends, though single year variations are not able to be replicated by the model (e.g.
-the high velocity and temperature values in 1974, 1994 and 2003) (see Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}).
+As can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}, naturally, the fit models match with the general data trends, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994 and 2003).
 \begin{figure*}
@@
 \end{figure*}
-The comparison with the yearly data median values over SSN shows that the from the model obtained medians have a quite similar slope (see Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}).
+The comparison with the yearly data median values over SSN shows that the medians obtained from the modeling have a quite similar slope as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
 \begin{figure}
@@
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
-The SSN dependent median (\ref{eq:median_with_ssn}) is from the lognormal model fit (dashed).
-For the velocity the median is derived from the SSN weighting of the slow and fast model parts, whose magnitudes are SSN independent (dotted).}
+The SSN dependent median (\ref{eq:median_with_ssn}) is derived from the lognormal model fit (dashed line).
+For the velocity the median is derived from the SSN weighting of the slow and fast model parts, whose magnitudes are SSN independent (dotted line).}
 	\label{fig:OMNI_yearly_BVNTvsSSN_a}
@@
 
-Again, the velocity gets a special treatment with the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-It is known that slow and fast solar wind stream occurrence rates follow the solar cycle, yet their magnitudes stay fairly stable (cite?).
-Thus we keep the two velocity components' positions constant and vary instead their balance with the SSN:
+Again, the solar wind velocity needs a special treatment because of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycleand basically maintain characteristic speeds (\hl{ref.}), we keep the two velocity components' positions constant and vary their balance with the SSN:
 \begin{align}
@@
 \end{align}
-The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).\\
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) yields a model in which three years after solar cycle minimum (SSN of zero) the contribution of slow solar wind to the overall solar wind distribution reaches a maximum value of about \SI{64}{\percent} and decreases with increasing SSN as shown in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_f_plot.pdf}}
-	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN.
-The yearly ratios (+) and their weighted linear fit (solid) are obtained from OMNI data with a threshold velocity of $v_\text{th} = \SI{400}{\km\per\s}$.
+	\caption{Ratio of slow to fast solar wind for a by 3~years lagged SSN.
+The yearly ratios (+) and their weighted linear fit (solid line) are obtained from OMNI data with a threshold velocity of $v_\text{th} = \SI{400}{\km\per\s}$.
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
@@
 \end{figure}
-% 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
-To compare the ratios of slow to fast wind between model and data, we simply apply the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (cite?).
-The linear fit to the yearly data ratio and the derived model ratio are quite similar (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
-Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the to some degree steeper balance parameter of this model.
-The model's balance may represent the actual ratios of the solar wind types in a more realistic way than a specific velocity threshold does, since the velocity ranges of both types overlap \citep{McGregor2011b}.
+% 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).
+
+To investigate the amount of slow and fast wind contributions depending on solar activity, we apply the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (\hl{cite?}).
+The linear fit to the yearly data ratio and the derived model ratio show a good agreement (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
+Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the to some degree steeper balance parameter of the double fit function used in this model.
+However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citep{McGregor2011b}.
 %(i.e. there exists slow wind with properties of fast wind and vice versa)
@@
 \label{sec:solar_distance_dependency}
-In this section we use Helios data to obtain power law fit functions for the heliocentric distance dependency and also evaluate the fits' extrapolation behavior in direction to the Sun.
-To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data.
-This results in models comprising of with distance shifted lognormal functions.
+In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit a power law dependency to the Helios data.
+We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step it will be extrapolated to the PSP orbit.
+We use the fitting methods of Sect.~\ref{sec:frequency_distribution} for the distance-binned combined data from both Helios probes.
+Helios’ highly elliptical orbits in the ecliptic covered a solar distance range of \SIrange{0.31}{0.98}{\au} in case of Helios~1 and \SIrange{0.29}{0.98}{\au} in case of Helios~2.
+Launched during solar cycle minimum, the data of both probes cover the rise to the maximum of cycle~21, covering $\sim$6.5~years at varying distances to the Sun.
 
-%Helios data
-\subsection{Helios distance data}
-\label{sec:helios_distance_data}
-The Helios probes were the only spacecraft measuring in situ solar wind over large solar distance ranges in the inner heliosphere.
-We use the combined data from both Helios~1 and Helios~2 probes.
-Helios~1's (Helios~2's) highly elliptical orbit in the ecliptic covered a solar distance range of \SIrange{0.31}{0.98}{\au} (\SIrange{0.29}{0.98}{\au}).
-Launched during solar cycle minimum, the data of both probes cover the rise to the maximum of cycle 21 ($\sim$6.5~years at varying distances).
-
-%hourly data
-Again we choose data with hourly resolution to allow its use along with the hourly OMNI data.
-As \citet{Schwenn1983} pointed out, the many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions, nevertheless their effect is insignificant in the treatment of the bulk data.	%\citet[p.~491]{Schwenn1983}
-
-Helios~1's (Helios~2's) merged hourly data set from the magnetometer and plasma instruments \citep{Rosenbauer1977} includes $\sim$12.5~orbits ($\sim$8~orbits) in the time range \mbox{1974-12-10} to \mbox{1981-06-14} (\mbox{1976-01-01} to \mbox{1980-03-04}).
+In the same way as the OMNI data we investigate hourly averages of the Helios data.
+The Helios~1 merged hourly data from the magnetometer and plasma instruments \citep{Rosenbauer1977} include $\sim$12.5~orbits for the time range 10~December 1974 until 14~June 1981, those for Helios~2 include $\sim$8~orbits for the time span 1~January 1976 until 4~March 1980.
+The data are retrieved from the Coordinated~Data~Analysis~Web (CDAWeb) interface at NASA's GSFC/SPDF\footnote{\url{http://spdf.gsfc.nasa.gov/}}.
 %Helios plasma instrument (E1); Helios magnetometer instrument (E2)
@@
 %data sources
-The Helios data was retrieved from the Coordinated~Data~Analysis~Web (CDAWeb) interface at NASA's GSFC/SPDF\footnote{\url{http://spdf.gsfc.nasa.gov/}}.
 
-The Helios~1 (Helios~2) magnetometer data coverage is about 43~\% (54~\%) and amounts to 2.8~years (2.3~years) in total.
-The plasma data coverage is 76~\% (92~\%) and amounts to 5.0~years (3.9~years) in total.
+The Helios~1 magnetometer data coverage for this data set is about \SI{43}{\%} (i.e., 2.8~years), that of Helios~2 amounts to \SI{54}{\%} (i.e., 2.3~years).
+The plasma data coverage is \SI{76}{\%} (i.e., 5.0~years) in case of Helios~1 and \SI{92}{\%} (i.e., 3.9~years) in case of Helios~2.
 % temporal coverage of merged data\\
@@
 % Plasma data coverage: 91.8~\%; 3.913~years (78~\% of H1)\\
-Thus, the Helios data cover only fractions of a solar cycle and cannot be used for deriving representative time-independent solar wind multi-cycle conditions like the OMNI data can.
 
 %Helios data biased towards solar minimum
-Using this data, we also have to keep in mind that its time coverage is unequally distributed over the solar cycle.
-Dividing the data by the transition from cycle minimum to maximum (mid 1977) and considering the data gap distributions, the Helios data covers about \SI{68}{\percent} during cycle minimum whereas during maximum only \SI{38}{\percent}.
-
+Thus, using this data, one has to keep in mind that its time coverage is unequally distributed over the solar cycle.
+Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
+This Helios data bias towards solar minimum is the reason why in this study the OMNI solar wind data are used instead to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
 % data gaps -> uneven coverage -> solar cycle minimum dominates; ratio of max vs min cycle data coverage; for OMNI data negligible\\
@@
 
-For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.
-
-\subsection{Power law fitting}
-\label{sec:power_law_fitting}
-%why power law function?
-A power law scaling distance behavior is expected from all four parameters (cites?). Therefore we use the power function
+The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution of the data set, which is \SI{0.01}{\au}.
+Previous analyses have shown that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described well through power law scaling (e.g., \hl{ref.
+not correct} \citet[p.~155]{Schwenn1990}).
+Therefore we use the power function
 \begin{align}
@@
 \end{align}
-with the solar distance $r$ for the regression fit of the median and mean. The fits are weighted by data counts per bin.
+for the regression fit of the median and mean, with $r$ being the solar distance. The fits are weighted through the different data counts per bin.
 %fit result table and figure
-With $r$ in astronomical units we get the fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) as given in Table~\ref{tab:mean_median_fit_parameter}.
+With $r$ in astronomical units we derive the fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) as listed in Table~\ref{tab:mean_median_fit_parameter}.
 \begin{table*}
-	\caption{Fit coefficients for the median and mean solar distance dependencies of the four parameters from the combined Helios data set.
+	\caption{Fit coefficients for the median and mean solar distance dependencies of the four solar wind parameters derived from the combined Helios~1 and 2 data.
 The errors in brackets are the estimated standard deviations of each fit parameter.
-The crossing distance is the point where the fitted median and mean intersect.
-The year variation is the weighted standard deviation from all yearly fitted exponents.}
+The crossing distances indicate where the median and mean fits intersect each other.
+The yearly variation is the weighted standard deviation derived from all yearly fit exponents.}
 	\label{tab:mean_median_fit_parameter}
@@
 		\hline\hline
-		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Year variation}\\
+		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Yearly variation}\\
 		\cline{2-3}	\cline{5-6}
@@
 % comparison with other Helios studies (Schwenn, Bougeret)
-As expected, the velocity exponents match with those from \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately ($v_\text{H1}(r) \propto r^{0.083}$ and $v_\text{H2}(r) \propto r^{0.036}$).
-%Helios results, radial gradients see \citet{Schwenn1990} p.~155\\
-Likewise, the density exponents agree well with the Helios plasma density model, which \citet{Bougeret1984} derived from Helios data and normed to the 1976 \SI{1}{\au} density ($n(r) = 6.14\,r^{-2.10}\,\text{cm}^{-3}$).
+%Helios results, radial gradients see \citet{Schwenn1990} p.~155
+As expected, the found velocity exponents match with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1}(r) \propto r^{0.083}$ and $v_\text{H2}(r) \propto r^{0.036}$.
+
+The calculated density exponent agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding a to the year 1976 normalized  \SI{1}{\au} density of $n(r) = 6.14\,r^{-2.10}\,\text{cm}^{-3}$).
+{\color{red} Those of the magnetic field strength and the temperature similarly agree with the studies by \hl{xxx} and \hl{xxx}}.
 
 %crossing distances
-The next step is to fit the bulk of the solar wind parameters with lognormal functions.
-At all considered solar distances the mean of the three plasma parameters is larger than their median (Fig.~\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}).
+Fig.~\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot} shows the radial dependence of the solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} and the mean and median values and their respective power law fits.
+The mean and median velocity fit exponents are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
 \begin{figure*}
@@
 
-The large velocity's crossing distance and its large error indicate that the median's and mean's distance behavior can be kept identical and so the frequency's shape distance independent.
+Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} and the mean is lower than the median at smaller distances (Table~\ref{tab:mean_median_fit_parameter}).
+Thus, below that distance the distribution function cannot well be described anymore by a lognormal function.
+The fits for the proton temperature show a similar behavior,
+having an intersection at \SI{0.082}{\au}.
+Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
+To circumvent such limitations we set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical for all four parameters.
+It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
 
-However, the magnetic field strength's mean crosses the median at \SI{0.339}{\au} and is lower at smaller distances (Table~\ref{tab:mean_median_fit_parameter}).
-At the crossing point and below the magnetic field strength can therefore not be described anymore with a lognormal function.
-For an extrapolation to the PSP perihelion the same happens for the temperature at \SI{0.082}{\au}.
-
-Those crossings limit the possible extrapolation distances with lognormal functions.
-To circumvent these limitations for all four solar wind parameters we set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical, avoiding crossing of median and mean.
-Then the distribution's width has a power law scaling with solar distance.
-Applying this approximation, we have to accept larger model errors, especially for the magnetic field strength.
-It also limits the extrapolation accuracy, however it keeps the model simpler.
-
-\subsection{Power law lognormal fitting}
-To retrieve the frequency distributions for every \SI{0.01}{\au} solar distance bin, we choose the same solar wind parameter binning as with the OMNI data (Sect.~\ref{sec:frequency_distribution}).
+%\subsection{Power law lognormal fitting}
+Next we retrieve the frequency distributions of the four parameters in distance bins of \SI{0.01}{\au},  choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution}---the distributions are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
 % Helios histogram bin sizes for mean of frequency distribution (at specific solar distance):\\
@@
 
-As mentioned before, we set the exponents of median and average to be identical.
-Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get three fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
-Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
-The additional fit parameters are the balancing parameter $c'$ and from the second lognormal part $d'_\text{med,2}$ and $d'_\text{avg,2}$.
+For simplification, as mentioned before, we treat the exponents of the median and average fit functions as being identical.
+Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
+Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
+The additional fit parameters are the balancing parameter $c'$ and for the second lognormal part $d'_\text{med,2}$ and $d'_\text{avg,2}$.
 The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
@@
 	\tablefoot{
-		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
+		\tablefoottext{a}{In units of \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
 		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
@@
 
-With $c' = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to $c(59) = 0.53$; see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
+The velocity balancing parameter $c' = 0.557$ is in good agreement with the results for the SSN dependency (\ref{eq:balance_with_ssn}), because with a mean SSN of 59 during the Helios time period, $c(59) = 0.53$, as also presented in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
 
-The fit models seem to resemble the data quite well (Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}).
-The magnetic field strength frequency is more focused (around \SI{40}{nT}) at the lower distance boundary than the model's is.
-This is expected because of our fixed distance independent shape approximation.
+The frequency distribution data for the four solar wind parameters with respect to the radial distance from the Sun are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}, together with their power law lognormal fits and the double lognormal fit for the velocity with their median values.
+
+Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot} shows that the fits represent the data well.
+The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the frequency distribution implies.
+This behavior is expected because of the distance independent shape approximation applied.
+The velocity and temperature models’ upper values, showing a higher abundance of these values than the actual
+data, see zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 \begin{figure*}
@@
 	\caption{Solar wind parameter's frequency distributions over solar distance.
-Plotted are the binned Helios data and the power law lognormal fit model (double lognormal for the velocity) with their median values (white).}
+Plotted are the binned Helios data and the power law lognormal fit model (double lognormal for the velocity) with their median values (white).
+\hl{see text}}
 	\label{fig:mixed_fit_fixed_4_paper_f_plot}
 \end{figure*}
-The velocity and temperature models' upper values have a higher frequency than the data shows.
-This is due to the systematic fit discrepancy of the lognormal distribution's high value tails (see zoom box in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}).
 
-\subsection{Distance scaling law variations}
-\label{sec:distance_scaling_law_variations}
-
-relocate section to 5.3?\\
-
-This radial solar wind model represents the Helios time frame around the rise of solar cycle~21.
-It is known that the solar wind parameters' magnitudes vary with solar activity.
-Looking at the variation of the yearly distance scaling laws (Fig.~\ref{fig:yearly_gradients_b}), there is no systematic variation for the magnetic field.
-The exponents of velocity and temperature seem to follow the SSN and the density not...
+%\subsection{Distance scaling law variations}
+%\label{sec:distance_scaling_law_variations}
+This established solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
+The variation of the yearly power law fits’ exponents are shown in Fig.~\ref{fig:yearly_gradients_b} together with the yearly SSN for the time period \numrange{1974}{1982}.
+It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_b.pdf}}
-	\caption{Helios year variation of the solar wind parameters' fit exponents and SIDC 13-month smoothed monthly SSN. In this plot the year 1974 is omitted because the 21 days covered only }
+	\caption{Helios yearly variation of the solar wind parameters' fit exponents together with the SIDC 13-month smoothed monthly SSN.
+In this plot the year 1974 is omitted because of merely 21~days since Helios launch that year.}
 	\label{fig:yearly_gradients_b}
@@
 
-For simplicity we assume that the distance scaling laws are time independent and account for this approximation with including the calculated exponents' yearly variations (Table~\ref{tab:mean_median_fit_parameter}) as uncertainities.\\
+However, for simplicity we assume, that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$ summarized in Table~\ref{tab:mean_median_fit_parameter} as relative uncertainties.
 
-make remark about influence of unequal solar cycle coverage... (sect.~5.1)\\
+\section{Empirical solar wind model}
+\label{sec:empirical_solar_wind_model}
+In order to estimate the solar wind environment for the PSP orbit, we combine the results from the solar wind frequency distributions’ solar activity relationships and their distance dependencies derived from the OMNI and Helios data.
+The result is an empirical solar wind model for the inner heliosphere which will then be extrapolated to the PSP orbit in Sec.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
-Possible differing scaling laws at smaller heliocentric distances are discussed in Sect.~\ref{sec:model_extrapolation_to_psp_orbital_time_and_position}.
-
-\section{General solar wind model}
-\label{sec:general_solar_wind_model}
-
-Finally, we combine the obtained solar activity and distance dependencies for shifting the frequency distributions. The result is an empirical solar wind model for the inner heliosphere.\\
-
-%are the exponents time-independent?
-Under the assumption that the fall-off laws do not change with time/solar activity (as shown above...), they can be used in general.
-
-We combine the fit coefficients of the median relation for solar activity dependence (\ref{eq:median_with_ssn}) with the ones from the power law distance dependence (previous section)
+Since we neglect possible variations of the distance scaling laws, we combine the frequency distribution’s median solar activity dependency (\ref{eq:median_with_ssn}) derived for \SI{1}{\au} from the OMNI data with the power law exponents (\ref{eq:power_function}) derived from the Helios data:
 \begin{align}
@@
 \end{align}
+Thus we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
 
-to get the combined model function $W'''(x,ssn,r)$. And for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).\\
+\section{Model extrapolation to PSP orbit}
+\label{sec:model_extrapolation_to_psp_orbit}
+To estimate PSP’s solar wind environment during its mission time for its orbital positions, SSN predictions are included into the in the previous sections derived empirical solar wind model and extrapolations down to the PSP perihelion region are performed.
 
-%model errors
-%give model errors sizes/uncertainties (sigmas); $W'''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\
+%\subsection{SSN prediction for PSP mission time}
+%SSN prediction
+For SSN short-term predictions several sources are available.
+The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter combined method).
+The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
 
-% model requirements:\\
-% - modeling the frequency distribution with sufficient accuracy -> error size (changing distribution shape with distance)\\
-% - modeling the distance dependency with sufficient accuracy -> error size (different scaling law at smaller distances?)\\
-% - possibility to extrapolate model down to \SI{0.0459}{\au}\\
+For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
+Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
 
-%model limits
-empirical model limits (spherical coordinates):\\
-- heliocentric distance range \SIrange{0.29}{0.98}{\au}\\
-- rotational symmetry\\
-- confined to ecliptic (\SI{+-7.2}{\degree} HGI)\\
-model constrictions:\\
-- solar distance dependency function\\
-- frequency distribution functions\\
-- neglected influence from heliolatitude variation\\
-
-\section{Model extrapolation to PSP orbital time and position}
-\label{sec:model_extrapolation_to_psp_orbital_time_and_position}
-To estimate the solar wind environment at PSP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the PSP perihelion region are performed.
-
-\subsection{SSN prediction for PSP mission time}
-%SSN prediction
-For the SSN short-term prediction are several sources available.
-The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g.
-Kalman filter combined method).
-The Space Weather Prediction Center's (SWPC) prediction follows a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}} (until end of 2019).
-
-For the prediction of the next solar cycle~25 we simply assume a course similar to the last and thus we shift the last cycle by 11~years.
-Additionally we consider the two alternatives of half and twice its amplitude.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).
 \begin{figure}
@@
 Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), i.e.
-SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
 	\label{fig:SPP_orbit_predicted_SSN_overview_e_plot}
@@
 
-\subsection{Near-Sun extrapolation for PSP orbit}
+%\subsection{Near-Sun extrapolation for PSP orbit}
 %PSP orbit
 Parker Solar Probe is planned to launch in mid 2018.
-With its first Venus flyby it will swing into Venus' orbital plane (\SI{3.86}{\degree} to Sun's equator/\SI{3.39}{\degree} to ecliptic), which allows for additional seven flybys to finally reduce its perihelion distance to a minimum of less than \SI{10}{R_s} \citep{Fox2015} (Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).\\
+With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
+Seven additional Venus flybys allow to finally reduce its perihelion distance to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
 
-For the extrapolation to PSP's orbital range we just assume that our derived distance scaling laws do not change.
-The comparison with existing near-Sun models reveals that this is not entirely true (Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}).\\
+We extrapolate the derived empirical solar wind model to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}.
 \begin{figure*}
@@
 %magnetic field:
-The magnetic field magnitude from our extrapolation is flatter than the analytical magnetic field model from \citet{Banaszkiewicz1998}, who constructed a dipole plus quadrupole plus current sheet (DQCS) model.
-We attribute this effect to the from a lognormal shape deviating distribution (see Sect.~\ref{sec:power_law_fitting}).\\
+The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of 0.
+Taking a SSN of 200 increases the value to \SI{69}{\nT} at \SI{0.25}{\au} and \SI{1152}{\nT} at \SI{0.046}{\au}.
+Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed a dipole plus quadrupole plus current sheet (DQCS) model.
+
+This difference is arguably due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) with solar distance changing shape of the frequency distribution, which for smaller distances deviates more from the model’s lognormal distribution.
 
 %velocity:
-%critical surfaces
-Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
-in direction to the Sun is at about \SI{2.5}{R_s} the source surface (Schatten1969)\\
-sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
-sonic point and slow solar wind origin \citep{Sheeley1997}\\
-approaching these regions, acceleration plays a role\\
-
-\citet{Wang2000}, sources of slow solar wind + IMF regulation mechanism + blobs; compare with our slow V lognormal part; Parker solution\\
--> below 20~Rs PSP will fly well into sw acceleration region\\
-
-\citet{Sheeley1997} -> LASCO coronagraph observed speed profile of coronal features tracing the slow solar wind, 2--30~Rs\\
-%- parabolic eq.~(2) and exponential eq.~(3)\\
-- sonic point 5--6~Rs\\
-- slow solar wind origin 3--4~Rs\\
-
-The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
-The \citet{Parker1958} model of an isothermal expanding corona with a temperature of \SI{e6}{\K} and a critical radius of \SI{5.8}{R_s}.\\
+The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} for a SSN of 0.
+Whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
+Comparing the results with those found by \citep{Sheeley1997} and \citet{Wang2000}, who used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind, shows an overestimation in our extrapolated velocity values for distances \hl{below} \SI{20}{\Rs}.
+Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates and thus it will measure solar wind acceleration processes \hl{below} \SI{30}{\Rs} \citep{Sheeley1997,McComas2008}.
 
 %density:
-We expect that even our Sun-nearest extrapolated density at PSP perihelion agrees well with the actual, since \citet{Leblanc1998} derived an electron density model from type~III radio burst observations.
-Their model shows that the density distance dependency scales with $r^{-2}$ and steepens not until below \SI{10}{R_s} with $r^{-6}$ (see Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}).\\
+The proton density increases from about \SI{84}{\per\cm\cubed} at  \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} for a SSN of 0.
+Being almost independent of the SSN the values for a SSN of 200 are only \SI{17}{\%} larger.
+The results are in good agreement with those of \citet{Leblanc1998}, who derived an electron density model from type~III radio burst observations.
+Their model shows that the density distance dependency scales with $r^{-2}$ and steepens just below \SI{10}{\Rs} with $r^{-6}$.
+For the comparison we assumed a solar wind helium abundance of \SI{5}{\%}.
 
-magnetic field and temperature:\\
-crossing distance effect\\
+%temperature:
+The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} for a SSN of 0 and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
+Knowing that near-Sun coronal temperatures are in the range of \hl{1--3 MK (ref.)}, the model obviously overestimates the extrapolated temperatures at the PSP perihelion distance.
+{\color{red} The results can be compared to...}
 
-% The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
-% L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
+%\subsection{PSP solar wind environment estimation}
+Implementing the predicted SSN for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment to infer which solar wind parameter magnitudes can be expected.
 
-\subsection{PSP solar wind environment estimation}
-Implementing the orbital distance data and predicted SSN for the mission time we can derive PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
-The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot}).\\
+$W'''(x,ssn,r)$
+
+Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12~days, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
+In the beginning of the mission median peak values of about  \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and\SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and\SI{1930000}{\K} during the closest approach at \SI{0.046}{\au} (\SI{9.86}{\Rs}).
 \begin{figure}
@@
 
-\subsection{Model validity and error sources}
-\label{sec:model_validity_and_errors}
+\hl{XXXXXXXXXXXXXXXXXXXXXXXX}\\
 
-validity and estimation of error size outside of valid model range...\\
-derive heliocentric distance depending error...\\
-
-list simplifications/approximations...\\
-
-error estimation for general model and extreme value tendencies\\
-
-error sources:\\
-- extrapolation\\
-- lognormal model\\
-- SSN variance\\
-
-all estimates outside these boundaries are extrapolations with large uncertainties.\\
-
-discuss high value zoom figures\\
+discuss high value zoom figures; read in Veselovsky2010\\
 
@@
 
-\section{Results and discussion}
-
+\section{Discussion}
 list of results:\\
@@
 
+The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
+The \citet{Parker1958} model of an isothermal expanding corona with a temperature of \SI{e6}{\K} and a critical radius of \SI{5.8}{R_s}.\\
+
 individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
@@
 
-In most studies the density distance dependence is assumed to scale with $r^{-2}$ (cites), assuming a constant velocity.\\
+%critical surfaces
+approaching these regions, acceleration plays a role\\
+Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
+in direction to the Sun is at about \SI{2.5}{R_s} the source surface (Schatten1969)\\
+sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
+sonic point and slow solar wind origin \citep{Sheeley1997}\\
+% The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
+% L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
 
-\section{Conclusions}
+%\subsection{Model validity and error sources}
+validity and estimation of error size outside of valid model range...\\
+derive heliocentric distance depending error...\\
+list simplifications/approximations...\\
+error estimation for general model and extreme value tendencies\\
+error sources:\\
+- extrapolation\\
+- lognormal model\\
+- SSN variance\\
+all estimates outside these boundaries are extrapolations with large uncertainties.\\
+
+\section{Summary and conclusions}
 
@@
 
-Further questions:\\
-nearer to the Sun (at and below the source surface) the solar wind expansion in the ecliptic should be less spherical but more circular due to the influx from higher latitudes.
-=> density exponent > -2\\
-see Li2011 Fig.~1\\
-% n	v
-% -2.05	0.05
-% -2	0
-% -1.8	-0.2
-% -1.5	-0.5
+The estimated solar wind median values during PSP’s first perihelion and the modeled values for PSP’s closest perihelia.
+The velocity and temperature values are clearly overestimated below ~20 Rs in comparison with existing observations.
+This empirical model shows that solar wind acceleration and heating processes below 20 Rs limit the simple back-extrapolation from existing in situ measurements.

### 2017-08-14 paperMVVB/sections/content.tex
some references...

@@
 In order to help optimize the WISPR and PSP preplanning of the science operations knowledge of the expected solar wind environment is needed.
-For this purpose the solar wind environment is extrapolated down to the closest perihelion of \SI{9.86}{R_s} distance to the Sun using in situ solar wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the NASA/GSFC OMNI solar wind database.\\
+For this purpose the solar wind environment is extrapolated down to the closest perihelion of \SI{9.86}{\Rs} distance to the Sun using in situ solar wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the NASA/GSFC OMNI solar wind database.
 
@@
 %section{Solar wind}
-
-Generally, two types of solar wind are observed in the heliosphere, slow and fast streams \citep{Neugebauer1966}\hl{, Schwenn (19xx)}.
+Generally, two types of solar wind are observed in the heliosphere, slow and fast streams \citep{Neugebauer1966,Schwenn1983}.
 Slow solar wind has typical speeds \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[p.~144]{Schwenn1990}.
@@
 Fast streams are found to originate from coronal holes as confirmed by Ulysses out-of-ecliptic measurements \citep{McComas1998}.
-The source of slow wind and its eventually different types (\hl{Schwenn19xx}), is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, {\color{red} such as ...intermittent reconnection at the top of streamers and pseudostreamers, coronal hole boundaries, ...
+The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, {\color{red} such as ...intermittent reconnection at the top of streamers and pseudostreamers, coronal hole boundaries, ...
 (\hl{ref.}).} The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
-
 Embedded in the slow and fast solar wind streams are transient flows of coronal mass ejections (CMEs), the faster ones driving shock waves ahead \hl{(ref.)}.
@@
 
+%solar wind parameters
 It is not known which specific solar wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar wind parameters from existing solar wind measurements and take solar cycle dependencies into account.
-
-%solar wind parameters
 As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \textit{density}, \textit{temperature} and \textit{magnetic field strength}.
@@
 
+%sections
 Our approach is to obtain analytical representations of the shapes of the solar wind parameter’s frequency distributions in Sect.~\ref{sec:frequency_distribution}, of their solar activity dependence in Sect.~\ref{sec:solar_activity_variations} and of their solar distance scaling in Sect.~\ref{sec:solar_distance_dependency}.
@@
 %data binning
+According to the OMNI data precision and maximal parameter ranges we specify the bin sizes to \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
 The frequency distributions of the solar wind magnetic field strength, proton velocity, density and temperature are shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-According to the OMNI data precision and maximal parameter ranges we specify the bin sizes to \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
-
 The solar wind magnetic field strength is in the range \SIrange{0.4}{62}{nT}, the velocity in the range \SIrange{156}{1189}{\km\per\s}, the density in the range \SIrange{0}{117}{\per\cm\cubed}, and the temperature in the range \SIrange{3450}{6.63e6}{\K}, the mean values are at \SI{6.28}{\nT}, \SI{436}{\km\per\s}, \SI{6.8}{\per\cm\cubed} and \SI{1.05e5}{\K}.
 These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
-
-Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 ICME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.\\
+Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 ICME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
 
@@
 
-From visual inspection, the resulting curves describe the shape of the magnetic field strength, density and temperature distributions well as shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+From visual inspection, the resulting curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
 However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its maximum and in the higher velocity range.
@@
 The balancing parameter $c$ ensures that the resulting function remains normalized as it represents a probability distribution.
-
 The fitting of $W_\text{II}(x)$ to the velocity's frequency distribution yields the values of the now five fit parameters ($c$, $x_\text{med,1}$, $x_\text{avg,1}$, $x_\text{med,2}$ and $x_\text{avg,2}$) as listed in Table~\ref{tab:lognormal_fit_parameters} together with the median and mean values of the composed distribution, which can be derived via solving
@@
 The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
-
 %transition
 For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, but differ for the extreme values, mainly caused by CME events.
-
 The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is overestimated as seen by the insets in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
@@
 \label{sec:solar_activity_variations}
-
 In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity.
@@
 
-The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}, \hl{ref. zu Korrelationen}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
-For instance the fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by \citet[\hl{Figure~XX, p.~XX}]{Bothmer2007}.
+The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
+For instance the fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by \citet[\hl{p.~XX, Figure~XX}]{Bothmer2007}.
 Therefore the solar wind velocity, density and temperature maxima exhibit time-lags to the SSN maxima.
@@
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
-
 Velocity and temperature show a lag time of 3~years with peak correlation coefficients of 0.453 and 0.540.
@@
 %\subsection{SSN fitting}
-To enable to shifts of the solar wind frequency distributions with the SSN, we add a linear SSN dependency to the median
+To enable shifts of the solar wind frequency distributions with the SSN, we add a linear SSN dependency to the median
 \begin{align}
@@
 Again, the solar wind velocity needs a special treatment because of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycleand basically maintain characteristic speeds (\hl{ref.}), we keep the two velocity components' positions constant and vary their balance with the SSN:
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle and basically maintain characteristic speeds (\hl{ref.}), we keep the two velocity components' positions constant and vary their balance with the SSN:
 \begin{align}
@@
 
-To investigate the amount of slow and fast wind contributions depending on solar activity, we apply the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (\hl{cite?}).
+To investigate the amount of slow and fast wind contributions depending on solar activity, we apply the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ \citep[p.~144]{Schwenn1990}.
 The linear fit to the yearly data ratio and the derived model ratio show a good agreement (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
@@
 % Plasma data coverage: 91.8~\%; 3.913~years (78~\% of H1)\\
-
 %Helios data biased towards solar minimum
@@
 The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution of the data set, which is \SI{0.01}{\au}.
-Previous analyses have shown that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described well through power law scaling (e.g., \hl{ref.
-not correct} \citet[p.~155]{Schwenn1990}).
+Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
 Therefore we use the power function
@@
 %Helios results, radial gradients see \citet{Schwenn1990} p.~155
-As expected, the found velocity exponents match with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1}(r) \propto r^{0.083}$ and $v_\text{H2}(r) \propto r^{0.036}$.
-
-The calculated density exponent agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding a to the year 1976 normalized  \SI{1}{\au} density of $n(r) = 6.14\,r^{-2.10}\,\text{cm}^{-3}$).
-{\color{red} Those of the magnetic field strength and the temperature similarly agree with the studies by \hl{xxx} and \hl{xxx}}.
+As anticipated, the derived exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$.
+%$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
+The velocity exponent matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
+The calculated density exponent agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding $n \propto r^{-2.10}\,\text{cm}^{-3}$.
+%to the year 1976 normalized   a \SI{1}{\au} density of $n = 6.14\cdot r^{-2.10}\,\text{cm}^{-3}$.
+The temperature exponent is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} = \propto r^{-0.74}$ and $T_\text{slow} = \propto r^{-0.58}$.
+%$T_\text{fast} = \num{2.5e5} (R/R_0)^{-0.74}$\,K and $T_\text{slow} = \num{6.2e4} (R/R_0)^{-0.58}$\,K.
+%\citet{Marsch1982}	$T_\text{||,slow} \propto r^{-1.03}$ and $T_\text{||,fast} \propto r^{-0.69}$.
 
@@
 \end{figure*}
-
 Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} and the mean is lower than the median at smaller distances (Table~\ref{tab:mean_median_fit_parameter}).
@@
 % $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
-
 For simplification, as mentioned before, we treat the exponents of the median and average fit functions as being identical.
@@
 The frequency distribution data for the four solar wind parameters with respect to the radial distance from the Sun are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}, together with their power law lognormal fits and the double lognormal fit for the velocity with their median values.
-
 Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot} shows that the fits represent the data well.
@@
 This behavior is expected because of the distance independent shape approximation applied.
-The velocity and temperature models’ upper values, showing a higher abundance of these values than the actual
+The velocity and temperature models’ upper values show a higher abundance of these values than the actual
 data, see zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
@@
 	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_f_plot.pdf}
-	\caption{Solar wind parameter's frequency distributions over solar distance.
-Plotted are the binned Helios data and the power law lognormal fit model (double lognormal for the velocity) with their median values (white).
-\hl{see text}}
+	\caption{Frequency distributions of the four solar wind parameters with respect to the solar distance.
+Plotted are the binned Helios data and the power law lognormal fit models with their median values (white lines).
+The double lognormal model is used for the velocity.}
 	\label{fig:mixed_fit_fixed_4_paper_f_plot}
@@
 \end{figure}
-
 However, for simplicity we assume, that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$ summarized in Table~\ref{tab:mean_median_fit_parameter} as relative uncertainties.
@@
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-
 For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
 Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
-
 The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed a dipole plus quadrupole plus current sheet (DQCS) model.
-
 This difference is arguably due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) with solar distance changing shape of the frequency distribution, which for smaller distances deviates more from the model’s lognormal distribution.
@@
 The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} for a SSN of 0 and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
-Knowing that near-Sun coronal temperatures are in the range of \hl{1--3 MK (ref.)}, the model obviously overestimates the extrapolated temperatures at the PSP perihelion distance.
+Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \hl{may overestimate} the extrapolated temperatures at the PSP perihelion distance.
 {\color{red} The results can be compared to...}
@@
 %\subsection{PSP solar wind environment estimation}
-Implementing the predicted SSN for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment to infer which solar wind parameter magnitudes can be expected.
-
-$W'''(x,ssn,r)$
+Implementing the predicted SSN for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected.
 
 Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12~days, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
-In the beginning of the mission median peak values of about  \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and\SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and\SI{1930000}{\K} during the closest approach at \SI{0.046}{\au} (\SI{9.86}{\Rs}).
+In the beginning of the mission median peak values of about  \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au} (\SI{9.86}{\Rs}).
 \begin{figure}

### 2017-08-16 paperMVVB/sections/abstract.tex
text flow streamlining

@@
 
-\date{First draft 9 August 2016; first changes 21 June 2017; received date; accepted date }
+\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; received date; accepted date}
 
@@
 Visiting this yet uncharted region is of special interest, because it will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
-The solar wind extrapolation of this study is performed within the project CGAUSS (Coronagraphic German And US Solar~Probe Survey) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
+The solar wind extrapolation of this study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
 {We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data.
 The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
-The OMNI database at NASA's Space Physics Data Facility (SPDF) consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au}.
+The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au}.
 The solar wind model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters PSP will encounter during its mission.}	%aims
-{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
+{The model covers the solar wind's magnetic field strength and its plasma parameters proton velocity, density and temperature.
 Their individual frequency distributions are represented with lognormal functions.
@@
 Finally, by combining the found solar cycle and solar distance relations, we obtain a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic region.}	%methods
-{The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its prime mission duration 2018--2025.
+{The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its mission duration.
 The estimated solar wind median values during PSP's first perihelion \hl{are} \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.

### 2017-08-16 paperMVVB/sections/content.tex
text flow streamlining

@@
 The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
-Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in the case of Voyager~1 as far away as \SI{138}{\au} in July 2017\footnote{\url{https://voyager.jpl.nasa.gov/}}, having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
 Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with Wind \hl{(ref.)}, ACE \hl{(ref.)} and DSCOVR \hl{(ref.)} still orbiting around the L1 point \SI{1.5}{million \km} ahead of Earth in the sunward direction.
-Additional measurements at other distances were provided by planetary missions to Venus and Mercury, such as PVO \hl{(ref.)} or MESSENGER \hl{(ref.)}.
-Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind at polar latitudes \citep{McComas1998}.
-The nearest in situ solar wind measurements to date were obtained by the Helios mission.
+Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \hl{(ref.)} or MESSENGER \hl{(ref.)}.
+Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
+The Sun-nearest in situ solar wind measurements to date were obtained by the Helios mission.
 The in 1974 launched Helios~1 spacecraft reached distances of \SI{0.31}{\au}, Helios~2 launched two years later and approached the Sun up to \SI{0.29}{\au} \citep{Rosenbauer1977}.
@@
 In order to help optimize the WISPR and PSP preplanning of the science operations knowledge of the expected solar wind environment is needed.
-For this purpose the solar wind environment is extrapolated down to the closest perihelion of \SI{9.86}{\Rs} distance to the Sun using in situ solar wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the NASA/GSFC OMNI solar wind database.
+For this purpose the solar wind environment is extrapolated down to the closest perihelion of \SI{9.86}{\Rs} distance to the Sun using in situ solar wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the OMNI solar wind database.
 
@@
 Their different compositions and characteristics indicate different sources and generation processes \citep{McGregor2011a}.
-Fast streams are found to originate from coronal holes as confirmed by Ulysses out-of-ecliptic measurements \citep{McComas1998}.
+Fast streams are found to originate from coronal holes as confirmed by Ulysses' out-of-ecliptic measurements \citep{McComas1998}.
 The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, {\color{red} such as ...intermittent reconnection at the top of streamers and pseudostreamers, coronal hole boundaries, ...
@@
 Embedded in the slow and fast solar wind streams are transient flows of coronal mass ejections (CMEs), the faster ones driving shock waves ahead \hl{(ref.)}.
-Their rate follows the activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
+Their rate follows the solar activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
 
@@
 \label{sec:frequency_distribution}
-
 The solar wind parameters are highly variable, due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on the phase of the solar activity cycle.
@@
 %about OMNI data
-The OMNI~2 data set \citep{King2005} combines solar wind plasma and magnetic field data collected by various satellites since 1963.
+The OMNI~2 data set \citep{King2005} combines solar wind magnetic field and plasma data collected by various satellites since 1963.
 This intercalibrated multi-spacecraft data is time-shifted to the nose of the Earth’s bow shock.
@@
 In this study the whole hourly data until 31 December 2016 is used, starting from 27 November 1963 (for the temperature from 26 July 1965).
-The data coverage of the parameters is in the range \SIrange{67}{74}{\percent},  corresponding to a total duration of 36--40~years.
+The data coverage of the different parameters is in the range \SIrange{67}{74}{\percent},  corresponding to a total duration of 36--40~years.
 %OMNI 1963-01-01 data
@@
 %hourly data
-It should be noted that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016, did not show significant differences in our results.
+It should be noted that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
 
 %data binning
-According to the OMNI data precision and maximal parameter ranges we specify the bin sizes to \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
+According to the OMNI data precision and maximal parameter ranges we specify bin sizes of \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
 The frequency distributions of the solar wind magnetic field strength, proton velocity, density and temperature are shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-The solar wind magnetic field strength is in the range \SIrange{0.4}{62}{nT}, the velocity in the range \SIrange{156}{1189}{\km\per\s}, the density in the range \SIrange{0}{117}{\per\cm\cubed}, and the temperature in the range \SIrange{3450}{6.63e6}{\K}, the mean values are at \SI{6.28}{\nT}, \SI{436}{\km\per\s}, \SI{6.8}{\per\cm\cubed} and \SI{1.05e5}{\K}.
+The solar wind magnetic field strength is in the range \SIrange{0.4}{62}{nT}, the velocity in the range \SIrange{156}{1189}{\km\per\s}, the density in the range \SIrange{0}{117}{\per\cm\cubed}, and the temperature in the range \SIrange{3450}{6.63e6}{\K}, the mean data values are at \SI{6.28}{\nT}, \SI{436}{\km\per\s}, \SI{6.8}{\per\cm\cubed} and \SI{1.05e5}{\K}.
 These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
@@
 The mean absolute errors and sums of absolute residuals are also listed.
-The values in brackets are the estimated standard deviations of each fit parameter.}
+The values in brackets are the estimated standard deviations of the fit parameters.}
 	\label{tab:lognormal_fit_parameters}
@@
 		@{}c@{}
-		S[table-format = 1.2e+2]
+		S[table-format = 2.3]
 		S[table-format = 2.2]
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{2}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
-		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{}	&\multicolumn{1}{c}{[\%]}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{1}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
+		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[$10^{-4}$]}	&\multicolumn{1}{c}{[\%]}\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&5.51e-4	&6.83\\
-		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&1.80e-3	&18.69\\
-		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&5.49e-4	&6.48\\
-		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&8.71e-5	&5.78\\
+		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&5.51	&6.83\\
+		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&18.0	&18.69\\
+		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&5.49	&6.48\\
+		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&0.871	&5.78\\
 		\hline
@@
 		\cline{2-7}
-			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{b}	&4.42(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98e-4	&4.20\\
+			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{b}	&4.42(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98	&4.20\\
 		\hline
@@
 
-From visual inspection, the resulting curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its maximum and in the higher velocity range.
+From visual inspection, the resulting fit curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
 This also can be inferred from the sum of absolute residuals (SAR) between data and fit listed in Table~\ref{tab:lognormal_fit_parameters}, being almost three times larger than those from the other parameters.
@@
 The histograms have bins of \SI{0.5}{\nT}, \SI{10}{\km\per\s}, \SI{1}{\per\cm\cubed} and \SI{10000}{\K}.
-The fit's median and mean values are indicated as well.
+The fits' median and mean values are indicated as well.
 The insets show zoomed-in frequency axes.}
@@
 %justification for compositional lognormal fit
-In order to find a better fit result for the velocity distribution we assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
+In order to find a better fit result for the velocity distribution, we assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
 Therefore a compositional approach  is chosen by combining two lognormal functions (\ref{eq:single_lognormal_fit_function}), involving more fit variables:
@@
 \end{align}
-This more complex fit function is more accurately in describing the velocity's frequency distribution as shown in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+This more complex fit function is more accurate in describing the velocity's frequency distribution as shown in Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 \begin{figure}
@@
 The fit's median and mean values and its two fit parts are indicated as well.
-The inset only has a zoomed-in frequency axis, its x-axis stays the same.}
+The inset has a zoomed-in frequency axis.}
 	\label{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}
@@
 
-The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
 %transition
 For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, but differ for the extreme values, mainly caused by CME events.
-The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is overestimated as seen by the insets in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is overestimated as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
 The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
+
+{\color{red} discuss high value zoom figures; read in Veselovsky2010}
 
@@
 In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity.
-Therefore we examine their correlation with the sunspot number, being a commonly used long-term solar activity index and determine the time lags with the highest correlation coefficients.
+Therefore we examine their correlation with the sunspot number, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.
 
@@
 Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} shows yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number.
-The reason for correlating the SSN to the solar wind median values is, because the position of a lognormal function is defined by its median.
+The reason for correlating the SSN to the solar wind median values is because the position of a lognormal function is defined by its median.
 The data are averaged to yearly values to avoid seasonal effects during the Earth’s orbit around the Sun caused by its variations in solar latitude and distance.
-The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
 \begin{figure}
@@
 
-The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength which has no time lag.
+The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
+As expected, the correlation coefficients' amplitudes of all parameters decline with increasing time lag and show a frequency of about 11~years.
+The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
 Velocity and temperature show a lag time of 3~years with peak correlation coefficients of 0.453 and 0.540.
-The density with a correlation coefficient of 0.468 has a lag time of 6~years, which is in agreement with the by \citet{Bougeret1984} reported density anticorrelation to the SSN.	%p.~406\\
+The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the by \citet{Bougeret1984} reported density anticorrelation to the SSN.	%p.~406\\
 % maximal correlation coefficients and their lag times:\\
@@
 % temperature: lag -3, 0.540\\
-As expected, the correlation coefficients' amplitudes of all parameters decline with increasing lag time and show a frequency of about 11~years.
 
@@
 For the velocity the fit parameters from the double lognormal fit and their balancing function are given.
-The values in brackets are the estimated standard deviation of each fit parameter.}
+The values in brackets are the estimated standard deviation of the fit parameters.}
 	\label{tab:ssn_fit_parameters}
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{2}{c}{Balance}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
 		\cline{3-4}\cline{6-7}
@@
 	\includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_e_plot.pdf}
-	\caption{Solar wind parameter data frequencies, lognormal fit models with their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016.
-The for the models shifted SSN is indicated by a black line.
-The velocity median is derived from the SSN weighted constant lognormal parts (dotted).}
+	\caption{Solar wind parameter yearly data frequencies and lognormal fit models, both with their median values (white lines) over the OMNI time period 1963--2016.
+The corresponding yearly SSN and the for the models shifted SSN are indicated by grey and black lines.
+The velocity median is derived from the SSN weighted constant lognormal parts (dotted lines).}
 	\label{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}
 \end{figure*}
-The comparison with the yearly data median values over SSN shows that the medians obtained from the modeling have a quite similar slope as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
+The comparison of this model with the yearly data median values with respect to the lagged SSN shows that the medians obtained from the modeling have a quite similar slope as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN_a.pdf}}
-	\caption{Solar wind parameter median over lagged SSN.
-The yearly data medians (+) with their weighted linear fit (solid) are obtained from OMNI data.
+	\caption{Solar wind parameter median with respect to the lagged SSN.
+The yearly data medians (+) with their weighted linear fit (solid lines) are obtained from OMNI data.
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
 The SSN dependent median (\ref{eq:median_with_ssn}) is derived from the lognormal model fit (dashed line).
-For the velocity the median is derived from the SSN weighting of the slow and fast model parts, whose magnitudes are SSN independent (dotted line).}
+For the velocity the median is derived from the SSN weighting (\ref{eq:balance_with_ssn}) of the slow and fast model parts, whose magnitudes are SSN independent (dotted line).}
 	\label{fig:OMNI_yearly_BVNTvsSSN_a}
@@
 
-Again, the solar wind velocity needs a special treatment because of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle and basically maintain characteristic speeds (\hl{ref.}), we keep the two velocity components' positions constant and vary their balance with the SSN:
+Again, the solar wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle and basically maintain characteristic speeds (\hl{ref.}), we keep the two velocity components' positions constant and vary instead their balance with the SSN:
 \begin{align}
@@
 Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the to some degree steeper balance parameter of the double fit function used in this model.
-However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citep{McGregor2011b}.
+However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
 %(i.e. there exists slow wind with properties of fast wind and vice versa)
@@
 Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
-This Helios data bias towards solar minimum is the reason why in this study the OMNI solar wind data are used instead to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
+This Helios data bias towards solar minimum is the reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
 % data gaps -> uneven coverage -> solar cycle minimum dominates; ratio of max vs min cycle data coverage; for OMNI data negligible\\
@@
 
-The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution of the data set, which is \SI{0.01}{\au}.
+The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set, see Fig.~\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}.
 Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
-Therefore we use the power function
+Therefore we use the power law function
 \begin{align}
-	x(r) = d\,r^e	\label{eq:power_function}
+	x(r) = d\cdot r^e	\label{eq:power_function}
 \end{align}
-for the regression fit of the median and mean, with $r$ being the solar distance. The fits are weighted through the different data counts per bin.
+for the regression fit of the median and mean, with $r$ being the solar distance in astronomical units, $d$ the magnitude at \SI{1}{\au} and $e$ the exponent.
+The fits are weighted through the different data counts per bin.
 %fit result table and figure
-With $r$ in astronomical units we derive the fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) as listed in Table~\ref{tab:mean_median_fit_parameter}.
+The fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter}.
 \begin{table*}
@@
 The crossing distances indicate where the median and mean fits intersect each other.
-The yearly variation is the weighted standard deviation derived from all yearly fit exponents.}
+The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_b}.}
 	\label{tab:mean_median_fit_parameter}
@@
 %Helios results, radial gradients see \citet{Schwenn1990} p.~155
-As anticipated, the derived exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$.
+As anticipated, our derived exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$.
 %$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
 The velocity exponent matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
-The calculated density exponent agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding $n \propto r^{-2.10}\,\text{cm}^{-3}$.
+The calculated density exponent agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding $n \propto r^{-2.10}$.
 %to the year 1976 normalized   a \SI{1}{\au} density of $n = 6.14\cdot r^{-2.10}\,\text{cm}^{-3}$.
-The temperature exponent is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} = \propto r^{-0.74}$ and $T_\text{slow} = \propto r^{-0.58}$.
+The temperature exponent is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} \propto r^{-0.74}$ and $T_\text{slow} \propto r^{-0.58}$.
 %$T_\text{fast} = \num{2.5e5} (R/R_0)^{-0.74}$\,K and $T_\text{slow} = \num{6.2e4} (R/R_0)^{-0.58}$\,K.
@@
 The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well.
-The Helios data has a native distance resolution of \SI{0.01}{\au}.
-To make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.}
+The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.}
 	\label{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}
@@
 % $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
-For simplification, as mentioned before, we treat the exponents of the median and average fit functions as being identical.
-Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$).
+For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical.
+Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and their common exponent $e'$).
 Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
@@
 \begin{table*}
-	\caption{Fit coefficients from the single lognormal power function, respectively double lognormal for the velocity (combined Helios data).
-The errors in brackets are the estimated standard deviations of each fit parameter.}
+	\caption{Fit coefficients from the single lognormal power function, respectively double lognormal for the velocity from the combined Helios data.
+The errors in brackets are the estimated standard deviations of the fit parameters.}
 	\label{tab:extrapolation_model_fit_parameters}
@@
 
-The velocity balancing parameter $c' = 0.557$ is in good agreement with the results for the SSN dependency (\ref{eq:balance_with_ssn}), because with a mean SSN of 59 during the Helios time period, $c(59) = 0.53$, as also presented in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
+The velocity balancing parameter $c' = 0.557$ is in good agreement with the results for the SSN dependency (\ref{eq:balance_with_ssn}), because with a mean SSN of 59 during the Helios time period, $c(59) = 0.53$, as can be seen from Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
 
 The frequency distribution data for the four solar wind parameters with respect to the radial distance from the Sun are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}, together with their power law lognormal fits and the double lognormal fit for the velocity with their median values.
-Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot} shows that the fits represent the data well.
-The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the frequency distribution implies.
-This behavior is expected because of the distance independent shape approximation applied.
-The velocity and temperature models’ upper values show a higher abundance of these values than the actual
-data, see zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 \begin{figure*}
@@
 Plotted are the binned Helios data and the power law lognormal fit models with their median values (white lines).
-The double lognormal model is used for the velocity.}
+The double lognormal model is used for the velocity, its slow and fast parts are indicated by dotted lines.}
 	\label{fig:mixed_fit_fixed_4_paper_f_plot}
 \end{figure*}
-
-%\subsection{Distance scaling law variations}
-%\label{sec:distance_scaling_law_variations}
-This established solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The variation of the yearly power law fits’ exponents are shown in Fig.~\ref{fig:yearly_gradients_b} together with the yearly SSN for the time period \numrange{1974}{1982}.
-It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature.
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_b.pdf}}
-	\caption{Helios yearly variation of the solar wind parameters' fit exponents together with the SIDC 13-month smoothed monthly SSN.
-In this plot the year 1974 is omitted because of merely 21~days since Helios launch that year.}
-	\label{fig:yearly_gradients_b}
-\end{figure}
-However, for simplicity we assume, that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$ summarized in Table~\ref{tab:mean_median_fit_parameter} as relative uncertainties.
+The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the data's frequency distribution implies.
+This behavior is expected because of the distance independent shape approximation applied.
+The velocity and temperature models’ upper values show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 
@@
 
+%\subsection{Distance scaling law variations}
+%\label{sec:distance_scaling_law_variations}
+This established solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
+The variation of yearly power law fit exponents are shown in Fig.~\ref{fig:yearly_gradients_b} together with the yearly SSN for the time period \numrange{1974}{1982}.
+It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature.
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_b.pdf}}
+	\caption{Helios yearly variation of the solar wind parameters' fit exponents together with the SIDC 13-month smoothed monthly SSN.
+The weighted standard deviations are indicated with dotted lines.
+In this plot the year 1974 is omitted because of merely 21~days since Helios launch that year.}
+	\label{fig:yearly_gradients_b}
+\end{figure}
+However, for simplicity we assume, that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$, summarized in Table~\ref{tab:mean_median_fit_parameter}, as relative uncertainties.
+
 Since we neglect possible variations of the distance scaling laws, we combine the frequency distribution’s median solar activity dependency (\ref{eq:median_with_ssn}) derived for \SI{1}{\au} from the OMNI data with the power law exponents (\ref{eq:power_function}) derived from the Helios data:
 \begin{align}
-	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^{e'}
+	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^{e'}	\,.	\label{eq:general_sw_model}
 \end{align}
@@
 
-%\subsection{SSN prediction for PSP mission time}
-%SSN prediction
-For SSN short-term predictions several sources are available.
-The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter combined method).
-The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
-Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}).
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_e_plot.pdf}}
-	\caption{PSP's solar distance during its mission time (top).
-Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
-	\label{fig:SPP_orbit_predicted_SSN_overview_e_plot}
-\end{figure}
-
 %\subsection{Near-Sun extrapolation for PSP orbit}
@@
 
-We extrapolate the derived empirical solar wind model to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}.
+We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}.
 \begin{figure*}
@@
 The magnetic field radial dependence is slightly flatter than the analytic DQCS model for solar minimum which \citet{Banaszkiewicz1998} derived.
-Below \SI{20}{R_s} the slow wind velocity is overestimated in comparison to the measurements from \citet{Wang2000}) and \citep{Sheeley1997}.
-They derived temperature and sonic point values for slow solar wind with the isothermal expansion model \citep{Parker1958}.
+\hl{Below} \SI{20}{\Rs} the slow wind velocity is overestimated in comparison to the measurements from \citet{Wang2000}) and \citet{Sheeley1997}.
 Down to PSP's perihelion the density is in good agreement with the model from \citet{Leblanc1998}.
@@
 Whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
-Comparing the results with those found by \citep{Sheeley1997} and \citet{Wang2000}, who used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind, shows an overestimation in our extrapolated velocity values for distances \hl{below} \SI{20}{\Rs}.
-Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates and thus it will measure solar wind acceleration processes \hl{below} \SI{30}{\Rs} \citep{Sheeley1997,McComas2008}.
+Comparing the results with those found by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated velocity values for distances \hl{below} \SI{20}{\Rs}.
+They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model \citep{Parker1958}.
+Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates and thus PSP will measure solar wind acceleration processes \hl{below} \SI{30}{\Rs} \citep{Sheeley1997,McComas2008}.
 
@@
 
+%\subsection{SSN prediction for PSP mission time}
+%SSN prediction
+For SSN short-term predictions several sources are available.
+The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter combined method).
+The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
+For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
+Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes.
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_e_plot.pdf}}
+	\caption{PSP's solar distance during its mission time (top).
+Consecutive Venus flybys bring its perihelia nearer to the Sun.
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+	\label{fig:SPP_orbit_predicted_SSN_overview_e_plot}
+\end{figure}
+
 %\subsection{PSP solar wind environment estimation}
@@
 
-Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12~days, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
-In the beginning of the mission median peak values of about  \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au} (\SI{9.86}{\Rs}).
+Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
+In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_e_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during 12 days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
-For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted).}
+	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12 days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
+For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
 	\label{fig:SPP_perihelia_prediction_e_plot}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_e_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during during 12 days in 2024 with PSP's nearest perihelion at \SI{0.0459}{\au}.
-For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted).}
+	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during during 12 days in 2024 with PSP's nearest perihelion at \SI{0.0459}{\au}.
+For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
 	\label{fig:SPP_perihelia_prediction_nearest_e_plot}
@@
 
-discuss high value zoom figures; read in Veselovsky2010\\
-
-The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS).\\
+\section{Discussion}
+\label{sec:discussion}
+The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS).
 The OMNI data is time-shifted to the nose of the Earth's bow shock.
-This leads to yearly solar distance variations of \SI{>2}{\percent} (cite?) as the Earth orbits the Sun.
-Furthermore, its orbit within the ecliptic leads to a yearly variation of \SI{+-7.2}{\degree} in heliospheric latitude.\\
-The HCS's position in latitude is highly variable around the solar equator \citep[p.~127~ff.?]{Schwenn1990}.\\
-
-Error estimation over the year (seasonal/monthly) -> we expect variations to be less than 5~\%\\
-
-%OMNI data is not corrected for solar distace. only available for 1-/5-min data\\
+This leads to yearly solar distance variations of \SI{>2}{\percent} as the Earth orbits the Sun.
+Error estimation over the year (seasonal) -> we expect variations to be less than \SI{5}{\%}.
+Furthermore, its orbit within the ecliptic leads to a yearly variation of \SI{+-7.2}{\degree} in heliospheric latitude.
+The HCS's position in latitude is highly variable around the solar equator \citep[p.~127~ff.?]{Schwenn1990}.
+-> error estimation?.
 
 %[limited parameter ranges... (minV: 171~km/s; Schwenn1983)]\\
-
-\section{Discussion}
-list of results:\\
-- empirical solar wind model for inner heliosphere within ecliptic\\
-- low velocity at 0.0459~au\\
-- slow/fast ratio SSN dependency\\
-- application validity of lognormal distributions\\
---> B inversion of frequency distribution\\
----> magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
-varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
-
-%solar wind -> structures\\
-\citet{Balogh1999} p.~162~ff (origin and formation of CIRs in inner heliosphere with Helios data; latitude V dependence)\\
-Balogh2009 (HMF review + inner heliosheath)\\
-Aschwanden2004, p.~29\\
-
-The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\
-The \citet{Parker1958} model of an isothermal expanding corona with a temperature of \SI{e6}{\K} and a critical radius of \SI{5.8}{R_s}.\\
-
-individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
-Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\
-
-The ratio of both varies with solar activity, e.g. 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use \citet{Bougeret1984} p.~498...\\
-
-larger influx from higher latitudes (see figure b))\\
-
-%critical surfaces
-approaching these regions, acceleration plays a role\\
-Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
-in direction to the Sun is at about \SI{2.5}{R_s} the source surface (Schatten1969)\\
-sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
-sonic point and slow solar wind origin \citep{Sheeley1997}\\
-% The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
-% L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
 
@@
 
+discuss results:\\
+- empirical solar wind model for inner heliosphere within ecliptic\\
+- low velocity at 0.0459~au\\
+- slow/fast ratio SSN dependency\\
+- application validity of lognormal distributions\\
+--> B inversion of frequency distribution\\
+---> magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
+varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
+
+The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between \SIrange{15}{30}{\Rs} (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose correct references...), up to which the solar wind is believed to be accelerated.\\
+The \citet{Parker1958} model of an isothermal expanding corona with a temperature of \SI{e6}{\K} and a critical radius of \SI{5.8}{\Rs}.\\
+
+individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
+Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\
+
+The ratio of both varies with solar activity, e.g., 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use \citet{Bougeret1984} p.~498...\\
+
+for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
+
+%critical surfaces
+approaching these regions, acceleration plays a role\\
+Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
+in direction to the Sun is at about \SI{2.5}{\Rs} the source surface (Schatten1969)\\
+sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
+sonic point and slow solar wind origin \citep{Sheeley1997}\\
+% The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
+% L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
+
+CMEs...\\
+
+%solar wind -> structures\\
+\citet{Balogh1999} p.~162~ff (origin and formation of CIRs in inner heliosphere with Helios data; latitude V dependence)\\
+Balogh2009 (HMF review + inner heliosheath)\\
+Aschwanden2004, p.~29\\
+
 \section{Summary and conclusions}
 
-Further investigations should be done into structure extrapolations; outward extension of model to Mars seems feasable...\\
+WISPR mission operations implications...\\
 
-The estimated solar wind median values during PSP’s first perihelion and the modeled values for PSP’s closest perihelia.
-The velocity and temperature values are clearly overestimated below ~20 Rs in comparison with existing observations.
-This empirical model shows that solar wind acceleration and heating processes below 20 Rs limit the simple back-extrapolation from existing in situ measurements.
+- further investigations should be done into structure extrapolations\\
+- outward extension of model seems feasable (e.g., to Mars)\\
+
+We estimated solar wind median values during PSP’s first perihelion and modeled the values for PSP’s closest perihelia.
+The velocity and temperature values are clearly overestimated below \SI{20}{\Rs} in comparison with existing observations.
+This empirical model shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.

### 2017-08-16 paperMVVB/sections/content.tex
summary; version without figures added

@@
 \section{Summary and conclusions}
+We obtained lognormal representations of the frequency distributions' shapes of the four key solar wind parameters magnetic field strength, proton velocity, density and temperature.
+We derived analytical relations for the parameters' solar activity dependencies and for their solar distance scaling.
+An empirical solar wind model was build from the combination of the obtained frequency distributions, SSN dependence relations and solar distance dependence functions, representing the solar wind's solar activity and distance behavior.
+This empirical model was fed with SSN predictions and extrapolated to the orbit of PSP.
+We estimated solar wind median values during PSP’s first perihelion and modeled the values for PSP’s closest perihelia.
+
+The velocity and temperature values are overestimated below \SI{20}{\Rs} in comparison with existing observations.
+This shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.\\
 
@@
 - outward extension of model seems feasable (e.g., to Mars)\\
-
-We estimated solar wind median values during PSP’s first perihelion and modeled the values for PSP’s closest perihelia.
-The velocity and temperature values are clearly overestimated below \SI{20}{\Rs} in comparison with existing observations.
-This empirical model shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.

### 2017-08-16 paperMVVB/sections/content.tex
some references

@@
 \section{Introduction}
-
 %solar wind beginnings
 From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun.
-With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1962 \citep{Neugebauer1966} \hl{+ ref.
-to Russian measurements}.
+With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1959 \citep{Gringauz1960,Neugebauer1966}.
 %in situ spacecraft
@@
 Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with Wind \hl{(ref.)}, ACE \hl{(ref.)} and DSCOVR \hl{(ref.)} still orbiting around the L1 point \SI{1.5}{million \km} ahead of Earth in the sunward direction.
+Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \hl{(ref.)}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \hl{(ref.)} or MESSENGER \hl{(ref.)}.
@@
 Even its first perihelion, 93~days after launch in 2018, will take PSP to an unprecedented distance of \SI{0.16}{\au} (\SI{35.7}{\Rs}).
-{\color{Red2} In comparison, the ESA Solar Orbiter mission with a planned launch in 2019 will have a closest perihelion of \SI{0.289}{\au} \hl{(ref.)}.}
+In comparison, the ESA Solar Orbiter mission with a planned launch in February 2019 will have its closest perihelia at \SI{0.28}{\au} \citep{Muller2013}.
 
@@
 Fast streams are found to originate from coronal holes as confirmed by Ulysses' out-of-ecliptic measurements \citep{McComas1998}.
-The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, {\color{red} such as ...intermittent reconnection at the top of streamers and pseudostreamers, coronal hole boundaries, ...
-(\hl{ref.}).} The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
-Embedded in the slow and fast solar wind streams are transient flows of coronal mass ejections (CMEs), the faster ones driving shock waves ahead \hl{(ref.)}.
+The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, such as intermittent reconnection at the top of helmet streamers and from coronal hole boundaries \citep{Kilpua2016}.
+The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
+Embedded in the slow and fast solar wind streams are transient flows of coronal mass ejections (CMEs), the faster ones driving shock waves ahead \citep{Gosling1974}.
 Their rate follows the solar activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
@@
 The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
-For instance the fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by \citet[\hl{p.~XX, Figure~XX}]{Bothmer2007}.
+For instance the fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
 Therefore the solar wind velocity, density and temperature maxima exhibit time-lags to the SSN maxima.

### 2017-08-21 paperMVVB/sections/content.tex
implementation discussion + summary

@@
 Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \hl{(ref.)}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
-Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \hl{(ref.)} or MESSENGER \hl{(ref.)}.
+Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
 Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
@@
 
-\hl{XXXXXXXXXXXXXXXXXXXXXXXX}\\
-
 \section{Discussion}
 \label{sec:discussion}
-The solar wind parameters vary with solar distance as well as with latitudinal separation from the heliospheric current sheet (HCS).
-The OMNI data is time-shifted to the nose of the Earth's bow shock.
-This leads to yearly solar distance variations of \SI{>2}{\percent} as the Earth orbits the Sun.
-Error estimation over the year (seasonal) -> we expect variations to be less than \SI{5}{\%}.
-Furthermore, its orbit within the ecliptic leads to a yearly variation of \SI{+-7.2}{\degree} in heliospheric latitude.
-The HCS's position in latitude is highly variable around the solar equator \citep[p.~127~ff.?]{Schwenn1990}.
--> error estimation?.
 
-%[limited parameter ranges... (minV: 171~km/s; Schwenn1983)]\\
+We started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by lognormally fitting the about 40~years of in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, velocity, density and temperature.
+The OMNI multi-satellite solar wind data is intercalibrated, covers almost five solar cycles and thus represents solar wind gathered at different phases of solar activity in the ecliptic plane.
+In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
+The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}.
+The herefrom derived power law fit functions were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years 2018--2025, i.e., for the prime mission phase that gets PSP to closest perihelia of 9.86~solar radii distance to the Sun.
+The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
+The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field {\color{red} , as shown by \hl{xxx (ref.)},} and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.
 
-%\subsection{Model validity and error sources}
-validity and estimation of error size outside of valid model range...\\
+However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+The from direct measurements differing velocity and temperature extrapolations below \hl{20~solar radii} indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and correlates with solar activity between \SI{15}{\Rs} in minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+
+In our study we have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
+The Helios solar wind measurements plotted over radial distance in \hl{Fig.~}\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot} show several extreme values far above the usual solar wind magnetic field strengths, velocities, densities, and temperatures likely to be associated with individual CMEs.
+{\color{red} The results by \hl{Srivastava et al.
+(2017)}} indicate that due to the solar wind drag the speeds of fast CMEs will commonly slow down substantially up to distances of \hl{40~solar radii}.
+Therefore, it is expected that PSP will encounter CMEs with much higher speeds than those observed during the Helios mission.
+Also, the magnetic field, density and temperature values are expected to be much larger than in the average solar wind in individual fast shock associated CME events.
+PSP will thus also substantially improve our understanding of the near-Sun evolution of CMEs and their expansion with radial distance.
+
+a\\
+
+note special velocity treatment with double lognormal fits\\
+
 derive heliocentric distance depending error...\\
-list simplifications/approximations...\\
 error estimation for general model and extreme value tendencies\\
-error sources:\\
-- extrapolation\\
-- lognormal model\\
-- SSN variance\\
-all estimates outside these boundaries are extrapolations with large uncertainties.\\
 
-discuss results:\\
-- empirical solar wind model for inner heliosphere within ecliptic\\
-- low velocity at 0.0459~au\\
-- slow/fast ratio SSN dependency\\
-- application validity of lognormal distributions\\
---> B inversion of frequency distribution\\
----> magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
+magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
 varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
 
-The near-Sun (PSP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between \SIrange{15}{30}{\Rs} (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose correct references...), up to which the solar wind is believed to be accelerated.\\
-The \citet{Parker1958} model of an isothermal expanding corona with a temperature of \SI{e6}{\K} and a critical radius of \SI{5.8}{\Rs}.\\
-
+slow/fast ratio SSN dependency\\
 individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
 Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\
-
 The ratio of both varies with solar activity, e.g., 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use \citet{Bougeret1984} p.~498...\\
-
 for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
 
-%critical surfaces
-approaching these regions, acceleration plays a role\\
-Alfvénic critical surface i.e. source surface (see Fox before 2.1)\\
-in direction to the Sun is at about \SI{2.5}{\Rs} the source surface (Schatten1969)\\
-sonic and Alfvénic critical point positions (see \citet{Sittler1999})\\
-sonic point and slow solar wind origin \citep{Sheeley1997}\\
-% The model of \citet{Sittler1999} is based on Skylab coronagraph and Ulysses data. it is a 2d semiempirical MHD model (time static)\\
-% L-> compare with their radial density function eq. (18a); B-field function eq. (19a+b); V(r) eq. (24); T(r)...\\
-
-CMEs...\\
-
-%solar wind -> structures\\
-\citet{Balogh1999} p.~162~ff (origin and formation of CIRs in inner heliosphere with Helios data; latitude V dependence)\\
-Balogh2009 (HMF review + inner heliosheath)\\
 Aschwanden2004, p.~29\\
 
-\section{Summary and conclusions}
-We obtained lognormal representations of the frequency distributions' shapes of the four key solar wind parameters magnetic field strength, proton velocity, density and temperature.
-We derived analytical relations for the parameters' solar activity dependencies and for their solar distance scaling.
-An empirical solar wind model was build from the combination of the obtained frequency distributions, SSN dependence relations and solar distance dependence functions, representing the solar wind's solar activity and distance behavior.
-This empirical model was fed with SSN predictions and extrapolated to the orbit of PSP.
-We estimated solar wind median values during PSP’s first perihelion and modeled the values for PSP’s closest perihelia.
+\section{Summary of the results}
+For the near-Earth solar wind OMNI data and the Helios~1 and 2 data, obtained over the distance range \SIrange{0.29}{0.98}{\au}, we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, density and proton temperature.
+The dependencies of these frequency distributions on the solar activity cycle and on radial distance to the Sun have been modeled with analytical relations and extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
+This empirical CGAUSS solar wind model for PSP, representing the solar wind’s solar activity and distance behavior, yields the following main results for the bulk solar wind:\\
+
+{\color{red}
+parameter relationships as bullets...\\
+
+Bmed(SSN,r) = ...\\
+V...\\
+give valid ranges [a--b]...\\
+We estimated solar wind median values during PSP’s first perihelion and the values for PSP’s first minimum perihelion of 9.86~Rs in 2024.\\
+}
 
@@
 
-WISPR mission operations implications...\\
+%Implications for WISPR mission operations and SoloHI on Solar Orbiter...
+The knowledge of the expected solar wind environment helps to optimize the WISPR and PSP preplanning of the science operations.
+This also applies for the Heliospheric Imager (SoloHI) onboard the Solar Orbiter spacecraft (Howard2013).\\
 
-- further investigations should be done into structure extrapolations\\
-- outward extension of model seems feasable (e.g., to Mars)\\
+\hl{To be moved into end of Sect. 5!}\\
+As the OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it the Earth orbits the Sun.\\
+{\color{red}
+The maximal solar wind parameter variation amplitudes over the year can thus be estimated from the derived power law exponents to about X \% for the m, to X \% for the v, ...\\
+calculate them and put them into Tab.3.\\
+The error estimation over the year caused by this varying radial difference can be expected to be smaller than 5 \% derived from investigation of the power law exponents of the solar wind parameters.\\
+}
+
+\hl{To be moved into Sect. 5!}\\
+\citet{Bruno1986,Balogh1999} have pointed out, that the solar wind parameters also vary with latitudinal separation from the heliospheric current sheet (HCS).
+Its The HCS’s position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
+However, the additional analysis of but this aspect is beyond the scope of this study.\\	%Balogh et al.
+(p.~162, 1999);	 (Schwenn 1990, p.~126)
+\hl{-> error estimation?}\\

### 2017-08-21 paperMVVB/sections/content.tex
fig 9 and references

@@
 Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \hl{(ref.)}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
@@
 %about OMNI data
-The OMNI~2 data set \citep{King2005} combines solar wind magnetic field and plasma data collected by various satellites since 1963.
+The OMNI~2 data set \citep{King2005} combines solar wind magnetic field and plasma data collected by various satellites since 1963, currently by WIND and by ACE.
 This intercalibrated multi-spacecraft data is time-shifted to the nose of the Earth’s bow shock.
@@
 Again, the solar wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle and basically maintain characteristic speeds (\hl{ref.}), we keep the two velocity components' positions constant and vary instead their balance with the SSN:
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle we keep the two velocity components' positions constant and vary instead their balance with the SSN:
 \begin{align}
@@
 The crossing distances indicate where the median and mean fits intersect each other.
-The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_b}.}
+The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
 	\label{tab:mean_median_fit_parameter}
@@
 This established solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The variation of yearly power law fit exponents are shown in Fig.~\ref{fig:yearly_gradients_b} together with the yearly SSN for the time period \numrange{1974}{1982}.
+The variation of yearly power law fit exponents are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
 It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature.
+exponents
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_b.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}
 	\caption{Helios yearly variation of the solar wind parameters' fit exponents together with the SIDC 13-month smoothed monthly SSN.
-The weighted standard deviations are indicated with dotted lines.
-In this plot the year 1974 is omitted because of merely 21~days since Helios launch that year.}
-	\label{fig:yearly_gradients_b}
+The weighted standard deviations and average values for all years are indicated by the shaded areas.
+In this plot the 21~days since Helios launch in the year 1974 are omitted because a distance range of merely \SIrange{0.95}{0.98}{\au} was covered that year.}
+	\label{fig:yearly_gradients_c}
 \end{figure}
+%yearly variation of the solar wind parameters' average fit function exponents
 However, for simplicity we assume, that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$, summarized in Table~\ref{tab:mean_median_fit_parameter}, as relative uncertainties.
@@
 In our study we have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
-The Helios solar wind measurements plotted over radial distance in \hl{Fig.~}\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot} show several extreme values far above the usual solar wind magnetic field strengths, velocities, densities, and temperatures likely to be associated with individual CMEs.
-{\color{red} The results by \hl{Srivastava et al.
-(2017)}} indicate that due to the solar wind drag the speeds of fast CMEs will commonly slow down substantially up to distances of \hl{40~solar radii}.
+The Helios solar wind measurements plotted over radial distance in \hl{Fig.~}\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot} show several extreme values far above the usual solar wind velocities likely to be associated with individual CMEs.
+The results by \citet{Sachdeva2017} indicate that due to the prevailing of solar wind drag the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
 Therefore, it is expected that PSP will encounter CMEs with much higher speeds than those observed during the Helios mission.
@@
 note special velocity treatment with double lognormal fits\\
+slow/fast streams basically maintain characteristic speeds with solar cycle\\
 
@@
 for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
-
-Aschwanden2004, p.~29\\
 

### 2017-08-22 paperMVVB/sections/content.tex
seasonal variation

@@
 		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
-		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.005\\
+		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
 		\hline
@@
 	\caption{Fit coefficients from the single lognormal power function, respectively double lognormal for the velocity from the combined Helios data.
-The errors in brackets are the estimated standard deviations of the fit parameters.}
+The errors in brackets are the estimated standard deviations of the fit parameters.
+The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
 	\label{tab:extrapolation_model_fit_parameters}
@@
 	S[table-format = +1.4(2)]
-	S[table-format = 1.3(2)]}
+	S[table-format = 1.3(2)]
+	S[table-format = 1.2]}
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
-			&	&\multicolumn{1}{c}{$d'_\text{med}$}	&\multicolumn{1}{c}{$d'_\text{avg}$}	&\multicolumn{1}{c}{$e'$}	&$c'$\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{Seasonal variation}\\
+			&	&\multicolumn{1}{c}{$d'_\text{med}$}	&\multicolumn{1}{c}{$d'_\text{avg}$}	&\multicolumn{1}{c}{$e'$}	&$c'$	&\multicolumn{1}{c}{$\Delta d$ [\%]}\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}\\
-		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}\\
-		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}\\
+		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
+		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
+		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\
 		\hline
-		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}\\
-			&$W''_2$	&5.26(13)	&5.42(11)	&	&\\
-		\cline{2-6}
-		\multicolumn{2}{r}{$W''_\text{II}$}	&4.13(13)\tablefootmark{b}	&4.47(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
+			&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\
+		\cline{2-7}
+		\multicolumn{2}{r}{$W''_\text{II}$}	&4.13(13)\tablefootmark{b}	&4.47(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
 		\hline
@@
 % median = 413.33
+%
+% Yearly Earth distance variations from Earth_orbit_variation_impact_estimate.ods
 
@@
 In order to estimate the solar wind environment for the PSP orbit, we combine the results from the solar wind frequency distributions’ solar activity relationships and their distance dependencies derived from the OMNI and Helios data.
-The result is an empirical solar wind model for the inner heliosphere which will then be extrapolated to the PSP orbit in Sec.~\ref{sec:model_extrapolation_to_psp_orbit}.
+The result is an empirical solar wind model for the inner heliosphere which will then be extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
@@
 The variation of yearly power law fit exponents are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
-It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature.
-exponents
+It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature exponents.
 \begin{figure}
@@
 Thus we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
+
+This model averages over seasonal variations because it is based on yearly data.
+As the OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
+The resulting maximal solar wind parameter variation amplitudes over the year can thus be derived from the derived power law exponents.
+They are estimated to be smaller than \SI{4}{\percent} as seen in Tab.~\ref{tab:extrapolation_model_fit_parameters}.
+\citet{Bruno1986,Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet (HCS).
+Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
+However, the additional analysis of this aspect is beyond the scope of this study.	%Balogh et al.
+(p.~162, 1999);	 (Schwenn 1990, p.~126)
 
@@
 This also applies for the Heliospheric Imager (SoloHI) onboard the Solar Orbiter spacecraft (Howard2013).\\
-
-\hl{To be moved into end of Sect. 5!}\\
-As the OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it the Earth orbits the Sun.\\
-{\color{red}
-The maximal solar wind parameter variation amplitudes over the year can thus be estimated from the derived power law exponents to about X \% for the m, to X \% for the v, ...\\
-calculate them and put them into Tab.3.\\
-The error estimation over the year caused by this varying radial difference can be expected to be smaller than 5 \% derived from investigation of the power law exponents of the solar wind parameters.\\
-}
-
-\hl{To be moved into Sect. 5!}\\
-\citet{Bruno1986,Balogh1999} have pointed out, that the solar wind parameters also vary with latitudinal separation from the heliospheric current sheet (HCS).
-Its The HCS’s position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
-However, the additional analysis of but this aspect is beyond the scope of this study.\\	%Balogh et al.
-(p.~162, 1999);	 (Schwenn 1990, p.~126)
-\hl{-> error estimation?}\\

### 2017-08-23 paperMVVB/sections/abstract.tex
implementation discussion + summary
fig 7+10, summary bullets

@@
 
-\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; received date; accepted date}
+\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; received date; accepted date}
 
@@
 {The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its mission duration.
-The estimated solar wind median values during PSP's first perihelion \hl{are} \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
-The modeled values for PSP’s closest perihelia \hl{are} \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}, where these velocity and temperature values are clearly overestimated in comparison with existing observations.}	%results
-{This empirical model shows that solar wind acceleration and heating processes \hl{below 20}~solar radii limit a simple back-extrapolation from existing in situ measurements.}	%conclusions
+The estimated solar wind median values during PSP's first perihelion are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
+The modeled values for PSP’s closest perihelia are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}, where these velocity and temperature values are clearly overestimated in comparison with existing observations.}	%results
+{This empirical model shows that solar wind acceleration and heating processes below about 20~solar radii limit a simple back-extrapolation from existing in situ measurements.}	%conclusions
 

### 2017-08-23 paperMVVB/sections/content.tex
fig 7+10, summary bullets

@@
 It is not known which specific solar wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar wind parameters from existing solar wind measurements and take solar cycle dependencies into account.
-As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \textit{density}, \textit{temperature} and \textit{magnetic field strength}.
+As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \textit{magnetic field strength}, \textit{density} and \textit{temperature}.
 Furthermore, the bulk flow \textit{velocity} is the defining parameter of the two types of solar wind.
 Solar wind quantities, like flux densities, mass flux and plasma beta, can directly be derived from these four parameters.
+In the analyses we treat the solar wind as a proton plasma---the average helium abundance is about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
 
@@
 
-The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set, see Fig.~\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}.
+The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set, see Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.
 Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
@@
 %crossing distances
-Fig.~\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot} shows the radial dependence of the solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} and the mean and median values and their respective power law fits.
+Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} shows the radial dependence of the solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} and the mean and median values and their respective power law fits.
 The mean and median velocity fit exponents are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_skip_pdfcairo_plot.pdf}
+	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_b_skip.pdf}
 	\caption{Helios hourly data plots of the four solar wind parameters over solar distance.
 The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well.
-The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.}
-	\label{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot}
+The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
+The maximal velocities of CME events larger than \SI{800}{\km\per\s} are indicated with circles.}
+	\label{fig:radial_fit_4_thesis_light_b_skip}
 \end{figure*}
@@
 
-We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}.
+We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}.
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_b_plot.pdf}
-	\caption{Radial extrapolation of the solar wind parameters to the PSP orbit region.
+	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_d_plot.pdf}
+	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
 The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the extreme cases of solar minimum (SSN = 0) and maximum (SSN = 200).
 Note that there is a time lag to the SSN depending on the solar wind parameter.
-The magnetic field radial dependence is slightly flatter than the analytic DQCS model for solar minimum which \citet{Banaszkiewicz1998} derived.
-\hl{Below} \SI{20}{\Rs} the slow wind velocity is overestimated in comparison to the measurements from \citet{Wang2000}) and \citet{Sheeley1997}.
-Down to PSP's perihelion the density is in good agreement with the model from \citet{Leblanc1998}.
-to 1-column...?}
-	\label{fig:sw_extrapolation_ssn_b_plot}
+Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \citet{Wang2000} and \citet{Sheeley1997}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
+	\label{fig:sw_extrapolation_ssn_d_plot}
 \end{figure*}
@@
 The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of 0.
-Taking a SSN of 200 increases the value to \SI{69}{\nT} at \SI{0.25}{\au} and \SI{1152}{\nT} at \SI{0.046}{\au}.
-Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed a dipole plus quadrupole plus current sheet (DQCS) model.
+Taking a SSN of 200 increases the values to \SI{69}{\nT} and \SI{1152}{\nT}.
+Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
 This difference is arguably due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) with solar distance changing shape of the frequency distribution, which for smaller distances deviates more from the model’s lognormal distribution.
@@
 Whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
-Comparing the results with those found by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated velocity values for distances \hl{below} \SI{20}{\Rs}.
-They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model \citep{Parker1958}.
+Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar wind velocity values for distances below about \SI{20}{\Rs}.
+They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model from \citet{Parker1958}.
 Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates and thus PSP will measure solar wind acceleration processes \hl{below} \SI{30}{\Rs} \citep{Sheeley1997,McComas2008}.
@@
 The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} for a SSN of 0 and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
-Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \hl{may overestimate} the extrapolated temperatures at the PSP perihelion distance.
-{\color{red} The results can be compared to...}
+Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model overestimate the extrapolated temperatures at the PSP perihelion distance.
 
@@
 We started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by lognormally fitting the about 40~years of in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, velocity, density and temperature.
-The OMNI multi-satellite solar wind data is intercalibrated, covers almost five solar cycles and thus represents solar wind gathered at different phases of solar activity in the ecliptic plane.
+The OMNI multi-spacecraft solar wind data is intercalibrated and covers almost five solar cycles.
+It thus represents solar wind gathered at different phases of solar activity in the ecliptic plane.
 In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
 The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}.
-The herefrom derived power law fit functions were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years 2018--2025, i.e., for the prime mission phase that gets PSP to closest perihelia of 9.86~solar radii distance to the Sun.
+The herefrom derived power law fit functions were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years 2018--2025, i.e., for the prime mission phase that gets PSP to closest perihelia of 9.86~solar radii distance.
 The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
 Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
-The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field {\color{red} , as shown by \hl{xxx (ref.)},} and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.
+The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.
 
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-The from direct measurements differing velocity and temperature extrapolations below \hl{20~solar radii} indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_b_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and correlates with solar activity between \SI{15}{\Rs} in minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
 
 In our study we have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
-The Helios solar wind measurements plotted over radial distance in \hl{Fig.~}\ref{fig:radial_fit_4_thesis_light_skip_pdfcairo_plot} show several extreme values far above the usual solar wind velocities likely to be associated with individual CMEs.
+The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, likely to be associated with individual CMEs.
 The results by \citet{Sachdeva2017} indicate that due to the prevailing of solar wind drag the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
@@
 Also, the magnetic field, density and temperature values are expected to be much larger than in the average solar wind in individual fast shock associated CME events.
-PSP will thus also substantially improve our understanding of the near-Sun evolution of CMEs and their expansion with radial distance.
+PSP will thus also substantially improve our understanding of the near-Sun evolution of CMEs and their expansion with radial distance.\\
 
-a\\
-
+{\color{red}
 note special velocity treatment with double lognormal fits\\
@@
 for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
+}
 
-\section{Summary of the results}
-For the near-Earth solar wind OMNI data and the Helios~1 and 2 data, obtained over the distance range \SIrange{0.29}{0.98}{\au}, we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, density and proton temperature.
+\section{Summary}
+For the near-Earth solar wind OMNI data and the Helios~1 and 2 data, obtained over the distance range \SIrange{0.29}{0.98}{\au}, we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature.
 The dependencies of these frequency distributions on the solar activity cycle and on radial distance to the Sun have been modeled with analytical relations and extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
-This empirical CGAUSS solar wind model for PSP, representing the solar wind’s solar activity and distance behavior, yields the following main results for the bulk solar wind:\\
+This empirical CGAUSS solar wind model for PSP, representing the solar wind’s solar activity and distance behavior, yields estimations for the solar wind median values at PSP’s first perihelion in 2018 and at PSP’s closest perihelion in 2024.
+The model yields the following main results for the bulk solar wind parameters:
+\begin{itemize}
+	\item The empirical dependency of the magnetic field strength median value on solar activity and radial distance is
+	\begin{align}
+		B_\text{med}(ssn,r) = (\SI{0.0131}{\nT} \cdot ssn + \SI{4.29}{\nT}) \cdot r^{-1.66}	\,.
+	\end{align}
+	This approximation appears to be valid for PSP's full distance range, however near its closest perihelion the actual median values might lie within \SI{20}{\%} higher.
+The estimated median values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+	\item Averaging over fast and slow solar wind streams, the derived median velocity value dependence is
+	\begin{align}
+		v_\text{med}(ssn,r) = \left(\SI{1.31}{\km\per\s} \cdot ssn + \SI{429}{\km\per\s}\right) \cdot r^{0.099}	\,.
+	\end{align}
+	This relation is valid above about \SI{20}{\Rs}, below this solar distance it overestimates the actual velocities obtained from remote measurements.
+The estimated median values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+	\item The density relation is found to be
+	\begin{align}
+		n_\text{med}(ssn,r) = \left(\SI{0.0038}{\per\cm\cubed} \cdot ssn + \SI{4.50}{\per\cm\cubed}\right) \cdot r^{-2.11}	\,.
+	\end{align}
+	It seems valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+The estimated median values for PSP's first and closest perihelion are \SI{4015}{\per\cm\cubed} and \SI{9733}{\per\cm\cubed}.
+	\item The derived correlation function for the temperature is
+	\begin{align}
+		T_\text{med}(ssn,r) = (\SI{197}{\K} \cdot ssn + \SI{57300}{\K}) \cdot r^{-1.10}	\,.
+	\end{align}
+	Near PSP's perihelion the validity of this relation is difficult to evaluate. The estimated median values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+\end{itemize}
 
 {\color{red}
-parameter relationships as bullets...\\
-
-Bmed(SSN,r) = ...\\
-V...\\
-give valid ranges [a--b]...\\
-We estimated solar wind median values during PSP’s first perihelion and the values for PSP’s first minimum perihelion of 9.86~Rs in 2024.\\
-}
-
 The velocity and temperature values are overestimated below \SI{20}{\Rs} in comparison with existing observations.
 This shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.\\
+}
 
@@
 The knowledge of the expected solar wind environment helps to optimize the WISPR and PSP preplanning of the science operations.
-This also applies for the Heliospheric Imager (SoloHI) onboard the Solar Orbiter spacecraft (Howard2013).\\
+This also applies for the Heliospheric Imager (SoloHI) onboard the Solar Orbiter spacecraft \citep{Howard2013}.

### 2017-08-24 paperMVVB/sections/abstract.tex
velocity treatment in discussion and summary

@@
 The estimated solar wind median values during PSP's first perihelion are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
-The modeled values for PSP’s closest perihelia are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}, where these velocity and temperature values are clearly overestimated in comparison with existing observations.}	%results
-{This empirical model shows that solar wind acceleration and heating processes below about 20~solar radii limit a simple back-extrapolation from existing in situ measurements.}	%conclusions
+The modeled values for PSP’s closest perihelia are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}, where these velocity and temperature values are clearly overestimated in comparison with existing observations.
+This empirical model shows that solar wind acceleration and heating processes below about 20~solar radii limit a simple back-extrapolation from existing in situ measurements.}	%results
+{}	%conclusions
 

### 2017-08-24 paperMVVB/sections/content.tex
velocity treatment in discussion and summary

@@
 
-{\color{red} discuss high value zoom figures; read in Veselovsky2010}
+%{\color{red} discuss high value zoom figures; read in Veselovsky2010}
 
@@
 This behavior is expected because of the distance independent shape approximation applied.
-The velocity and temperature models’ upper values show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The velocity model's with distance increasing high velocity tail comes from using the same exponent for both slow and fast components.
+This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
+%\citep{Sanchez-Diaz2016} p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction)
 
@@
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
-The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the extreme cases of solar minimum (SSN = 0) and maximum (SSN = 200).
+The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas).
 Note that there is a time lag to the SSN depending on the solar wind parameter.
@@
 They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model from \citet{Parker1958}.
-Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates and thus PSP will measure solar wind acceleration processes \hl{below} \SI{30}{\Rs} \citep{Sheeley1997,McComas2008}.
+Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates, thus PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
 
@@
 \label{sec:discussion}
-
 We started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by lognormally fitting the about 40~years of in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, velocity, density and temperature.
@@
 The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and its position correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
 
-In our study we have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
+Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
+Each velocity part is fitted with a lognormal function, which allows for the overlap of both velocity ranges.
+
+We have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
 The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, likely to be associated with individual CMEs.
@@
 Also, the magnetic field, density and temperature values are expected to be much larger than in the average solar wind in individual fast shock associated CME events.
-PSP will thus also substantially improve our understanding of the near-Sun evolution of CMEs and their expansion with radial distance.\\
+PSP will thus also substantially improve our understanding of the near-Sun evolution of CMEs and their expansion with radial distance.
 
-{\color{red}
-note special velocity treatment with double lognormal fits\\
-slow/fast streams basically maintain characteristic speeds with solar cycle\\
+%derive heliocentric distance depending error...\\
+%error estimation for general model and extreme value tendencies\\
 
-derive heliocentric distance depending error...\\
-error estimation for general model and extreme value tendencies\\
+%magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
+%varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
 
-magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
-varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
-
-slow/fast ratio SSN dependency\\
-individual velocity part discussion -> there is no specific velocity threshold between slow and fast solar wind types, the velocity ranges of both types overlap.\\
-Not only the slowest wind but also the fastest wind is expected to converge to the average speed (Sanchez-Diaz2016 p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction).\\
-The ratio of both varies with solar activity, e.g., 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use \citet{Bougeret1984} p.~498...\\
-for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
-}
+%slow/fast streams basically maintain characteristic speeds with solar cycle; slow/fast ratio SSN dependency\\
+%for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
+%The ratio of both varies with solar activity, e.g., 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use citet{Bougeret1984} p.~498...\\
 
 \section{Summary}
+\label{sec:summary}
 For the near-Earth solar wind OMNI data and the Helios~1 and 2 data, obtained over the distance range \SIrange{0.29}{0.98}{\au}, we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature.
 The dependencies of these frequency distributions on the solar activity cycle and on radial distance to the Sun have been modeled with analytical relations and extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
-This empirical CGAUSS solar wind model for PSP, representing the solar wind’s solar activity and distance behavior, yields estimations for the solar wind median values at PSP’s first perihelion in 2018 and at PSP’s closest perihelion in 2024.
+This empirical CGAUSS solar wind model for PSP, representing the solar wind’s solar activity and distance behavior, yields estimations for the solar wind median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelion in 2024 at \SI{0.046}{\au}.
 The model yields the following main results for the bulk solar wind parameters:
@@
 The estimated median values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
-	\item Averaging over fast and slow solar wind streams, the derived median velocity value dependence is
+	\item The radial dependency of the median velocity value for slow solar wind is
 	\begin{align}
-		v_\text{med}(ssn,r) = \left(\SI{1.31}{\km\per\s} \cdot ssn + \SI{429}{\km\per\s}\right) \cdot r^{0.099}	\,.
+		v_\text{slow}(r) &= \SI{363}{\km\per\s} \cdot r^{0.099}
+		\intertext{and that for fast solar wind is}
+		v_\text{fast}(r) &= \SI{483}{\km\per\s} \cdot r^{0.099}	\,.
 	\end{align}
-	This relation is valid above about \SI{20}{\Rs}, below this solar distance it overestimates the actual velocities obtained from remote measurements.
-The estimated median values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+	These relations are valid above about \SI{20}{\Rs}, below this solar distance they overestimate the actual velocities obtained from remote measurements.
+Their combined frequency distribution (\ref{eq:double_lognormal_fit_function}) is balanced by $c(ssn) = -0.00180 \cdot ssn + 0.64$, that is, at solar minimum ($ssn = 0$) the slow wind has a share of \SI{64}{\%}, dropping to only \SI{28}{\%} during maximum ($ssn = 200$).
+The calculated median values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
 	\item The density relation is found to be
@@
 	\end{align}
-	Near PSP's perihelion the validity of this relation is difficult to evaluate. The estimated median values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+	The evaluation of the validity of this relation shows, that the temperature values near PSP's perihelion are too high in comparison to coronal measurements.
+The estimated median values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}
 
-{\color{red}
 The velocity and temperature values are overestimated below \SI{20}{\Rs} in comparison with existing observations.
-This shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.\\
-}
+This shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.
 

### 2017-08-24 paperMVVB/sections/content.tex
fig 10 fix; added version without figures

@@
 
-We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}.
+We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_d_plot.pdf}
+	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_e_plot.pdf}
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
@@
 Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \citet{Wang2000} and \citet{Sheeley1997}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
-	\label{fig:sw_extrapolation_ssn_d_plot}
+	\label{fig:sw_extrapolation_ssn_e_plot}
 \end{figure*}
@@
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_d_plot}).
+The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
 The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and its position correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).

### 2017-08-24 paperMVVB/sections/abstract.tex
referee version; vb edits summary + abstract; mvcolor

@@
 
-\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; received date; accepted date}
+\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; fourth changes 24 August 2017; received date; accepted date}
 

### 2017-08-25 paperMVVB/sections/abstract.tex
edits implemented

@@
 \abstract
-{In view of the planned near-Sun spacecraft mission Parker~Solar~Probe (PSP) (formerly Solar~Probe~Plus) the solar wind environment for its prime mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data.
-The PSP mission will be humanity's first in situ exploration of the solar corona.
-Visiting this yet uncharted region is of special interest, because it will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
-The solar wind extrapolation of this study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
-{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data.
+{The Parker Solar Probe (PSP) (formerly Solar Probe Plus) mission will be humanity’s first in situ exploration of the solar corona with closest perihelia at \num{9.86}~solar radii (\si{\Rs}) distance to the Sun.
+It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
+The scope of this study is to model the solar wind environment for PSP’s unprecedented distances during its prime mission phase during the years \numrange{2018}{2025}.
+The study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
+{We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data.
 The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
-The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au}.
-The solar wind model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters PSP will encounter during its mission.}	%aims
-{The model covers the solar wind's magnetic field strength and its plasma parameters proton velocity, density and temperature.
-Their individual frequency distributions are represented with lognormal functions.
-In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part.
-The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions.
-We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data.
-Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
-Finally, by combining the found solar cycle and solar distance relations, we obtain a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic region.}	%methods
-{The inclusion of SSN predictions and the extrapolation to the PSP perihelion region enables us to estimate the solar wind environment for PSP's planned trajectory during its mission duration.
-The estimated solar wind median values during PSP's first perihelion are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
-The modeled values for PSP’s closest perihelia are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}, where these velocity and temperature values are clearly overestimated in comparison with existing observations.
-This empirical model shows that solar wind acceleration and heating processes below about 20~solar radii limit a simple back-extrapolation from existing in situ measurements.}	%results
+The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au} over more than five solar cycles.
+The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar wind parameters on solar activity and to forecast their properties for the PSP mission.}	%aims
+{The frequency distributions for the solar wind key parameters magnetic field strength, proton velocity, density and temperature are represented by lognormal functions.
+In addition, we consider the velocity distribution’s bi-componental shape, consisting of a slower and a faster part.
+Functional relations to solar activity are compiled with use of the OMNI data by correlating and fitting the frequency distributions with the SSN.
+Further, based on the combined data set from both Helios probes, the parameters’ frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
+Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
+Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
+{The CGAUSS empirical solar wind model for PSP yields dependencies of the solar wind parameters on solar activity and radial distance.
+The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
+The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}.
+Though, the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations.
+Thus, PSP is expected to directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.}	%results
 {}	%conclusions

### 2017-08-25 paperMVVB/sections/acknowledgments.tex
edits implemented

@@
 \begin{acknowledgements}
-	This work was done within the scope of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS), funded by the German Aerospace Center (DLR) under grant 50~OL~1601.\\
+	The authors acknowledge support of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS) project for WISPR by the German Aerospace Center (DLR) under grant 50~OL~1601 as national contribution to the Parker Solar Probe mission.
 The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data.
-The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive (NSSDCA) and the Space Physics Data Facility (SPDF) at NASA's Goddard Space Flight Center (GSFC).\\
-	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
-	The PSP SPICE kernel was kindly provided by Angelos~Vourlidas.\\
+The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive (NSSDCA) and the Space Physics Data Facility (SPDF) at NASA's Goddard Space Flight Center (GSFC).
+Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
+The PSP SPICE kernel was kindly provided by Angelos~Vourlidas.
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.

### 2017-08-25 paperMVVB/sections/content.tex
edits implemented

@@
 \label{sec:summary}
-For the near-Earth solar wind OMNI data and the Helios~1 and 2 data, obtained over the distance range \SIrange{0.29}{0.98}{\au}, we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature.
-The dependencies of these frequency distributions on the solar activity cycle and on radial distance to the Sun have been modeled with analytical relations and extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
-This empirical CGAUSS solar wind model for PSP, representing the solar wind’s solar activity and distance behavior, yields estimations for the solar wind median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelion in 2024 at \SI{0.046}{\au}.
-The model yields the following main results for the bulk solar wind parameters:
+The scientific objective of this study, being part of the German contribution Coronagraphic German and US Solar Probe Plus Survey (CGAUSS) to the Wide field Imager for Solar Probe (WISPR), is to model the solar wind environment for the Parker Solar Probe mission (formerly Solar probe Plus) to be launched mid 2018.
+
+For this purpose we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature for the near-Earth solar wind OMNI data, and the Helios~1 and 2 data obtained over the solar distance range \SIrange{0.29}{0.98}{\au}.
+The dependencies of these frequency distributions on solar activity, as measured by the international sunspot number, and on radial distance to the Sun were modeled with analytical relations and then extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
+With the resulting CGAUSS empirical solar wind model for PSP the following main results for the bulk solar wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
 \begin{itemize}
-	\item The empirical dependency of the magnetic field strength median value on solar activity and radial distance is
+	\item The dependency of the magnetic field strength median value on solar activity and radial distance is:
 	\begin{align}
@@
 	\end{align}
-	This approximation appears to be valid for PSP's full distance range, however near its closest perihelion the actual median values might lie within \SI{20}{\%} higher.
-The estimated median values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
-	\item The radial dependency of the median velocity value for slow solar wind is
+	This approximation seems valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
+	\item The estimated  magnetic field strength values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.	
+	\item The radial dependencies of the proton velocity median values for slow and fast solar wind are:
 	\begin{align}
-		v_\text{slow}(r) &= \SI{363}{\km\per\s} \cdot r^{0.099}
-		\intertext{and that for fast solar wind is}
+		v_\text{slow}(r) &= \SI{363}{\km\per\s} \cdot r^{0.099}	\,,\\
+%		\intertext{and}
 		v_\text{fast}(r) &= \SI{483}{\km\per\s} \cdot r^{0.099}	\,.
 	\end{align}
-	These relations are valid above about \SI{20}{\Rs}, below this solar distance they overestimate the actual velocities obtained from remote measurements.
-Their combined frequency distribution (\ref{eq:double_lognormal_fit_function}) is balanced by $c(ssn) = -0.00180 \cdot ssn + 0.64$, that is, at solar minimum ($ssn = 0$) the slow wind has a share of \SI{64}{\%}, dropping to only \SI{28}{\%} during maximum ($ssn = 200$).
-The calculated median values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
-	\item The density relation is found to be
+	These relations appear valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
+	\item The calculated median velocity values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+
+	\item The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity, their balance was found to be $c(ssn) = -0.00180 \cdot ssn + 0.64$.
+Thus, at solar minimum with sunspot number around 0 the slow wind contributes about \SI{64}{\%} and dropping to \SI{28}{\%} during solar maximum conditions with sunspot numbers around 200.
+	\item The median proton density relation is found to be:
 	\begin{align}
@@
 	\end{align}
-	It seems valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-The estimated median values for PSP's first and closest perihelion are \SI{4015}{\per\cm\cubed} and \SI{9733}{\per\cm\cubed}.
-	\item The derived correlation function for the temperature is
+	This relation seems valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+	\item The estimated density values for PSP's first and closest perihelion are \SI{4015}{\per\cm\cubed} and \SI{9733}{\per\cm\cubed}.
+	\item The derived correlation function for the median proton temperature is:
 	\begin{align}
@@
 	\end{align}
-	The evaluation of the validity of this relation shows, that the temperature values near PSP's perihelion are too high in comparison to coronal measurements.
-The estimated median values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+	Around PSP’s perihelion this relation seems to provide too high temperature values in comparison to coronal measurements.
+	\item The estimated temperature values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}
-
-The velocity and temperature values are overestimated below \SI{20}{\Rs} in comparison with existing observations.
-This shows that solar wind acceleration and heating processes below \SI{20}{\Rs} limit the simple back-extrapolation from existing in situ measurements.
+The overestimation of the extrapolated velocity and temperature values at distances below \SI{20}{\Rs} indicate the occurrence of solar wind acceleration and heating processes, which PSP will thus be able to directly measure as planned.
 
 %Implications for WISPR mission operations and SoloHI on Solar Orbiter...
-The knowledge of the expected solar wind environment helps to optimize the WISPR and PSP preplanning of the science operations.
-This also applies for the Heliospheric Imager (SoloHI) onboard the Solar Orbiter spacecraft \citep{Howard2013}.
+The results of the modeled solar wind environment will be useful to help optimize the WISPR and in situ instrument science plannings and PSP mission operations.
+This also applies for the Heliospheric Imager (SoloHI) \citep{Howard2013} and the in situ instruments on board the Solar Orbiter spacecraft.

### 2017-10-06 paperMVVB_referee/referee_report_responses.txt
highlighted referee comments; notes in report

Referee Report

This paper discusses a method of using OMNI and Helios solar wind data to estimate the solar wind parameters that might be expected during the upcoming Parker Solar Probe mission. It includes an estimate of how these parameters might vary with solar cycle, though this is a relatively small correction, and the likely sunspot number during the mission is anyway highly uncertain. The analysis appears to be thorough, retaining information on the log-normal distribution of the parameters that is used to produce “model” representations of the distributions and their variation during the solar cycle. However, in the end, this information isn’t used in the predictions at PSP, where only median values are considered. It’s also not clear whether this type of analysis has any advantage over say a simple-minded approach where you use the radial dependence of averaged Helios values to propagate averaged 1 AU values, perhaps taken at different times in the solar cycle, down to the PSP orbit. My suspicion is that the results might not be all that different, but the authors might like to address this point. The extrapolated values do appear to be fairly consistent with previous estimates of near Sun parameters, and deviations, e.g. in the speed profile can be plausibly accounted for, so the results appear to be reasonable.

- 
+ add perihelia figures of distributions
+ ...

Some steps in the procedure could be explained more clearly in the text, as noted below, and the tables are rather cryptic since the meaning of the various parameters is not always clear. If they are fit parameters, it would be helpful to state the function that is being fitted in the table. There are conclusions and summary sections that both, yet again, go through the analysis procedure, which is unnecessary. They could be combined. There are also useful functions that give the radial dependences of the parameters that are only shown in the summary section. They could be included in the main results section.

- 
+ link the fit equations in table captions
+ ...

The English is reasonable overall, but there are a number of cases where a long phrase is used as an adjective. Suggestions have been made to rephrase these sentences.

Overall, I anticipate that the paper will be acceptable for publication after the comments in this review are considered.

Specific Points:

Page 2, Results, line 5: Suggest: Since the modeled velocity and temperature values below about 20 Rs appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below 20 Rs as planned.

+ highlighted
+ can be adopted

Introduction, line 8: “Until today” is unnecessary – suggest removing. SOHO is also at L1 and returns solar wind observations from CELIAS. But maybe it’s not necessary to list the spacecraft, especially as other spacecraft not listed contributed earlier observations to OMNI.

+ highlighted
+ can be removed
+ highlighted
+ add SOHO

Line 15: Suggest: The in-situ solar wind measurements closest to the Sun to date were made by ...

+ highlighted
+ can be adopted

Line 16: Suggest: Helios 1, launched in 1974, reached distances… au. Helios 2, launched two years later, approached the Sun as close as 0.29 au.

+ highlighted
+ can be adopted

Page 6, Table 1:

Suggest writing the units together with the parameters in the first column, e.g. “Magnetic field (nT)”, rather than in a table footnote.

+ highlighted
+ can be adopted

I don’t really understand what the numbers in brackets (“estimated standard deviations”) represent. Why are they much larger than the parameter values and whole numbers?

+ highlighted
+ highlighted
+ explain both

How are the mean absolute errors and sums of absolute errors defined?

+ highlighted
+ explain

Page 7, Figure 1 caption, last sentence, suggest: show zoomed-in views of the high value tails of the distributions.

+ highlighted
+ can be adopted
+ change in fig 2 too

Line 5 below caption: Supporting reference or other evidence that the extreme values are associated with “CME events” (ICMEs?)?

+ highlighted
+ explaining sentence and reference

Line 7: Is this “overestimation” because [I]CMEs have abnormally low, not high, temperatures?

+ highlighted
+ v not T, look into it

Page 8, last paragraph, line 2: Maybe avoid the word "correlated" since it is used below, and there is no correlation here. E.g., … fast solar wind occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle as pointed out by..... Therefore... exhibit time lags relative to the SSN maxima.

+ highlighted
+ highlighted
+ change both
+ 'time lags' without hyphen!

Page 9, Figure 3: What does the grey shading in the top panels represent? Mention this in the caption.

+ explain

Three lines below figure caption: It's the amplitudes of the variations in the correlations that decline with increasing lag, not the amplitudes of the correlation coefficients.

+ highlighted
+ reword

Next line: a period [not frequency] of about 11 years.

+ highlighted
+ can be adopted
+ below, change 'lag time' to 'time lag'

Page 10, Table 2: Similar comments to those for Table 1 apply.

+ highlighted
+ change

Three lines below table and following: I find this step difficult to follow. It seems that the sunspot numbers are shifted according to the lags, and there is some fit to the data which is then used to produce a model of the particular parameter as a function of SSN, but the text doesn't explain the motivation (apparently to produce a "model" distribution as a function of SSN) procedure very clearly.

+ highlighted
+ explain in detail

Below equation 8: I don't understand what "with the implementation of these relations into the lognormal function" means exactly. How are the fit coefficients obtained?

+ highlighted
+ explain

Page 13, Table 3: Give the equation for the fit, to place the parameters in context.

+ highlighted
+ link the fit equation
+ change other table things

Third paragraph below table, line 2: “See Figure 7”: Why not explain Figure 7 more fully here, then the coefficients d med, davg, etc. obtained from the fits will make more sense?

+ highlighted
+ look into that

Last paragraph of page: “As anticipated…” - especially since the same data are used! Also give the results in the text to make the comparison easier with the values given in this paragraph.

+ highlighted
+ look into that

Page 14, last paragraph, line 6: The curves are still very close together after the crossing, so is this an important feature?

+ highlighted
+ look into that

Line 8: But this distance (0.082 AU) is beyond the range shown in the figure, and the data, so is it reliable? I don't understand the comment "therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited. What does “limited” mean? Perhaps the comment arises because the mean is larger than the median for a log normal distribution, as noted several pages earlier, and so this crossing indicates that the distribution is no longer log normal. Maybe a few more words of explanation would help the reader understand this point, and the significance of the crossing point.

+ highlighted
+ highlighted
+ explain

Line 10: How are the identical exponents chosen? E.g., was emed always used, or eavg, or some other value? This sentence reads as though the values were the same for all four parameters, but presumably it really means that a different exponent was used for each parameter.

+ highlighted
+ reword to clarify

Page 15, paragraph 3, line 2: The figure is introduced twice, here and two paragraphs above. Can this be avoided?

+ highlighted
+ rework table reference
+ work table things

Line 7, suggest: The increasing high velocity tail with distance comes from.

+ highlighted
+ can be adopted

Page 16, line below figure: Not sure what "established" means here. Remove?

+ highlighted
+ remove

Line 3: What parameter is used for the power law fits? Presumably it's the radial distance, but this could be stated specifically.

+ highlighted
+ state specifically

Page 17, figure caption: solar wind parameter power exponents for the dependence on radial distance

+ highlighted
+ can be adopted

Last sentence of paragraph, suggest: Since this separation is highly variable, and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.

+ highlighted
+ adopt reworded

Section 6, line 2, suggest: predictions of the SSN during the mission are incorporated into the empirical solar wind model derived in the previous sections

+ highlighted
+ can be adopted

Next paragraph, last sentence, suggest: the perihelion distance to be reduced to a minimum of 9.86 Rs. Reverse figures 10 and 11, since figure 11 is referenced first, or just remove the mention of Figure 11 here, which isn't necessary; the statement can be understood without looking at the figure.

Last line of page: How are the ranges of median values for different SSN shown in the figure? I'm guessing that it's the thickness of the shaded regions, but this could be stated specifically to guide the reader in interpreting the figure.

Figure 10 caption, line 1: The models obtained from Helios and OMNI measurements are …

Line 3: But do the extreme values really occur for min and max SSN? E.g. the highest speeds could be at intermediate SSN? How can a time lag be “noted” in this figure which there is no obvious time dependence?

Line 4 below figure: “Arguably”: There's no argument here; this just seems to be a suggestion.

Line 5, suggest: mentioned changing shape of the frequency distribution with heliocentric distance

Line 6: But the largest difference appears to be at ~1 AU, so isn't there also a problem with the dipole/quadrapole model matching the observed fields at 1 AU?

Line 7: “Whereas”: Combine the sentences; whereas isn’t used at the beginning of a sentence. Since the peak speeds are on the declining phase of the cycle, wouldn't the peak predicted speeds occur for some intermediate sunspot number, not at SSN=200?

Last line: New sentence at “Thus”.

Page 19, line 6: What is the relevance of the comment on assuming a helium abundance? It's not clear how it relates to the comparison of the density profiles.

Line 10: overestimates

Paragraph 2, line 2: There is an abrupt change of topic here, and it's not immediately obvious why short term SSN predictions are relevant. There could be an introductory sentence saying that since the solar wind predictions depend on SSN, they may be refined using predictions of the SSN during the PSP mission.

Line 5: Why should the last cycle be used rather than say a previous one? Is this based on expectations that the next cycle will also be small?

Line 8, suggest: the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle 25, cannot be predicted at this time. Suggest moving this up to before "For the prediction of the next solar cycle..."

Paragraph 3: How are the error bands in Figures 12 and 13 calculated? E.g., do they use different assumptions for the predicted SSN?

Figure 11, lower legend in figure: “Cycle 24” amplitude rather than "its".

Page 21, line 4, suggest: au, deriving power law fit functions that were used

Line 6, suggest: -2025, encompassing the prime mission up to the closest approach of 9.86 Rs.

Paragraph 2, line 3, suggest: Differences from the results of these other studies suggest that below about 20 Rs, PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur.

Last line on page, suggest: because the solar wind is believed to be accelerated up to the height of the Alfvenic critical surface, which is predicted to lie on average around 17 Rs, with a range of between 15 Rs at solar minimum and 30 Rs at solar maximum.

Page 22, paragraph 2, line 5, suggest: that due to solar wind drag, the speeds

Summary, paragraph 2: It's not really necessary to go though the procedure yet again; there is already a synopsis in the conclusions. Is it necessary to have both a conclusions and a summary section? They could be combined.

Equation 12 and following equations: The formulas presented here have not been shown above, but are much easier to interpret than the results above. I'd suggest moving them into the results section above.

Page 23, last but one paragraph: Again, there are points here that have already been said twice above.

### 2017-10-06 paperMVVB/sections/abstract.tex
referee and w/o figures versions added
vb summary addition; raw abstract for submitting
highlighted referee comments; notes in report

@@
 
-\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; fourth changes 24 August 2017; received date; accepted date}
+\date{received date; accepted date}
+%First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; fourth changes 24 August 2017; submitted 25 August 2017
 
@@
 The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}.
-Though, the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations.
-Thus, PSP is expected to directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.}	%results
+\hl{Though, the modeled velocity and temperature values below about } \SI{20}{\Rs} \hl{appear overestimated in comparison with existing observations.
+Thus, PSP is expected to directly measure solar wind acceleration and heating processes below } \SI{20}{\Rs} \hl{as planned.
+} }	%results
 {}	%conclusions
@@
 
-%\SI{0.0459}{\au}
-%extrapolated ranges \SI{95.45}{\percent} of the solar wind parameter values lie within.
-The ranges are for the magnetic field strength \SIrange{522}{2725}{nT}, for the velocity \SIrange{209.4}{506}{\km\per\s}, for the density \SIrange[scientific-notation=fixed, fixed-exponent=3, range-units=brackets]{1.319e3}{1.72e4}{\per\cm\cubed} and for the temperature \SIrange[scientific-notation=fixed, fixed-exponent=6, range-units=brackets]{4.18e5}{1.59e7}{\K}.
-%These ranges are consistent with... and differ with...
+%title and abstract for submitting:
+
+%Solar wind predictions for the Parker Solar Probe orbit
+%Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations
+
+%The Parker Solar Probe (PSP) (formerly Solar Probe Plus) mission will be humanity’s first in situ exploration of the solar corona with closest perihelia at 9.86 solar radii (Rs) distance to the Sun.
+It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
+The scope of this study is to model the solar wind environment for PSP’s unprecedented distances during its prime mission phase during the years 2018--2025.
+The study is performed within the project Coronagraphic German And US Solar Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).
+%We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data.
+The German-US space probes Helios 1 and Helios 2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of 0.29--0.98 au.
+The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near 1 au over more than five solar cycles.
+The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar wind parameters on solar activity and to forecast their properties for the PSP mission.
+%The frequency distributions for the solar wind key parameters magnetic field strength, proton velocity, density and temperature are represented by lognormal functions.
+In addition, we consider the velocity distribution’s bi-componental shape, consisting of a slower and a faster part.
+Functional relations to solar activity are compiled with use of the OMNI data by correlating and fitting the frequency distributions with the SSN.
+Further, based on the combined data set from both Helios probes, the parameters’ frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
+Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
+Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.
+%The CGAUSS empirical solar wind model for PSP yields dependencies of the solar wind parameters on solar activity and radial distance.
+The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of 0.16 au are 87 nT, 340 km s-1, 4015 cm-3 and 503000 K.
+The estimates for PSP’s closest perihelia, beginning in 2024 at 0.046 au (9.86 Rs), are 943 nT, 290 km s-1, 9733 cm-3 and 1930000 K.
+Though, the modeled velocity and temperature values below about 20 Rs appear overestimated in comparison with existing observations.
+Thus, PSP is expected to directly measure solar wind acceleration and heating processes below 20 Rs as planned.

### 2017-10-06 paperMVVB/sections/content.tex
vb summary addition; raw abstract for submitting
highlighted referee comments; notes in report

@@
 Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-Until today various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+\hl{Until today } various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} \hl{still orbiting } around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
 Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
-The Sun-nearest in situ solar wind measurements to date were obtained by the Helios mission.
-The in 1974 launched Helios~1 spacecraft reached distances of \SI{0.31}{\au}, Helios~2 launched two years later and approached the Sun up to \SI{0.29}{\au} \citep{Rosenbauer1977}.
+\hl{The Sun-nearest in situ solar wind measurements to date were obtained by the Helios mission.
+} \hl{The in 1974 launched Helios~1 spacecraft reached distances of } \SI{0.31}{\au}, \hl{Helios~2 launched two years later and approached the Sun up to } \SI{0.29}{\au} \citep{Rosenbauer1977}.
 %Solar Probe Plus mission
@@
 For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
-The mean absolute errors and sums of absolute residuals are also listed.
-The values in brackets are the estimated standard deviations of the fit parameters.}
+The \hl{mean absolute errors } and \hl{sums of absolute residuals } are also listed.
+The values in brackets are the \hl{estimated standard deviations } of the fit parameters.}
 	\label{tab:lognormal_fit_parameters}
@@
 	\tablefoot{
-		\tablefoottext{a}{In units of \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
+		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
 		\tablefoottext{b}{Error estimates derived from the individual fit part errors.}
@@
 The fits' median and mean values are indicated as well.
-The insets show zoomed-in frequency axes.}
+\hl{The insets show zoomed-in frequency axes.
+} }
 	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
@@
 The fit's median and mean values and its two fit parts are indicated as well.
-The inset has a zoomed-in frequency axis.}
+\hl{The inset has a zoomed-in frequency axis.
+} }
 	\label{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}
@@
 %transition
-For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, but differ for the extreme values, mainly caused by CME events.
+For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, \hl{but differ for the extreme values, mainly caused by CME events. } 
 The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is overestimated as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The velocity's compositional lognormal fit only slightly \hl{overestimates } its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
@@
 The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
-For instance the fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
-Therefore the solar wind velocity, density and temperature maxima exhibit time-lags to the SSN maxima.
+For instance the \hl{fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by } \citet[p.~75, Figure~3.52]{Bothmer2007}.
+Therefore the solar wind velocity, density and temperature maxima \hl{exhibit time-lags to the SSN maxima.
+}
 
 The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
-As expected, the correlation coefficients' amplitudes of all parameters decline with increasing time lag and show a frequency of about 11~years.
-The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
+As expected, \hl{the correlation coefficients' amplitudes of all parameters decline with increasing time lag } and show \hl{a frequency of about 11~years.
+} The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
@@
 %\subsection{SSN fitting}
-To enable shifts of the solar wind frequency distributions with the SSN, we add a linear SSN dependency to the median
+\hl{To enable shifts of the solar wind frequency distributions with the SSN } , we add a linear SSN dependency to the median
 \begin{align}
@@
 \end{align}
-With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data.
+\hl{With the implementation of these relations into the lognormal function } (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data.
 The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
@@
 For the velocity the fit parameters from the double lognormal fit and their balancing function are given.
-The values in brackets are the estimated standard deviation of the fit parameters.}
+The values in brackets are the \hl{estimated standard deviation} of the fit parameters.}
 	\label{tab:ssn_fit_parameters}
@@
 	\tablefoot{
-		\tablefoottext{a}{In units of \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
+		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
 	}
@@
 
-The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set, see Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.
+The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set\hl{, see } Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.
 Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
@@
 \begin{table*}
-	\caption{Fit coefficients for the median and mean solar distance dependencies of the four solar wind parameters derived from the combined Helios~1 and 2 data.
-The errors in brackets are the estimated standard deviations of each fit parameter.
+	\caption{Fit coefficients for \hl{the median and mean solar distance dependencies } of the four solar wind parameters derived from the combined Helios~1 and 2 data.
+The errors in brackets are the \hl{estimated standard deviations} of each fit parameter.
 The crossing distances indicate where the median and mean fits intersect each other.
@@
 %Helios results, radial gradients see \citet{Schwenn1990} p.~155
-As anticipated, our derived exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$.
+\hl{As anticipated, our derived exponents agree with those found in existing studies from the Helios observations: } \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$.
 %$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
@@
 \end{figure*}
-Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} and the mean is lower than the median at smaller distances (Table~\ref{tab:mean_median_fit_parameter}).
+Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} and the mean \hl{is lower than the median at smaller distances } (Table~\ref{tab:mean_median_fit_parameter}).
 Thus, below that distance the distribution function cannot well be described anymore by a lognormal function.
 The fits for the proton temperature show a similar behavior,
-having an intersection at \SI{0.082}{\au}.
-Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
-To circumvent such limitations we set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical for all four parameters.
-It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
+\hl{having an intersection at } \SI{0.082}{\au}.
+\hl{Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
+} To circumvent such limitations we \hl{set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical for all four parameters.
+} It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
 
@@
 	\caption{Fit coefficients from the single lognormal power function, respectively double lognormal for the velocity from the combined Helios data.
-The errors in brackets are the estimated standard deviations of the fit parameters.
+The errors in brackets are the \hl{estimated standard deviations} of the fit parameters.
 The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
@@
 	\tablefoot{
-		\tablefoottext{a}{In units of \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
+		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
 		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
@@
 
-The frequency distribution data for the four solar wind parameters with respect to the radial distance from the Sun are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}, together with their power law lognormal fits and the double lognormal fit for the velocity with their median values.
+The frequency distribution data for the four solar wind parameters with respect to the radial distance from the Sun \hl{are plotted in } Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}, \hl{together with their power law lognormal fits and the double lognormal fit for the velocity with their median values.
+}
 \begin{figure*}
@@
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-The velocity model's with distance increasing high velocity tail comes from using the same exponent for both slow and fast components.
+\hl{The velocity model's with distance increasing high velocity tail comes from } using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 %\label{sec:distance_scaling_law_variations}
-This established solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The variation of yearly power law fit exponents are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
+This \hl{established} solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
+The variation of yearly \hl{power law fit} exponents are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
 It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature exponents.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}
-	\caption{Helios yearly variation of the solar wind parameters' fit exponents together with the SIDC 13-month smoothed monthly SSN.
+	\caption{Helios yearly variation of the \hl{solar wind parameters' fit exponents } together with the SIDC 13-month smoothed monthly SSN.
 The weighted standard deviations and average values for all years are indicated by the shaded areas.
@@
 Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
-However, the additional analysis of this aspect is beyond the scope of this study.	%Balogh et al.
+\hl{However, the additional analysis of this aspect is beyond the scope of this study.
+} 	%Balogh et al.
 (p.~162, 1999);	 (Schwenn 1990, p.~126)
@@
 \label{sec:model_extrapolation_to_psp_orbit}
-To estimate PSP’s solar wind environment during its mission time for its orbital positions, SSN predictions are included into the in the previous sections derived empirical solar wind model and extrapolations down to the PSP perihelion region are performed.
+To estimate PSP’s solar wind environment during its mission time for its orbital positions, \hl{SSN predictions are included into the in the previous sections derived empirical solar wind model } and extrapolations down to the PSP perihelion region are performed.
 
@@
 \end{figure*}
-
 %magnetic field:
@@
 This difference is arguably due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) with solar distance changing shape of the frequency distribution, which for smaller distances deviates more from the model’s lognormal distribution.
-
 %velocity:
@@
 Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates, thus PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
-
 %density:
@@
 For the comparison we assumed a solar wind helium abundance of \SI{5}{\%}.
-
 %temperature:
@@
 Implementing the predicted SSN for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected.
-
 Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
@@
 We started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by lognormally fitting the about 40~years of in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, velocity, density and temperature.
+Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
+Each velocity part is fitted with a lognormal function, which allows for the overlap of both velocity ranges.
 The OMNI multi-spacecraft solar wind data is intercalibrated and covers almost five solar cycles.
@@
 The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and its position correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
-
-Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
-Each velocity part is fitted with a lognormal function, which allows for the overlap of both velocity ranges.
 
@@
 The overestimation of the extrapolated velocity and temperature values at distances below \SI{20}{\Rs} indicate the occurrence of solar wind acceleration and heating processes, which PSP will thus be able to directly measure as planned.
+Note that the study of extreme solar wind parameters associated with extreme CMEs was beyond the scope of this study as well as an estimate of the level of turbulence increasing with distance to the Sun as observed by the Helios probes inside individual solar wind streams.
 

### 2017-10-07 paperMVVB_referee/referee_report_responses.txt
#2 highlighted referee comments; notes in report

@@
 
-- 
+- ...
 + add perihelia figures of distributions
@@
 
-- 
+- ...
 + link the fit equations in table captions
@@
 
++ highlighted
++ can be adopted
++ highlighted
++ manage fig references
+
 Last line of page: How are the ranges of median values for different SSN shown in the figure?
@@
 
++ highlighted
++ explain thickness of shaded region
+
 Figure 10 caption, line 1: The models obtained from Helios and OMNI measurements are …
+
++ highlighted
++ can be adopted
 
@@
 
++ answer question
++ answer question
++ answer question
+
 Line 4 below figure: “Arguably”: There's no argument here; this just seems to be a suggestion.
+
++ highlighted
++ reword
 
@@
 
++ highlighted
++ can be adopted
+
 Line 6: But the largest difference appears to be at ~1 AU, so isn't there also a problem with the dipole/quadrapole model matching the observed fields at 1 AU?
+
++ highlighted
++ look into this
 
@@
 
++ highlighted
++ combine
++ explain
+
 Last line: New sentence at “Thus”.
+
++ highlighted
++ can be adopted
 
@@
 
++ highlighted
++ explain
+
 Line 10: overestimates
+
++ highlighted
++ can be adopted
 
@@
 
++ highlighted
++ look into it
++ additional argument is first perihelion
+
 Line 5: Why should the last cycle be used rather than say a previous one? Is this based on expectations that the next cycle will also be small?
+
++ highlighted
++ explain
 
@@
 
++ highlighted
++ can be adopted
++ move up
+
 Paragraph 3: How are the error bands in Figures 12 and 13 calculated? E.g., do they use different assumptions for the predicted SSN?
+
++ answer/explain
 
@@
 
++ fig legend
++ can be adopted
+
 Page 21, line 4, suggest: au, deriving power law fit functions that were used
+
++ highlighted
++ can be adopted
 
@@
 
++ highlighted
++ can be adopted
++ search text for solar radii and replace with Rs
+
 Paragraph 2, line 3, suggest: Differences from the results of these other studies suggest that below about 20 Rs, PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur.
+
++ highlighted
++ can be adopted, but
++ pay attention to wording
 
@@
 
++ highlighted
++ can be adopted, but
++ check wording
+
 Page 22, paragraph 2, line 5, suggest: that due to solar wind drag, the speeds
+
++ highlighted
++ can be adopted
 
@@
 
++ highlighted
++ combine both
+
 Equation 12 and following equations: The formulas presented here have not been shown above, but are much easier to interpret than the results above.
@@
 
++ move equations or explain
+
 Page 23, last but one paragraph: Again, there are points here that have already been said twice above.
+
++ highlighted
++ remove or merge with above

### 2017-10-07 paperMVVB/sections/content.tex
#2 highlighted referee comments; notes in report

@@
 \label{sec:model_extrapolation_to_psp_orbit}
-To estimate PSP’s solar wind environment during its mission time for its orbital positions, \hl{SSN predictions are included into the in the previous sections derived empirical solar wind model } and extrapolations down to the PSP perihelion region are performed.
+To estimate PSP’s solar wind environment during its mission time for its orbital positions, \hl{SSN predictions are included into the in the previous sections derived empirical solar wind model }++ and extrapolations down to the PSP perihelion region are performed.
 
@@
 With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
-Seven additional Venus flybys allow to finally reduce its perihelion distance to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
+Seven additional Venus flybys allow \hl{to finally reduce its perihelion distance to a minimum of } \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \hl{Fig.
+} ~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
 
@@
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
-The from Helios and OMNI measurements obtained models are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas).
+\hl{The from Helios and OMNI measurements obtained models are } extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas).
 Note that there is a time lag to the SSN depending on the solar wind parameter.
@@
 %magnetic field:
-The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of 0.
-Taking a SSN of 200 increases the values to \SI{69}{\nT} and \SI{1152}{\nT}.
+The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} \hl{for a SSN of 0.
+Taking a SSN of 200 } increases the values to \SI{69}{\nT} and \SI{1152}{\nT}.
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-This difference is arguably due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) with solar distance changing shape of the frequency distribution, which for smaller distances deviates more from the model’s lognormal distribution.
+This difference is \hl{arguably } due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \hl{with solar distance changing shape of the frequency distribution } , \hl{which for smaller distances deviates more from the } model’s lognormal distribution.
 %velocity:
-The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} for a SSN of 0.
-Whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
+The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} for a SSN of 0\hl{.
+Whereas} using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
 Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar wind velocity values for distances below about \SI{20}{\Rs}.
 They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model from \citet{Parker1958}.
-Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates, thus PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
+Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates\hl{, thus } PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
 %density:
@@
 Their model shows that the density distance dependency scales with $r^{-2}$ and steepens just below \SI{10}{\Rs} with $r^{-6}$.
-For the comparison we assumed a solar wind helium abundance of \SI{5}{\%}.
+\hl{For the comparison we assumed a solar wind helium abundance of } \SI{5}{\%}.
 %temperature:
 The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} for a SSN of 0 and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
-Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model overestimate the extrapolated temperatures at the PSP perihelion distance.
+Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \hl{overestimate } the extrapolated temperatures at the PSP perihelion distance.
 
@@
 %SSN prediction
-For SSN short-term predictions several sources are available.
+\hl{For SSN short-term predictions } several sources are available.
 The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter combined method).
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
-Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes.
+\hl{For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
+} Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s \hl{closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes.
+}
 \begin{figure}
@@
 In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
-The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}.
-The herefrom derived power law fit functions were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years 2018--2025, i.e., for the prime mission phase that gets PSP to closest perihelia of 9.86~solar radii distance.
-The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au} \hl{.
+The herefrom derived power law fit functions were used } to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years \hl{2018--2025, i.e., for the prime mission phase that gets PSP to closest perihelia of 9.86~solar radii distance.
+} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
 Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
@@
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the region of the Alfvénic critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} and its position correlates with solar activity between \SI{15}{\Rs} in cycle minimum and \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+\hl{The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances } (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, \hl{because the region of the } Alfvénic \hl{critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around } \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} \hl{and its position correlates with solar activity between } \SI{15}{\Rs} \hl{in cycle minimum and } \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
 
@@
 The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, likely to be associated with individual CMEs.
-The results by \citet{Sachdeva2017} indicate that due to the prevailing of solar wind drag the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
+The results by \citet{Sachdeva2017} indicate \hl{that due to the prevailing of solar wind drag the speeds } of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
 Therefore, it is expected that PSP will encounter CMEs with much higher speeds than those observed during the Helios mission.
@@
 
-For this purpose we derived lognormal representations of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature for the near-Earth solar wind OMNI data, and the Helios~1 and 2 data obtained over the solar distance range \SIrange{0.29}{0.98}{\au}.
+\hl{For this purpose we derived lognormal representations } of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature for the near-Earth solar wind OMNI data, and the Helios~1 and 2 data obtained over the solar distance range \SIrange{0.29}{0.98}{\au}.
 The dependencies of these frequency distributions on solar activity, as measured by the international sunspot number, and on radial distance to the Sun were modeled with analytical relations and then extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
@@
 \end{itemize}
-The overestimation of the extrapolated velocity and temperature values at distances below \SI{20}{\Rs} indicate the occurrence of solar wind acceleration and heating processes, which PSP will thus be able to directly measure as planned.
+\hl{The overestimation of the extrapolated velocity and temperature values at distances below } \SI{20}{\Rs} \hl{ indicate the occurrence of solar wind acceleration and heating processes, which PSP will thus be able to directly measure as planned.
 Note that the study of extreme solar wind parameters associated with extreme CMEs was beyond the scope of this study as well as an estimate of the level of turbulence increasing with distance to the Sun as observed by the Helios probes inside individual solar wind streams.
+}
 

### 2017-10-08 paperMVVB_referee/referee_report_responses.txt
adopted easy referee comments; made changes bold face

@@
 + add perihelia figures of distributions
-+ ...
++ state advantage over simple-minded approach
++ how different are the results?
 
@@
 - ...
-+ link the fit equations in table captions
++ link the fit equations in table captions...
 + ...
@@
 
+- adopted
 + highlighted
@@
 
+- removed
 + highlighted
 + can be removed
+
 + highlighted
@@
 
+- changed
 + highlighted
 + can be adopted
+
++ do that for all tables
 
@@
 
+- adopted
 + highlighted
 + can be adopted
+
+- changed in fig 2 too
 + change in fig 2 too
@@
 
+- both adopted
 + highlighted
@@
 
+- adopted
 + highlighted
 + can be adopted
+
+- changed 'lag time' to 'time lag'
 + below, change 'lag time' to 'time lag'
@@
 
+- removed
 + highlighted
@@
 
+- adopted
 + highlighted
 + can be adopted
+
 + highlighted
@@
 
+- combined
 + highlighted
 + combine
+
 + explain
@@
 
+- adopted
 + highlighted
 + can be adopted
+
+- moved up
 + move up
@@
 
+- adopted
 + highlighted
 + can be adopted
+
+- replaced solar radii with Rs in discussion
 + search text for solar radii and replace with Rs

### 2017-10-08 paperMVVB/sections/abstract.tex
adopted easy referee comments; made changes bold face

@@
 The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}.
-\hl{Though, the modeled velocity and temperature values below about } \SI{20}{\Rs} \hl{appear overestimated in comparison with existing observations.
-Thus, PSP is expected to directly measure solar wind acceleration and heating processes below } \SI{20}{\Rs} \hl{as planned.
+\textbf{Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.
 } }	%results

### 2017-10-08 paperMVVB/sections/content.tex
adopted easy referee comments; made changes bold face

@@
 Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-\hl{Until today } various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} \hl{still orbiting } around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} \hl{still orbiting } around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
 Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
-\hl{The Sun-nearest in situ solar wind measurements to date were obtained by the Helios mission.
-} \hl{The in 1974 launched Helios~1 spacecraft reached distances of } \SI{0.31}{\au}, \hl{Helios~2 launched two years later and approached the Sun up to } \SI{0.29}{\au} \citep{Rosenbauer1977}.
+\textbf{The in situ solar wind measurements closest to the Sun to date were made by} the Helios mission.
+\textbf{Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}.
+Helios~2, launched two years later, approached the Sun as close as} \SI{0.29}{\au} \citep{Rosenbauer1977}.
 %Solar Probe Plus mission
@@
 	\sisetup{table-figures-integer=1, table-figures-decimal=4, table-figures-exponent=0}
-	\begin{tabular}{l@{} c
+	\begin{tabular}{l c
 		S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{1}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{1}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
 		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[$10^{-4}$]}	&\multicolumn{1}{c}{[\%]}\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&5.51	&6.83\\
-		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&18.0	&18.69\\
-		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&5.49	&6.48\\
-		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&0.871	&5.78\\
+		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.661(16)	&6.164(18)	&--	&5.51	&6.83\\
+		\multicolumn{2}{l}{\textbf{Velocity [\SI{e2}{\km\per\s}]}}	&4.085(19)	&4.183(20)	&--	&18.0	&18.69\\
+		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.276(24)	&6.484(34)	&--	&5.49	&6.48\\
+		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&7.470(17)	&11.301(32)	&--	&0.871	&5.78\\
 		\hline
-		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
-			&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+		\multirow{2}{*}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
 		\cline{2-7}
-			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{b}	&4.42(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98	&4.20\\
+			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{a}	&4.42(14)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&3.98	&4.20\\
 		\hline
@@
 	\tablefoot{
-		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
-		\tablefoottext{b}{Error estimates derived from the individual fit part errors.}
+		\tablefoottext{a}{Error estimates derived from the individual fit part errors.}
 	}
@@
 The fits' median and mean values are indicated as well.
-\hl{The insets show zoomed-in frequency axes.
+The insets show zoomed-in \textbf{views of the high value tails of the distributions.
 } }
@@
 The fit's median and mean values and its two fit parts are indicated as well.
-\hl{The inset has a zoomed-in frequency axis.
+\textbf{The inset is a zoomed-in view of the high value tail of the distribution.
 } }
@@
 The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
-For instance the \hl{fast solar wind is correlated with the presence of polar coronal hole extensions to lower latitudes being a typical feature of the solar cycle, being the reason for the common velocity peak in the decreasing phase of the SSN, as pointed out by } \citet[p.~75, Figure~3.52]{Bothmer2007}.
-Therefore the solar wind velocity, density and temperature maxima \hl{exhibit time-lags to the SSN maxima.
-}
+For instance the fast solar wind \textbf{occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle} as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
+Therefore the solar wind velocity, density and temperature maxima exhibit \textbf{time lags relative} to the SSN maxima.
 
 The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
-As expected, \hl{the correlation coefficients' amplitudes of all parameters decline with increasing time lag } and show \hl{a frequency of about 11~years.
-} The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
+As expected, \hl{the correlation coefficients' amplitudes of all parameters decline with increasing time lag } and show a \textbf{period} of about 11~years.
+The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
-Velocity and temperature show a lag time of 3~years with peak correlation coefficients of 0.453 and 0.540.
+Velocity and temperature show a \textbf{time lag} of 3~years with peak correlation coefficients of 0.453 and 0.540.
 The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the by \citet{Bougeret1984} reported density anticorrelation to the SSN.	%p.~406\\
-% maximal correlation coefficients and their lag times:\\
+% maximal correlation coefficients and their time lags:\\
 % magnetic field strength: lag 0, 0.728\\
@@
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-\hl{The velocity model's with distance increasing high velocity tail comes from } using the same exponent for both slow and fast components.
+\textbf{The increasing high velocity tail with distance} comes from using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 %\label{sec:distance_scaling_law_variations}
-This \hl{established} solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
+\textbf{This solar wind model} for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
 The variation of yearly \hl{power law fit} exponents are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}
-	\caption{Helios yearly variation of the \hl{solar wind parameters' fit exponents } together with the SIDC 13-month smoothed monthly SSN.
+	\caption{Helios yearly variation of the solar wind \textbf{parameter power exponents for the dependence on radial distance} together with the SIDC 13-month smoothed monthly SSN.
 The weighted standard deviations and average values for all years are indicated by the shaded areas.
@@
 \label{sec:model_extrapolation_to_psp_orbit}
-To estimate PSP’s solar wind environment during its mission time for its orbital positions, \hl{SSN predictions are included into the in the previous sections derived empirical solar wind model }++ and extrapolations down to the PSP perihelion region are performed.
+To estimate PSP’s solar wind environment during its mission time for its orbital positions, \textbf{predictions of the SSN during the mission are incorporated into the empirical solar wind model derived in the previous sections} and extrapolations down to the PSP perihelion region are performed.
 
@@
 With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
-Seven additional Venus flybys allow \hl{to finally reduce its perihelion distance to a minimum of } \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \hl{Fig.
+Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \hl{Fig.
 } ~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
@@
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
-\hl{The from Helios and OMNI measurements obtained models are } extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas).
+\textbf{The models obtained from Helios and OMNI measurements} are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas).
 Note that there is a time lag to the SSN depending on the solar wind parameter.
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-This difference is \hl{arguably } due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \hl{with solar distance changing shape of the frequency distribution } , \hl{which for smaller distances deviates more from the } model’s lognormal distribution.
+This difference is \hl{arguably } due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , \hl{which for smaller distances deviates more from the } model’s lognormal distribution.
 %velocity:
-The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} for a SSN of 0\hl{.
-Whereas} using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
+The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} for a SSN of 0\textbf{, whereas} using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
 Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar wind velocity values for distances below about \SI{20}{\Rs}.
 They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model from \citet{Parker1958}.
-Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates\hl{, thus } PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
+Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates\textbf{.
+Thus} PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
 %density:
@@
 The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} for a SSN of 0 and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
-Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \hl{overestimate } the extrapolated temperatures at the PSP perihelion distance.
+Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \textbf{overestimates} the extrapolated temperatures at the PSP perihelion distance.
 
@@
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas \textbf{the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.}
 \hl{For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
 } Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas PSP’s \hl{closest perihelia, which commence at the maximum phase of cycle~25 end of 2024, will experience as of now incalculable SSN amplitudes.
-}
 \begin{figure}
@@
 In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
-The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au} \hl{.
-The herefrom derived power law fit functions were used } to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years \hl{2018--2025, i.e., for the prime mission phase that gets PSP to closest perihelia of 9.86~solar radii distance.
-} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
 Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
@@
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-\hl{The from direct measurements differing velocity and temperature extrapolations below about 20~solar radii indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances } (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
+\hl{The from direct measurements differing velocity and temperature extrapolations below about } \SI{20}{\Rs} \hl{indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances } (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
 The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, \hl{because the region of the } Alfvénic \hl{critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around } \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} \hl{and its position correlates with solar activity between } \SI{15}{\Rs} \hl{in cycle minimum and } \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
@@
 The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, likely to be associated with individual CMEs.
-The results by \citet{Sachdeva2017} indicate \hl{that due to the prevailing of solar wind drag the speeds } of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
+The results by \citet{Sachdeva2017} indicate that due to \textbf{solar wind drag,} the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
 Therefore, it is expected that PSP will encounter CMEs with much higher speeds than those observed during the Helios mission.

### 2017-10-09 paperMVVB_referee/referee_report_responses.txt
adopted referee comments; made changes bold face

@@
 
+- SOHO added
 + highlighted
-+ add SOHO
++ add SOHO?
++ SOHO/CELIAS not real-time (ca. +3 hours)
++ SOHO/CELIAS does not contribute to OMNI data set
 
@@
 
+- explained
 + explain
@@
 
+- changed
 + highlighted
-+ reword
++ change
 
@@
 Page 10, Table 2: Similar comments to those for Table 1 apply.
+
+- table caption equation references added
+- in section 3 sentence with equation (9) clarified
 
@@
 
+- referenced the fit equation
 + highlighted
 + link the fit equation
-+ change other table things
+
+- referenced fit equations in all other table captions
++ reference fit equations for all other tables
 
@@
 + highlighted
-+ reword to clarify
++ reword to clarify both
 
@@
 + highlighted
-+ rework table reference
-+ work table things
 
@@
 
+- stated specifically and added equation reference
 + highlighted
@@
 
+- adopted
 + highlighted
 + adopt reworded
+
+- a few lines before: added 'and' between references 'Bruno et al. (1986) and Balogh et al. (1999)'
 
@@
 
+- reworded beginning of sentence
 + highlighted
@@
 
+- changed
 + fig legend
@@
 + remove or merge with above
+
+- added referee acknowledgment

### 2017-10-09 paperMVVB/sections/content.tex
adopted referee comments; made changes bold face

@@
 Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} \hl{still orbiting } around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, \hl{SOHO} \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
-	\caption{The solar wind parameter yearly medians derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
+	\caption{The solar wind parameter yearly \textbf{frequencies (grey shading) with yearly medians (lines)} derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
 Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
@@
 \end{figure}
-
+ Solar wind parameter yearly data frequencies
 The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
@@
 The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
-As expected, \hl{the correlation coefficients' amplitudes of all parameters decline with increasing time lag } and show a \textbf{period} of about 11~years.
+As expected, the \textbf{amplitudes of the variations in the correlations} of all parameters decline with increasing time lag and show a \textbf{period} of about 11~years.
 The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
@@
 \begin{table*}
-	\caption{Resulting fit coefficients from the OMNI data fitting with lagged SSN.
-For the velocity the fit parameters from the double lognormal fit and their balancing function are given.
+	\caption{Resulting fit coefficients from the OMNI data fitting with \textbf{the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}.
+For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given.
 The values in brackets are the \hl{estimated standard deviation} of the fit parameters.}
@@
 Again, the solar wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle we keep the two velocity components' positions constant and vary instead their balance with the SSN:
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle we keep the two velocity components' positions \textbf{SSN-independent ($x_\text{med} =  b_\text{med}$)} and vary instead their balance with the SSN:
 \begin{align}
@@
 \begin{table*}
-	\caption{Fit coefficients for \hl{the median and mean solar distance dependencies } of the four solar wind parameters derived from the combined Helios~1 and 2 data.
+	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data.
 The errors in brackets are the \hl{estimated standard deviations} of each fit parameter.
@@
 \begin{table*}
-	\caption{Fit coefficients from the single lognormal power function, respectively double lognormal for the velocity from the combined Helios data.
+	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data.
 The errors in brackets are the \hl{estimated standard deviations} of the fit parameters.
@@
 		\hline
-		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
+		\multirow{2}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
 			&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\
@@
 \textbf{This solar wind model} for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The variation of yearly \hl{power law fit} exponents are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
+The variation of yearly power law fit exponents \textbf{by fitting the solar distance dependency (\ref{eq:power_function})} are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
 It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature exponents.
@@
 They are estimated to be smaller than \SI{4}{\percent} as seen in Tab.~\ref{tab:extrapolation_model_fit_parameters}.
-\citet{Bruno1986,Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet (HCS).
+\citet{Bruno1986} \textbf{and} \citet{Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet (HCS).
 Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
-\hl{However, the additional analysis of this aspect is beyond the scope of this study.
-} 	%Balogh et al.
+\textbf{Since this latitudinal separation is highly variable, and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.}	%Balogh et al.
 (p.~162, 1999);	 (Schwenn 1990, p.~126)
@@
 Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \hl{Fig.
-} ~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
+} ~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
 
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-This difference is \hl{arguably } due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , \hl{which for smaller distances deviates more from the } model’s lognormal distribution.
+\textbf{We suggest that this difference is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , \hl{which for smaller distances deviates more from the } model’s lognormal distribution.
 %velocity:
@@
 \hl{For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
-} Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_e_plot}.
+} Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_e_plot.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
 	\caption{PSP's solar distance during its mission time (top).
@@
 Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
-	\label{fig:SPP_orbit_predicted_SSN_overview_e_plot}
+	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
 \end{figure}

### 2017-10-10 paperMVVB_referee/referee_report_responses.txt
worked on referee comments; made changes bold face

@@
 - ...
-+ add perihelia figures of distributions
-+ state advantage over simple-minded approach
-+ how different are the results?
++ use the distributions for the predictions (add perihelia figures of distributions)
++ state advantage over simple-minded approach (example of simple-minded approach; state how different the results are)
 
@@
 - ...
-+ link the fit equations in table captions...
-+ ...
++ procedural steps to be explained in detail
++ clarify the meaning of the parameters in tables
++ link the fit equations in table captions
++ combine conclusion and summary sections
++ include final functions in results section
 
@@
 - SOHO added
+- should we keep it?
 + highlighted
-+ add SOHO?
++ add SOHO
 + SOHO/CELIAS not real-time (ca. +3 hours)
@@
 - changed
+- should we keep it? doesn't it look too packed?
 + highlighted
@@
 
+- added notation explanation
 + highlighted
-+ highlighted
-+ explain both
++ explain
+
+- added notation explanation in all tables
++ explain in all tables??
+
++ explain also errors??
 
@@
 
+- mean absolute errors unnecessary (they are not referred to in paper), removed from table
++ highlighted
+
+- explained more clearly in text and table caption
 + highlighted
@@
 + highlighted
-+ v not T, look into it
++ look into that
 
@@
 
-- both adopted
+- changed
 + highlighted
++ change
+
+- adopted
 + highlighted
-+ change both
++ adopt
 + 'time lags' without hyphen!
@@
 - in section 3 sentence with equation (9) clarified
-
 + highlighted
@@
 
+- explained more clearly
 + highlighted
-+ explain in detail
++ explain motivation more clearly
+
+- section 3, second sentence: abbreviated 'sunspot number'
+- section 3, switched second and third paragraph
+- section 3, added a sentence to now second paragraph
 
@@
 
+- phrased this point more clearly
 + highlighted

### 2017-10-10 paperMVVB/sections/content.tex
worked on referee comments; made changes bold face

@@
 For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
-The \hl{mean absolute errors } and \hl{sums of absolute residuals } are also listed.
-The values in brackets are the \hl{estimated standard deviations } of the fit parameters.}
+\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} \textbf{For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}}
 	\label{tab:lognormal_fit_parameters}
@@
 		@{}c@{}
-		S[table-format = 2.3]
 		S[table-format = 2.2]
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{1}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
-		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[$10^{-4}$]}	&\multicolumn{1}{c}{[\%]}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{SAR}\\
+		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[\%]}\\
 		\hline
-		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.661(16)	&6.164(18)	&--	&5.51	&6.83\\
-		\multicolumn{2}{l}{\textbf{Velocity [\SI{e2}{\km\per\s}]}}	&4.085(19)	&4.183(20)	&--	&18.0	&18.69\\
-		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.276(24)	&6.484(34)	&--	&5.49	&6.48\\
-		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&7.470(17)	&11.301(32)	&--	&0.871	&5.78\\
+		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.661(16)	&6.164(18)	&--	&6.83\\
+		\multicolumn{2}{l}{\textbf{Velocity [\SI{e2}{\km\per\s}]}}	&4.085(19)	&4.183(20)	&--	&18.69\\
+		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.276(24)	&6.484(34)	&--	&6.48\\
+		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&7.470(17)	&11.301(32)	&--	&5.78\\
 		\hline
-		\multirow{2}{*}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
-		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
-		\cline{2-7}
-			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{a}	&4.42(14)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&3.98	&4.20\\
+		\multirow{2}{*}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
+		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
+		\cline{2-6}
+			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{a}	&4.42(14)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&4.20\\
 		\hline
@@
 However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
-This also can be inferred from the sum of absolute residuals (SAR) between data and fit listed in Table~\ref{tab:lognormal_fit_parameters}, being almost three times larger than those from the other parameters.
+This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} \textbf{in percentage of the distribution area}, being almost three times larger than those from the other parameters.
 \begin{figure*}
@@
 In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity.
-Therefore we examine their correlation with the sunspot number, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.
-
-%\subsection{SSN data}
-The international sunspot number (\citeyear{sidc}) is provided by the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
+Therefore we examine their correlation with the \textbf{SSN}, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.
 
@@
 For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN.
+\textbf{Thus we obtain on solar activity depending models for the frequency distributions of all four solar wind parameters.}
+
+%\subsection{SSN data}
+The international sunspot number (\citeyear{sidc}) is provided by the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
 
@@
 %\subsection{SSN fitting}
-\hl{To enable shifts of the solar wind frequency distributions with the SSN } , we add a linear SSN dependency to the median
+\textbf{Next we create solar activity dependent analytical representations of the solar wind frequency distributions.
+This is achieved by shifting the median positions of the lognormal distributions as a linear function of SSN.
+To enable these shifts }, we add a linear SSN dependency to the median
 \begin{align}
@@
 \end{align}
-\hl{With the implementation of these relations into the lognormal function } (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data.
-The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
+\textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$.
+This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to profit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
 \begin{table*}
@@
 For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given.
-The values in brackets are the \hl{estimated standard deviation} of the fit parameters.}
+\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.}}
 	\label{tab:ssn_fit_parameters}
@@
 	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data.
-The errors in brackets are the \hl{estimated standard deviations} of each fit parameter.
-The crossing distances indicate where the median and mean fits intersect each other.
+\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The crossing distances indicate where the median and mean fits intersect each other.
 The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
@@
 	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data.
-The errors in brackets are the \hl{estimated standard deviations} of the fit parameters.
-The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
+\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
 	\label{tab:extrapolation_model_fit_parameters}

### 2017-10-11 paperMVVB_referee/referee_report_responses.txt
#2 worked on referee comments; made changes bold face

@@
 + state advantage over simple-minded approach (example of simple-minded approach; state how different the results are)
++ maybe stress Helios data bias to cycle minimum (section 4, third paragraph)
 
@@
 
+- introduced figure properly
+- moved second figure reference to end of this paragraph
 + highlighted
-+ look into that
 
@@
 
+- removed 'As anticipated'
+- added exponents into text
 + highlighted
-+ look into that
+
++ is both sufficient?
 
@@
 + highlighted
-+ look into that
++ what does that mean?
 
@@
 
+- explained more clearly
 + highlighted
++ what does limited mean?
++ limited in the sense of a correct distribution shape
+
++ is it reliable? it is calculated from that data
+
+- clarified the significance of the crossing point
 + highlighted
-+ explain
++ explain significance of crossing point
 
@@
 
+- reworded sentence
+- added remark in next paragraph
 + highlighted

### 2017-10-11 paperMVVB/sections/content.tex
#2 worked on referee comments; made changes bold face

@@
 
-The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set\hl{, see } Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.
+\textbf{The radial dependencies of the key solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.}
+\begin{figure*}
+	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_b_skip.pdf}
+	\caption{Helios hourly data plots of the four solar wind parameters over solar distance.
+The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well.
+The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
+The maximal velocities of CME events larger than \SI{800}{\km\per\s} are indicated with circles.}
+	\label{fig:radial_fit_4_thesis_light_b_skip}
+\end{figure*}
 Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
@@
 %fit result table and figure
-The fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter}.
+\textbf{The obtained coefficients for the median and mean power law fits ($d_\text{med}$, $e_\text{med}$, $d_\text{avg}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter} and their corresponding curves are shown in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.}
 \begin{table*}
@@
 %Helios results, radial gradients see \citet{Schwenn1990} p.~155
-\hl{As anticipated, our derived exponents agree with those found in existing studies from the Helios observations: } \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$.
+\textbf{Our derived} exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$\textbf{, ours is $B_\text{avg} \propto r^{-1.55}$}.
 %$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
-The velocity exponent matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
-The calculated density exponent agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding $n \propto r^{-2.10}$.
+The velocity exponent \textbf{$v_\text{avg} \propto r^{0.049}$} matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
+The calculated density exponent \textbf{$n_\text{avg} \propto r^{-2.01}$} agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding $n \propto r^{-2.10}$.
 %to the year 1976 normalized   a \SI{1}{\au} density of $n = 6.14\cdot r^{-2.10}\,\text{cm}^{-3}$.
-The temperature exponent is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} \propto r^{-0.74}$ and $T_\text{slow} \propto r^{-0.58}$.
+The temperature exponent \textbf{$T_\text{avg} \propto r^{-0.79}$} is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} \propto r^{-0.74}$ and $T_\text{slow} \propto r^{-0.58}$.
 %$T_\text{fast} = \num{2.5e5} (R/R_0)^{-0.74}$\,K and $T_\text{slow} = \num{6.2e4} (R/R_0)^{-0.58}$\,K.
@@
 %crossing distances
-Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} shows the radial dependence of the solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} and the mean and median values and their respective power law fits.
-The mean and median velocity fit exponents are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
-\begin{figure*}
-	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_b_skip.pdf}
-	\caption{Helios hourly data plots of the four solar wind parameters over solar distance.
-The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well.
-The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
-The maximal velocities of CME events larger than \SI{800}{\km\per\s} are indicated with circles.}
-	\label{fig:radial_fit_4_thesis_light_b_skip}
-\end{figure*}
-Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} and the mean \hl{is lower than the median at smaller distances } (Table~\ref{tab:mean_median_fit_parameter}).
-Thus, below that distance the distribution function cannot well be described anymore by a lognormal function.
-The fits for the proton temperature show a similar behavior,
-\hl{having an intersection at } \SI{0.082}{\au}.
-\hl{Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
-} To circumvent such limitations we \hl{set the exponents $e_\text{med}$ and $e_\text{avg}$ to be identical for all four parameters.
-} It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
+\textbf{Our from the Helios data fit acquired} mean and median velocity fit exponents are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
+Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean \hl{is \textbf{getting slightly} lower than the median at smaller distances }.
+Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as mentioned in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, \hl{having an \textbf{extrapolated} intersection at } \SI{0.082}{\au}.
+Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
+\textbf{The crossing points limit the regions where the distribution's shapes can still be considered lognormal.}
+
+\textbf{For being able to still fit and extrapolate lognormal functions with the data, we assume that the shapes keep being lognormal at all distances.
+For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.} It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
 
@@
 % $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
-For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical.
-Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and their common exponent $e'$).
+For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and their common exponent $e'$).
 Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.

### 2017-10-12 paperMVVB_referee/referee_report_responses.txt
#3 worked on referee comments; made changes bold face

@@
 + highlighted
-+ what does that mean?
++ what does that mean? no?
 
@@
 
+- rephrased figure references
 + highlighted
++ aviod this
 
@@
 
+- switched order of figures 10 and 11
+- added top and bottom pointers to both references of now figure 10
 + highlighted
@@
 
+- added remark about that
 + highlighted
 + explain thickness of shaded region
+
+- added further explanation in figure caption
 
@@
 
+- ordered the references Sheeley 1997 and Wang 2000 by year
+
 Line 3: But do the extreme values really occur for min and max SSN?
@@
 
-+ answer question
-+ answer question
-+ answer question
++ yes, in average, see figure 5
+
+- correct, removed remark about time lag from figure caption
++ remove remark about time lag from caption
+
+- added column to table 2: SSN time lag
 
@@
 + highlighted
-+ look into this
++ DQCS model assumes 3.1 nT at 1 au coming from CHs at +-60° latitudes (excluding field from equatorial slow wind belt)
 
@@
 
+- correct, it is a shifted SSN. added value of time lag (at each solar wind parameter)
 + explain
@@
 
+- reworded
 + highlighted
 + explain
+
++ is that ok?
 
@@
 
+- adopted with addition
 + highlighted

### 2017-10-12 paperMVVB/sections/content.tex
#3 worked on referee comments; made changes bold face

@@
 For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given.
-\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.}}
+\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The listed SSN time lags are used for the fits.}}
 	\label{tab:ssn_fit_parameters}
@@
 		S[table-format = +1.3(2)e+1]
-		c
+		c c
 		}
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}	&\multicolumn{1}{c}{SSN lag}\\
 		\cline{3-4}\cline{6-7}
-		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
+		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}	&\multicolumn{1}{c}{[years]}\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
+		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
 %		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
-		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
-		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--\\
+		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
+		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
 		\hline
-		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
-			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
+		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
+			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
 		\hline
@@
 %\subsection{Power law lognormal fitting}
-Next we retrieve the frequency distributions of the four parameters in distance bins of \SI{0.01}{\au},  choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution}---the distributions are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
+Next we retrieve the frequency distributions of the four \textbf{solar wind parameters in solar} distance bins of \SI{0.01}{\au}, choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution}---the distributions \textbf{and their median values} are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
+\begin{figure*}
+	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_f_plot.pdf}
+	\caption{Frequency distributions of the four solar wind parameters with respect to the solar distance.
+Plotted are the binned Helios data and the power law lognormal fit models with their median values (white lines).
+The double lognormal model is used for the velocity, its slow and fast parts are indicated by dotted lines.}
+	\label{fig:mixed_fit_fixed_4_paper_f_plot}
+\end{figure*}
 % Helios histogram bin sizes for mean of frequency distribution (at specific solar distance):\\
@@
 % $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
-For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and their common exponent $e'$).
+For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$).
 Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
@@
 
-The frequency distribution data for the four solar wind parameters with respect to the radial distance from the Sun \hl{are plotted in } Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}, \hl{together with their power law lognormal fits and the double lognormal fit for the velocity with their median values.
-}
-\begin{figure*}
-	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_f_plot.pdf}
-	\caption{Frequency distributions of the four solar wind parameters with respect to the solar distance.
-Plotted are the binned Helios data and the power law lognormal fit models with their median values (white lines).
-The double lognormal model is used for the velocity, its slow and fast parts are indicated by dotted lines.}
-	\label{fig:mixed_fit_fixed_4_paper_f_plot}
-\end{figure*}
-The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the data's frequency distribution implies.
+\textbf{The power law lognormal models and the power law double lognormal model for the velocity, which result from the fitting, are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot} together with their median values.} The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the data's frequency distribution implies.
 This behavior is expected because of the distance independent shape approximation applied.
@@
 With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
-Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \hl{Fig.
-} ~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
+Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \textbf{the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
+	\caption{PSP's solar distance during its mission time (top).
+Consecutive Venus flybys bring its perihelia nearer to the Sun.
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
+\end{figure}
 
-We extrapolate the derived empirical solar wind model (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
+We extrapolate the derived empirical solar wind models (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
 \begin{figure*}
@@
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
-\textbf{The models obtained from Helios and OMNI measurements} are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$ (shaded areas).
-Note that there is a time lag to the SSN depending on the solar wind parameter.
-Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \citet{Wang2000} and \citet{Sheeley1997}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
+\textbf{The models obtained from Helios and OMNI measurements} are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$\textbf{.
+The lower edges of the shaded areas correspond to solar minimum, the upper edges to maximum.} Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \textbf{\citet{Sheeley1997} and \citet{Wang2000}}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
 	\label{fig:sw_extrapolation_ssn_e_plot}
 \end{figure*}
+\textbf{The model and the extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.}
 %magnetic field:
-The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} \hl{for a SSN of 0.
-Taking a SSN of 200 } increases the values to \SI{69}{\nT} and \SI{1152}{\nT}.
+The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of 0.
+Taking a SSN of 200 increases the values to \SI{69}{\nT} and \SI{1152}{\nT}.
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
@@
 %velocity:
-The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} for a SSN of 0\textbf{, whereas} using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
+The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} \textbf{3~years after a} SSN of 0 \textbf{occurred, whereas} using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
 Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar wind velocity values for distances below about \SI{20}{\Rs}.
@@
 %density:
-The proton density increases from about \SI{84}{\per\cm\cubed} at  \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} for a SSN of 0.
+The proton density increases from about \SI{84}{\per\cm\cubed} at \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} \textbf{6~years after a SSN of 0 occurred}.
 Being almost independent of the SSN the values for a SSN of 200 are only \SI{17}{\%} larger.
@@
 Their model shows that the density distance dependency scales with $r^{-2}$ and steepens just below \SI{10}{\Rs} with $r^{-6}$.
-\hl{For the comparison we assumed a solar wind helium abundance of } \SI{5}{\%}.
+\textbf{We assumed a solar wind helium abundance of \SI{5}{\%} to convert their electron densities to proton densities.}
 %temperature:
-The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} for a SSN of 0 and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
+The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} \textbf{3~years after a SSN of 0 occurred} and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
 Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \textbf{overestimates} the extrapolated temperatures at the PSP perihelion distance.
@@
 \hl{For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
-} Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
-\begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
-	\caption{PSP's solar distance during its mission time (top).
-Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
-	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
-\end{figure}
+} Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in \textbf{the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.}
 
@@
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-\hl{The from direct measurements differing velocity and temperature extrapolations below about } \SI{20}{\Rs} \hl{indicate that PSP will indeed dive into the acceleration and heating regions of the solar wind to be expected at these distances } (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, \hl{because the region of the } Alfvénic \hl{critical surface, up to which the solar wind is believed to be accelerated, is predicted to lie in average around } \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000} \hl{and its position correlates with solar activity between } \SI{15}{\Rs} \hl{in cycle minimum and } \SI{30}{\Rs} in maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+\textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements of the other studies.
+This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is believed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
 

### 2017-10-13 paperMVVB_referee/referee_report_responses.txt
#4 worked on referee comments; made changes bold face

@@
 
-- ...
+- procedural steps explained in detail
+- clarified the meaning of the parameters in the tables
+- linked the fit equations in the table captions
 + procedural steps to be explained in detail
@@
 + explain in all tables??
-
-+ explain also errors??
 
@@
 - table caption equation references added
-- in section 3 sentence with equation (9) clarified
 + highlighted
@@
 
+- section 3, sentence with equation (9) clarified
 - section 3, second sentence: abbreviated 'sunspot number'
@@
 
++ is it ok?
+
 - a few lines before: added 'and' between references 'Bruno et al. (1986) and Balogh et al. (1999)'
@@
 - switched order of figures 10 and 11
-- added top and bottom pointers to both references of now figure 10
+- added 'top' and 'bottom' pointers to both references of now figure 10
 + highlighted
@@
 
-- adopted
+- corrected
 + highlighted
@@
 
+- added introductory sentences
 + highlighted
-+ look into it
++ smooth topic change
++ why are short-term SSN predictions relevant?
 + additional argument is first perihelion
@@
 
+- yes, added reference
 + highlighted
-+ explain
++ yes, maybe note these expectations and add reference
 
@@
 
-+ answer/explain
+- yes, explained which SSN the predictions and error bands are based on
++ yes, they use different assumptions for the predicted SSN; SWPC expected ranges...
++ explain which SSN the predictions are based on...
++ explain which SSN ranges the error bands are based on...
 
@@
 
++ equations only to be used with lognormal distribution, because median is not actual median
+
 Page 23, last but one paragraph: Again, there are points here that have already been said twice above.

### 2017-10-13 paperMVVB/sections/content.tex
#4 worked on referee comments; made changes bold face

@@
 %SSN prediction
-\hl{For SSN short-term predictions } several sources are available.
+\textbf{Aside from the solar distance the derived solar wind parameter models depend on the SSN.
+Short-term predictions of the SSN can be used for the solar wind predictions of PSP's early perihelia and also for refining the solar wind predictions during PSP's mission.} Several sources are available for SSN short-term predictions.
 The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter combined method).
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas \textbf{the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.}
-\hl{For the prediction of the next solar cycle we simply assume a pattern similar to the last cycle and thus shift the last cycle by 11~years.
-} Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in \textbf{the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.}
+The SSN for PSP's first perihelion will be small---certainly below 20, whereas \textbf{the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.} \textbf{However \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
+Therefore we simply assume a pattern similar to the last cycle for the prediction of the next solar} cycle and thus shift the last cycle by 11~years.
+Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in \textbf{the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.}
 
 %\subsection{PSP solar wind environment estimation}
-Implementing the predicted SSN for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected.
+Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected.
 Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
-In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
 \begin{figure}
@@
 \end{figure}
+\textbf{Monthly SSNs---shifted by the time lags specific to the solar wind parameters---are used in the calculation of the solar wind predictions.
+These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
+The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.} In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
 

### 2017-10-16 paperMVVB_referee/referee_report_responses.txt
#5 worked on referee comments; made changes bold face

@@
 
-- procedural steps explained in detail
+- procedural steps explained in detail, following the specific comments
 - clarified the meaning of the parameters in the tables
 - linked the fit equations in the table captions
+- combined the conclusion and summary sections
+- moved final functions into section 5
 + procedural steps to be explained in detail
@@
 + highlighted
-+ what does that mean? no?
++ if median and mean are of similar values, this is an indication that the distribution is symmetrical (gaussian perhaps?)
 
@@
 
-+ is it reliable? it is calculated from that data
++ is it reliable? it is calculated from that data, added: extrapolated intersection
 
@@
 
+- added an explaining sentence
 + highlighted
 + DQCS model assumes 3.1 nT at 1 au coming from CHs at +-60° latitudes (excluding field from equatorial slow wind belt)
+
++ need new magnetic field model?
 
@@
 
+- combined discussion and summary sections
+- integrated first paragraph of summary into beginning of discussion section
+- removed the second mentioning of the procedure
 + highlighted
 + combine both
+
+- removed summary caption
++ retain section caption?
 
@@
 
-+ move equations or explain
+- inserted all final equations into end of section 5, after equation (11)
+- removed equations from summary and referenced them instead
++ move equations
 
@@
 
+- integrated list item about slow/fast wind balance into velocity list item
+
 Page 23, last but one paragraph: Again, there are points here that have already been said twice above.
 
+- removed paragraph
 + highlighted

### 2017-10-16 paperMVVB/sections/content.tex
#5 worked on referee comments; made changes bold face

@@
 For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, \hl{but differ for the extreme values, mainly caused by CME events. } 
-The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is overestimated as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-The velocity's compositional lognormal fit only slightly \hl{overestimates } its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is \hl{overestimated} as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
@@
 Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean \hl{is \textbf{getting slightly} lower than the median at smaller distances }.
-Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as mentioned in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, \hl{having an \textbf{extrapolated} intersection at } \SI{0.082}{\au}.
+Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as mentioned in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, having an \textbf{extrapolated} intersection at \SI{0.082}{\au}.
 Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
@@
 \end{align}
-Thus we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
+Thus\textbf{, implementing the median and average relations into the lognormal function (\ref{eq:single_lognormal_fit_function}),} we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
+\textbf{The corresponding median and average relations for each solar wind parameter, with the values resulting from our analyses, are listed in the following.
+Their numerical values are the fit parameters from Table~\ref{tab:ssn_fit_parameters} and the exponents from Table~\ref{tab:extrapolation_model_fit_parameters}.}
 
-This model averages over seasonal variations because it is based on yearly data.
+\textbf{\begin{itemize}
+	\item The magnetic field strength relations, depending on solar activity and solar distance, are:
+	\begin{align}
+		B_\text{med}(ssn,r) &= (\SI{0.0131}{\nT} \cdot ssn + \SI{4.29}{\nT}) \cdot r^{-1.66}	\,,	\label{eq:median_B}\\
+		B_\text{avg}(ssn,r) &= 1.0879 \cdot B_\text{med}(ssn,r)\,.
+	\end{align}
+	\item The proton velocity relations for the slow and fast components, depending on solar distance, are:
+	\begin{align}
+		v_\text{med}^\text{slow}(r) &= \SI{363}{\km\per\s} \cdot r^{0.099}	\,,&	&	&v_\text{med}^\text{fast}(r) &= \SI{483}{\km\per\s} \cdot r^{0.099}	\,,	\label{eq:median_v}\\
+		v_\text{avg}^\text{slow}(r) &= 1.0101 \cdot v_\text{med}^\text{slow}(r)	\,,&	&	&v_\text{avg}^\text{fast}(r) &= 1.023 \cdot v_\text{med}^\text{fast}(r)	\,.
+	\end{align}
+	The share of both components is balanced with solar activity:
+	\begin{align}
+		c(ssn) = -0.00180 \cdot ssn + 0.64	\,.	\label{eq:balance_v}
+	\end{align}
+	\item The relations of the proton density are:
+	\begin{align}
+		n_\text{med}(ssn,r) &= \left(\SI{0.0038}{\per\cm\cubed} \cdot ssn + \SI{4.50}{\per\cm\cubed}\right) \cdot r^{-2.11}	\,,	\label{eq:median_n}\\
+		n_\text{avg}(ssn,r) &= 1.305 \cdot n_\text{med}(ssn,r)\,.
+	\end{align}
+	\item The proton temperature relations are:
+	\begin{align}
+		T_\text{med}(ssn,r) &= (\SI{197}{\K} \cdot ssn + \SI{57300}{\K}) \cdot r^{-1.10}	\,,	\label{eq:median_T}\\
+		T_\text{avg}(ssn,r) &= 1.654 \cdot T_\text{med}(ssn,r)\,.
+	\end{align}
+\end{itemize}}
+
+\textbf{These models average} over seasonal variations because \textbf{they are} based on yearly data.
 As the OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
@@
 
-We extrapolate the derived empirical solar wind models (\ref{eq:general_sw_model}) to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
+We extrapolate the derived empirical solar wind \textbf{models} to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
 \begin{figure*}
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-\textbf{We suggest that this difference is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , \hl{which for smaller distances deviates more from the } model’s lognormal distribution.
+\textbf{We cannot compare with their absolute values, because their DQCS model assumes fields of \SI{3.1}{\nT} at \SI{1}{\au} coming from coronal holes with boundaries at \SI{+-60}{\degree} latitudes (it excludes the fields from the equatorial slow wind belt).}
+\textbf{We suggest that the difference in slope is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , which for smaller distances deviates more from the model’s lognormal distribution.
 %velocity:
@@
 \label{sec:discussion}
-We started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by lognormally fitting the about 40~years of in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, velocity, density and temperature.
+\textbf{The scientific objective of this study, being part of the German contribution Coronagraphic German and US Solar Probe Plus Survey (CGAUSS) to the Wide field Imager for Solar Probe (WISPR), is to model the solar wind environment for the Parker Solar Probe mission (formerly Solar probe Plus) to be launched mid 2018.}
+
+\textbf{For this purpose we} started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by \textbf{deriving lognormal representations of the} in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, \textbf{proton} velocity, density and temperature.
 Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
@@
 In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
-The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, combined with SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
 Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
@@
 
-\section{Summary}
-\label{sec:summary}
-The scientific objective of this study, being part of the German contribution Coronagraphic German and US Solar Probe Plus Survey (CGAUSS) to the Wide field Imager for Solar Probe (WISPR), is to model the solar wind environment for the Parker Solar Probe mission (formerly Solar probe Plus) to be launched mid 2018.
-
-\hl{For this purpose we derived lognormal representations } of the frequency distributions’ shapes of the four key solar wind parameters magnetic field strength, proton velocity, proton density and proton temperature for the near-Earth solar wind OMNI data, and the Helios~1 and 2 data obtained over the solar distance range \SIrange{0.29}{0.98}{\au}.
-The dependencies of these frequency distributions on solar activity, as measured by the international sunspot number, and on radial distance to the Sun were modeled with analytical relations and then extrapolated to the Parker Solar Probe orbit, taking into account predictions of the sunspot number.
+%\section{Summary}
+%\label{sec:summary}
 With the resulting CGAUSS empirical solar wind model for PSP the following main results for the bulk solar wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
 \begin{itemize}
-	\item The dependency of the magnetic field strength median value on solar activity and radial distance is:
-	\begin{align}
-		B_\text{med}(ssn,r) = (\SI{0.0131}{\nT} \cdot ssn + \SI{4.29}{\nT}) \cdot r^{-1.66}	\,.
-	\end{align}
-	This approximation seems valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
-	\item The estimated  magnetic field strength values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.	
-	\item The radial dependencies of the proton velocity median values for slow and fast solar wind are:
-	\begin{align}
-		v_\text{slow}(r) &= \SI{363}{\km\per\s} \cdot r^{0.099}	\,,\\
-%		\intertext{and}
-		v_\text{fast}(r) &= \SI{483}{\km\per\s} \cdot r^{0.099}	\,.
-	\end{align}
-	These relations appear valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
+	\item The dependency of the magnetic field strength median value \textbf{(\ref{eq:median_B})} on solar activity and radial \textbf{distance seems} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
+	\item The estimated magnetic field strength median values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
+The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity \textbf{with their balance relation (\ref{eq:balance_v})}.
+Thus, at solar minimum with sunspot number around 0 the slow wind \textbf{component} contributes about \SI{64}{\%} and dropping to \SI{28}{\%} during solar maximum conditions with sunspot numbers around 200.
 	\item The calculated median velocity values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
-
-	\item The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity, their balance was found to be $c(ssn) = -0.00180 \cdot ssn + 0.64$.
-Thus, at solar minimum with sunspot number around 0 the slow wind contributes about \SI{64}{\%} and dropping to \SI{28}{\%} during solar maximum conditions with sunspot numbers around 200.
-	\item The median proton density relation is found to be:
-	\begin{align}
-		n_\text{med}(ssn,r) = \left(\SI{0.0038}{\per\cm\cubed} \cdot ssn + \SI{4.50}{\per\cm\cubed}\right) \cdot r^{-2.11}	\,.
-	\end{align}
-	This relation seems valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+	\item The median proton density \textbf{relation (\ref{eq:median_n}) seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
 	\item The estimated density values for PSP's first and closest perihelion are \SI{4015}{\per\cm\cubed} and \SI{9733}{\per\cm\cubed}.
-	\item The derived correlation function for the median proton temperature is:
-	\begin{align}
-		T_\text{med}(ssn,r) = (\SI{197}{\K} \cdot ssn + \SI{57300}{\K}) \cdot r^{-1.10}	\,.
-	\end{align}
-	Around PSP’s perihelion this relation seems to provide too high temperature values in comparison to coronal measurements.
+	\item The derived correlation function for the median proton \textbf{temperature (\ref{eq:median_T}) seems} to provide too high temperature values \textbf{around PSP’s perihelion} in comparison to coronal measurements.
 	\item The estimated temperature values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}
-\hl{The overestimation of the extrapolated velocity and temperature values at distances below } \SI{20}{\Rs} \hl{ indicate the occurrence of solar wind acceleration and heating processes, which PSP will thus be able to directly measure as planned.
-Note that the study of extreme solar wind parameters associated with extreme CMEs was beyond the scope of this study as well as an estimate of the level of turbulence increasing with distance to the Sun as observed by the Helios probes inside individual solar wind streams.
-}
 

### 2017-10-17 paperMVVB_referee/referee_report_responses.txt
corrected PSP density error in text and figs 12+13; created new figure 14

@@
 
+- other changes:
 - added referee acknowledgment
+- We found mismatching density values and corrected a typo in our density calculation.
+The error affected the densities for the first and nearest perihelia and the curves for density in figures 12 and 13.
+(abstract, section 6 and summary: corrected values 4015 to 214 and 9733 to 2951 cm-3)
+- caption figure 13: removed a duplicate 'during'; replaced nearest with closest
+- added a new figure: figure 14

### 2017-10-17 paperMVVB/sections/abstract.tex
corrected PSP density error in text and figs 12+13; created new figure 14

@@
 {The CGAUSS empirical solar wind model for PSP yields dependencies of the solar wind parameters on solar activity and radial distance.
-The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K}.
-The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K}.
+The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}.
+The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
 \textbf{Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.

### 2017-10-17 paperMVVB/sections/content.tex
corrected PSP density error in text and figs 12+13; created new figure 14

@@
 Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected.
-Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
+Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_e_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12 days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
 For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
-	\label{fig:SPP_perihelia_prediction_e_plot}
+	\label{fig:SPP_perihelia_prediction_f_plot}
 \end{figure}
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_e_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during during 12 days in 2024 with PSP's nearest perihelion at \SI{0.0459}{\au}.
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
+	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's \textbf{closest} perihelion at \SI{0.0459}{\au}.
 For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
-	\label{fig:SPP_perihelia_prediction_nearest_e_plot}
+	\label{fig:SPP_perihelia_prediction_nearest_f_plot}
 \end{figure}
@@
 These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
-The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.} In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{4015}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{9733}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
+The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.} In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
+%B
+% 87.3642361846083
+%N
+% 213.613795298952	first
+% 2950.67837375615	nearest
+% 2925.63248639046	SSN 0
+% 3421.59065204775	SSN 200
+%T
+% 503136.759398494
+
+(see Fig.~\ref{fig:SPP_sw_distributions})\\
+\begin{figure}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions.pdf}}
+	\caption{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those extrapolated to PSP's first and closest perihelia.}
+	\label{fig:SPP_sw_distributions}
+\end{figure}
 
@@
 	\item The median proton density \textbf{relation (\ref{eq:median_n}) seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-	\item The estimated density values for PSP's first and closest perihelion are \SI{4015}{\per\cm\cubed} and \SI{9733}{\per\cm\cubed}.
+	\item The estimated density values for PSP's first and closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
 	\item The derived correlation function for the median proton \textbf{temperature (\ref{eq:median_T}) seems} to provide too high temperature values \textbf{around PSP’s perihelion} in comparison to coronal measurements.

### 2017-10-18 paperMVVB_referee/referee_report_responses.txt
text to figure 14; difference to simple-minded approach; made changes bold face

@@
 
-- ...
+- added a new figure in end of section 6: figure 14 shows the predicted solar wind distributions at the first and closest perihelia
 + use the distributions for the predictions (add perihelia figures of distributions)
+
+- true, the results would not be that different. We stated that in the discussion section and explained the advantage of our method
 + state advantage over simple-minded approach (example of simple-minded approach; state how different the results are)
-+ maybe stress Helios data bias to cycle minimum (section 4, third paragraph)
 
@@
 - switched order of figures 10 and 11
-- added 'top' and 'bottom' pointers to both references of now figure 10
+- added 'top' and 'bottom' pointers to both references of now figure 10 and added the time when the closest perihelion will occur at the first figure reference
 + highlighted
@@
 (abstract, section 6 and summary: corrected values 4015 to 214 and 9733 to 2951 cm-3)
-- caption figure 13: removed a duplicate 'during'; replaced nearest with closest
-- added a new figure: figure 14
+- caption figure 13: removed a duplicate 'during'; replaced nearest with first closest

### 2017-10-18 paperMVVB/sections/abstract.tex
text to figure 14; difference to simple-minded approach; made changes bold face

@@
 Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
-{The CGAUSS empirical solar wind model for PSP yields dependencies of the solar wind parameters on solar activity and radial distance.
+{The CGAUSS empirical solar wind model for PSP yields dependencies \textbf{on solar activity and solar distance for the solar wind parameters' frequency distributions}.
 The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}.
-The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
+The estimates for PSP’s \textbf{first closest perihelion, occuring} in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
 \textbf{Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.

### 2017-10-18 paperMVVB/sections/content.tex
text to figure 14; difference to simple-minded approach; made changes bold face

@@
 % $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
-For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters ($d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$).
+For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters $d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$.
 Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
@@
 With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
-Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs} \citep{Fox2015} as plotted in \textbf{the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
+Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs}\textbf{.
+This distance will be reached with the 22nd perihelion in December 2024 \citep{Fox2015} as plotted in the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
 \begin{figure}
@@
 %\subsection{PSP solar wind environment estimation}
-Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, we can finally derive the estimated solar wind environment $W'''(x,ssn,r)$, to infer which solar wind parameter magnitudes can be expected.
-Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the closest perihelion in December 2024.
+Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, \textbf{we can infer} which solar wind parameter magnitudes can be expected.
+Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show \textbf{the median values (\ref{eq:median_with_ssn}) of} the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the \textbf{first} closest perihelion in December 2024.
 \begin{figure}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's \textbf{closest} perihelion at \SI{0.0459}{\au}.
+	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) \textbf{during} 12~days in 2024 with PSP's \textbf{22nd (the first closest)} perihelion at \SI{0.0459}{\au}.
 For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
@@
 \end{figure}
+In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the \textbf{first} closest approach at \SI{0.046}{\au}.
 \textbf{Monthly SSNs---shifted by the time lags specific to the solar wind parameters---are used in the calculation of the solar wind predictions.
 These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
-The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.} In the beginning of the mission peak median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the closest approach at \SI{0.046}{\au}.
+The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.}
 %B
@@
 
-(see Fig.~\ref{fig:SPP_sw_distributions})\\
+\textbf{Now the estimated solar wind environment can finally be derived from the function $W'''(x,ssn,r)$.
+The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelia are plotted in Fig.~\ref{fig:SPP_sw_distributions}.}
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions.pdf}}
-	\caption{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those extrapolated to PSP's first and closest perihelia.}
+	\caption{\textbf{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelia.
+In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}}
 	\label{fig:SPP_sw_distributions}
 \end{figure}
+\textbf{Note again that the velocity and temperature distributions for the 22nd perihelion are only upper limits and the actual by PSP to be encountered values are expected to be smaller.}
 
@@
 The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
-Though, it is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
+
+\textbf{For determining solar activity and solar distance dependent relations exclusively for the median and average solar wind values, we would have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data---scaled with the SSN.
+The results of this simpler analysis method would be similar (at least the distance scaling results are similar; compare the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}) and would be sufficient for this purpose.
+Though, we are not only interested in the averages but in the bulk distributions, that is, the whole range of values which might occur.
+For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and average values determines the width of the lognormal distributions.
+With our approach we are able to control and fit this distance.}
+
+\textbf{It} is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
 The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.
-
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
@@
 \begin{itemize}
-	\item The dependency of the magnetic field strength median value \textbf{(\ref{eq:median_B})} on solar activity and radial \textbf{distance seems} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
-	\item The estimated magnetic field strength median values for PSP's first and closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance seems} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
+	\item The estimated magnetic field strength \textbf{median values (\ref{eq:median_B})} for PSP's first and \textbf{first} closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
 	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
 The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity \textbf{with their balance relation (\ref{eq:balance_v})}.
-Thus, at solar minimum with sunspot number around 0 the slow wind \textbf{component} contributes about \SI{64}{\%} and dropping to \SI{28}{\%} during solar maximum conditions with sunspot numbers around 200.
-	\item The calculated median velocity values for PSP's first and closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
-	\item The median proton density \textbf{relation (\ref{eq:median_n}) seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-	\item The estimated density values for PSP's first and closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
-	\item The derived correlation function for the median proton \textbf{temperature (\ref{eq:median_T}) seems} to provide too high temperature values \textbf{around PSP’s perihelion} in comparison to coronal measurements.
-	\item The estimated temperature values for PSP's first and closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+Thus, at solar minimum with \textbf{a SSN} around 0 the slow wind \textbf{component} contributes about \SI{64}{\%} and \textbf{drops} to \SI{28}{\%} during solar maximum conditions with \textbf{a SSN} around 200.
+	\item The calculated median velocity values for PSP's first and \textbf{first} closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+	\item The \textbf{proton density relation seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+	\item The estimated density \textbf{median values (\ref{eq:median_n})} for PSP's first and \textbf{first} closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
+	\item The derived correlation function for the \textbf{proton temperature seems} to provide too high temperature values \textbf{around PSP’s closest perihelion} in comparison to coronal measurements.
+	\item The estimated temperature \textbf{median values (\ref{eq:median_T})} for PSP's first and \textbf{first} closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}

### 2017-10-21 paperMVVB/sections/content.tex
integrated changes by MVVB

@@
 Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, \hl{SOHO} \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, SOHO \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
@@
 %transition
-For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, \hl{but differ for the extreme values, mainly caused by CME events. } 
-The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is \hl{overestimated} as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well\textbf{.
+The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.} The simple lognormal fit functions underestimate the \textbf{frequencies in} their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}\textbf{, this appears to be because CMEs do not come with abnormally high temperatures.} The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}	&\multicolumn{1}{c}{SSN lag}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}	&\multicolumn{1}{c}{SSN lag}\\
 		\cline{3-4}\cline{6-7}
@@
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
+		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
 %		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
-		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
-		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
+		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
+		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
 		\hline
-		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
-			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
+		\multicolumn{1}{l}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
+		\multicolumn{1}{l}{\textbf{[\SI{e2}{\km\per\s}]}}	&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
 		\hline
 	\end{tabular}
-	\tablefoot{
-		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
-	}
 \end{table*}
@@
 		\cline{2-3}	\cline{5-6}
-			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
+			&\multicolumn{1}{c}{$d_\text{med}$}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
 		\hline
-		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
-		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
-		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
-		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
+		\textbf{Magnetic field [\si{nT}]}	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
+		\textbf{Velocity [\SI{e2}{\km\per\s}]}	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
+		\textbf{Density [\si{\per\cm\cubed}]}	&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
+		\textbf{Temperature [\SI{e4}{\K}]}	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
 		\hline
 	\end{tabular}
-	\tablefoot{
-		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
-	}
 \end{table*}
@@
 		\hline\hline
-		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{Seasonal variation}\\
+		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{Seasonal variation}\\
 			&	&\multicolumn{1}{c}{$d'_\text{med}$}	&\multicolumn{1}{c}{$d'_\text{avg}$}	&\multicolumn{1}{c}{$e'$}	&$c'$	&\multicolumn{1}{c}{$\Delta d$ [\%]}\\
 		\hline
-		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
-		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
-		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\
+		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
+		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
+		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\
 		\hline
-		\multirow{2}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
-			&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\
+		\multirow{2}{*}{\textbf{Velocity}}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
+		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}}	&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\
 		\cline{2-7}
-		\multicolumn{2}{r}{$W''_\text{II}$}	&4.13(13)\tablefootmark{b}	&4.47(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
+			&$W''_\text{II}$	&4.13(13)\tablefootmark{a}	&4.47(11)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
 		\hline
@@
 	\tablefoot{
-		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
-		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
+		\tablefoottext{a}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
 	}

### 2017-10-22 paperMVVB/sections/content.tex
#2 integrated changes by MVVB

@@
 For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN.
-\textbf{Thus we obtain on solar activity depending models for the frequency distributions of all four solar wind parameters.}
+\textbf{Thus we obtain solar activity depending models for the frequency distributions of all four solar wind parameters.}
 
@@
 \textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$.
-This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to profit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
+This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to benefit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
 \begin{table*}
-	\caption{Resulting fit coefficients from the OMNI data fitting with \textbf{the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}.
+	\caption{Resulting fit coefficients from the OMNI data \textbf{based on the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}.
 For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given.
@@
 The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
-The maximal velocities of CME events larger than \SI{800}{\km\per\s} are indicated with circles.}
+The higher velocity data points above \SI{800}{\km\per\s} \hl{identified as CME events by BS1998, Sheeley1981 are circled red.}}
 	\label{fig:radial_fit_4_thesis_light_b_skip}
@@
 %crossing distances
-\textbf{Our from the Helios data fit acquired} mean and median velocity fit exponents are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
+\textbf{The mean and median velocity fit exponents acquired from the Helios data} are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
 Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean \hl{is \textbf{getting slightly} lower than the median at smaller distances }.
@@
 
-\textbf{For being able to still fit and extrapolate lognormal functions with the data, we assume that the shapes keep being lognormal at all distances.
+\textbf{In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
 For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.} It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.

### 2017-10-23 paperMVVB/sections/acknowledgments.tex
referee and w/o figures versions added
adopted referee comments; made changes bold face
#2 integrated changes by MVVB

@@
 \begin{acknowledgements}
-	The authors acknowledge support of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS) project for WISPR by the German Aerospace Center (DLR) under grant 50~OL~1601 as national contribution to the Parker Solar Probe mission.
+	The authors acknowledge support of the Coronagraphic German and US SolarProbePlus Survey (CGAUSS) project for WISPR by the German Aerospace Center (DLR) under grant 50~OL~1601 as national contribution to the Parker Solar Probe mission.
 The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data.
@@
 The PSP SPICE kernel was kindly provided by Angelos~Vourlidas.
+\textbf{The authors thank the referee for the careful review of this manuscript and helpful comments and suggestions.}
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.
-
 %	facilities/persons which made available the Helios and OMNI data\\

### 2017-10-23 paperMVVB/sections/content.tex
#2 integrated changes by MVVB

@@
 \begin{table*}
-	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data.
+	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, based on equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data.
 \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
@@
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-\textbf{The increasing high velocity tail with distance} comes from using the same exponent for both slow and fast components.
+\textbf{The increasing high velocity tail with distance arises} from using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 \textbf{This solar wind model} for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The variation of yearly power law fit exponents \textbf{by fitting the solar distance dependency (\ref{eq:power_function})} are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
+The \textbf{variations of the} yearly power law fit exponents \textbf{from fitting the solar distance dependency (\ref{eq:power_function})} are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
 It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature exponents.
@@
 Thus\textbf{, implementing the median and average relations into the lognormal function (\ref{eq:single_lognormal_fit_function}),} we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
-\textbf{The corresponding median and average relations for each solar wind parameter, with the values resulting from our analyses, are listed in the following.
+\textbf{The corresponding median and average relations for each solar wind parameter, based on values resulting from our analyses, are listed below.
 Their numerical values are the fit parameters from Table~\ref{tab:ssn_fit_parameters} and the exponents from Table~\ref{tab:extrapolation_model_fit_parameters}.}
@@
 	\end{align}
-	The share of both components is balanced with solar activity:
+	The share of both components is found to be balanced with solar activity:
 	\begin{align}
@@
 	\end{align}
-	\item The relations of the proton density are:
+	\item The derived relations of the proton density are:
 	\begin{align}
@@
 	\end{align}
-	\item The proton temperature relations are:
+	\item The derived proton temperature relations are:
 	\begin{align}
@@
 
-\textbf{These models average} over seasonal variations because \textbf{they are} based on yearly data.
+\textbf{These relations average} over seasonal variations because \textbf{they are} based on yearly data.
 As the OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
@@
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
-\textbf{The models obtained from Helios and OMNI measurements} are extrapolated to the PSP region---for the range between the extreme cases of solar minimum and maximum, i.e., $0 \le ssn \le 200$\textbf{.
-The lower edges of the shaded areas correspond to solar minimum, the upper edges to maximum.} Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \textbf{\citet{Sheeley1997} and \citet{Wang2000}}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
+\textbf{The models obtained from Helios and OMNI measurements} are extrapolated to the PSP region \textbf{for SSN values between} solar minimum and maximum, i.e., $0 \le ssn \le 200$\textbf{.
+The lower edges of the shaded areas correspond to solar minimum, the upper edges to solar maximum.} Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \textbf{\citet{Sheeley1997} and \citet{Wang2000}}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
 	\label{fig:sw_extrapolation_ssn_e_plot}
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-\textbf{We cannot compare with their absolute values, because their DQCS model assumes fields of \SI{3.1}{\nT} at \SI{1}{\au} coming from coronal holes with boundaries at \SI{+-60}{\degree} latitudes (it excludes the fields from the equatorial slow wind belt).}
+\textbf{It should be noted that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.}
+%Since we cannot compare with their absolute values, because their DQCS model assumes fields of \SI{3.1}{\nT} at \SI{1}{\au} assumed to originate from coronal holes with boundaries at \SI{+-60}{\degree} latitude, excluding the fields from the equatorial slow wind belt.
 \textbf{We suggest that the difference in slope is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , which for smaller distances deviates more from the model’s lognormal distribution.
@@
 Their model shows that the density distance dependency scales with $r^{-2}$ and steepens just below \SI{10}{\Rs} with $r^{-6}$.
-\textbf{We assumed a solar wind helium abundance of \SI{5}{\%} to convert their electron densities to proton densities.}
+\textbf{We assumed a solar wind helium abundance of \SI{5}{\%} to convert these electron densities to proton densities.}
 %temperature:
@@
 \end{figure}
+% SSN sources and error ranges for first perihelion
+% magnetic field:
+% SWPC prediction - 0 years
+% SWPC expected SSN ranges
+% velocity:
+% actual monthly SSN - 3 years
+% not plotted
+% density:
+% actual monthly SSN - 6 years
+% SIDC given std. dev. from stations
+% temperature:
+% actual monthly SSN - 3 years
+% SIDC given std. dev. from stations
 \begin{figure}
@@
 \end{figure}
+% SSN sources and error ranges for first closest perihelion
+% magnetic field:
+% actual monthly SSN - 11 years
+% half/twice SSN
+% velocity:
+% actual monthly SSN - 14 years
+% not plotted
+% density:
+% SWPC prediction - 0 years
+% SWPC expected SSN ranges
+% temperature:
+% actual monthly SSN - 14 years
+% half/twice SSN
 In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the \textbf{first} closest approach at \SI{0.046}{\au}.
@@
 These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
-The error bands given in both figures, calculated by error propagation, include these SSN ranges and the derived fit parameter errors.}
+The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.}
 %B
@@
 
-\textbf{Now the estimated solar wind environment can finally be derived from the function $W'''(x,ssn,r)$.
+\textbf{Finally the estimated solar wind environment can be derived from the function $W'''(x,ssn,r)$.
 The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelia are plotted in Fig.~\ref{fig:SPP_sw_distributions}.}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions.pdf}}
-	\caption{\textbf{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelia.
+	\caption{\textbf{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelion.
 In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}}
@@
 
-\section{Discussion}
-\label{sec:discussion}
+\section{Discussion and summary}
+\label{sec:discussion_and_summary}
 \textbf{The scientific objective of this study, being part of the German contribution Coronagraphic German and US Solar Probe Plus Survey (CGAUSS) to the Wide field Imager for Solar Probe (WISPR), is to model the solar wind environment for the Parker Solar Probe mission (formerly Solar probe Plus) to be launched mid 2018.}
@@
 
-\textbf{For determining solar activity and solar distance dependent relations exclusively for the median and average solar wind values, we would have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data---scaled with the SSN.
-The results of this simpler analysis method would be similar (at least the distance scaling results are similar; compare the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}) and would be sufficient for this purpose.
-Though, we are not only interested in the averages but in the bulk distributions, that is, the whole range of values which might occur.
+\textbf{For determining solar activity and solar distance dependent relations for the median and average solar wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
+It is expected that the results of a simpler analysis would have similar distance scaling results, as can be inferred from the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}.
+However, in our study we are not only interested in averages but rather in bulk distributions, that is, the whole range of values that might occur.
 For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and average values determines the width of the lognormal distributions.
@@
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-\textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements of the other studies.
+\textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements seen in existing studies.
 This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is believed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
 
@@
 \begin{itemize}
-	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance seems} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
+	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance appears} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
 	\item The estimated magnetic field strength \textbf{median values (\ref{eq:median_B})} for PSP's first and \textbf{first} closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
@@
 	\item The calculated median velocity values for PSP's first and \textbf{first} closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
-	\item The \textbf{proton density relation seems} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+	\item The \textbf{proton density relation appears} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
 	\item The estimated density \textbf{median values (\ref{eq:median_n})} for PSP's first and \textbf{first} closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
-	\item The derived correlation function for the \textbf{proton temperature seems} to provide too high temperature values \textbf{around PSP’s closest perihelion} in comparison to coronal measurements.
+	\item The derived correlation function for the \textbf{proton temperature appears} to provide too high temperature values \textbf{around PSP’s closest perihelion} in comparison to coronal measurements.
 	\item The estimated temperature \textbf{median values (\ref{eq:median_T})} for PSP's first and \textbf{first} closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.

### 2017-10-25 paperMVVB/sections/content.tex
#4 integrated changes by MVVB; improved figures

@@
 For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well\textbf{.
-The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.} The simple lognormal fit functions underestimate the \textbf{frequencies in} their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}\textbf{, this appears to be because CMEs do not come with abnormally high temperatures.} The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.} The simple lognormal fit functions underestimate the \textbf{frequencies in} their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}\textbf{, this appears to be because CMEs do not come with abnormally high temperatures, but rather with temperatures lower than those of the average solar wind \citep{Forsyth2006}.} The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
@@
 The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
-The higher velocity data points above \SI{800}{\km\per\s} \hl{identified as CME events by BS1998, Sheeley1981 are circled red.}}
+\textbf{The high velocity data points above \SI{800}{\km\per\s} (circled red) are identified as CME events \citep[e.g.,][]{Bothmer1998}.}}
 	\label{fig:radial_fit_4_thesis_light_b_skip}
@@
 \textbf{The mean and median velocity fit exponents acquired from the Helios data} are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
-Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean \hl{is \textbf{getting slightly} lower than the median at smaller distances }.
+Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean is \textbf{getting slightly} lower than the median at smaller distances.
 Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as mentioned in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, having an \textbf{extrapolated} intersection at \SI{0.082}{\au}.
@@
 Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC \textbf{Standard Curves Kalman filter} prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
 	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
@@
 
-We extrapolate the derived empirical solar wind \textbf{models} to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}.
+We extrapolate the derived empirical solar wind \textbf{models} to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}.
 \begin{figure*}
-	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_e_plot.pdf}
+	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_f_plot.pdf}
 	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
@@
 The lower edges of the shaded areas correspond to solar minimum, the upper edges to solar maximum.} Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \textbf{\citet{Sheeley1997} and \citet{Wang2000}}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
-	\label{fig:sw_extrapolation_ssn_e_plot}
+	\label{fig:sw_extrapolation_ssn_f_plot}
 \end{figure*}
@@
 Short-term predictions of the SSN can be used for the solar wind predictions of PSP's early perihelia and also for refining the solar wind predictions during PSP's mission.} Several sources are available for SSN short-term predictions.
-The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter combined method).
+The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter \textbf{Standard Curve} method).
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
@@
 	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
-For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
+For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
 	\label{fig:SPP_perihelia_prediction_f_plot}
@@
 	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) \textbf{during} 12~days in 2024 with PSP's \textbf{22nd (the first closest)} perihelion at \SI{0.0459}{\au}.
-For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted lines).}
+For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
 	\label{fig:SPP_perihelia_prediction_nearest_f_plot}
@@
 \textbf{Finally the estimated solar wind environment can be derived from the function $W'''(x,ssn,r)$.
-The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelia are plotted in Fig.~\ref{fig:SPP_sw_distributions}.}
+The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelia are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.}
 \begin{figure}
-	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions.pdf}}
+	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions_b.pdf}}
 	\caption{\textbf{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelion.
 In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}}
-	\label{fig:SPP_sw_distributions}
+	\label{fig:SPP_sw_distributions_b}
 \end{figure}
@@
 However, in our study we are not only interested in averages but rather in bulk distributions, that is, the whole range of values that might occur.
-For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and average values determines the width of the lognormal distributions.
-With our approach we are able to control and fit this distance.}
+For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and average values determines the width of the lognormal distributions.}
 
@@
 \textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements seen in existing studies.
-This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_e_plot}).
+This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}).
 The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).

### 2017-10-26 paperMVVB/sections/abstract.tex
improved wording and grammar; adopted A&A style; improved figures 6 and 14

@@
 
-\date{received date; accepted date}
+\date{Received 25 August 2017; accepted date}
 %First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; fourth changes 24 August 2017; submitted 25 August 2017
@@
 It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
-The scope of this study is to model the solar wind environment for PSP’s unprecedented distances during its prime mission phase during the years \numrange{2018}{2025}.
-The study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
+The scope of this study is to model the solar wind environment for PSP’s unprecedented distances \textbf{in} its prime mission phase during the years \numrange{2018}{2025}.
+The study is performed within the project Coronagraphic German And US \textbf{SolarProbePlus} Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).}	%context
 {We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data.
@@
 Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
-Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
+Finally, the inclusion of SSN predictions and the extrapolation \textbf{down} to PSP’s perihelion \textbf{region} enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
 {The CGAUSS empirical solar wind model for PSP yields dependencies \textbf{on solar activity and solar distance for the solar wind parameters' frequency distributions}.

### 2017-10-26 paperMVVB/sections/content.tex
improved wording and grammar; adopted A&A style; improved figures 6 and 14

@@
 The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
-Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (\textbf{October} 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
 \textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, SOHO \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
@@
 Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
-\textbf{The in situ solar wind measurements closest to the Sun to date were made by} the Helios mission.
+\textbf{The in situ solar wind measurements closest to the Sun to date were made by} the Helios missions.
 \textbf{Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}.
@@
 The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” as stated in \citet{Fox2015}.
-To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurements of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
+To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurements of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles \textbf{(SEPs)} \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
 
 %CGAUSS and WISPR
-The study presented in this paper is undertaken in the Coronagraphic German And US Solar Probe Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).
+The study presented in this paper is undertaken in the Coronagraphic German And US \textbf{SolarProbePlus} Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).
 WISPR will contribute to the PSP science goals by deriving the 3D structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
 It will provide density power spectra over a wide range of structures (e.g., streamers, pseudostreamers and equatorial coronal holes) for determining the roles of turbulence, waves and pressure-balanced structures in the solar wind.
-It will also measure the physical properties, such as speed and density jumps of SEP-producing shocks and their CME drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.
+It will also measure the physical properties, such as speed and density jumps of SEP-producing shocks and their \textbf{coronal mass ejection (CME)} drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.
 
@@
 %section{Solar wind}
-Generally, two types of solar wind are observed in the heliosphere, slow and fast streams \citep{Neugebauer1966,Schwenn1983}.
+Generally two types of solar wind are observed in the heliosphere -- slow and fast streams \citep{Neugebauer1966,Schwenn1983}.
 Slow solar wind has typical speeds \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[p.~144]{Schwenn1990}.
@@
 The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
-Embedded in the slow and fast solar wind streams are transient flows of coronal mass ejections (CMEs), the faster ones driving shock waves ahead \citep{Gosling1974}.
+Embedded in the slow and fast solar wind streams are transient flows of \textbf{CMEs} -- the faster ones driving shock waves ahead \citep{Gosling1974}.
 Their rate follows the solar activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
@@
 It is not known which specific solar wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar wind parameters from existing solar wind measurements and take solar cycle dependencies into account.
-As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \textit{magnetic field strength}, \textit{density} and \textit{temperature}.
-Furthermore, the bulk flow \textit{velocity} is the defining parameter of the two types of solar wind.
+As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \emph{magnetic field strength}, \emph{density} and \emph{temperature}.
+Furthermore, the bulk flow \emph{velocity} is the defining parameter of the two types of solar wind.
 Solar wind quantities, like flux densities, mass flux and plasma beta, can directly be derived from these four parameters.
-In the analyses we treat the solar wind as a proton plasma---the average helium abundance is about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
+In the analyses we treat the solar wind as a proton plasma -- the average helium abundance is about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
 
@@
 From combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions a general solar wind model is build in Sect.~\ref{sec:empirical_solar_wind_model}, representing the solar activity and distance behavior.
-Finally, this empirical model is fed with a SSN prediction and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+Finally, this empirical model is fed with \textbf{SSN predictions} and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
@@
 \label{sec:frequency_distribution}
-The solar wind parameters are highly variable, due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on the phase of the solar activity cycle.
+The solar wind parameters are highly variable due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on the phase of the solar activity cycle.
 Hence, for deriving characteristic frequency distributions for the solar wind parameters, measurements over long-term time spans are needed.
@@
 %hourly data
-It should be noted that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
+\textbf{We note} that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
 
@@
 These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
-Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 ICME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
+Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 \textbf{CME} with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
 
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/histogram_fits_V_a_zoom_dbl_paper_pdfplot.pdf}}
-	\caption{The velocity's frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
+	\caption{\textbf{Velocity} frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
 The fit's median and mean values and its two fit parts are indicated as well.
@@
 
-Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} shows yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number.
+Yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number \textbf{are shown in the upper part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}}.
 The reason for correlating the SSN to the solar wind median values is because the position of a lognormal function is defined by its median.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
-	\caption{The solar wind parameter yearly \textbf{frequencies (grey shading) with yearly medians (lines)} derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
+	\caption{\textbf{Solar} wind parameter yearly \textbf{frequencies (grey shading) with yearly medians (lines)} derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
 Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
@@
 \end{figure}
- Solar wind parameter yearly data frequencies
 The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
@@
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
-Velocity and temperature show a \textbf{time lag} of 3~years with peak correlation coefficients of 0.453 and 0.540.
-The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the by \citet{Bougeret1984} reported density anticorrelation to the SSN.	%p.~406\\
+Velocity and temperature show \textbf{time lags} of 3~years with peak correlation coefficients of 0.453 and 0.540.
+The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the \textbf{density anticorrelation to the SSN} reported by \citet{Bougeret1984}.	%p.~406\\
 % maximal correlation coefficients and their time lags:\\
@@
 \textbf{Next we create solar activity dependent analytical representations of the solar wind frequency distributions.
-This is achieved by shifting the median positions of the lognormal distributions as a linear function of SSN.
-To enable these shifts }, we add a linear SSN dependency to the median
+This is achieved by shifting the median positions of the lognormal distributions as a linear function of the SSN.
+To enable these shifts}, we add a linear SSN dependency to the median
 \begin{align}
@@
 \begin{align}
-	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
+	x_\text{avg}(ssn) &= \left(1 + a_\text{avg}\right) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
 \end{align}
 \textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$.
-This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to benefit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
+This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags determined before for each parameter, to benefit from the higher correlation.
+The values of} the three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
 \begin{table*}
-	\caption{Resulting fit coefficients from the OMNI data \textbf{based on the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}.
+	\caption{Resulting fit coefficients from the OMNI data\textbf{, based on the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}.
 For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given.
@@
 
-As can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}, naturally, the fit models match with the general data trends, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994 and 2003).
+Naturally, the fit models match with the general data trends\textbf{, as can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}}, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994 and 2003).
 \begin{figure*}
@@
 	\caption{Solar wind parameter yearly data frequencies and lognormal fit models, both with their median values (white lines) over the OMNI time period 1963--2016.
-The corresponding yearly SSN and the for the models shifted SSN are indicated by grey and black lines.
-The velocity median is derived from the SSN weighted constant lognormal parts (dotted lines).}
+The corresponding yearly SSN and the \textbf{shifted SSN} for the models are indicated by grey and black lines.
+The velocity median is derived from the SSN-weighted constant lognormal parts (dotted lines).}
 	\label{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}
 \end{figure*}
-The comparison of this model with the yearly data median values with respect to the lagged SSN shows that the medians obtained from the modeling have a quite similar slope as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
+The comparison of this model with the yearly data median values with respect to the lagged SSN shows that the medians obtained from the modeling have a quite similar slope, as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN_a.pdf}}
-	\caption{Solar wind parameter median with respect to the lagged SSN.
+	\caption{Solar wind parameter medians with respect to the lagged SSN.
 The yearly data medians (+) with their weighted linear fit (solid lines) are obtained from OMNI data.
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
-The SSN dependent median (\ref{eq:median_with_ssn}) is derived from the lognormal model fit (dashed line).
-For the velocity the median is derived from the SSN weighting (\ref{eq:balance_with_ssn}) of the slow and fast model parts, whose magnitudes are SSN independent (dotted line).}
+The SSN-dependent median \textbf{(dashed lines)} is derived from the lognormal model fit.
+For the velocity the median is derived from the SSN-weighting (\ref{eq:balance_with_ssn}) of the slow and fast model parts \textbf{(dotted lines)}, whose magnitudes are SSN independent.}
 	\label{fig:OMNI_yearly_BVNTvsSSN_a}
@@
 Again, the solar wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle we keep the two velocity components' positions \textbf{SSN-independent ($x_\text{med} =  b_\text{med}$)} and vary instead their balance with the SSN:
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle, we keep the two velocity components' positions \textbf{SSN-independent ($x_\text{med} =  b_\text{med}$)} and vary instead their balance with the SSN:
 \begin{align}
@@
 \end{align}
-The fit result (see Table~\ref{tab:ssn_fit_parameters}) yields a model in which three years after solar cycle minimum (SSN of zero) the contribution of slow solar wind to the overall solar wind distribution reaches a maximum value of about \SI{64}{\percent} and decreases with increasing SSN as shown in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) yields a model in which three years after solar cycle minimum (SSN of zero) the contribution of slow solar wind to the overall solar wind distribution reaches a maximum value \textbf{(about \SI{64}{\percent})} and decreases with increasing SSN as shown in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
 \begin{figure}
@@
 The linear fit to the yearly data ratio and the derived model ratio show a good agreement (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
-Specific velocity thresholds between slow and fast solar wind cannot be directly compared with the to some degree steeper balance parameter of the double fit function used in this model.
+\textbf{The to some degree steeper balance parameter of the double fit function used in this model cannot be compared directly with} specific velocity thresholds between slow and fast solar wind.
 However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
@@
 \label{sec:solar_distance_dependency}
-In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit a power law dependency to the Helios data.
-We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step it will be extrapolated to the PSP orbit.
+In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit \textbf{power law dependencies} to the Helios data.
+We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step \textbf{they are} extrapolated to the PSP orbit.
 We use the fitting methods of Sect.~\ref{sec:frequency_distribution} for the distance-binned combined data from both Helios probes.
@@
 
-In the same way as the OMNI data we investigate hourly averages of the Helios data.
+We investigate hourly averages of the Helios data \textbf{in the same way as with the OMNI data}.
 The Helios~1 merged hourly data from the magnetometer and plasma instruments \citep{Rosenbauer1977} include $\sim$12.5~orbits for the time range 10~December 1974 until 14~June 1981, those for Helios~2 include $\sim$8~orbits for the time span 1~January 1976 until 4~March 1980.
@@
 %Helios data biased towards solar minimum
-Thus, using this data, one has to keep in mind that its time coverage is unequally distributed over the solar cycle.
-Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
-This Helios data bias towards solar minimum is the reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
+Thus, using this data, \textbf{we point out} that its time coverage is unequally distributed over the solar cycle.
+Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} \textbf{of this period} whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
+This Helios data bias towards solar minimum is \textbf{one} reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
 % data gaps -> uneven coverage -> solar cycle minimum dominates; ratio of max vs min cycle data coverage; for OMNI data negligible\\
@@
 %Helios results, radial gradients see \citet{Schwenn1990} p.~155
-\textbf{Our derived} exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and the slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$\textbf{, ours is $B_\text{avg} \propto r^{-1.55}$}.
+\textbf{Our derived} exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$\textbf{, ours is $B_\text{avg} \propto r^{-1.55}$}.
 %$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
 The velocity exponent \textbf{$v_\text{avg} \propto r^{0.049}$} matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
-The calculated density exponent \textbf{$n_\text{avg} \propto r^{-2.01}$} agrees well with the Helios plasma density model derived by \citet{Bougeret1984}, yielding $n \propto r^{-2.10}$.
+The calculated density exponent \textbf{$n_\text{avg} \propto r^{-2.01}$} agrees well with the Helios plasma density model derived by \citet{Bougeret1984} yielding $n \propto r^{-2.10}$.
 %to the year 1976 normalized   a \SI{1}{\au} density of $n = 6.14\cdot r^{-2.10}\,\text{cm}^{-3}$.
@@
 Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean is \textbf{getting slightly} lower than the median at smaller distances.
-Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as mentioned in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, having an \textbf{extrapolated} intersection at \SI{0.082}{\au}.
+Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as pointed out in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, having an \textbf{extrapolated} intersection at \SI{0.082}{\au}.
 Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
@@
 \textbf{In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
-For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.} It should be noted that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
+For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
+We note} that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
 
 %\subsection{Power law lognormal fitting}
-Next we retrieve the frequency distributions of the four \textbf{solar wind parameters in solar} distance bins of \SI{0.01}{\au}, choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution}---the distributions \textbf{and their median values} are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
+Next we retrieve the frequency distributions of the four \textbf{solar wind parameters in solar} distance bins of \SI{0.01}{\au}, choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution} -- the distributions \textbf{and their median values} are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
 \begin{figure*}
 	\includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_f_plot.pdf}
-	\caption{Frequency distributions of the four solar wind parameters with respect to the solar distance.
+	\caption{Frequency distributions of the four solar wind parameters with respect to solar distance.
 Plotted are the binned Helios data and the power law lognormal fit models with their median values (white lines).
@@
 For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters $d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$.
-Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$.
+Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit -- resulting in $W''_\text{II}(x,r)$.
 The additional fit parameters are the balancing parameter $c'$ and for the second lognormal part $d'_\text{med,2}$ and $d'_\text{avg,2}$.
@@
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-\textbf{The increasing high velocity tail with distance arises} from using the same exponent for both slow and fast components.
+\textbf{The with distance increasing high velocity tail arises} from using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 In order to estimate the solar wind environment for the PSP orbit, we combine the results from the solar wind frequency distributions’ solar activity relationships and their distance dependencies derived from the OMNI and Helios data.
-The result is an empirical solar wind model for the inner heliosphere which will then be extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+The result is an empirical solar wind model for the inner heliosphere which \textbf{is then} extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
@@
 The \textbf{variations of the} yearly power law fit exponents \textbf{from fitting the solar distance dependency (\ref{eq:power_function})} are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
-It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity---at least for the velocity and temperature exponents.
+It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity -- at least for the velocity and temperature exponents.
 \begin{figure}
@@
 %yearly variation of the solar wind parameters' average fit function exponents
-However, for simplicity we assume, that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$, summarized in Table~\ref{tab:mean_median_fit_parameter}, as relative uncertainties.
+However, for simplicity we assume that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$, summarized in Table~\ref{tab:mean_median_fit_parameter}, as relative uncertainties.
 
@@
 \begin{align}
-	x_\text{med}(ssn,r) &= (a_\text{med} \cdot ssn + b_\text{med}) \cdot r^{e'}	\,.	\label{eq:general_sw_model}
+	x_\text{med}(ssn,r) &= \left(a_\text{med} \cdot ssn + b_\text{med}\right) \cdot r^{e'}	\,.	\label{eq:general_sw_model}
 \end{align}
-Thus\textbf{, implementing the median and average relations into the lognormal function (\ref{eq:single_lognormal_fit_function}),} we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
-\textbf{The corresponding median and average relations for each solar wind parameter, based on values resulting from our analyses, are listed below.
+Thus\textbf{, implementing the median and mean relations into the lognormal function (\ref{eq:single_lognormal_fit_function}),} we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
+\textbf{The corresponding median and mean relations for each solar wind parameter, based on the values resulting from our analyses, are listed below.
 Their numerical values are the fit parameters from Table~\ref{tab:ssn_fit_parameters} and the exponents from Table~\ref{tab:extrapolation_model_fit_parameters}.}
@@
 	\begin{align}
-		B_\text{med}(ssn,r) &= (\SI{0.0131}{\nT} \cdot ssn + \SI{4.29}{\nT}) \cdot r^{-1.66}	\,,	\label{eq:median_B}\\
+		B_\text{med}(ssn,r) &= \left(\SI{0.0131}{\nT} \cdot ssn + \SI{4.29}{\nT}\right) \cdot r^{-1.66}	\,,	\label{eq:median_B}\\
 		B_\text{avg}(ssn,r) &= 1.0879 \cdot B_\text{med}(ssn,r)\,.
@@
 	\end{align}
-	The share of both components is found to be balanced with solar activity:
+	The share of both components balanced with solar activity is found to be:
 	\begin{align}
@@
 \textbf{These relations average} over seasonal variations because \textbf{they are} based on yearly data.
-As the OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
+\textbf{The} OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
 The resulting maximal solar wind parameter variation amplitudes over the year can thus be derived from the derived power law exponents.
 They are estimated to be smaller than \SI{4}{\percent} as seen in Tab.~\ref{tab:extrapolation_model_fit_parameters}.
-\citet{Bruno1986} \textbf{and} \citet{Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet (HCS).
+\citet{Bruno1986} \textbf{and} \citet{Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet.
 Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
-\textbf{Since this latitudinal separation is highly variable, and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.}	%Balogh et al.
+\textbf{Since this latitudinal separation is highly variable and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.}	%Balogh et al.
 (p.~162, 1999);	 (Schwenn 1990, p.~126)
@@
 \label{sec:model_extrapolation_to_psp_orbit}
-To estimate PSP’s solar wind environment during its mission time for its orbital positions, \textbf{predictions of the SSN during the mission are incorporated into the empirical solar wind model derived in the previous sections} and extrapolations down to the PSP perihelion region are performed.
+To estimate PSP’s solar wind environment during its mission time for its orbital positions, \textbf{predictions of the SSN during the mission are incorporated into the empirical solar wind model, derived in the previous sections,} and extrapolations down to the PSP perihelion region are performed.
 
@@
 Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs}\textbf{.
-This distance will be reached with the 22nd perihelion in December 2024 \citep{Fox2015} as plotted in the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
+This distance will be reached with the 22nd perihelion in December 2024 \citep{Fox2015}, as plotted in the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
 \begin{figure}
@@
 	\includegraphics[width=18cm]{figures/sw_extrapolation_ssn_f_plot.pdf}
-	\caption{Radial extrapolation of the solar wind median parameters to the PSP orbit region.
-\textbf{The models obtained from Helios and OMNI measurements} are extrapolated to the PSP region \textbf{for SSN values between} solar minimum and maximum, i.e., $0 \le ssn \le 200$\textbf{.
+	\caption{Radial extrapolation of the solar wind parameters to the PSP orbit region.
+\textbf{The median values from the models, obtained from Helios and OMNI measurements,} are extrapolated to the PSP region \textbf{for SSN values between} solar minimum and maximum, i.e., $0 \le ssn \le 200$\textbf{.
 The lower edges of the shaded areas correspond to solar minimum, the upper edges to solar maximum.} Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \textbf{\citet{Sheeley1997} and \citet{Wang2000}}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
@@
 \end{figure*}
-\textbf{The model and the extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.}
+\textbf{The model and its extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.}
 %magnetic field:
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-\textbf{It should be noted that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.}
+\textbf{We note that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.}
 %Since we cannot compare with their absolute values, because their DQCS model assumes fields of \SI{3.1}{\nT} at \SI{1}{\au} assumed to originate from coronal holes with boundaries at \SI{+-60}{\degree} latitude, excluding the fields from the equatorial slow wind belt.
-\textbf{We suggest that the difference in slope is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance} , which for smaller distances deviates more from the model’s lognormal distribution.
+\textbf{We suggest that the difference in slope is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance}, which for smaller distances deviates more from the model’s lognormal distribution.
 %velocity:
@@
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-The SSN for PSP's first perihelion will be small---certainly below 20, whereas \textbf{the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.} \textbf{However \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
+The SSN for PSP's first perihelion will be small -- certainly below 20, whereas \textbf{the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.} \textbf{However \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
 Therefore we simply assume a pattern similar to the last cycle for the prediction of the next solar} cycle and thus shift the last cycle by 11~years.
@@
 In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the \textbf{first} closest approach at \SI{0.046}{\au}.
-\textbf{Monthly SSNs---shifted by the time lags specific to the solar wind parameters---are used in the calculation of the solar wind predictions.
+\textbf{Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions.
 These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
@@
 \textbf{Finally the estimated solar wind environment can be derived from the function $W'''(x,ssn,r)$.
-The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelia are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.}
+The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelion are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.}
 \begin{figure}
@@
 \end{figure}
-\textbf{Note again that the velocity and temperature distributions for the 22nd perihelion are only upper limits and the actual by PSP to be encountered values are expected to be smaller.}
+\textbf{Again, we point out that the velocity and temperature distributions for the 22nd perihelion are only upper limits and the actual values to be encountered by PSP are expected to be smaller.}
 
@@
 \label{sec:discussion_and_summary}
-\textbf{The scientific objective of this study, being part of the German contribution Coronagraphic German and US Solar Probe Plus Survey (CGAUSS) to the Wide field Imager for Solar Probe (WISPR), is to model the solar wind environment for the Parker Solar Probe mission (formerly Solar probe Plus) to be launched mid 2018.}
-
-\textbf{For this purpose we} started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit by \textbf{deriving lognormal representations of the} in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, \textbf{proton} velocity, density and temperature.
+\textbf{The scientific objective of this study, being part of the CGAUSS project -- the German contribution to the WISPR instrument, is to model the solar wind environment for the PSP mission to be launched mid 2018.
+For this purpose we} started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit\textbf{.
+We derived lognormal representations of the} in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, \textbf{proton} velocity, density and temperature.
 Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
@@
 In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
-The radial dependencies of the solar wind distribution functions were then analyzed using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+The radial dependencies of the solar wind distribution functions were then analyzed, using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
 
-\textbf{For determining solar activity and solar distance dependent relations for the median and average solar wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
+\textbf{For determining solar activity and solar distance dependent relations for the median and mean solar wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
 It is expected that the results of a simpler analysis would have similar distance scaling results, as can be inferred from the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}.
 However, in our study we are not only interested in averages but rather in bulk distributions, that is, the whole range of values that might occur.
-For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and average values determines the width of the lognormal distributions.}
+For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and mean values determines the width of the lognormal distributions.}
 
@@
 We have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
-The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, likely to be associated with individual CMEs.
+The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, \textbf{which are} associated with individual CMEs.
 The results by \citet{Sachdeva2017} indicate that due to \textbf{solar wind drag,} the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
@@
 \begin{itemize}
-	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance appears} valid above \SI{20}{\Rs}, however near PSP's closest perihelion the actual values might be found to be slightly higher.
+	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance appears to be} valid above \SI{20}{\Rs}, however near PSP's closest perihelia the actual values might be found to be slightly higher.
 	\item The estimated magnetic field strength \textbf{median values (\ref{eq:median_B})} for PSP's first and \textbf{first} closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
-	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
+	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear to be} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
 The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity \textbf{with their balance relation (\ref{eq:balance_v})}.
@@
 	\item The calculated median velocity values for PSP's first and \textbf{first} closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
-	\item The \textbf{proton density relation appears} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+	\item The \textbf{proton density relation appears to be} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
 	\item The estimated density \textbf{median values (\ref{eq:median_n})} for PSP's first and \textbf{first} closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.

### 2017-10-27 paperMVVB_referee/referee_report_responses_final.txt
added references to figure 7

--- 2017-10-16 paperMVVB_referee/referee_report_responses.txt
@@
-Referee Report
+Cover letter to the editor
+
+Reference: AA/2017/31831
+
+Reply to the reviewer comments on "Solar wind predictions for the Parker Solar Probe orbit - Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations", submitted by M.
+S.
+Venzmer and V.
+Bothmer to Astronomy and Astrophysics, 25 August 2017.
+
+We are grateful to the referee for the thorough review of the manuscript and for the very helpful comments which we have carefully taken into account.
+All modifications appear as bold text in the revised version of the manuscript.
+
+Major changes to the manuscript:
+- We have adressed the general comments and the specific points made by the referee. We have added explanations and phrased some points more clearly.
+- A new figure has been added, providing the predicted solar wind distributions for the first and the first closest perihelion.
+- The discussion and summary sections have been combined. The equations have been moved from the summary to section 5.
+- The tables and table captions have been improved for clarification.
+- We found mismatching density values and corrected a typo in our density calculation.
+The error affected the densities for the first and nearest perihelia and the curves for the densities in figures 12 and 13.
+Corrections have been made to the abstract, section 6 and summary section: changed values 4015 to 214 and 9733 to 2951 cm-3.
+- We updated Voyager 1’s distance in the introduction and the new sunspot numbers in figure 10.
+- We have added a referee acknowledgment.
+- We considered the suggestions concerning the English and further rephrased a few sentences for better readability.
+
+#####
+
+Reply to the referee
 
@@
 It includes an estimate of how these parameters might vary with solar cycle, though this is a relatively small correction, and the likely sunspot number during the mission is anyway highly uncertain.
-The analysis appears to be thorough, retaining information on the log-normal distribution of the parameters that is used to produce “model” representations of the distributions and their variation during the solar cycle.
+The analysis appears to be thorough, retaining information on the log-normal distribution of the parameters that is used to produce "model" representations of the distributions and their variation during the solar cycle.
 However, in the end, this information isn’t used in the predictions at PSP, where only median values are considered.
@@
 
-- ...
-+ use the distributions for the predictions (add perihelia figures of distributions)
-+ state advantage over simple-minded approach (example of simple-minded approach; state how different the results are)
-+ maybe stress Helios data bias to cycle minimum (section 4, third paragraph)
+- We have tried answering the comments made through the specific comments below and by adding a new Figure providing the predicted solar wind distributions for the first overall, and the first “closest” perihelion.
+We have also explained that the results would not be that different but what our motivation was (see specific comments below).
 
@@
 
-- procedural steps explained in detail, following the specific comments
-- clarified the meaning of the parameters in the tables
-- linked the fit equations in the table captions
-- combined the conclusion and summary sections
-- moved final functions into section 5
-+ procedural steps to be explained in detail
-+ clarify the meaning of the parameters in tables
-+ link the fit equations in table captions
-+ combine conclusion and summary sections
-+ include final functions in results section
+- We have carefully incorporated the specific comments raised below and provided more explanations.
+The Tables and captions have been improved for clarification.
+The discussion and summary sections have been combined.
+The functions have been moved as suggested.
 
@@
 
+- We considered the suggestions and further rephrased a few sentences for better readability.
+
 Overall, I anticipate that the paper will be acceptable for publication after the comments in this review are considered.
 
-Specific Points:
+#####
+
+Specific points:
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
+- We have modified the text accordingly.
 
@@
 
-- removed
-+ highlighted
-+ can be removed
-
-- SOHO added
-- should we keep it?
-+ highlighted
-+ add SOHO
-+ SOHO/CELIAS not real-time (ca. +3 hours)
-+ SOHO/CELIAS does not contribute to OMNI data set
+- Removed as requested. We added a reference to the SOHO measurements, because we wanted to mention the current spacecraft in operation around L1 providing solar wind data.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
+- Changed as suggested.
 
@@
 
-- changed
-- should we keep it? doesn't it look too packed?
-+ highlighted
-+ can be adopted
-
-+ do that for all tables
+- Modified as suggested, also for all other Tables of the paper.
 
@@
 
-- added notation explanation
-+ highlighted
-+ explain
-
-- added notation explanation in all tables
-+ explain in all tables??
+- The explanation for the number in brackets has been added to the Table caption, as well as to all other Tables: The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
 
@@
 
-- mean absolute errors unnecessary (they are not referred to in paper), removed from table
-+ highlighted
-
-- explained more clearly in text and table caption
-+ highlighted
-+ explain
+- The mean absolute errors are unnecessary in this context and are not referred to in the paper.
+So we removed them from the Table.
+The following text has been added to the caption, as well as it is mentioned in the text: For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
-
-- changed in fig 2 too
-+ change in fig 2 too
+- Changed as suggested, also in caption of Figure 2.
 
@@
 
-+ highlighted
-+ explaining sentence and reference
+- We have clarified this aspect by adding: “The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by Richardson and Cane (2012).”
 
@@
 
-+ highlighted
-+ look into that
+- Indeed this appears to be the case. We have picked this up and have also added a reference.
 
@@
 
-- changed
-+ highlighted
-+ change
-
-- adopted
-+ highlighted
-+ adopt
-+ 'time lags' without hyphen!
+- Changed as suggested.
 
@@
 
-- explained
-+ explain
+- The grey shading is now explained in the caption.
 
@@
 
-- changed
-+ highlighted
-+ change
+- The text has been changed accordingly.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
-
-- changed 'lag time' to 'time lag'
-+ below, change 'lag time' to 'time lag'
+- Changed, also “lag time” to “time lag”.
 
@@
 
-- table caption equation references added
-+ highlighted
-+ change
+- Has been changed, see reply to Table 1.
 
@@
 
-- explained more clearly
-+ highlighted
-+ explain motivation more clearly
-
-- section 3, sentence with equation (9) clarified
-- section 3, second sentence: abbreviated 'sunspot number'
-- section 3, switched second and third paragraph
-- section 3, added a sentence to now second paragraph
+- Explanatory text has been added. Small changes added to section 3 too:
+  - sentence with equation (9) clarified
+  - second sentence: abbreviated 'sunspot number'
+  - switched second and third paragraph
+  - added a sentence to now second paragraph
 
@@
 
-- phrased this point more clearly
-+ highlighted
-+ explain
+- The text has been modified to explain this point more clearly.
 
@@
 
-- referenced the fit equation
-+ highlighted
-+ link the fit equation
-
-- referenced fit equations in all other table captions
-+ reference fit equations for all other tables
+- The reference to the fit equation is provided now, as is the case now for all other Table captions.
 
@@
 
-- introduced figure properly
-- moved second figure reference to end of this paragraph
-+ highlighted
+- Figure 7 has been introduced properly and the second reference moved to the end of this paragraph. A reference has been added to the figure caption.
 
@@
 
-- removed 'As anticipated'
-- added exponents into text
-+ highlighted
-
-+ is both sufficient?
+- We removed “As anticipated” since it is obvious and we added the exponents we obtained.
 
@@
 
-+ highlighted
-+ if median and mean are of similar values, this is an indication that the distribution is symmetrical (gaussian perhaps?)
+- We do not consider this aspect as a special feature but have clarified the crossing aspect in the text, see the answer to the next comment.
 
@@
 
-- explained more clearly
-+ highlighted
-+ what does limited mean?
-+ limited in the sense of a correct distribution shape
-
-+ is it reliable? it is calculated from that data, added: extrapolated intersection
-
-- clarified the significance of the crossing point
-+ highlighted
-+ explain significance of crossing point
+- These distances are calculated from both fit curves.
+The questions have been addressed and clarified in the text, including the significance of the crossing point: “Thus, below that distance the frequency distribution cannot well be described anymore by a lognormal function, because the mean of a lognormal function has to be larger than its median… the crossing indicates that the parameter’s distribution is not anymore of a lognormal shape thereafter.” …  “The crossing points limit the regions where the distribution’s shapes can still be considered lognormal.”
 
@@
 
-- reworded sentence
-- added remark in next paragraph
-+ highlighted
-+ reword to clarify both
+- We have reworded the sentence for clarification, including a remark in the following paragraph.
 
@@
 
-- rephrased figure references
-+ highlighted
-+ aviod this
+- The figure references have been adjusted as suggested.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
+- Modified as suggested.
 
@@
 
-- removed
-+ highlighted
-+ remove
+- “Established” has been removed.
 
@@
 
-- stated specifically and added equation reference
-+ highlighted
-+ state specifically
+- The parameter is the radial distance and has been stated specifically now. A reference to the equation has been added.
 
@@
 
-- adopted
-+ highlighted
-+ adopt reworded
-
-+ is it ok?
-
-- a few lines before: added 'and' between references 'Bruno et al. (1986) and Balogh et al. (1999)'
+- Modified as suggested and added 'and' between references 'Bruno et al. (1986) and Balogh et al. (1999)'.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
-
-- switched order of figures 10 and 11
-- added 'top' and 'bottom' pointers to both references of now figure 10
-+ highlighted
-+ manage fig references
+- Modified as suggested and switched order of figures 10 and 11. The time when the closest perihelion has been added to the first figure reference.
 
@@
 
-- added remark about that
-+ highlighted
-+ explain thickness of shaded region
-
-- added further explanation in figure caption
+- A remark about this has been added, also to the figure caption.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
-
-- ordered the references Sheeley 1997 and Wang 2000 by year
+- Modified as suggested and references to Sheeley 1997 and Wang 2000 have been ordered by year.
 
@@
 
-+ yes, in average, see figure 5
-
-- correct, removed remark about time lag from figure caption
-+ remove remark about time lag from caption
-
-- added column to table 2: SSN time lag
+- To avoid misunderstandings, we have rephrased the wording of the caption to: “The models obtained from Helios and OMNI measurements are extrapolated to the PSP region for SSN values between solar minimum and maximum, i.e., 0 ≤ ssn ≤ 200.”
+- Further on, the remark about the time lag has been removed from the figure caption. For clarification, a column for the time lag has been added to Table 2.
 
@@
 
-- reworded beginning of sentence
-+ highlighted
-+ reword
+- Has been rephrased.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
+- Is now as suggested.
 
@@
 
-- added an explaining sentence
-+ highlighted
-+ DQCS model assumes 3.1 nT at 1 au coming from CHs at +-60° latitudes (excluding field from equatorial slow wind belt)
-
-+ need new magnetic field model?
+- This is correct and we have added an explaining sentence to the text: “It should be noted, that one cannot straightforward compare the absolute values of our study with the values obtained by Banaszkiewicz et al.
+because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.”
 
@@
 
-- combined
-+ highlighted
-+ combine
-
-- correct, it is a shifted SSN. added value of time lag (at each solar wind parameter)
-+ explain
+- The sentences have been combined. The comment is correct, it is a shifted SSN. We added the value of the time lag for each solar wind parameter.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
+- Has been modified.
 
@@
 
-- reworded
-+ highlighted
-+ explain
-
-+ is that ok?
+- The statement about the helium abundance has been reworded.
 
@@
 
-- corrected
-+ highlighted
-+ can be adopted
+- Corrected.
 
@@
 
-- added introductory sentences
-+ highlighted
-+ smooth topic change
-+ why are short-term SSN predictions relevant?
-+ additional argument is first perihelion
+- Introductory sentences have been incorporated, addressing short-term SSN predictions relevance as well as an additional argument on the prediction for the first perihelion.
 
@@
 
-- yes, added reference
-+ highlighted
-+ yes, maybe note these expectations and add reference
+- Correct, we explained that we used the assumptions of Hathaway and Upton 2016.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
-
-- moved up
-+ move up
+- Has been modified and moved as suggested.
 
@@
 
-- yes, explained which SSN the predictions and error bands are based on
-+ yes, they use different assumptions for the predicted SSN; SWPC expected ranges...
-+ explain which SSN the predictions are based on...
-+ explain which SSN ranges the error bands are based on...
+- We have explained now which SSN the predictions are based on and how the error bands have been calculated.
 
@@
 
-- changed
-+ fig legend
-+ can be adopted
+- Changed.
 
@@
 
-- adopted
-+ highlighted
-+ can be adopted
-
-- replaced solar radii with Rs in discussion
-+ search text for solar radii and replace with Rs
+- Modified as suggested. Replaced solar radii with Rs in discussion.
 
@@
 
-- adopted with addition
-+ highlighted
-+ can be adopted, but
-+ pay attention to wording
+- Modified as suggested and a remark has been added.
 
@@
 
-- adopted with addition
-+ highlighted
-+ can be adopted, but
-+ check wording
+- Modified as suggested and a remark has been added.
 
@@
 
-- combined discussion and summary sections
-- integrated first paragraph of summary into beginning of discussion section
-- removed the second mentioning of the procedure
-+ highlighted
-+ combine both
-
-- removed summary caption
-+ retain section caption?
+- We have combined discussion and summary sections by integrating the first paragraph of the summary into the beginning of the discussion section and have removed the second description of the procedure.
+The section is now “Discussion and Summary”.
 
@@
 
-- inserted all final equations into end of section 5, after equation (11)
-- removed equations from summary and referenced them instead
-+ move equations
-
-+ equations only to be used with lognormal distribution, because median is not actual median
-
-- integrated list item about slow/fast wind balance into velocity list item
+- We have moved the equations to the end of section 5 and added the formulas for the corresponding averages.
+The list statement about slow/fast wind balance has been implemented into the list statement about the velocity dependencies.
 
@@
 
-- removed paragraph
-+ highlighted
-+ remove or merge with above
+- We have removed the paragraph.
 
-- added referee acknowledgment
+#####
+
+Additional changes applied:
+
+- We found mismatching density values and corrected a typo in our density calculation.
+The error affected the densities for the first and nearest perihelia and the curves for the densities in figures 12 and 13.
+Corrections have been made to the abstract, section 6 and summary section: changed values 4015 to 214 and 9733 to 2951 cm-3.
+- We have removed a duplicate 'during' in the caption of figure 13 and have replaced “nearest” with “first closest”.
+- We changed km/s to km s-1 in all figures.
+- We recalculated the error bands in figures 12 and 13. They changed slightly due to a previously not considered uncertainty in the error propagation.
+- We changed the color in figure 14.
+- We also added error bands for the velocity median values in figures 12 and 13.
+- We updated the SSN and its predictions in figure 10 and noted in the caption which SIDC predictionmethod is plotted.
+- Throughout the manuscript we corrected the appearance order of some phrases with their abbreviations. We further removed some abbreviations from the acknowledgments.
+- We removed the article in the first sentence of figures 2 and 3.
+- Introduction: We updated Voyager 1’s distance.
+- We have added references to figure 7.
+- We have adopted the formatting style of the A&A guidelines for some remaining elements (e.g., correct dash symbol).
+- We have added a referee acknowledgment.

### 2017-11-05 paperMVVB/sections/abstract.tex
removed bold text

--- 2017-10-17 paperMVVB/sections/abstract.tex
@@
 It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
-The scope of this study is to model the solar wind environment for PSP’s unprecedented distances during its prime mission phase during the years \numrange{2018}{2025}.
-The study is performed within the project Coronagraphic German And US Solar~Probe Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide field Imager for Solar PRobe (WISPR).}	%context
+The scope of this study is to model the solar wind environment for PSP’s unprecedented distances in its prime mission phase during the years \numrange{2018}{2025}.
+The study is performed within the project Coronagraphic German And US SolarProbePlus Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).}	%context
 {We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data.
@@
 Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
-Finally, the inclusion of SSN predictions and the extrapolation to PSP’s perihelion enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
-{The CGAUSS empirical solar wind model for PSP yields dependencies of the solar wind parameters on solar activity and radial distance.
+Finally, the inclusion of SSN predictions and the extrapolation down to PSP’s perihelion region enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}	%methods
+{The CGAUSS empirical solar wind model for PSP yields dependencies on solar activity and solar distance for the solar wind parameters' frequency distributions.
 The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}.
-The estimates for PSP’s closest perihelia, beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
-\textbf{Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.
-} }	%results
+The estimates for PSP’s first closest perihelion, occuring in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
+Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.}	%results
 {}	%conclusions

### 2017-11-05 paperMVVB/sections/acknowledgments.tex
removed bold text

@@
 The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data.
-The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive (NSSDCA) and the Space Physics Data Facility (SPDF) at NASA's Goddard Space Flight Center (GSFC).
-Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
+The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive and the Space Physics Data Facility at NASA's Goddard Space Flight Center.
+Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations at the Solar Influences Data Analysis Center, Royal Observatory of Belgium.
 The PSP SPICE kernel was kindly provided by Angelos~Vourlidas.
-\textbf{The authors thank the referee for the careful review of this manuscript and helpful comments and suggestions.}
+The authors thank the referee for the careful review of this manuscript and helpful comments and suggestions.
 %	We thank the referees for /very important comments and suggestions. /careful review of this paper.

### 2017-11-05 paperMVVB/sections/content.tex
removed bold text

@@
 The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
-Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (\textbf{October} 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, SOHO \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+Various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
 Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
-\textbf{The in situ solar wind measurements closest to the Sun to date were made by} the Helios missions.
-\textbf{Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}.
-Helios~2, launched two years later, approached the Sun as close as} \SI{0.29}{\au} \citep{Rosenbauer1977}.
+The in situ solar wind measurements closest to the Sun to date were made by the Helios missions.
+Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}.
+Helios~2, launched two years later, approached the Sun as close as \SI{0.29}{\au} \citep{Rosenbauer1977}.
 %Solar Probe Plus mission
@@
 The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” as stated in \citet{Fox2015}.
-To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurements of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles \textbf{(SEPs)} \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
+To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurements of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles (SEPs) \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
 
 %CGAUSS and WISPR
-The study presented in this paper is undertaken in the Coronagraphic German And US \textbf{SolarProbePlus} Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).
+The study presented in this paper is undertaken in the Coronagraphic German And US SolarProbePlus Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).
 WISPR will contribute to the PSP science goals by deriving the 3D structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
 It will provide density power spectra over a wide range of structures (e.g., streamers, pseudostreamers and equatorial coronal holes) for determining the roles of turbulence, waves and pressure-balanced structures in the solar wind.
-It will also measure the physical properties, such as speed and density jumps of SEP-producing shocks and their \textbf{coronal mass ejection (CME)} drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.
+It will also measure the physical properties, such as speed and density jumps of SEP-producing shocks and their coronal mass ejection (CME) drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.
 
@@
 The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
-Embedded in the slow and fast solar wind streams are transient flows of \textbf{CMEs} -- the faster ones driving shock waves ahead \citep{Gosling1974}.
+Embedded in the slow and fast solar wind streams are transient flows of CMEs -- the faster ones driving shock waves ahead \citep{Gosling1974}.
 Their rate follows the solar activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
@@
 From combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions a general solar wind model is build in Sect.~\ref{sec:empirical_solar_wind_model}, representing the solar activity and distance behavior.
-Finally, this empirical model is fed with \textbf{SSN predictions} and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+Finally, this empirical model is fed with SSN predictions and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
@@
 %hourly data
-\textbf{We note} that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
+We note that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
 
@@
 These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
-Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 \textbf{CME} with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
+Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 CME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
 
@@
 For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
-\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} \textbf{For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}}
+The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
 	\label{tab:lognormal_fit_parameters}
@@
 		\hline
-		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.661(16)	&6.164(18)	&--	&6.83\\
-		\multicolumn{2}{l}{\textbf{Velocity [\SI{e2}{\km\per\s}]}}	&4.085(19)	&4.183(20)	&--	&18.69\\
-		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.276(24)	&6.484(34)	&--	&6.48\\
-		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&7.470(17)	&11.301(32)	&--	&5.78\\
+		\multicolumn{2}{l}{Magnetic field [\si{nT}]}	&5.661(16)	&6.164(18)	&--	&6.83\\
+		\multicolumn{2}{l}{Velocity [\SI{e2}{\km\per\s}]}	&4.085(19)	&4.183(20)	&--	&18.69\\
+		\multicolumn{2}{l}{Density [\si{\per\cm\cubed}]}	&5.276(24)	&6.484(34)	&--	&6.48\\
+		\multicolumn{2}{l}{Temperature [\SI{e4}{\K}]}	&7.470(17)	&11.301(32)	&--	&5.78\\
 		\hline
-		\multirow{2}{*}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
-		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
+		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
+		\multirow{2}{*}{[\SI{e2}{\km\per\s}]~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
 		\cline{2-6}
@@
 However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
-This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} \textbf{in percentage of the distribution area}, being almost three times larger than those from the other parameters.
+This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} in percentage of the distribution area, being almost three times larger than those from the other parameters.
 \begin{figure*}
@@
 The fits' median and mean values are indicated as well.
-The insets show zoomed-in \textbf{views of the high value tails of the distributions.
-} }
+The insets show zoomed-in views of the high value tails of the distributions.}
 	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/histogram_fits_V_a_zoom_dbl_paper_pdfplot.pdf}}
-	\caption{\textbf{Velocity} frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
+	\caption{Velocity frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
 The fit's median and mean values and its two fit parts are indicated as well.
-\textbf{The inset is a zoomed-in view of the high value tail of the distribution.
-} }
+The inset is a zoomed-in view of the high value tail of the distribution.}
 	\label{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}
@@
 %transition
-For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well\textbf{.
-The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.} The simple lognormal fit functions underestimate the \textbf{frequencies in} their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}\textbf{, this appears to be because CMEs do not come with abnormally high temperatures, but rather with temperatures lower than those of the average solar wind \citep{Forsyth2006}.} The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well.
+The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.
+The simple lognormal fit functions underestimate the frequencies in their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}, this appears to be because CMEs do not come with abnormally high temperatures, but rather with temperatures lower than those of the average solar wind \citep{Forsyth2006}.
+The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
 The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.
@@
 In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity.
-Therefore we examine their correlation with the \textbf{SSN}, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.
+Therefore we examine their correlation with the SSN, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.
 
@@
 For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN.
-\textbf{Thus we obtain solar activity depending models for the frequency distributions of all four solar wind parameters.}
+Thus we obtain solar activity depending models for the frequency distributions of all four solar wind parameters.
 
@@
 
-Yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number \textbf{are shown in the upper part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}}.
+Yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number are shown in the upper part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.
 The reason for correlating the SSN to the solar wind median values is because the position of a lognormal function is defined by its median.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
-	\caption{\textbf{Solar} wind parameter yearly \textbf{frequencies (grey shading) with yearly medians (lines)} derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
+	\caption{Solar wind parameter yearly frequencies (grey shading) with yearly medians (lines) derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
 Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
@@
 The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
-For instance the fast solar wind \textbf{occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle} as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
-Therefore the solar wind velocity, density and temperature maxima exhibit \textbf{time lags relative} to the SSN maxima.
+For instance the fast solar wind occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
+Therefore the solar wind velocity, density and temperature maxima exhibit time lags relative to the SSN maxima.
 
 The correlation coefficients of the solar wind parameters with the yearly SSN shown in the bottom part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot} are calculated for time lags back to \num{-15}~years to cover a time span longer than a solar cycle.
-As expected, the \textbf{amplitudes of the variations in the correlations} of all parameters decline with increasing time lag and show a \textbf{period} of about 11~years.
+As expected, the amplitudes of the variations in the correlations of all parameters decline with increasing time lag and show a period of about 11~years.
 The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
-Velocity and temperature show \textbf{time lags} of 3~years with peak correlation coefficients of 0.453 and 0.540.
-The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the \textbf{density anticorrelation to the SSN} reported by \citet{Bougeret1984}.	%p.~406\\
+Velocity and temperature show time lags of 3~years with peak correlation coefficients of 0.453 and 0.540.
+The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the density anticorrelation to the SSN reported by \citet{Bougeret1984}.	%p.~406\\
 % maximal correlation coefficients and their time lags:\\
@@
 %\subsection{SSN fitting}
-\textbf{Next we create solar activity dependent analytical representations of the solar wind frequency distributions.
+Next we create solar activity dependent analytical representations of the solar wind frequency distributions.
 This is achieved by shifting the median positions of the lognormal distributions as a linear function of the SSN.
-To enable these shifts}, we add a linear SSN dependency to the median
+To enable these shifts, we add a linear SSN dependency to the median
 \begin{align}
@@
 \end{align}
-\textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$.
-This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags determined before for each parameter, to benefit from the higher correlation.
-The values of} the three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
+These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$.
+This function is then fitted to the yearly data, using the yearly SSN as input parameter.
+The SSN is offset with the individual time lags determined before for each parameter, to benefit from the higher correlation.
+The values of the three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
 \begin{table*}
-	\caption{Resulting fit coefficients from the OMNI data\textbf{, based on the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}.
-For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given.
-\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
-The listed SSN time lags are used for the fits.}}
+	\caption{Resulting fit coefficients from the OMNI data, based on the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn}).
+For the velocity the fit parameters from the double lognormal fit (\ref{eq:double_lognormal_fit_function}) and their balancing function (\ref{eq:balance_with_ssn}) are given.
+The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The listed SSN time lags are used for the fits.}
 	\label{tab:ssn_fit_parameters}
@@
 		\hline
-		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
+		\multicolumn{2}{l}{Magnetic field [\si{nT}]}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
 %		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
-		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
-		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
+		\multicolumn{2}{l}{Density [\si{\per\cm\cubed}]}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
+		\multicolumn{2}{l}{Temperature [\SI{e4}{\K}]}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
 		\hline
-		\multicolumn{1}{l}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
-		\multicolumn{1}{l}{\textbf{[\SI{e2}{\km\per\s}]}}	&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
+		\multicolumn{1}{l}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
+		\multicolumn{1}{l}{[\SI{e2}{\km\per\s}]}	&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
 		\hline
@@
 
-Naturally, the fit models match with the general data trends\textbf{, as can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}}, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994 and 2003).
+Naturally, the fit models match with the general data trends, as can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994 and 2003).
 \begin{figure*}
@@
 	\caption{Solar wind parameter yearly data frequencies and lognormal fit models, both with their median values (white lines) over the OMNI time period 1963--2016.
-The corresponding yearly SSN and the \textbf{shifted SSN} for the models are indicated by grey and black lines.
+The corresponding yearly SSN and the shifted SSN for the models are indicated by grey and black lines.
 The velocity median is derived from the SSN-weighted constant lognormal parts (dotted lines).}
@@
 The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage.
-The SSN-dependent median \textbf{(dashed lines)} is derived from the lognormal model fit.
-For the velocity the median is derived from the SSN-weighting (\ref{eq:balance_with_ssn}) of the slow and fast model parts \textbf{(dotted lines)}, whose magnitudes are SSN independent.}
+The SSN-dependent median (dashed lines) is derived from the lognormal model fit.
+For the velocity the median is derived from the SSN-weighting (\ref{eq:balance_with_ssn}) of the slow and fast model parts (dotted lines), whose magnitudes are SSN independent.}
 	\label{fig:OMNI_yearly_BVNTvsSSN_a}
@@
 Again, the solar wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle, we keep the two velocity components' positions \textbf{SSN-independent ($x_\text{med} =  b_\text{med}$)} and vary instead their balance with the SSN:
+Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle, we keep the two velocity components' positions SSN-independent ($x_\text{med} =  b_\text{med}$) and vary instead their balance with the SSN:
 \begin{align}
@@
 \end{align}
-The fit result (see Table~\ref{tab:ssn_fit_parameters}) yields a model in which three years after solar cycle minimum (SSN of zero) the contribution of slow solar wind to the overall solar wind distribution reaches a maximum value \textbf{(about \SI{64}{\percent})} and decreases with increasing SSN as shown in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
+The fit result (see Table~\ref{tab:ssn_fit_parameters}) yields a model in which three years after solar cycle minimum (SSN of zero) the contribution of slow solar wind to the overall solar wind distribution reaches a maximum value (about \SI{64}{\percent}) and decreases with increasing SSN as shown in Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}.
 \begin{figure}
@@
 The linear fit to the yearly data ratio and the derived model ratio show a good agreement (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
-\textbf{The to some degree steeper balance parameter of the double fit function used in this model cannot be compared directly with} specific velocity thresholds between slow and fast solar wind.
+The to some degree steeper balance parameter of the double fit function used in this model cannot be compared directly with specific velocity thresholds between slow and fast solar wind.
 However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
@@
 \label{sec:solar_distance_dependency}
-In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit \textbf{power law dependencies} to the Helios data.
-We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step \textbf{they are} extrapolated to the PSP orbit.
+In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit power law dependencies to the Helios data.
+We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step they are extrapolated to the PSP orbit.
 We use the fitting methods of Sect.~\ref{sec:frequency_distribution} for the distance-binned combined data from both Helios probes.
@@
 
-We investigate hourly averages of the Helios data \textbf{in the same way as with the OMNI data}.
+We investigate hourly averages of the Helios data in the same way as with the OMNI data.
 The Helios~1 merged hourly data from the magnetometer and plasma instruments \citep{Rosenbauer1977} include $\sim$12.5~orbits for the time range 10~December 1974 until 14~June 1981, those for Helios~2 include $\sim$8~orbits for the time span 1~January 1976 until 4~March 1980.
@@
 %Helios data biased towards solar minimum
-Thus, using this data, \textbf{we point out} that its time coverage is unequally distributed over the solar cycle.
-Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} \textbf{of this period} whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
-This Helios data bias towards solar minimum is \textbf{one} reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
+Thus, using this data, we point out that its time coverage is unequally distributed over the solar cycle.
+Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} of this period whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
+This Helios data bias towards solar minimum is one reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
 % data gaps -> uneven coverage -> solar cycle minimum dominates; ratio of max vs min cycle data coverage; for OMNI data negligible\\
@@
 
-\textbf{The radial dependencies of the key solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.}
+The radial dependencies of the key solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.
 \begin{figure*}
@@
 The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
-\textbf{The high velocity data points above \SI{800}{\km\per\s} (circled red) are identified as CME events \citep[e.g.,][]{Bothmer1998}.}}
+The high velocity data points above \SI{800}{\km\per\s} (circled red) are identified as CME events \citep[e.g.,][]{Sheeley1985,Bothmer1996,Bothmer1998}.}
 	\label{fig:radial_fit_4_thesis_light_b_skip}
@@
 %fit result table and figure
-\textbf{The obtained coefficients for the median and mean power law fits ($d_\text{med}$, $e_\text{med}$, $d_\text{avg}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter} and their corresponding curves are shown in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.}
+The obtained coefficients for the median and mean power law fits ($d_\text{med}$, $e_\text{med}$, $d_\text{avg}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter} and their corresponding curves are shown in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.
 \begin{table*}
-	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data.
-\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The crossing distances indicate where the median and mean fits intersect each other.
+	\caption{Fit coefficients for the median and mean solar distance dependencies (\ref{eq:power_function}) of the four solar wind parameters derived from the combined Helios~1 and 2 data.
+The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The crossing distances indicate where the median and mean fits intersect each other.
 The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
@@
 		\hline
-		\textbf{Magnetic field [\si{nT}]}	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
-		\textbf{Velocity [\SI{e2}{\km\per\s}]}	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
-		\textbf{Density [\si{\per\cm\cubed}]}	&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
-		\textbf{Temperature [\SI{e4}{\K}]}	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
+		Magnetic field [\si{nT}]	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
+		Velocity [\SI{e2}{\km\per\s}]	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
+		Density [\si{\per\cm\cubed}]	&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
+		Temperature [\SI{e4}{\K}]	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
 		\hline
@@
 %Helios results, radial gradients see \citet{Schwenn1990} p.~155
-\textbf{Our derived} exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$\textbf{, ours is $B_\text{avg} \propto r^{-1.55}$}.
+Our derived exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$, ours is $B_\text{avg} \propto r^{-1.55}$.
 %$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
-The velocity exponent \textbf{$v_\text{avg} \propto r^{0.049}$} matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
-The calculated density exponent \textbf{$n_\text{avg} \propto r^{-2.01}$} agrees well with the Helios plasma density model derived by \citet{Bougeret1984} yielding $n \propto r^{-2.10}$.
+The velocity exponent $v_\text{avg} \propto r^{0.049}$ matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
+The calculated density exponent $n_\text{avg} \propto r^{-2.01}$ agrees well with the Helios plasma density model derived by \citet{Bougeret1984} yielding $n \propto r^{-2.10}$.
 %to the year 1976 normalized   a \SI{1}{\au} density of $n = 6.14\cdot r^{-2.10}\,\text{cm}^{-3}$.
-The temperature exponent \textbf{$T_\text{avg} \propto r^{-0.79}$} is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} \propto r^{-0.74}$ and $T_\text{slow} \propto r^{-0.58}$.
+The temperature exponent $T_\text{avg} \propto r^{-0.79}$ is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} \propto r^{-0.74}$ and $T_\text{slow} \propto r^{-0.58}$.
 %$T_\text{fast} = \num{2.5e5} (R/R_0)^{-0.74}$\,K and $T_\text{slow} = \num{6.2e4} (R/R_0)^{-0.58}$\,K.
@@
 %crossing distances
-\textbf{The mean and median velocity fit exponents acquired from the Helios data} are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
-Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} \textbf{(see Table~\ref{tab:mean_median_fit_parameter})} and the mean is \textbf{getting slightly} lower than the median at smaller distances.
-Thus, below that distance the \textbf{frequency distribution} cannot well be described anymore by a lognormal function\textbf{, because the mean of a lognormal function has to be larger than its median (as pointed out in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.} The fits for the proton temperature show a similar behavior, having an \textbf{extrapolated} intersection at \SI{0.082}{\au}.
+The mean and median velocity fit exponents acquired from the Helios data are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
+Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} (see Table~\ref{tab:mean_median_fit_parameter}) and the mean is getting slightly lower than the median at smaller distances.
+Thus, below that distance the frequency distribution cannot well be described anymore by a lognormal function, because the mean of a lognormal function has to be larger than its median (as pointed out in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.
+The fits for the proton temperature show a similar behavior, having an extrapolated intersection at \SI{0.082}{\au}.
 Therefore the extrapolation of the magnetic field and temperature distribution frequencies to the PSP orbit by applying lognormal functions is limited.
-\textbf{The crossing points limit the regions where the distribution's shapes can still be considered lognormal.}
+The crossing points limit the regions where the distribution's shapes can still be considered lognormal.
 
-\textbf{In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
+In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
 For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
-We note} that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
+We note that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
 
 %\subsection{Power law lognormal fitting}
-Next we retrieve the frequency distributions of the four \textbf{solar wind parameters in solar} distance bins of \SI{0.01}{\au}, choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution} -- the distributions \textbf{and their median values} are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
+Next we retrieve the frequency distributions of the four solar wind parameters in solar distance bins of \SI{0.01}{\au}, choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution} -- the distributions and their median values are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
 \begin{figure*}
@@
 % $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
-For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical\textbf{, using one fit parameter for both.} Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters $d'_\text{med}$, $d'_\text{avg}$ and \textbf{the} common exponent $e'$.
+For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical, using one fit parameter for both.
+Implementing the power law distance dependency~(\ref{eq:power_function}) into the lognormal function (\ref{eq:single_lognormal_fit_function}), we get the fit parameters $d'_\text{med}$, $d'_\text{avg}$ and the common exponent $e'$.
 Again, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit -- resulting in $W''_\text{II}(x,r)$.
@@
 \begin{table*}
-	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, based on equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data.
-\textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
+	\caption{Fit coefficients for the distance depending single lognormal function, based on equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}), respectively double lognormal function (\ref{eq:double_lognormal_fit_function}) for the velocity from the combined Helios data.
+The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
 	\label{tab:extrapolation_model_fit_parameters}
@@
 		\hline
-		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
-		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
-		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\
+		\multicolumn{2}{l}{Magnetic field [\si{nT}]}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
+		\multicolumn{2}{l}{Density [\si{\per\cm\cubed}]}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
+		\multicolumn{2}{l}{Temperature [\SI{e4}{\K}]}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\
 		\hline
-		\multirow{2}{*}{\textbf{Velocity}}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
-		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}}	&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\
+		\multirow{2}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
+		\multirow{2}{*}{[\SI{e2}{\km\per\s}]}	&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\
 		\cline{2-7}
@@
 
-\textbf{The power law lognormal models and the power law double lognormal model for the velocity, which result from the fitting, are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot} together with their median values.} The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the data's frequency distribution implies.
+The power law lognormal models and the power law double lognormal model for the velocity, which result from the fitting, are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot} together with their median values.
+The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the data's frequency distribution implies.
 This behavior is expected because of the distance independent shape approximation applied.
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-\textbf{The with distance increasing high velocity tail arises} from using the same exponent for both slow and fast components.
+The with distance increasing high velocity tail arises from using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 In order to estimate the solar wind environment for the PSP orbit, we combine the results from the solar wind frequency distributions’ solar activity relationships and their distance dependencies derived from the OMNI and Helios data.
-The result is an empirical solar wind model for the inner heliosphere which \textbf{is then} extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+The result is an empirical solar wind model for the inner heliosphere which is then extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
@@
 %\label{sec:distance_scaling_law_variations}
-\textbf{This solar wind model} for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The \textbf{variations of the} yearly power law fit exponents \textbf{from fitting the solar distance dependency (\ref{eq:power_function})} are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
+This solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
+The variations of the yearly power law fit exponents from fitting the solar distance dependency (\ref{eq:power_function}) are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
 It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity -- at least for the velocity and temperature exponents.
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}
-	\caption{Helios yearly variation of the solar wind \textbf{parameter power exponents for the dependence on radial distance} together with the SIDC 13-month smoothed monthly SSN.
+	\caption{Helios yearly variation of the solar wind parameter power exponents for the dependence on radial distance together with the SIDC 13-month smoothed monthly SSN.
 The weighted standard deviations and average values for all years are indicated by the shaded areas.
@@
 \end{align}
-Thus\textbf{, implementing the median and mean relations into the lognormal function (\ref{eq:single_lognormal_fit_function}),} we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
-\textbf{The corresponding median and mean relations for each solar wind parameter, based on the values resulting from our analyses, are listed below.
-Their numerical values are the fit parameters from Table~\ref{tab:ssn_fit_parameters} and the exponents from Table~\ref{tab:extrapolation_model_fit_parameters}.}
+Thus, implementing the median and mean relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
+The corresponding median and mean relations for each solar wind parameter, based on the values resulting from our analyses, are listed below.
+Their numerical values are the fit parameters from Table~\ref{tab:ssn_fit_parameters} and the exponents from Table~\ref{tab:extrapolation_model_fit_parameters}.
 
-\textbf{\begin{itemize}
+\begin{itemize}
 	\item The magnetic field strength relations, depending on solar activity and solar distance, are:
@@
 	\end{align}
-\end{itemize}}
+\end{itemize}
 
-\textbf{These relations average} over seasonal variations because \textbf{they are} based on yearly data.
-\textbf{The} OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
+These relations average over seasonal variations because they are based on yearly data.
+The OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
 The resulting maximal solar wind parameter variation amplitudes over the year can thus be derived from the derived power law exponents.
 They are estimated to be smaller than \SI{4}{\percent} as seen in Tab.~\ref{tab:extrapolation_model_fit_parameters}.
-\citet{Bruno1986} \textbf{and} \citet{Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet.
+\citet{Bruno1986} and \citet{Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet.
 Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
-\textbf{Since this latitudinal separation is highly variable and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.}	%Balogh et al.
+Since this latitudinal separation is highly variable and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.	%Balogh et al.
 (p.~162, 1999);	 (Schwenn 1990, p.~126)
@@
 \label{sec:model_extrapolation_to_psp_orbit}
-To estimate PSP’s solar wind environment during its mission time for its orbital positions, \textbf{predictions of the SSN during the mission are incorporated into the empirical solar wind model, derived in the previous sections,} and extrapolations down to the PSP perihelion region are performed.
+To estimate PSP’s solar wind environment during its mission time for its orbital positions, predictions of the SSN during the mission are incorporated into the empirical solar wind model, derived in the previous sections, and extrapolations down to the PSP perihelion region are performed.
 
@@
 With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
-Seven additional Venus flybys allow \textbf{the perihelion distance to be reduced} to a minimum of \SI{9.86}{\Rs}\textbf{.
-This distance will be reached with the 22nd perihelion in December 2024 \citep{Fox2015}, as plotted in the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}}.
+Seven additional Venus flybys allow the perihelion distance to be reduced to a minimum of \SI{9.86}{\Rs}.
+This distance will be reached with the 22nd perihelion in December 2024 \citep{Fox2015}, as plotted in the top panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
 \begin{figure}
@@
 Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC \textbf{Standard Curves Kalman filter} prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC Standard Curves Kalman filter prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
 	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
@@
 
-We extrapolate the derived empirical solar wind \textbf{models} to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}.
+We extrapolate the derived empirical solar wind models to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}.
 \begin{figure*}
@@
 	\caption{Radial extrapolation of the solar wind parameters to the PSP orbit region.
-\textbf{The median values from the models, obtained from Helios and OMNI measurements,} are extrapolated to the PSP region \textbf{for SSN values between} solar minimum and maximum, i.e., $0 \le ssn \le 200$\textbf{.
-The lower edges of the shaded areas correspond to solar minimum, the upper edges to solar maximum.} Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \textbf{\citet{Sheeley1997} and \citet{Wang2000}}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
+The median values from the models, obtained from Helios and OMNI measurements, are extrapolated to the PSP region for SSN values between solar minimum and maximum, i.e., $0 \le ssn \le 200$.
+The lower edges of the shaded areas correspond to solar minimum, the upper edges to solar maximum.
+Also plotted are the radial dependencies of the analytic DQCS magnetic field model for solar minimum from \citet{Banaszkiewicz1998}, the slow wind velocity models from \citet{Sheeley1997} and \citet{Wang2000}, the density model from \citet{Leblanc1998} and the range of temperature measurements from \citet{Billings1959} and \citet{Liebenberg1975}.}
 	\label{fig:sw_extrapolation_ssn_f_plot}
 \end{figure*}
-\textbf{The model and its extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.}
+The model and its extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.
 %magnetic field:
@@
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-\textbf{We note that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.}
+We note that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.
 %Since we cannot compare with their absolute values, because their DQCS model assumes fields of \SI{3.1}{\nT} at \SI{1}{\au} assumed to originate from coronal holes with boundaries at \SI{+-60}{\degree} latitude, excluding the fields from the equatorial slow wind belt.
-\textbf{We suggest that the difference in slope is} due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) \textbf{changing shape of the frequency distribution with heliocentric distance}, which for smaller distances deviates more from the model’s lognormal distribution.
+We suggest that the difference in slope is due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) changing shape of the frequency distribution with heliocentric distance, which for smaller distances deviates more from the model’s lognormal distribution.
 %velocity:
-The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} \textbf{3~years after a} SSN of 0 \textbf{occurred, whereas} using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
+The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} 3~years after a SSN of 0 occurred, whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
 Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar wind velocity values for distances below about \SI{20}{\Rs}.
 They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model from \citet{Parker1958}.
-Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates\textbf{.
-Thus} PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
+Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates.
+Thus PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
 %density:
-The proton density increases from about \SI{84}{\per\cm\cubed} at \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} \textbf{6~years after a SSN of 0 occurred}.
+The proton density increases from about \SI{84}{\per\cm\cubed} at \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} 6~years after a SSN of 0 occurred.
 Being almost independent of the SSN the values for a SSN of 200 are only \SI{17}{\%} larger.
@@
 Their model shows that the density distance dependency scales with $r^{-2}$ and steepens just below \SI{10}{\Rs} with $r^{-6}$.
-\textbf{We assumed a solar wind helium abundance of \SI{5}{\%} to convert these electron densities to proton densities.}
+We assumed a solar wind helium abundance of \SI{5}{\%} to convert these electron densities to proton densities.
 %temperature:
-The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} \textbf{3~years after a SSN of 0 occurred} and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
-Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model \textbf{overestimates} the extrapolated temperatures at the PSP perihelion distance.
+The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} 3~years after a SSN of 0 occurred and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
+Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model overestimates the extrapolated temperatures at the PSP perihelion distance.
 
@@
 %SSN prediction
-\textbf{Aside from the solar distance the derived solar wind parameter models depend on the SSN.
-Short-term predictions of the SSN can be used for the solar wind predictions of PSP's early perihelia and also for refining the solar wind predictions during PSP's mission.} Several sources are available for SSN short-term predictions.
-The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter \textbf{Standard Curve} method).
+Aside from the solar distance the derived solar wind parameter models depend on the SSN.
+Short-term predictions of the SSN can be used for the solar wind predictions of PSP's early perihelia and also for refining the solar wind predictions during PSP's mission.
+Several sources are available for SSN short-term predictions.
+The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter Standard Curve method).
 The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-The SSN for PSP's first perihelion will be small -- certainly below 20, whereas \textbf{the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.} \textbf{However \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
-Therefore we simply assume a pattern similar to the last cycle for the prediction of the next solar} cycle and thus shift the last cycle by 11~years.
-Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in \textbf{the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.}
+The SSN for PSP's first perihelion will be small -- certainly below 20, whereas the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.
+However \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
+Therefore we simply assume a pattern similar to the last cycle for the prediction of the next solar cycle and thus shift the last cycle by 11~years.
+Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
 
 %\subsection{PSP solar wind environment estimation}
-Implementing the \textbf{SSN predictions} for the PSP mission time and the orbital trajectory data, \textbf{we can infer} which solar wind parameter magnitudes can be expected.
-Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show \textbf{the median values (\ref{eq:median_with_ssn}) of} the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the \textbf{first} closest perihelion in December 2024.
+Implementing the SSN predictions for the PSP mission time and the orbital trajectory data, we can infer which solar wind parameter magnitudes can be expected.
+Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the median values (\ref{eq:median_with_ssn}) of the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the first closest perihelion in December 2024.
 \begin{figure}
@@
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
-	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) \textbf{during} 12~days in 2024 with PSP's \textbf{22nd (the first closest)} perihelion at \SI{0.0459}{\au}.
+	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's 22nd (the first closest) perihelion at \SI{0.0459}{\au}.
 For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
@@
 % half/twice SSN
-In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the \textbf{first} closest approach at \SI{0.046}{\au}.
+In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the first closest approach at \SI{0.046}{\au}.
 \textbf{Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions.
@@
 
-\textbf{Finally the estimated solar wind environment can be derived from the function $W'''(x,ssn,r)$.
-The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelion are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.}
+Finally the estimated solar wind environment can be derived from the function $W'''(x,ssn,r)$.
+The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelion are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.
 \begin{figure}
 	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions_b.pdf}}
-	\caption{\textbf{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelion.
-In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}}
+	\caption{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelion.
+In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}
 	\label{fig:SPP_sw_distributions_b}
 \end{figure}
-\textbf{Again, we point out that the velocity and temperature distributions for the 22nd perihelion are only upper limits and the actual values to be encountered by PSP are expected to be smaller.}
+Again, we point out that the velocity and temperature distributions for the 22nd perihelion are only upper limits and the actual values to be encountered by PSP are expected to be smaller.
 
@@
 \label{sec:discussion_and_summary}
-\textbf{The scientific objective of this study, being part of the CGAUSS project -- the German contribution to the WISPR instrument, is to model the solar wind environment for the PSP mission to be launched mid 2018.
-For this purpose we} started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit\textbf{.
-We derived lognormal representations of the} in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, \textbf{proton} velocity, density and temperature.
+The scientific objective of this study, being part of the CGAUSS project -- the German contribution to the WISPR instrument, is to model the solar wind environment for the PSP mission to be launched mid 2018.
+For this purpose we started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit.
+We derived lognormal representations of the in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, proton velocity, density and temperature.
 Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
@@
 In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
-The radial dependencies of the solar wind distribution functions were then analyzed, using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}\textbf{, deriving power law fit functions that} were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, \textbf{taking into account} SSN predictions for the years 2018--2025, \textbf{encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.} The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+The radial dependencies of the solar wind distribution functions were then analyzed, using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}, deriving power law fit functions that were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, taking into account SSN predictions for the years 2018--2025, encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.
+The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
 
-\textbf{For determining solar activity and solar distance dependent relations for the median and mean solar wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
+For determining solar activity and solar distance dependent relations for the median and mean solar wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
 It is expected that the results of a simpler analysis would have similar distance scaling results, as can be inferred from the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}.
 However, in our study we are not only interested in averages but rather in bulk distributions, that is, the whole range of values that might occur.
-For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and mean values determines the width of the lognormal distributions.}
+For the determination of the frequency distributions the use of the more complex fit model is important, because the distance between median and mean values determines the width of the lognormal distributions.
 
-\textbf{It} is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
+It is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
 The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.
 However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
-\textbf{The extrapolation results of the velocity and the temperature differ from the direct measurements seen in existing studies.
-This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur} (see Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the \textbf{solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar} maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+The extrapolation results of the velocity and the temperature differ from the direct measurements seen in existing studies.
+This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur (see Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
 
 We have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
-The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, \textbf{which are} associated with individual CMEs.
-The results by \citet{Sachdeva2017} indicate that due to \textbf{solar wind drag,} the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
+The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, which are associated with individual CMEs.
+The results by \citet{Sachdeva2017} indicate that due to solar wind drag, the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
 Therefore, it is expected that PSP will encounter CMEs with much higher speeds than those observed during the Helios mission.
@@
 \begin{itemize}
-	\item The dependency of the magnetic field strength \textbf{on solar activity and radial distance appears to be} valid above \SI{20}{\Rs}, however near PSP's closest perihelia the actual values might be found to be slightly higher.
-	\item The estimated magnetic field strength \textbf{median values (\ref{eq:median_B})} for PSP's first and \textbf{first} closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
-	\item The radial dependencies of the proton velocity median values for slow and fast solar \textbf{wind (\ref{eq:median_v}) appear to be} valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
-The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity \textbf{with their balance relation (\ref{eq:balance_v})}.
-Thus, at solar minimum with \textbf{a SSN} around 0 the slow wind \textbf{component} contributes about \SI{64}{\%} and \textbf{drops} to \SI{28}{\%} during solar maximum conditions with \textbf{a SSN} around 200.
-	\item The calculated median velocity values for PSP's first and \textbf{first} closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
-	\item The \textbf{proton density relation appears to be} valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-	\item The estimated density \textbf{median values (\ref{eq:median_n})} for PSP's first and \textbf{first} closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
-	\item The derived correlation function for the \textbf{proton temperature appears} to provide too high temperature values \textbf{around PSP’s closest perihelion} in comparison to coronal measurements.
-	\item The estimated temperature \textbf{median values (\ref{eq:median_T})} for PSP's first and \textbf{first} closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+	\item The dependency of the magnetic field strength on solar activity and radial distance appears to be valid above \SI{20}{\Rs}, however near PSP's closest perihelia the actual values might be found to be slightly higher.
+	\item The estimated magnetic field strength median values (\ref{eq:median_B}) for PSP's first and first closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+	\item The radial dependencies of the proton velocity median values for slow and fast solar wind (\ref{eq:median_v}) appear to be valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
+The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity with their balance relation (\ref{eq:balance_v}).
+Thus, at solar minimum with a SSN around 0 the slow wind component contributes about \SI{64}{\%} and drops to \SI{28}{\%} during solar maximum conditions with a SSN around 200.
+	\item The calculated median velocity values for PSP's first and first closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+	\item The proton density relation appears to be valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
+	\item The estimated density median values (\ref{eq:median_n}) for PSP's first and first closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
+	\item The derived correlation function for the proton temperature appears to provide too high temperature values around PSP’s closest perihelion in comparison to coronal measurements.
+	\item The estimated temperature median values (\ref{eq:median_T}) for PSP's first and first closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}

### 2017-11-08 paperMVVB/sections/content.tex
new folder referee_report_second

@@
 In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the first closest approach at \SI{0.046}{\au}.
-\textbf{Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions.
+Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions.
 These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
-The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.}
+The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.
 %B

### 2017-11-09 paperMVVB_referee_report_second/referee_report_second_responses.txt
implemented changes from second referee report

Cover letter to the editor

Reference: AA/2017/31831

Reply to the reviewer's comments on the revised version of "Solar wind predictions for the Parker Solar Probe orbit - Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations", submitted by M. S. Venzmer and V. Bothmer to Astronomy and Astrophysics, 25 August 2017.

We are grateful to the referee for the thorough review of the manuscript and for the very helpful comments which we have carefully taken into account. All modifications appear as bold text in the revised version of the manuscript.

There are no major changes to the manuscript. We have adressed the referee's comments and suggestions.

#####

Reply to the referee

The authors have responded commendably to the suggestions made in my previous report, and I recommend acceptance of this paper. There were just a couple of minor points that might be considered (I’m using the version formatted for the journal):

Page 1
Column 1, 5 lines from bottom: Suggest: 2017, having crossed the heliopause into interstellar

- We changed it accordingly.

Column 2, line 2: Suggest: 2012) currently providing observations while orbiting

- We adopted the suggestion.

Page 2, column 2, 7 pages from bottom. This sentence isn’t very clear, e.g. suggest: The occurrence frequency of these slow and fast streams varies strongly with solar activity, and their interactions lead to phenomena such as stream interaction regions which may persist for many solar rotations (“corotating” interaction regions) if the coronal source regions are quasi-stationary (Balogh et al. 1999). Or just end the sentence at “stream interaction regions”.

- We adopted the suggestion.

In this version of the paper, Figure 2 is positioned before Figure 1, but presumably this will be corrected in the published version.

- Yes, the order is correct in the source, but is changed by the latex-compiler and might be corrected in the published version.

Page 4: The meaning of the numbers in brackets in Table 1, etc, is still rather cryptic. So to see if I understand, say for the field, then a change in the last digit (0.001) corresponds to 16 standard deviations away from mean, i.e., the standard deviation is 0.0000625? Is this the correct interpretation?

- The combination of the error source (estimated standard deviation of the fit parameter) and the notation description made it confusing. The interpretation for 5.661(16) is rather 0.016 nT. We clarified the situation, writing: "The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value. Their values are calculated from the estimated standard deviations of the fit parameters."

Page 6 
Column 1, 2 lines from bottom: Suggest: it appears to be a more realistic approach

- We changed it accordingly.

Section 4, line 3: Suggest: We then examine how the fits may be extrapolated towards the Sun and in particular in to the PSP orbit.

- We changed it accordingly.

Page 7 
Column 2, paragraph 3, line 5: Suggest: For the frequency distribution fit function to be discussed in the next paragraph,

- We changed it accordingly.

Page 8 
Figure 7 caption, line 2: “distribution” rather than “abundance”? I suppose this is to spread out the points rather than have them arranged vertically at separations of 0.01 AU.

- We changed it accordingly.

Page 9 
Column 1, line 3: Suggest: The high velocity tail that increases with distance arises

- We changed it accordingly.

Page 10 
Figure 10 caption: Is the Kalman filter prediction the blue shaded region? If so, this could be mentioned.

- The shaded regions are the expected ranges. We have added an explaining note for the shaded regions.

Page 13 
Column 2, second point: It wasn’t immediately obvious until I searched around the paper that the numbers in brackets here (12) and in the other points refer back to the similarly numbered equations. This could be mentioned specifically. Also, the next line should be “first and closest perihelia”; the second "first" added isn't necessary and confuses the meaning. Similarly in the later points.

- We now refer to the equation numbers with 'obtained from relation (12)'.
- Indeed 'first closest perihelion' might be confusing, so we have replaced it with '22nd perihelion'. We introduced it because there will be more perihelia at the closest distance - however with differing SSNs.

### 2017-11-09 paperMVVB/sections/content.tex
implemented changes from second referee report

@@
 The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
-Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-Various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having \textbf{crossed} the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+Various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} \textbf{currently providing observations while} orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
@@
 The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, such as intermittent reconnection at the top of helmet streamers and from coronal hole boundaries \citep{Kilpua2016}.
-The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
+The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions \textbf{which may persist for many solar rotations ("co-rotating" interaction regions) if the coronal source regions are quasi-stationary} \citep{Balogh1999}.
 Embedded in the slow and fast solar wind streams are transient flows of CMEs -- the faster ones driving shock waves ahead \citep{Gosling1974}.
@@
 For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
-For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
+The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
+Their values are calculated from the estimated standard deviations of the fit parameters.} For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
 	\label{tab:lognormal_fit_parameters}
@@
 From visual inspection, the resulting fit curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
-This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} in percentage of the distribution area, being almost three times larger than those from the other parameters.
 \begin{figure*}
@@
 \end{figure*}
+However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
+This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} in percentage of the distribution area, being almost three times larger than those from the other parameters.
 
@@
 For the velocity the fit parameters from the double lognormal fit (\ref{eq:double_lognormal_fit_function}) and their balancing function (\ref{eq:balance_with_ssn}) are given.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
-The listed SSN time lags are used for the fits.}
+The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
+Their values are calculated from the estimated standard deviations of the fit parameters.} The listed SSN time lags are used for the fits.}
 	\label{tab:ssn_fit_parameters}
@@
 The to some degree steeper balance parameter of the double fit function used in this model cannot be compared directly with specific velocity thresholds between slow and fast solar wind.
-However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
+However, it appears \textbf{to be} a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
 %(i.e. there exists slow wind with properties of fast wind and vice versa)
@@
 In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit power law dependencies to the Helios data.
-We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step they are extrapolated to the PSP orbit.
+We \textbf{then examine how the fits may be extrapolated towards the Sun and in particular in} to the PSP orbit.
 We use the fitting methods of Sect.~\ref{sec:frequency_distribution} for the distance-binned combined data from both Helios probes.
@@
 The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well.
-The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
+The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the \textbf{distribution} visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
 The high velocity data points above \SI{800}{\km\per\s} (circled red) are identified as CME events \citep[e.g.,][]{Sheeley1985,Bothmer1996,Bothmer1998}.}
@@
 	\caption{Fit coefficients for the median and mean solar distance dependencies (\ref{eq:power_function}) of the four solar wind parameters derived from the combined Helios~1 and 2 data.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
-The crossing distances indicate where the median and mean fits intersect each other.
+The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
+Their values are calculated from the estimated standard deviations of the fit parameters.} The crossing distances indicate where the median and mean fits intersect each other.
 The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
@@
 In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
-For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
+For the \textbf{frequency distribution fit function to be discussed in the next paragraph,} we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
 We note that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
@@
 	\caption{Fit coefficients for the distance depending single lognormal function, based on equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}), respectively double lognormal function (\ref{eq:double_lognormal_fit_function}) for the velocity from the combined Helios data.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
-The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
+The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
+Their values are calculated from the estimated standard deviations of the fit parameters.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
 	\label{tab:extrapolation_model_fit_parameters}
@@
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-The with distance increasing high velocity tail arises from using the same exponent for both slow and fast components.
+The \textbf{high velocity tail that increases with distance} arises from using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC Standard Curves Kalman filter prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC Standard Curves Kalman filter prediction \textbf{and SWPC prediction with their corresponding expected ranges (shaded areas).
+The SSN from previous cycle~24, shifted by 11~years, is plotted} together with two alternative trends of half and twice its amplitude.}
 	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
@@
 	\item The dependency of the magnetic field strength on solar activity and radial distance appears to be valid above \SI{20}{\Rs}, however near PSP's closest perihelia the actual values might be found to be slightly higher.
-	\item The estimated magnetic field strength median values (\ref{eq:median_B}) for PSP's first and first closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+	\item The estimated magnetic field strength median values \textbf{obtained from relation (\ref{eq:median_B})} for PSP's first and \textbf{22nd} perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
 	\item The radial dependencies of the proton velocity median values for slow and fast solar wind (\ref{eq:median_v}) appear to be valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
@@
 Thus, at solar minimum with a SSN around 0 the slow wind component contributes about \SI{64}{\%} and drops to \SI{28}{\%} during solar maximum conditions with a SSN around 200.
-	\item The calculated median velocity values for PSP's first and first closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+	\item The calculated median velocity values for PSP's first and \textbf{22nd} perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
 	\item The proton density relation appears to be valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-	\item The estimated density median values (\ref{eq:median_n}) for PSP's first and first closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
+	\item The estimated density median values \textbf{obtained from relation (\ref{eq:median_n})} for PSP's first and \textbf{22nd} perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
 	\item The derived correlation function for the proton temperature appears to provide too high temperature values around PSP’s closest perihelion in comparison to coronal measurements.
-	\item The estimated temperature median values (\ref{eq:median_T}) for PSP's first and first closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+	\item The estimated temperature median values \textbf{obtained from relation (\ref{eq:median_T})} for PSP's first and \textbf{22nd} perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}

### 2017-11-09 paperMVVB_referee_report_second/referee_report_second_responses_final.txt
implemented changes from second referee report #2

--- 2017-11-09 paperMVVB_referee_report_second/referee_report_second_responses.txt
@@
 
-We are grateful to the referee for the thorough review of the manuscript and for the very helpful comments which we have carefully taken into account.
+We are very grateful to the referee for the thorough review of the manuscript and for the helpful comments which we have carefully taken into account.
 All modifications appear as bold text in the revised version of the manuscript.
 
-There are no major changes to the manuscript. We have adressed the referee's comments and suggestions.
+We have carefully addressed the referee's comments and suggestions. No other changes have been made.
 
@@
 
-- We adopted the suggestion.
+- Changed as suggested.
 
@@
 
-- Yes, the order is correct in the source, but is changed by the latex-compiler and might be corrected in the published version.
+- The order is correct in the source file, but was changed by the A&A latex-compiler and shall be corrected in the version to be published.
 
@@
 
-- The combination of the error source (estimated standard deviation of the fit parameter) and the notation description made it confusing.
+- The combination of the error source (estimated standard deviation of the fit parameter) and the notation description was indeed confusing.
 The interpretation for 5.661(16) is rather 0.016 nT.
-We clarified the situation, writing: "The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
-Their values are calculated from the estimated standard deviations of the fit parameters."
+We clarified this by modifying the caption as follows: "The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+They are calculated from the estimated standard deviations of the fit parameters."
 
@@
 
-- The shaded regions are the expected ranges. We have added an explaining note for the shaded regions.
+- Yes, the shaded regions are the expected ranges. We have added an explaining note.
 
@@
 - Indeed 'first closest perihelion' might be confusing, so we have replaced it with '22nd perihelion'.
-We introduced it because there will be more perihelia at the closest distance - however with differing SSNs.
+We had phrased it like that because there will be several perihelia at the so-called closest distance.

### 2017-11-09 paperMVVB/sections/content.tex
implemented changes from second referee report #2

@@
 The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
-Their values are calculated from the estimated standard deviations of the fit parameters.} For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
+They are calculated from the estimated standard deviations of the fit parameters.} For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
 	\label{tab:lognormal_fit_parameters}
@@
 The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
-Their values are calculated from the estimated standard deviations of the fit parameters.} The listed SSN time lags are used for the fits.}
+They are calculated from the estimated standard deviations of the fit parameters.} The listed SSN time lags are used for the fits.}
 	\label{tab:ssn_fit_parameters}
@@
 The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
-Their values are calculated from the estimated standard deviations of the fit parameters.} The crossing distances indicate where the median and mean fits intersect each other.
+They are calculated from the estimated standard deviations of the fit parameters.} The crossing distances indicate where the median and mean fits intersect each other.
 The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
@@
 The numbers in parentheses are the \textbf{errors referred to the corresponding last digits of the quoted value.
-Their values are calculated from the estimated standard deviations of the fit parameters.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
+They are calculated from the estimated standard deviations of the fit parameters.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
 	\label{tab:extrapolation_model_fit_parameters}

### 2017-11-10 paperMVVB/sections/content.tex
removed unnecessary package and replaced Sachdeva2017 source with ADS bib

--- 2017-11-08 paperMVVB/sections/content.tex
@@
 The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
-Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-Various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having crossed the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+Various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} currently providing observations while orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
@@
 The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, such as intermittent reconnection at the top of helmet streamers and from coronal hole boundaries \citep{Kilpua2016}.
-The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions and for quasi-stationary coronal source regions to co-rotating interaction regions \citep{Balogh1999}.
+The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions which may persist for many solar rotations ("co-rotating" interaction regions) if the coronal source regions are quasi-stationary \citep{Balogh1999}.
 Embedded in the slow and fast solar wind streams are transient flows of CMEs -- the faster ones driving shock waves ahead \citep{Gosling1974}.
@@
 For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+They are calculated from the estimated standard deviations of the fit parameters.
 For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
@@
 For the velocity the fit parameters from the double lognormal fit (\ref{eq:double_lognormal_fit_function}) and their balancing function (\ref{eq:balance_with_ssn}) are given.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+They are calculated from the estimated standard deviations of the fit parameters.
 The listed SSN time lags are used for the fits.}
@@
 The to some degree steeper balance parameter of the double fit function used in this model cannot be compared directly with specific velocity thresholds between slow and fast solar wind.
-However, it appears being likely a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
+However, it appears to be a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
 %(i.e. there exists slow wind with properties of fast wind and vice versa)
@@
 In order to derive heliocentric distance relationships of the bulk solar wind distribution functions, we apply and fit power law dependencies to the Helios data.
-We evaluate the fits’ extrapolation behavior in direction to the Sun, because in a subsequent step they are extrapolated to the PSP orbit.
+We then examine how the fits may be extrapolated towards the Sun and in particular in to the PSP orbit.
 We use the fitting methods of Sect.~\ref{sec:frequency_distribution} for the distance-binned combined data from both Helios probes.
@@
 The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well.
-The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
+The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the distribution visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}.
 The high velocity data points above \SI{800}{\km\per\s} (circled red) are identified as CME events \citep[e.g.,][]{Sheeley1985,Bothmer1996,Bothmer1998}.}
@@
 	\caption{Fit coefficients for the median and mean solar distance dependencies (\ref{eq:power_function}) of the four solar wind parameters derived from the combined Helios~1 and 2 data.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+They are calculated from the estimated standard deviations of the fit parameters.
 The crossing distances indicate where the median and mean fits intersect each other.
@@
 In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
-For the coming frequency distribution fit function we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
+For the frequency distribution fit function to be discussed in the next paragraph, we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
 We note that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
@@
 	\caption{Fit coefficients for the distance depending single lognormal function, based on equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}), respectively double lognormal function (\ref{eq:double_lognormal_fit_function}) for the velocity from the combined Helios data.
-The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.
+The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+They are calculated from the estimated standard deviations of the fit parameters.
 The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
@@
 The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-The with distance increasing high velocity tail arises from using the same exponent for both slow and fast components.
+The high velocity tail that increases with distance arises from using the same exponent for both slow and fast components.
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
@@
 Consecutive Venus flybys bring its perihelia nearer to the Sun.
-Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC Standard Curves Kalman filter prediction, SWPC prediction and by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
+Actual and predicted SSN (bottom), that is, SIDC 13-month smoothed monthly actual SSN, SIDC Standard Curves Kalman filter prediction and SWPC prediction with their corresponding expected ranges (shaded areas).
+The SSN from previous cycle~24, shifted by 11~years, is plotted together with two alternative trends of half and twice its amplitude.}
 	\label{fig:SPP_orbit_predicted_SSN_overview_f_plot}
@@
 	\item The dependency of the magnetic field strength on solar activity and radial distance appears to be valid above \SI{20}{\Rs}, however near PSP's closest perihelia the actual values might be found to be slightly higher.
-	\item The estimated magnetic field strength median values (\ref{eq:median_B}) for PSP's first and first closest perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+	\item The estimated magnetic field strength median values obtained from relation (\ref{eq:median_B}) for PSP's first and 22nd perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
 	\item The radial dependencies of the proton velocity median values for slow and fast solar wind (\ref{eq:median_v}) appear to be valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
@@
 Thus, at solar minimum with a SSN around 0 the slow wind component contributes about \SI{64}{\%} and drops to \SI{28}{\%} during solar maximum conditions with a SSN around 200.
-	\item The calculated median velocity values for PSP's first and first closest perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+	\item The calculated median velocity values for PSP's first and 22nd perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
 	\item The proton density relation appears to be valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-	\item The estimated density median values (\ref{eq:median_n}) for PSP's first and first closest perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
+	\item The estimated density median values obtained from relation (\ref{eq:median_n}) for PSP's first and 22nd perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
 	\item The derived correlation function for the proton temperature appears to provide too high temperature values around PSP’s closest perihelion in comparison to coronal measurements.
-	\item The estimated temperature median values (\ref{eq:median_T}) for PSP's first and first closest perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+	\item The estimated temperature median values obtained from relation (\ref{eq:median_T}) for PSP's first and 22nd perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
 \end{itemize}

### 2017-11-10 paperMVVB_for_aanda/paperMVVB.tex
cleared tex files from comments; integrated all into one tex file

--- 2017-11-10 paperMVVB/sections/content.tex
@@
+\documentclass[]{aa}
+
+\usepackage[varg]{txfonts}
+\usepackage{graphicx}
+\usepackage{multirow}
+\newcommand{\Rs}{$R_\sun{}$}
+\usepackage{siunitx}
+	\DeclareSIUnit[number-unit-product=\,]\au{au}
+	\DeclareSIUnit[number-unit-product=\,]\nT{\nano\tesla}
+	\DeclareSIUnit[number-unit-product=\,]\Rs{\textit{R}_\sun{}}
+	\sisetup{table-figures-uncertainty=2, table-number-alignment=center, range-phrase=--, range-units=single}
+
+\begin{document}
+	\title{Solar wind predictions for the Parker Solar Probe orbit}
+	\subtitle{Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations}
+	\author{M.~S.~Venzmer
+	\and V.~Bothmer}
+	\institute{University of Goettingen, Institute for Astrophysics, Friedrich-Hund-Platz~1, 37077~Göttingen, Germany}
+	\date{Received 25 August 2017; accepted date}
+
+	\abstract
+	{The Parker Solar Probe (PSP) (formerly Solar Probe Plus) mission will be humanity’s first in situ exploration of the solar corona with closest perihelia at \num{9.86}~solar radii (\si{\Rs}) distance to the Sun.
+It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
+The scope of this study is to model the solar wind environment for PSP’s unprecedented distances in its prime mission phase during the years \numrange{2018}{2025}.
+The study is performed within the project Coronagraphic German And US SolarProbePlus Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).}
+	{We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data.
+The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
+The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au} over more than five solar cycles.
+The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar wind parameters on solar activity and to forecast their properties for the PSP mission.}
+	{The frequency distributions for the solar wind key parameters magnetic field strength, proton velocity, density and temperature are represented by lognormal functions.
+In addition, we consider the velocity distribution’s bi-componental shape, consisting of a slower and a faster part.
+Functional relations to solar activity are compiled with use of the OMNI data by correlating and fitting the frequency distributions with the SSN.
+Further, based on the combined data set from both Helios probes, the parameters’ frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
+Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
+Finally, the inclusion of SSN predictions and the extrapolation down to PSP’s perihelion region enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}
+	{The CGAUSS empirical solar wind model for PSP yields dependencies on solar activity and solar distance for the solar wind parameters' frequency distributions.
+The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}.
+The estimates for PSP’s first closest perihelion, occuring in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
+Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.}
+	{}
+	\keywords{solar wind -- sun: heliosphere -- sun: corona}
+
+	\maketitle
+
 	\section{Introduction}
-%solar wind beginnings
 	From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun.
 With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1959 \citep{Gringauz1960,Neugebauer1966}.
-%in situ spacecraft
 	The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
@@
 Helios~2, launched two years later, approached the Sun as close as \SI{0.29}{\au} \citep{Rosenbauer1977}.
-%Solar Probe Plus mission
 	The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rs), that is, \SI{0.0459}{\au} \citep{Fox2015}.
@@
 
-%PSP objectives and instruments
 	The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” as stated in \citet{Fox2015}.
@@
 
-%CGAUSS and WISPR
 	The study presented in this paper is undertaken in the Coronagraphic German And US SolarProbePlus Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).
@@
 
-%definition of sw environment
-%section{Solar wind}
 	Generally two types of solar wind are observed in the heliosphere -- slow and fast streams \citep{Neugebauer1966,Schwenn1983}.
@@
 
-%solar wind parameters
 	It is not known which specific solar wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar wind parameters from existing solar wind measurements and take solar cycle dependencies into account.
@@
 
-%sections
 	Our approach is to obtain analytical representations of the shapes of the solar wind parameter’s frequency distributions in Sect.~\ref{sec:frequency_distribution}, of their solar activity dependence in Sect.~\ref{sec:solar_activity_variations} and of their solar distance scaling in Sect.~\ref{sec:solar_distance_dependency}.
@@
 
-%lognormal fitting
 	\section{Frequency distributions of the solar wind parameters}
@@
 
-%about OMNI data
 	The OMNI~2 data set \citep{King2005} combines solar wind magnetic field and plasma data collected by various satellites since 1963, currently by WIND and by ACE.
@@
 The data is obtained from the OMNIWeb interface\footnote{\url{http://omniweb.gsfc.nasa.gov/}} at NASA's Space Physics Data Facility (SPDF), Goddard Space Flight Center (GSFC).
-%OMNIWeb Data Documentation: http://omniweb.gsfc.nasa.gov/html/ow_data.html
-% Acknowledgement to the SPDF OMNIWeb database as the source of data used in publications is requested: "The OMNI data were obtained from the GSFC/SPDF OMNIWeb interface at http://omniweb.gsfc.nasa.gov".
-Further, for recent years when few sources (IMP 8, Wind, ACE, Geotail) contributed to OMNI, it would be appropriate to also cite the PI's who provided the data to OMNI.
-Copies of preprints or reprints of OMNI-based publications sent to Natalia Papitashvili (address below) would be appreciated for tracking purposes.
-% The best citable reference to OMNI data is J.H.
-King and N.E.
-Papitashvili, Solar wind spatial scales in and comparisons of hourly Wind and ACE plasma and magnetic field data, J.
-Geophys.
-Res., Vol.
-110, No.
-A2, A02209, 10.1029/2004JA010804.
-%
-%data time range
 	In this study the whole hourly data until 31 December 2016 is used, starting from 27 November 1963 (for the temperature from 26 July 1965).
 The data coverage of the different parameters is in the range \SIrange{67}{74}{\percent},  corresponding to a total duration of 36--40~years.
-%OMNI 1963-01-01 data
-%B 1963-11-27 14:30
-%V 1963-11-27 12:30
-%N 1963-11-27 12:30
-%T 1965-07-26 00:30
-%1963-01-01~00:00--2016-12-31~23:30 all
-%19724 d; 54 y\\
-% B: 73.91 \%		39.91 y\\
-% V: 73.07 \%		39.46 y\\
-% N: 70.29 \%		37.96 y\\
-% T: 66.73 \%		36.03 y\\
-%
-%hourly data
 	We note that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
 
-%data binning
 	According to the OMNI data precision and maximal parameter ranges we specify bin sizes of \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
@@
 
-%subsection{Lognormal fitting}
-%choice of distribution function
 	The frequency distributions of the solar wind parameters magnetic field strength, proton density and temperature can
@@
 	\end{table*}
-% Vdbl fit:
-% medians = 489, 368
-% means = 500, 372
-% c = 0.504
-% via calculate_twolognormal_median.py:
-% mean = 442.38
-% median = 416.05
-% fit data difference (normed area):\\
-% B: 0.0682978\\
-% v: 0.186874 -> 0.0419676 (double fit)\\
-% n: 0.0648273\\
-% T: 0.0578349\\
 
@@
 
-%double lognormal fitting
-%%%%%%%%%%%%%%%%%%%%%%%%%
-%justification for compositional lognormal fit
 	In order to find a better fit result for the velocity distribution, we assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
@@
 
-%transition
 	For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well.
@@
 
-%{\color{red} discuss high value zoom figures; read in Veselovsky2010}
-
 	\section{Solar activity dependence of the solar wind frequency distributions}
@@
 
-%\subsection{SSN correlation}
 	For the correlations we fit lognormal functions to the frequency distributions as in Sect.~\ref{sec:frequency_distribution}, but implement linear relations to the yearly SSN, allowing shifting of the distribution functions with SSN.
@@
 
-%\subsection{SSN data}
 	The international sunspot number (\citeyear{sidc}) is provided by the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
@@
 	\end{figure}
-The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}. %density modulation with SSN \citep{Schwenn1983} p.~499\\
+	The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}.
 	For instance the fast solar wind occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
@@
 	Velocity and temperature show time lags of 3~years with peak correlation coefficients of 0.453 and 0.540.
-The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the density anticorrelation to the SSN reported by \citet{Bougeret1984}.	%p.~406\\
-% maximal correlation coefficients and their time lags:\\
-% magnetic field strength: lag 0, 0.728\\
-% velocity: lag -3, 0.453\\
-% density: lag -6, 0.468\\
-% temperature: lag -3, 0.540\\
+The density with a correlation coefficient of 0.468 has a time lag of 6~years, which is in agreement with the density anticorrelation to the SSN reported by \citet{Bougeret1984}.
 
-%\subsection{SSN fitting}
 	Next we create solar activity dependent analytical representations of the solar wind frequency distributions.
@@
 			\multicolumn{2}{l}{Magnetic field [\si{nT}]}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
-%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
 			\multicolumn{2}{l}{Density [\si{\per\cm\cubed}]}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
@@
 	\end{figure}
-% 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).
 
@@
 However, it appears to be a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
-%(i.e. there exists slow wind with properties of fast wind and vice versa)
 
-%exponential fitting
-%%%%%%%%%%%%%%%%%%%%
 	\section{Solar distance dependency}
@@
 The data are retrieved from the Coordinated~Data~Analysis~Web (CDAWeb) interface at NASA's GSFC/SPDF\footnote{\url{http://spdf.gsfc.nasa.gov/}}.
-%Helios plasma instrument (E1); Helios magnetometer instrument (E2)
-% Helios data ranges:\\
-% - time range Helios~1 [1974-12-10--1981-06-14] (12.5~orbits), Helios~2 [1976-01-01--1980-03-04] (8~orbits)\\
-% - solar distance range Helios~1 0.31--0.98~au, Helios~2 0.29--0.98~au\\
-%data sources
 
@@
 The plasma data coverage is \SI{76}{\%} (i.e., 5.0~years) in case of Helios~1 and \SI{92}{\%} (i.e., 3.9~years) in case of Helios~2.
-% temporal coverage of merged data\\
-% Helios 1: 1974-12-10--1981-06-14; 6y6m15d = 2388~d = 6.538~y\\
-% Mag data coverage: 42.6~\%; 2.785~years\\
-% Plasma data coverage: 76.4~\%; 4.995~years\\
-% Helios 2: 1976-01-01--1980-03-04; 4y3m4d = 1557~d = 4.263~y\\
-% Mag data coverage: 54.4~\%; 2.319~years (83~\% of H1)\\
-% Plasma data coverage: 91.8~\%; 3.913~years (78~\% of H1)\\
-%Helios data biased towards solar minimum
 	Thus, using this data, we point out that its time coverage is unequally distributed over the solar cycle.
@@
 This Helios data bias towards solar minimum is one reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
-% data gaps -> uneven coverage -> solar cycle minimum dominates; ratio of max vs min cycle data coverage; for OMNI data negligible\\
-% 13~months smoothed sunspot number \citep{sidc}: divide June~1977 (include figure)\\
-% put link on sidc webpage: http://sidc.be/sunspot-data/SIDCpub.php
-% begin: 1974-12 36.1\\
-% minimum: May/June 1976 18.3/17.9 (cite?)\\
-% divide 30~June~1977 37.7 from SIDC data (nearly same SSN as at Helios~1 beginning)\\
-% cycle 21 maximum: Dec 1979 232.9 (cite?)\\
-% end: 1981-06 200.9\\
-% 
-% data gap hours and percentages:\\
-% % H1 minimum 22416 h\\
-% % H1 maximum 34681 h\\
-% % H2 minimum 13128 h\\
-% % H2 maximum 23472 h\\
-% % sum 93697 h\\
-% solar minimum: 35\,544~h, 37.94~\%\\
-% solar maximum: 58\,153~h, 62.06~\%\\
-
-% 1974 11 1974.874   39.3   4.2    30  
-% 1974 12 1974.958   36.1   4.0    31  
-% 1975 01 1975.042   33.0   3.9    31  
-% 1975 02 1975.123   31.8   3.8    28  
-% 1975 03 1975.204   30.6   3.7    31  
-% 1975 04 1975.288   26.8   3.5    30  
-% 1975 05 1975.371   24.2   3.3    31  
-% 1975 06 1975.455   23.2   3.3    30  
-% 1975 07 1975.538   21.8   3.2    31  
-% 1975 08 1975.623   20.7   3.1    31  
-% 1975 09 1975.707   20.9   3.1    30  
-% 1975 10 1975.790   22.3   3.2    31  
-% 1975 11 1975.874   23.3   3.3    30  
-% 1975 12 1975.958   23.6   3.3    31  
-% 1976 01 1976.042   22.1   3.2    31  
-% 1976 02 1976.124   19.2   3.0    29  
-% 1976 03 1976.206   17.8   2.9    31  
-% 1976 04 1976.290   18.4   2.9    30  
-% 1976 05 1976.373   18.3   2.9    31  
-% 1976 06 1976.456   17.9   2.9    30  
-% 1976 07 1976.540   18.8   2.9    31  
-% 1976 08 1976.624   20.5   3.1    31  
-% 1976 09 1976.708   20.8   3.1    30  
-% 1976 10 1976.791   19.7   3.0    31  
-% 1976 11 1976.874   19.7   3.0    30  
-% 1976 12 1976.958   21.6   3.2    31  
-% 1977 01 1977.042   24.3   3.3    31  
-% 1977 02 1977.123   26.3   3.5    28  
-% 1977 03 1977.204   28.8   3.6    31  
-% 1977 04 1977.288   31.9   3.8    30  
-% 1977 05 1977.371   34.7   4.0    31  
-% 1977 06 1977.455   37.7   4.1    30  
-% 1977 07 1977.538   41.4   4.3    31  
-% 1977 08 1977.623   47.6   4.6    31  
-% 1977 09 1977.707   55.8   5.0    30  
-% 1977 10 1977.790   64.8   5.4    31  
-% 1977 11 1977.874   73.7   5.7    30  
-% 1977 12 1977.958   80.7   6.0    31  
-% 1978 01 1978.042   86.9   6.2    31  
-% 1978 02 1978.123   91.5   6.4    28  
-% 1978 03 1978.204   98.7   6.6    31  
-% 1978 04 1978.288  109.0   7.0    30  
-% 1978 05 1978.371  117.8   7.2    31  
-% 1978 06 1978.455  126.6   7.5    30  
-% 1978 07 1978.538  138.0   7.8    31  
-% 1978 08 1978.623  147.3   8.1    31  
-% 1978 09 1978.707  153.6   8.3    30  
-% 1978 10 1978.790  157.3   8.4    31  
-% 1978 11 1978.874  160.4   8.5    30  
-% 1978 12 1978.958  166.7   8.6    31  
-% 1979 01 1979.042  175.2   8.8    31  
-% 1979 02 1979.123  185.4   9.1    28  
-% 1979 03 1979.204  193.3   9.3    31  
-% 1979 04 1979.288  199.9   9.4    30  
-% 1979 05 1979.371  208.5   9.6    31  
-% 1979 06 1979.455  216.7   9.8    30  
-% 1979 07 1979.538  219.5   9.9    31  
-% 1979 08 1979.623  220.1   9.9    31  
-% 1979 09 1979.707  220.4   9.9    30  
-% 1979 10 1979.790  223.4  10.0    31  
-% 1979 11 1979.874  229.8  10.1    30  
-% 1979 12 1979.958  232.9  10.2    31  
-% 1980 01 1980.042  232.0  10.2    31  
-% 1980 02 1980.124  230.2  10.2    29  
-% 1980 03 1980.206  227.9  10.1    31  
-% 1980 04 1980.290  224.6  10.0    30  
-% 1980 05 1980.373  221.3  10.0    31  
-% 1980 06 1980.456  219.1   9.9    30  
-% 1980 07 1980.540  216.1   9.9    31  
-% 1980 08 1980.624  212.0  10.0    31  
-% 1980 09 1980.708  211.5  10.2    30  
-% 1980 10 1980.791  211.9  10.5    31  
-% 1980 11 1980.874  209.1  10.9    30  
-% 1980 12 1980.958  202.8  11.0    31  
-% 1981 01 1981.042  199.6  11.1   271  
-% 1981 02 1981.123  202.2  11.5   229  
-% 1981 03 1981.204  205.4  12.1   244  
-% 1981 04 1981.288  205.7  12.6   254  
-% 1981 05 1981.371  204.1  12.8   268  
-% 1981 06 1981.455  200.9  13.1   227  
-% 1981 07 1981.538  198.5  13.1   268
 
@@
 The fits are weighted through the different data counts per bin.
-%fit result table and figure
 	The obtained coefficients for the median and mean power law fits ($d_\text{med}$, $e_\text{med}$, $d_\text{avg}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter} and their corresponding curves are shown in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.
@@
 	\end{table*}
-% source year variation: fit_out_yearly_gradients_table_b_stats.txt
 
-% comparison with other Helios studies (Schwenn, Bougeret)
-%Helios results, radial gradients see \citet{Schwenn1990} p.~155
 	Our derived exponents agree with those found in existing studies from the Helios observations: \citet{Mariani1978} derived the exponents for the magnetic field strength separately for the fast and slow solar wind as $B_\text{fast} \propto r^{-1.54}$ and $B_\text{slow} \propto r^{-1.61}$, ours is $B_\text{avg} \propto r^{-1.55}$.
-%$B_\text{fast} = 5.79\cdot r^{-1.54}$\,nT and $B_\text{slow} = 5.11\cdot r^{-1.61}$\,nT.
 	The velocity exponent $v_\text{avg} \propto r^{0.049}$ matches with the values found by \citet{Schwenn1983,Schwenn1990}, who derived the distance dependencies for both Helios spacecraft separately as $v_\text{H1} \propto r^{0.083}$ and $v_\text{H2} \propto r^{0.036}$.
 The calculated density exponent $n_\text{avg} \propto r^{-2.01}$ agrees well with the Helios plasma density model derived by \citet{Bougeret1984} yielding $n \propto r^{-2.10}$.
-%to the year 1976 normalized   a \SI{1}{\au} density of $n = 6.14\cdot r^{-2.10}\,\text{cm}^{-3}$.
 	The temperature exponent $T_\text{avg} \propto r^{-0.79}$ is similar to those in the studies by \citet{Hellinger2011,Hellinger2013}, who also derived the exponents separately for the fast and the slow solar wind: $T_\text{fast} \propto r^{-0.74}$ and $T_\text{slow} \propto r^{-0.58}$.
-%$T_\text{fast} = \num{2.5e5} (R/R_0)^{-0.74}$\,K and $T_\text{slow} = \num{6.2e4} (R/R_0)^{-0.58}$\,K.
-%\citet{Marsch1982}	$T_\text{||,slow} \propto r^{-1.03}$ and $T_\text{||,fast} \propto r^{-0.69}$.
 
-%crossing distances
 	The mean and median velocity fit exponents acquired from the Helios data are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
@@
 
-%\subsection{Power law lognormal fitting}
 	Next we retrieve the frequency distributions of the four solar wind parameters in solar distance bins of \SI{0.01}{\au}, choosing the same resolution as for the OMNI data analyzed in Sect.~\ref{sec:frequency_distribution} -- the distributions and their median values are plotted in Fig.~\ref{fig:mixed_fit_fixed_4_paper_f_plot}.
@@
 	\end{figure*}
-% Helios histogram bin sizes for mean of frequency distribution (at specific solar distance):\\
-% $B$: bin size 0.5~nT, min 337, mean precision: 0.000545\\
-% $v$: bin size 1~cm$^{-3}$, min 497, mean precision: 0.00449\\
-% $n$: bin size 10~km/s, min 497, mean precision:  0.00449\\
-% $T$: bin size 10\,000~K, min 497, mean precision: 4.49--44.49\\
 	For simplification, as mentioned before, we treat the exponents of the median and mean fit functions as being identical, using one fit parameter for both.
@@
 	\end{table*}
-% Vdbl fit:
-% medians = 370.7, 526
-% means = 374.8, 542
-% c = 0.557
-% via calculate_twolognormal_median.py:
-% mean = 446.64
-% median = 413.33
-%
-% Yearly Earth distance variations from Earth_orbit_variation_impact_estimate.ods
 
@@
 This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
-%\citep{Sanchez-Diaz2016} p.~2835, using MHD-model -> very slow solar wind is continuation of slow wind) (because of interaction)
 
@@
 
-%\subsection{Distance scaling law variations}
-%\label{sec:distance_scaling_law_variations}
 	This solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
@@
 	\end{figure}
-%yearly variation of the solar wind parameters' average fit function exponents
 	However, for simplicity we assume that the distance scaling laws can be treated as time independent and include the calculated exponents’ yearly variations $\Delta e$, summarized in Table~\ref{tab:mean_median_fit_parameter}, as relative uncertainties.
@@
 Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
-Since this latitudinal separation is highly variable and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.	%Balogh et al.
-(p.~162, 1999);	 (Schwenn 1990, p.~126)
+Since this latitudinal separation is highly variable and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.
 
@@
 
-%\subsection{Near-Sun extrapolation for PSP orbit}
-%PSP orbit
 	Parker Solar Probe is planned to launch in mid 2018.
@@
 	The model and its extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.
-%magnetic field:
 	The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of 0.
@@
 We note that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.
-%Since we cannot compare with their absolute values, because their DQCS model assumes fields of \SI{3.1}{\nT} at \SI{1}{\au} assumed to originate from coronal holes with boundaries at \SI{+-60}{\degree} latitude, excluding the fields from the equatorial slow wind belt.
 	We suggest that the difference in slope is due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) changing shape of the frequency distribution with heliocentric distance, which for smaller distances deviates more from the model’s lognormal distribution.
-%velocity:
 	The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} 3~years after a SSN of 0 occurred, whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
@@
 Thus PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
-%density:
 	The proton density increases from about \SI{84}{\per\cm\cubed} at \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} 6~years after a SSN of 0 occurred.
@@
 We assumed a solar wind helium abundance of \SI{5}{\%} to convert these electron densities to proton densities.
-%temperature:
 	The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} 3~years after a SSN of 0 occurred and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
@@
 
-%\subsection{SSN prediction for PSP mission time}
-%SSN prediction
 	Aside from the solar distance the derived solar wind parameter models depend on the SSN.
@@
 
-%\subsection{PSP solar wind environment estimation}
 	Implementing the SSN predictions for the PSP mission time and the orbital trajectory data, we can infer which solar wind parameter magnitudes can be expected.
@@
 	\end{figure}
-% SSN sources and error ranges for first perihelion
-% magnetic field:
-% SWPC prediction - 0 years
-% SWPC expected SSN ranges
-% velocity:
-% actual monthly SSN - 3 years
-% not plotted
-% density:
-% actual monthly SSN - 6 years
-% SIDC given std. dev. from stations
-% temperature:
-% actual monthly SSN - 3 years
-% SIDC given std. dev. from stations
 	\begin{figure}
@@
 	\end{figure}
-% SSN sources and error ranges for first closest perihelion
-% magnetic field:
-% actual monthly SSN - 11 years
-% half/twice SSN
-% velocity:
-% actual monthly SSN - 14 years
-% not plotted
-% density:
-% SWPC prediction - 0 years
-% SWPC expected SSN ranges
-% temperature:
-% actual monthly SSN - 14 years
-% half/twice SSN
 	In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the first closest approach at \SI{0.046}{\au}.
@@
 The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.
-%B
-% 87.3642361846083
-%N
-% 213.613795298952	first
-% 2950.67837375615	nearest
-% 2925.63248639046	SSN 0
-% 3421.59065204775	SSN 200
-%T
-% 503136.759398494
 
@@
 This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur (see Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar maximum \citep{Katsikas2010,Goelzer2014}.	% in average around 17~Rs (e.g., 0.6~Rs Schatten 1969, 17~Rs Sittler1999, 17~Rs Exarhos2000) and scales with solar activity between 15~Rs in minimum and 30~Rs in maximum (19~Rs Katsikas2010, 15–30~Rs Goelzer2014).
+The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar maximum \citep{Katsikas2010,Goelzer2014}.
 
@@
 
-%derive heliocentric distance depending error...\\
-%error estimation for general model and extreme value tendencies\\
-
-%magnetic field distribution's with distance increasing high value tail -> source are compression regions (why with density no increase?); look into Parker1958's B-field formula...\\
-%varying shape with distance is indicator for internal physical processes (mixing/turbulence...)\\
-
-%slow/fast streams basically maintain characteristic speeds with solar cycle; slow/fast ratio SSN dependency\\
-%for the overlapping velocity model the SSN dependency is steeper than for a simple threshold\\
-%The ratio of both varies with solar activity, e.g., 3~years after maximum, polar coronal holes are observed to often have equatorial extensions (cite?). see and use citet{Bougeret1984} p.~498...\\
-
-%\section{Summary}
-%\label{sec:summary}
 	With the resulting CGAUSS empirical solar wind model for PSP the following main results for the bulk solar wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
@@
 
-%Implications for WISPR mission operations and SoloHI on Solar Orbiter...
 	The results of the modeled solar wind environment will be useful to help optimize the WISPR and in situ instrument science plannings and PSP mission operations.
 This also applies for the Heliospheric Imager (SoloHI) \citep{Howard2013} and the in situ instruments on board the Solar Orbiter spacecraft.
+
+	\begin{acknowledgements}
+		The authors acknowledge support of the Coronagraphic German and US SolarProbePlus Survey (CGAUSS) project for WISPR by the German Aerospace Center (DLR) under grant 50~OL~1601 as national contribution to the Parker Solar Probe mission.
+The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data.
+The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive and the Space Physics Data Facility at NASA's Goddard Space Flight Center.
+Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations at the Solar Influences Data Analysis Center, Royal Observatory of Belgium.
+The PSP SPICE kernel was kindly provided by Angelos~Vourlidas.
+The authors thank the referee for the careful review of this manuscript and helpful comments and suggestions.
+	\end{acknowledgements}
+
+	\bibliographystyle{aa}
+	\bibliography{literature_bibtex}
+\end{document}

### 2017-11-17 paperMVVB_for_aanda/paperMVVB.tex
implemented the *.tex file from the language editor

@@
 \begin{document}
-	\title{Solar wind predictions for the Parker Solar Probe orbit}
-	\subtitle{Near-Sun extrapolations derived from an empirical solar wind model based on Helios and OMNI observations}
+        \title{Solar-wind predictions for the Parker Solar Probe orbit}
+        \subtitle{Near-Sun extrapolations derived from an empirical solar-wind model based on Helios and OMNI observations}
         \author{M.~S.~Venzmer
@@
 It will help answer hitherto unresolved questions on the heating of the solar corona and the source and acceleration of the solar wind and solar energetic particles.
-The scope of this study is to model the solar wind environment for PSP’s unprecedented distances in its prime mission phase during the years \numrange{2018}{2025}.
-The study is performed within the project Coronagraphic German And US SolarProbePlus Survey (CGAUSS) which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).}
-	{We present an empirical solar wind model for the inner heliosphere which is derived from OMNI and Helios data.
+The scope of this study is to model the solar-wind environment for PSP’s unprecedented distances in its prime mission phase during the years \numrange{2018}{2025}.
+The study is performed within the Coronagraphic German And US SolarProbePlus Survey (CGAUSS)   which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).}
+        {We present an empirical solar-wind model for the inner heliosphere which is derived from OMNI and Helios data.
 The German-US space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}.
 The OMNI database consists of multi-spacecraft intercalibrated in situ data obtained near \SI{1}{\au} over more than five solar cycles.
-The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar wind parameters on solar activity and to forecast their properties for the PSP mission.}
-	{The frequency distributions for the solar wind key parameters magnetic field strength, proton velocity, density and temperature are represented by lognormal functions.
+The international sunspot number (SSN) and its predictions are used to derive dependencies of the major solar-wind parameters on solar activity and to forecast their properties for the PSP mission.}
+        {The frequency distributions for the solar-wind key parameters, magnetic field strength, proton velocity, density, and temperature, are represented by lognormal functions.
 In addition, we consider the velocity distribution’s bi-componental shape, consisting of a slower and a faster part.
@@
 Further, based on the combined data set from both Helios probes, the parameters’ frequency distributions are fitted with respect to solar distance to obtain power law dependencies.
-Thus an empirical solar wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
-Finally, the inclusion of SSN predictions and the extrapolation down to PSP’s perihelion region enables us to estimate the solar wind environment for PSP’s planned trajectory during its mission duration.}
-	{The CGAUSS empirical solar wind model for PSP yields dependencies on solar activity and solar distance for the solar wind parameters' frequency distributions.
-The estimated solar wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}.
-The estimates for PSP’s first closest perihelion, occuring in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K}.
-Since the modeled velocity and temperature values below about \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar wind acceleration and heating processes below \SI{20}{\Rs} as planned.}
+Thus an empirical solar-wind model for the inner heliosphere confined to the ecliptic region is derived, accounting for solar activity and for solar distance through adequate shifts of the lognormal distributions.
+Finally, the inclusion of SSN predictions and the extrapolation down to PSP’s perihelion region enables us to estimate the solar-wind environment for PSP’s planned trajectory during its mission duration.}
+        {The CGAUSS empirical solar-wind model for PSP yields dependencies on solar activity and solar distance for the solar-wind parameters' frequency distributions.
+The estimated solar-wind median values for PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} are \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K}.
+The estimates for PSP’s first closest perihelion, occurring in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}), are \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed}, and \SI{1930000}{\K}.
+Since the modeled velocity and temperature values below approximately \SI{20}{\Rs} appear overestimated in comparison with existing observations, this suggests that PSP will directly measure solar-wind acceleration and heating processes below \SI{20}{\Rs} as planned.}
         {}
@@
         \section{Introduction}
-	From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun.
-With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1959 \citep{Gringauz1960,Neugebauer1966}.
+        From observations of cometary tail fluctuations, \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun.
+With his theoretical solar-wind model, \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1959 \citep{Gringauz1960,Neugebauer1966}.
         The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}.
-Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having crossed the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
-	Various spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} currently providing observations while orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
+Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances.
+In the case of Voyager~1, this was as far away as \SI{140}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} in October 2017, having crossed the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
+        Various spacecraft have provided a wealth of solar-wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}, SOHO \citep{Domingo1995}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} currently providing observations while orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction.
 Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}.
 Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}.
-The in situ solar wind measurements closest to the Sun to date were made by the Helios missions.
+The in situ solar-wind measurements closest to the Sun to date were made by the Helios missions.
 Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}.
 Helios~2, launched two years later, approached the Sun as close as \SI{0.29}{\au} \citep{Rosenbauer1977}.
-	The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rs), that is, \SI{0.0459}{\au} \citep{Fox2015}.
+        The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, six years after its planned launch date in mid 2018, will reach its closest perihelia at a distance of 9.86~solar radii (\Rs), that is, \SI{0.0459}{\au} \citep{Fox2015}.
 This distance will be achieved through seven Venus gravity assists with orbital periods of 88--168~days.
@@
         The key PSP science objectives are to “trace the flow of energy that heats and accelerates the solar corona and solar wind, determine the structure and dynamics of the plasma and magnetic fields at the sources of the solar wind, and explore mechanisms that accelerate and transport energetic particles” as stated in \citet{Fox2015}.
-To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurements of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurements of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles (SEPs) \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
+To achieve these goals, PSP has four scientific instruments on board: FIELDS for the measurement of magnetic fields and AC/DC electric fields \citep{Bale2016}, SWEAP for the measurement of flux of electrons, protons and alphas \citep{Kasper2016}, IS\sun{}IS for the measurement of solar energetic particles (SEPs) \citep{McComas2016} and WISPR for the measurement of coronal and inner heliospheric structures \citep{Vourlidas2016}.
 
         The study presented in this paper is undertaken in the Coronagraphic German And US SolarProbePlus Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).
-WISPR will contribute to the PSP science goals by deriving the 3D structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
-It will provide density power spectra over a wide range of structures (e.g., streamers, pseudostreamers and equatorial coronal holes) for determining the roles of turbulence, waves and pressure-balanced structures in the solar wind.
+WISPR will contribute to the PSP science goals by deriving the three-dimensional structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
+It will provide density power spectra over a wide range of structures (e.g., streamers, pseudostreamers and equatorial coronal holes) for determining the roles of turbulence, waves, and pressure-balanced structures in the solar wind.
 It will also measure the physical properties, such as speed and density jumps of SEP-producing shocks and their coronal mass ejection (CME) drivers as they evolve in the corona and inner heliosphere \citep{Vourlidas2016}.
+        In order to help optimize the WISPR and PSP preplanning of the science operations, knowledge of the expected solar-wind environment is needed.
+For this purpose the solar-wind environment is extrapolated down to the closest perihelion of \SI{9.86}{\Rs} distance to the Sun using in situ solar-wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the OMNI solar-wind database.
 
-	In order to help optimize the WISPR and PSP preplanning of the science operations knowledge of the expected solar wind environment is needed.
-For this purpose the solar wind environment is extrapolated down to the closest perihelion of \SI{9.86}{\Rs} distance to the Sun using in situ solar wind data from the Helios probes and near \SI{1}{\au} data from various satellites compiled in the OMNI solar wind database.
-
-	Generally two types of solar wind are observed in the heliosphere -- slow and fast streams \citep{Neugebauer1966,Schwenn1983}.
-Slow solar wind has typical speeds \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[p.~144]{Schwenn1990}.
+        Generally, two types of solar wind are observed in the heliosphere -- slow and fast streams \citep{Neugebauer1966,Schwenn1983}.
+Slow solar wind has typical speeds of \SI{<400}{\km\per\s} and fast solar wind has speeds \SI{>600}{\km\per\s} \citep[p.~144]{Schwenn1990}.
 Their different compositions and characteristics indicate different sources and generation processes \citep{McGregor2011a}.
 Fast streams are found to originate from coronal holes as confirmed by Ulysses' out-of-ecliptic measurements \citep{McComas1998}.
-The source of slow wind and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, such as intermittent reconnection at the top of helmet streamers and from coronal hole boundaries \citep{Kilpua2016}.
+The source of slow wind, and its eventually different types \citep{Schwenn1983}, is still a subject of controversial discussions because several scenarios are possible to explain its origin from closed magnetic structures in the solar corona, such as intermittent reconnection at the top of helmet streamers and from coronal hole boundaries \citep{Kilpua2016}.
 The occurrence frequency of these slow and fast streams varies strongly with solar activity and their interactions lead to phenomena such as stream interaction regions which may persist for many solar rotations ("co-rotating" interaction regions) if the coronal source regions are quasi-stationary \citep{Balogh1999}.
-	Embedded in the slow and fast solar wind streams are transient flows of CMEs -- the faster ones driving shock waves ahead \citep{Gosling1974}.
+        Embedded in the slow and fast solar-wind streams are transient flows of CMEs -- the faster ones driving shock waves ahead \citep{Gosling1974}.
 Their rate follows the solar activity cycle and varies in near \SI{1}{\au} measurements between only one CME every couple of days during solar cycle minima up to multiple CMEs observed over several days at times of solar maxima, that is, the CME-associated flow share of the solar wind raises from about \SI{5}{\percent} up to about \SI{50}{\percent} \citep{Richardson2012}.
 
-	It is not known which specific solar wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar wind parameters from existing solar wind measurements and take solar cycle dependencies into account.
-	As a baseline we describe the solar wind environment through the key quantities of a magnetized plasma: \emph{magnetic field strength}, \emph{density} and \emph{temperature}.
-Furthermore, the bulk flow \emph{velocity} is the defining parameter of the two types of solar wind.
-Solar wind quantities, like flux densities, mass flux and plasma beta, can directly be derived from these four parameters.
-In the analyses we treat the solar wind as a proton plasma -- the average helium abundance is about \SI{4.5}{\percent} and in slow wind at solar cycle minimum even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
+        It is not known which specific solar-wind type or structure PSP will encounter at a given time during its mission, therefore we extrapolate the probability distributions of the major solar-wind parameters from existing solar-wind measurements and take solar cycle dependencies into account.
+        As a baseline we describe the solar-wind environment through the key quantities of a magnetized plasma: magnetic field strength, density and temperature.
+Furthermore, the bulk flow {velocity} is the defining parameter of the two types of solar wind.
+Solar-wind quantities, like flux densities, mass flux, and plasma beta, can be directly derived from these four parameters.
+In the analyses, we treat the solar wind as a proton plasma -- the average helium abundance is about \SI{4.5}{\percent} and in slow wind at solar cycle minimum is even less than \SI{2}{\percent} \citep{Feldman1978,Schwenn1983,Kasper2012}.
 
-	Our approach is to obtain analytical representations of the shapes of the solar wind parameter’s frequency distributions in Sect.~\ref{sec:frequency_distribution}, of their solar activity dependence in Sect.~\ref{sec:solar_activity_variations} and of their solar distance scaling in Sect.~\ref{sec:solar_distance_dependency}.
-The solar wind parameters’ frequency distributions and solar activity dependence is derived from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles.
-Their distance dependency is derived from Helios solar wind measurements covering more than two third of the distance to the Sun and more than half a solar cycle.
-From combination of the obtained frequency distributions, SSN dependence functions and solar distance dependence functions a general solar wind model is build in Sect.~\ref{sec:empirical_solar_wind_model}, representing the solar activity and distance behavior.
+        Our approach is to obtain analytical representations of the shapes of the solar-wind parameter’s frequency distributions in Sect.~\ref{sec:frequency_distribution}, of their solar activity dependence in Sect.~\ref{sec:solar_activity_variations} and of their solar distance scaling in Sect.~\ref{sec:solar_distance_dependency}.
+The solar-wind parameters’ frequency distributions and solar activity dependence is derived from near-Earth solar wind and sunspot number (SSN) time series with a duration of almost five solar cycles.
+Their distance dependency is derived from Helios solar-wind measurements covering more than two thirds of the distance to the Sun and more than half a solar cycle.
+From a combination of the obtained frequency distributions, SSN dependence functions, and solar distance dependence functions, a general solar-wind model is built in Sect.~\ref{sec:empirical_solar_wind_model}, representing the solar activity and distance behavior.
 Finally, this empirical model is fed with SSN predictions and extrapolated to PSP's planned orbital positions in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
-	\section{Frequency distributions of the solar wind parameters}
+        \section{Frequency distributions of the solar-wind parameters}
         \label{sec:frequency_distribution}
-	The solar wind parameters are highly variable due to short-term variations from structures like slow and fast wind streams, interaction regions and CMEs, whose rate and properties depend on the phase of the solar activity cycle.
-Hence, for deriving characteristic frequency distributions for the solar wind parameters, measurements over long-term time spans are needed.
-The abundance of the near-Earth hourly OMNI data set is ideally suited for this purpose, because it spans to date almost five solar cycles.
+        The solar-wind parameters are highly variable due to short-term variations from structures such as slow and fast wind streams, interaction regions, and CMEs, whose rate and properties depend on the phase of the solar activity cycle.
+Hence, for deriving characteristic frequency distributions for the solar-wind parameters, measurements over long-term time spans are needed.
+The abundance of the near-Earth hourly OMNI data set is ideally suited for this purpose, because to date it spans almost five solar cycles.
 
-	The OMNI~2 data set \citep{King2005} combines solar wind magnetic field and plasma data collected by various satellites since 1963, currently by WIND and by ACE.
+        The OMNI~2 data set \citep{King2005} combines solar-wind magnetic field and plasma data collected by various satellites since 1963, currently by WIND and by ACE.
 This intercalibrated multi-spacecraft data is time-shifted to the nose of the Earth’s bow shock.
@@
 The data coverage of the different parameters is in the range \SIrange{67}{74}{\percent},  corresponding to a total duration of 36--40~years.
-	We note that a test-comparison of hourly averaged with higher time resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
+        We note that a test-comparison of hourly averaged data with higher-time-resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
+        According to the OMNI data precision and maximal parameter ranges we specify bin sizes of \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
+The frequency distributions of the solar-wind magnetic field strength, proton velocity, density and temperature are shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+        The solar-wind magnetic field strength is in the range \SIrange{0.4}{62}{nT}, the velocity in the range \SIrange{156}{1189}{\km\per\s}, the density in the range \SIrange{0}{117}{\per\cm\cubed}, the temperature in the range \SIrange{3450}{6.63e6}{\K}, and the mean data values are at \SI{6.28}{\nT}, \SI{436}{\km\per\s}, \SI{6.8}{\per\cm\cubed} and \SI{1.05e5}{\K}.
+These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar-wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
+        Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 CME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013}, or the solar-wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
 
-	According to the OMNI data precision and maximal parameter ranges we specify bin sizes of \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
-The frequency distributions of the solar wind magnetic field strength, proton velocity, density and temperature are shown in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
-	The solar wind magnetic field strength is in the range \SIrange{0.4}{62}{nT}, the velocity in the range \SIrange{156}{1189}{\km\per\s}, the density in the range \SIrange{0}{117}{\per\cm\cubed}, and the temperature in the range \SIrange{3450}{6.63e6}{\K}, the mean data values are at \SI{6.28}{\nT}, \SI{436}{\km\per\s}, \SI{6.8}{\per\cm\cubed} and \SI{1.05e5}{\K}.
-These ranges and mean values are as statistically expected from previous analyses of near \SI{1}{\au} solar wind data (e.g., Table~3.3 in \citet[p.~39]{Bothmer2007}).
-	Much higher or lower peak values at \SI{1}{\au} have been observed in extraordinary events, such as the 23~July 2012 CME with a speed of over \SI{2000}{\km\per\s} and a peak field strength of about \SI{100}{\nT} that was observed by STEREO~A \citep{Russell2013} or the solar wind disappearance event observed in May 1999 with density values even down to \SI{0.2}{\per\cm\cubed} \citep{Lazarus2000}.
-
-	The frequency distributions of the solar wind parameters magnetic field strength, proton density and temperature can
-	well be approximated by lognormal distributions, whereas the proton velocity’s frequency has a differing shape, as shown in \citet{Veselovsky2010}.
-We investigate how well all four solar wind parameters’ frequency distributions can be represented by lognormal functions, which we use in the process of a least squares regression fitting.
-The lognormal function
+        The frequency distributions of the solar-wind parameters, magnetic field strength, proton density, and temperature, can be
+        well approximated by lognormal distributions, whereas the proton velocity’s frequency has a differing shape, as shown in \citet{Veselovsky2010}.
+We investigate how well all four solar-wind parameters’ frequency distributions can be represented by lognormal functions, which we use in the process of a least squares regression fitting.
+The lognormal function,
         \begin{align}
-		W(x) &= \frac{1}{\sigma \sqrt{2 \pi} x} \, \exp\left(- \frac{\left(\ln x - \mu\right)^2}{2 \sigma^2}\right)	\label{eq:lognormal_function}
+                W(x) &= \frac{1}{\sigma \sqrt{2 \pi} x} \, \exp\left(- \frac{\left(\ln x - \mu\right)^2}{2 \sigma^2}\right),    \label{eq:lognormal_function}
         \end{align}
@@
 Changes in $\mu$ affect both the horizontal and vertical scaling of the function whereas $\sigma$ influences its shape.
-The distribution's median $x_\text{med}$ and mean $x_\text{avg}$ (average) positions are straightforward to interprete and are directly calculated from $\mu$ and $\sigma$:
+The distribution's median $x_\text{med}$ and mean $x_\text{avg}$ (average) positions are easily interpreted and are directly calculated from $\mu$ and $\sigma$:
         \begin{align}
                 x_\text{med} &= \exp\left(\mu\right)    &       &\Longleftrightarrow    &       \mu &= \ln\left(x_\text{med}\right)\,,      \label{eq:lognormal_median}\\
-		x_\text{avg} &= \exp\left(\mu + \frac{\sigma^2}{2}\right)	&	&\Longleftrightarrow	&	\sigma &= \sqrt{2 \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)}\,.	\label{eq:lognormal_mean}
+                x_\text{avg} &= \exp\left(\mu + \frac{\sigma^2}{2}\right)       &       &\Longleftrightarrow    &       \sigma &= \sqrt{2 \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)}\,.
+\label{eq:lognormal_mean}
         \end{align}
@@
         \begin{align}
-		W(x) = \frac{1}{2 \sqrt{\pi \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)} \, x} \, \exp\left(- \frac{\ln^2\left(\frac{x}{x_\text{med}}\right)}{4 \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)}\right)\,.	\label{eq:single_lognormal_fit_function}
+                W(x) = \frac{1}{2 \sqrt{\pi \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)} \, x} \, \exp\left(- \frac{\ln^2\left(\frac{x}{x_\text{med}}\right)}{4 \ln\left(\frac{x_\text{avg}}{x_\text{med}}\right)}\right)\,.
+\label{eq:single_lognormal_fit_function}
         \end{align}
-	The values of $x_\text{med}$ and $x_\text{avg}$ obtained from fitting the individual solar wind frequency distributions are listed in Table~\ref{tab:lognormal_fit_parameters}.
+        The values of $x_\text{med}$ and $x_\text{avg}$ obtained from fitting the individual solar-wind frequency distributions are listed in Table~\ref{tab:lognormal_fit_parameters}.
         \begin{table*}
-		\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions from near \SI{1}{\au} OMNI hourly data.
-For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit.
-The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+                \caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar-wind parameters' frequency distributions from near \SI{1}{\au} OMNI hourly data.
+For the velocity, the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are also listed, as well as the median and mean values of the resulting velocity fit.
+The numbers in parentheses are the errors on the corresponding last digits of the quoted value.
 They are calculated from the estimated standard deviations of the fit parameters.
-For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
+For each parameter, the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}
                 \label{tab:lognormal_fit_parameters}
@@
 
-	From visual inspection, the resulting fit curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+        From visual inspection, the resulting fit curves describe the shape of the magnetic field strength, the density and the temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
         \begin{figure*}
                 \includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
-		\caption{Frequency distributions of the four solar wind parameters and their lognormal fits derived from the hourly OMNI data set.
+                \caption{Frequency distributions of the four solar-wind parameters and their lognormal fits derived from the hourly OMNI data set.
 The histograms have bins of \SI{0.5}{\nT}, \SI{10}{\km\per\s}, \SI{1}{\per\cm\cubed} and \SI{10000}{\K}.
 The fits' median and mean values are indicated as well.
-The insets show zoomed-in views of the high value tails of the distributions.}
+The insets show zoomed-in views of the high-value tails of the distributions.}
                 \label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
         \end{figure*}
-	However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
-This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} in percentage of the distribution area, being almost three times larger than those from the other parameters.
-
+        However, for the velocity, the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range.
+This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} as a percentage of the distribution area, being almost three times larger than those from the other parameters.
         In order to find a better fit result for the velocity distribution, we assume that the velocity distribution can be made up of at least two overlapping branches \citep{McGregor2011b}.
@@
         The balancing parameter $c$ ensures that the resulting function remains normalized as it represents a probability distribution.
-	The fitting of $W_\text{II}(x)$ to the velocity's frequency distribution yields the values of the now five fit parameters ($c$, $x_\text{med,1}$, $x_\text{avg,1}$, $x_\text{med,2}$ and $x_\text{avg,2}$) as listed in Table~\ref{tab:lognormal_fit_parameters} together with the median and mean values of the composed distribution, which can be derived via solving
+        The fitting of $W_\text{II}(x)$ to the velocity's frequency distribution yields the values of the now five fit parameters ($c$, $x_\text{med,1}$, $x_\text{avg,1}$, $x_\text{med,2}$ and $x_\text{avg,2}$) as listed in Table~\ref{tab:lognormal_fit_parameters} together with the median and mean values of the composed distribution, which can be derived by solving
         \begin{align}
@@
         \end{figure}
-	Thus in the following sections we keep the double lognormal ansatz for all velocity frequency fits.
+        Thus in the following Sections we keep the double lognormal ansatz for all velocity frequency fits.
 
         For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well.
-The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.
-The simple lognormal fit functions underestimate the frequencies in their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}, this appears to be because CMEs do not come with abnormally high temperatures, but rather with temperatures lower than those of the average solar wind \citep{Forsyth2006}.
+The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar-wind investigations by \citet{Richardson2012}.
+The simple lognormal fit functions underestimate the frequencies in their high-value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}.
+This appears to be because CMEs do not come with abnormally high temperatures, but rather with temperatures lower than those of the average solar wind \citep{Forsyth2006}.
 The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
@@
 
-	\section{Solar activity dependence of the solar wind frequency distributions}
+        \section{Solar activity dependence of the solar-wind frequency distributions}
         \label{sec:solar_activity_variations}
-	In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity.
+        In the next step we investigate how the long-term solar-wind distribution functions presented in the previous section depend on general solar activity.
 Therefore we examine their correlation with the SSN, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.
@@
 For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN.
-Thus we obtain solar activity depending models for the frequency distributions of all four solar wind parameters.
+Thus we obtain solar-activity-dependent models for the frequency distributions of all four solar-wind parameters.
 
-	The international sunspot number (\citeyear{sidc}) is provided by the online catalogue\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
+        The international sunspot number (\citeyear{sidc}) is provided by the online catalog\footnote{\url{http://www.sidc.be/silso/}} at the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO), Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).
 
-	Yearly medians of the solar wind parameters and the yearly SSN together with the solar cycle number are shown in the upper part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.
-The reason for correlating the SSN to the solar wind median values is because the position of a lognormal function is defined by its median.
+        Yearly medians of the solar-wind parameters and the yearly SSN together with the solar cycle number are shown in the upper part of Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.
+The reason for correlating the SSN to the solar-wind median values is because the position of a lognormal function is defined by its median.
 The data are averaged to yearly values to avoid seasonal effects during the Earth’s orbit around the Sun caused by its variations in solar latitude and distance.
@@
                 \resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
-		\caption{Solar wind parameter yearly frequencies (grey shading) with yearly medians (lines) derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
+                \caption{Solar-wind parameter yearly frequencies (gray shading) with yearly medians (lines) derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
 Their correlation coefficients with the yearly SSN are calculated for time lags back to -15 years (bottom).}
@@
         \end{figure}
-	The solar wind velocity, density and temperature depend on the state of the solar cycle \citep{Schwenn1983}.
-	For instance the fast solar wind occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle as pointed out by \citet[p.~75, Figure~3.52]{Bothmer2007}.
-Therefore the solar wind velocity, density and temperature maxima exhibit time lags relative to the SSN maxima.
+        The solar-wind velocity, density, and temperature depend on the state of the solar cycle \citep{Schwenn1983}.
+        For instance the fast solar wind occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle as pointed out by \citet[p.~75, Fig.~3.52]{Bothmer2007}.
+Therefore the solar-wind velocity, density, and temperature maxima exhibit time lags relative to the SSN maxima.
 
@@
 As expected, the amplitudes of the variations in the correlations of all parameters decline with increasing time lag and show a period of about 11~years.
-The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength, it has no time lag.
+The highest correlation coefficient of 0.728 to the SSN is found for the magnetic field strength; it has no time lag.
 This finding is anticipated because the SSN is found to be directly proportional to the evolution of the photospheric magnetic flux \citep{Smith2003}.
@@
 
-	Next we create solar activity dependent analytical representations of the solar wind frequency distributions.
+        Next we create solar-activity-dependent analytical representations of the solar wind frequency distributions.
 This is achieved by shifting the median positions of the lognormal distributions as a linear function of the SSN.
-To enable these shifts, we add a linear SSN dependency to the median
+To enable these shifts, we add a linear SSN dependency to the median,
         \begin{align}
@@
 For the velocity the fit parameters from the double lognormal fit (\ref{eq:double_lognormal_fit_function}) and their balancing function (\ref{eq:balance_with_ssn}) are given.
-The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+The numbers in parentheses are the errors on the corresponding last digits of the quoted value.
 They are calculated from the estimated standard deviations of the fit parameters.
@@
 
-	Naturally, the fit models match with the general data trends, as can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994 and 2003).
+        Naturally, the fit models match with the general data trends, as can be seen from Fig.~\ref{fig:OMNI_yearly_BVdblNTSSN_fit_e_plot}, though single year variations are not replicated by the model (e.g., the high velocity and temperature values in 1974, 1994, and 2003).
         \begin{figure*}
@@
                 \caption{Solar wind parameter yearly data frequencies and lognormal fit models, both with their median values (white lines) over the OMNI time period 1963--2016.
-The corresponding yearly SSN and the shifted SSN for the models are indicated by grey and black lines.
+The corresponding yearly SSN and the shifted SSN for the models are indicated by gray and black lines.
 The velocity median is derived from the SSN-weighted constant lognormal parts (dotted lines).}
@@
         \end{figure*}
-	The comparison of this model with the yearly data median values with respect to the lagged SSN shows that the medians obtained from the modeling have a quite similar slope, as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
+        The comparison of this model with the yearly data median values with respect to the lagged SSN shows that the medians obtained from the modeling have a similar slope, as shown in Fig.~\ref{fig:OMNI_yearly_BVNTvsSSN_a}.
         \begin{figure}
                 \resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN_a.pdf}}
-		\caption{Solar wind parameter medians with respect to the lagged SSN.
+                \caption{Solar-wind parameter medians with respect to the lagged SSN.
 The yearly data medians (+) with their weighted linear fit (solid lines) are obtained from OMNI data.
@@
 
-	Again, the solar wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
-Since it is well known that slow and fast solar wind stream occurrence rates follow the solar cycle, we keep the two velocity components' positions SSN-independent ($x_\text{med} =  b_\text{med}$) and vary instead their balance with the SSN:
+        Again, the solar-wind velocity needs a special treatment because of the application of the double lognormal distribution (\ref{eq:double_lognormal_fit_function}).
+Since it is well known that slow and fast solar-wind stream occurrence rates follow the solar cycle, we keep the two velocity components' positions SSN-independent ($x_\text{med} =  b_\text{med}$) and vary instead their balance with the SSN:
         \begin{align}
@@
                 \resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_f_plot.pdf}}
-		\caption{Ratio of slow to fast solar wind for a by 3~years lagged SSN.
+                \caption{Ratio of slow to fast solar wind for a SSN lagged by 3~years.
 The yearly ratios (+) and their weighted linear fit (solid line) are obtained from OMNI data with a threshold velocity of $v_\text{th} = \SI{400}{\km\per\s}$.
@@
 The linear fit to the yearly data ratio and the derived model ratio show a good agreement (see Fig.~\ref{fig:Vdbl_SSN_ratio_f_plot}).
-The to some degree steeper balance parameter of the double fit function used in this model cannot be compared directly with specific velocity thresholds between slow and fast solar wind.
+The to-some-degree steeper balance parameter of the double fit function used in this model cannot be compared directly with specific velocity thresholds between slow and fast solar wind.
 However, it appears to be a more realistic approach than just taking a specific velocity threshold for the slow and fast wind, in agreement with the overlapping nature of the velocity flows reported by \citet{McGregor2011b}.
@@
         We investigate hourly averages of the Helios data in the same way as with the OMNI data.
-The Helios~1 merged hourly data from the magnetometer and plasma instruments \citep{Rosenbauer1977} include $\sim$12.5~orbits for the time range 10~December 1974 until 14~June 1981, those for Helios~2 include $\sim$8~orbits for the time span 1~January 1976 until 4~March 1980.
+The Helios~1 merged hourly data from the magnetometer and plasma instruments \citep{Rosenbauer1977} include $\sim$12.5~orbits for the time range 10~December 1974 to 14~June 1981, and those for Helios~2 include $\sim$8~orbits for the time span 1~January 1976 to 4~March 1980.
 The data are retrieved from the Coordinated~Data~Analysis~Web (CDAWeb) interface at NASA's GSFC/SPDF\footnote{\url{http://spdf.gsfc.nasa.gov/}}.
 
-	The Helios~1 magnetometer data coverage for this data set is about \SI{43}{\%} (i.e., 2.8~years), that of Helios~2 amounts to \SI{54}{\%} (i.e., 2.3~years).
+        The Helios~1 magnetometer data coverage for this data set is about \SI{43}{\%} (i.e., 2.8~years), and that of Helios~2 amounts to \SI{54}{\%} (i.e., 2.3~years).
 The plasma data coverage is \SI{76}{\%} (i.e., 5.0~years) in case of Helios~1 and \SI{92}{\%} (i.e., 3.9~years) in case of Helios~2.
@@
 Considering the data gap distributions, the amount of data during solar cycle minimum up to mid~1977, that is, the transition from minimum to maximum, covers about \SI{68}{\percent} of this period whereas during maximum of cycle~21 data are available only \SI{38}{\percent} of the time.
-This Helios data bias towards solar minimum is one reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar cycle dependencies for the key solar wind parameters.
+This Helios data bias towards solar minimum is one reason why in this study the Helios solar wind data are not used to derive long-term frequency distributions and solar-cycle dependencies for the key solar wind parameters.
 
-	The radial dependencies of the key solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.
+        The radial dependencies of the key solar-wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.
         \begin{figure*}
@@
         \end{figure*}
-	Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
-Therefore we use the power law function
+        Assuming a radial solar-wind outflow, it is expected that the distance dependence of the solar-wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling.
+Therefore we use the power law function,
         \begin{align}
-		x(r) = d\cdot r^e	\label{eq:power_function}
+                x(r) = d\cdot r^e,       \label{eq:power_function}
         \end{align}
@@
                 \caption{Fit coefficients for the median and mean solar distance dependencies (\ref{eq:power_function}) of the four solar wind parameters derived from the combined Helios~1 and 2 data.
-The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+The numbers in parentheses are the errors on the corresponding last digits of the quoted value.
 They are calculated from the estimated standard deviations of the fit parameters.
@@
 
-	The mean and median velocity fit exponents acquired from the Helios data are very similar, which indicates that they just as well can be kept identical so that the basic shape of the frequency distribution does not change with distance.
-Contrary, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} (see Table~\ref{tab:mean_median_fit_parameter}) and the mean is getting slightly lower than the median at smaller distances.
-Thus, below that distance the frequency distribution cannot well be described anymore by a lognormal function, because the mean of a lognormal function has to be larger than its median (as pointed out in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is not anymore of a lognormal shape thereafter.
+        The mean and median velocity fit exponents acquired from the Helios data are very similar, which indicates that they can be kept identical so that the basic shape of the frequency distribution does not change with distance.
+Conversely, the mean and median fits for the magnetic field strength cross each other at \SI{0.339}{\au} (see Table~\ref{tab:mean_median_fit_parameter}) and the mean becomes slightly lower than the median at smaller distances.
+Thus, below that distance the frequency distribution can no longer be well described by a lognormal function, because the mean of a lognormal function has to be larger than its median (as pointed out in Sect.~\ref{sec:frequency_distribution}), that is, the location of the crossing indicates that the parameter's distribution is no longer of a lognormal shape thereafter.
 The fits for the proton temperature show a similar behavior, having an extrapolated intersection at \SI{0.082}{\au}.
@@
         In order to still fit and extrapolate lognormal functions with the data, we assume that the shapes can be considered lognormal at all distances.
-For the frequency distribution fit function to be discussed in the next paragraph, we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
+For the frequency distribution fit function to be discussed in the following paragraph, we reduce the fit exponents $e_\text{med}$ and $e_\text{avg}$ to only one.
 We note that this simplification leads to slightly larger modeling errors, especially in case of the magnetic field strength.
@@
         \begin{table*}
-		\caption{Fit coefficients for the distance depending single lognormal function, based on equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}), respectively double lognormal function (\ref{eq:double_lognormal_fit_function}) for the velocity from the combined Helios data.
-The numbers in parentheses are the errors referred to the corresponding last digits of the quoted value.
+                \caption{Fit coefficients for the distance-dependent single lognormal function, based on Equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}) from the combined Helios data.
+Regarding the velocity, the double lognormal function (\ref{eq:double_lognormal_fit_function}) is used instead.
+The numbers in parentheses are the errors on the corresponding last digits of the quoted value.
 They are calculated from the estimated standard deviations of the fit parameters.
@@
 The model’s magnetic field strength is broader around values of \SI{40}{nT} at the lower distance boundary than the data's frequency distribution implies.
-This behavior is expected because of the distance independent shape approximation applied.
-The velocity and temperature models’ upper values generally show a higher abundance than the actual data, see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
-The high velocity tail that increases with distance arises from using the same exponent for both slow and fast components.
-This effect is not seen in the data, more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
+This behavior is expected because of the applied distance-independent shape approximation.
+The velocity and temperature models’ upper values generally show a higher abundance than the actual data; see also zoom boxes in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
+The high-velocity tail that increases with distance arises from using the same exponent for both slow and fast components.
+This effect is not seen in the data; more specifically, not only the slowest wind but also the fastest wind is expected to converge to more average speeds \citep{Sanchez-Diaz2016}.
 
-	\section{Empirical solar wind model}
+        \section{Empirical solar-wind model}
         \label{sec:empirical_solar_wind_model}
-	In order to estimate the solar wind environment for the PSP orbit, we combine the results from the solar wind frequency distributions’ solar activity relationships and their distance dependencies derived from the OMNI and Helios data.
-The result is an empirical solar wind model for the inner heliosphere which is then extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+        In order to estimate the solar-wind environment for the PSP orbit, we combine the results from the solar-wind frequency distributions’ solar-activity relationships and their distance dependencies derived from the OMNI and Helios data.
+The result is an empirical solar-wind model for the inner heliosphere which is then extrapolated to the PSP orbit in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 
-	This solar wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
-The variations of the yearly power law fit exponents from fitting the solar distance dependency (\ref{eq:power_function}) are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
+        This solar-wind model for the radial distance dependence is representative for the time of the Helios observations around the rise of solar cycle~21.
+The variations of the yearly power law fit exponents from fitting the solar-distance dependency (\ref{eq:power_function}) are shown in Fig.~\ref{fig:yearly_gradients_c} together with the yearly SSN for the time period \numrange{1974}{1982}.
 It can be seen that during the Helios time period there might be some systematic  variation of the exponents with solar activity -- at least for the velocity and temperature exponents.
@@
 The weighted standard deviations and average values for all years are indicated by the shaded areas.
-In this plot the 21~days since Helios launch in the year 1974 are omitted because a distance range of merely \SIrange{0.95}{0.98}{\au} was covered that year.}
+In this plot, the 21~days since Helios launch in the year 1974 are omitted because a distance range of merely \SIrange{0.95}{0.98}{\au} was covered that year.}
                 \label{fig:yearly_gradients_c}
@@
         Thus, implementing the median and mean relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), we obtain the combined model function $W'''(x,ssn,r)$ and for the velocity $W_\text{II}'''(x,ssn,r)$ with the double lognormal function (\ref{eq:double_lognormal_fit_function}).
-The corresponding median and mean relations for each solar wind parameter, based on the values resulting from our analyses, are listed below.
+The corresponding median and mean relations for each solar-wind parameter, based on the values resulting from our analyses, are listed below.
 Their numerical values are the fit parameters from Table~\ref{tab:ssn_fit_parameters} and the exponents from Table~\ref{tab:extrapolation_model_fit_parameters}.
@@
                 \begin{align}
-			n_\text{med}(ssn,r) &= \left(\SI{0.0038}{\per\cm\cubed} \cdot ssn + \SI{4.50}{\per\cm\cubed}\right) \cdot r^{-2.11}	\,,	\label{eq:median_n}\\
-			n_\text{avg}(ssn,r) &= 1.305 \cdot n_\text{med}(ssn,r)\,.
+                        n_\text{med}(ssn,r) &= \left(\SI{0.0038}{\per\cm\cubed} \cdot ssn + \SI{4.50}{\per\cm\cubed}\right) \cdot r^{-2.11}     \,,     \label{eq:median_n}\\                   n_\text{avg}(ssn,r) &= 1.305 \cdot n_\text{med}(ssn,r)\,.
                 \end{align}
@@
         These relations average over seasonal variations because they are based on yearly data.
-The OMNI data are time-shifted to the nose of the Earth’s bow shock, this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
-The resulting maximal solar wind parameter variation amplitudes over the year can thus be derived from the derived power law exponents.
-They are estimated to be smaller than \SI{4}{\percent} as seen in Tab.~\ref{tab:extrapolation_model_fit_parameters}.
-\citet{Bruno1986} and \citet{Balogh1999} have pointed out, that the solar wind parameters vary with latitudinal separation from the heliospheric current sheet.
-Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990}, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
+The OMNI data are time-shifted to the nose of the Earth’s bow shock; this leads to yearly solar distance variations of \SI{+-1.67}{\%} as it orbits the Sun.
+The resulting maximal solar-wind parameter variation amplitudes over the year can thus be derived from the derived power law exponents.
+They are estimated to be smaller than \SI{4}{\percent} as seen in Table~\ref{tab:extrapolation_model_fit_parameters}.
+\citet{Bruno1986} and \citet{Balogh1999} have pointed out that the solar-wind parameters vary with latitudinal separation from the heliospheric current sheet.
+Its position in heliographic latitude is highly variable around the solar equator \citep{Schwenn1990} and, furthermore, the Earth’s orbit varies over the course of the year by \SI{+-7.2}{\degree} in latitude.
 Since this latitudinal separation is highly variable and requires significant effort to calculate for an extended time series, we have ignored this aspect in this analysis.
@@
         \label{sec:model_extrapolation_to_psp_orbit}
-	To estimate PSP’s solar wind environment during its mission time for its orbital positions, predictions of the SSN during the mission are incorporated into the empirical solar wind model, derived in the previous sections, and extrapolations down to the PSP perihelion region are performed.
+        To estimate PSP’s solar-wind environment during its mission time for its orbital positions, predictions of the SSN during the mission are incorporated into the empirical solar-wind model, derived in the previous Sections, and extrapolations down to the PSP perihelion region are performed.
 
         Parker Solar Probe is planned to launch in mid 2018.
-With its first Venus flyby it will swing into Venus' orbital plane, reaching already 93~days after launch in November 2018 a first perihelion with a distance of \SI{0.16}{\au}.
+With its first Venus flyby it will swing into Venus' orbital plane, reaching  a first perihelion with a distance of \SI{0.16}{\au  } just 93~days
+after launch, in November 2018.
 Seven additional Venus flybys allow the perihelion distance to be reduced to a minimum of \SI{9.86}{\Rs}.
@@
 
-	We extrapolate the derived empirical solar wind models to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}.
+        We extrapolate the derived empirical solar-wind models to PSP’s orbital distance range and compare the results with those from the existing models shown in Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}.
         \begin{figure*}
                 \includegraphics[width=18cm]{figures/sw_extrapolation_ssn_f_plot.pdf}
-		\caption{Radial extrapolation of the solar wind parameters to the PSP orbit region.
-The median values from the models, obtained from Helios and OMNI measurements, are extrapolated to the PSP region for SSN values between solar minimum and maximum, i.e., $0 \le ssn \le 200$.
+                \caption{Radial extrapolation of the solar-wind parameters to the PSP orbit region.
+The median values from the models, obtained from Helios and OMNI measurements, are extrapolated to the PSP region for SSN values between solar minimum and maximum, that is, $0 \le ssn \le 200$.
 The lower edges of the shaded areas correspond to solar minimum, the upper edges to solar maximum.
@@
         \end{figure*}
-	The model and its extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the figure.
-	The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of 0.
+        The model and its extrapolation are visualized for the SSN range between solar minimum and maximum ($0 \le ssn \le 200$), indicated by the shaded regions in the Figure.
+        The magnetic field strength is found to increase from median values of about \SI{43}{\nT} at \SI{0.25}{\au} to \SI{715}{\nT} at \SI{0.046}{\au} for a SSN of zero.
 Taking a SSN of 200 increases the values to \SI{69}{\nT} and \SI{1152}{\nT}.
 Our extrapolation results are slightly flatter than those derived from the analytical magnetic field model by \citet{Banaszkiewicz1998}, who constructed an analytic dipole plus quadrupole plus current sheet (DQCS) model for solar minimum.
-We note that one cannot straightforeward compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar wind belt.
+We note that one cannot easily compare the absolute values of our study with the values obtained by \citet{Banaszkiewicz1998} because the DQCS model assumes solar wind originating from coronal holes at higher heliographic latitudes only, neglecting the slow solar-wind belt.
         We suggest that the difference in slope is due to the previously mentioned (Sect.~\ref{sec:solar_distance_dependency}) changing shape of the frequency distribution with heliocentric distance, which for smaller distances deviates more from the model’s lognormal distribution.
-	The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} 3~years after a SSN of 0 occurred, whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
-Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar wind velocity values for distances below about \SI{20}{\Rs}.
+        The average velocity is found to decrease from \SI{340}{\km\per\s} at \SI{0.25}{\au} to about \SI{290}{\km\per\s} at \SI{0.046}{\au} 3~years after a SSN of zero occurred, whereas using a SSN of 200 it decreases from \SI{390}{\km\per\s} to \SI{330}{\km\per\s}.
+Comparing the results with the measurements by \citet{Sheeley1997} and \citet{Wang2000} shows an overestimation in our extrapolated slow solar-wind velocity values for distances below approximately \SI{20}{\Rs}.
 They used LASCO coronagraph observations to track moving coronal features (blobs) in the distance range \SIrange{2}{30}{\Rs} to determine speed profiles and sources of the slow solar wind and they derived temperature and sonic point values for slow solar wind with the isothermal expansion model from \citet{Parker1958}.
-Therefore, it generally can be expected that PSP will encounter a slower solar wind environment close to the Sun than our model estimates.
-Thus PSP will measure solar wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
-	The proton density increases from about \SI{84}{\per\cm\cubed} at \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} 6~years after a SSN of 0 occurred.
-Being almost independent of the SSN the values for a SSN of 200 are only \SI{17}{\%} larger.
+Therefore, it generally can be expected that PSP will encounter a slower solar-wind environment close to the Sun than our model estimates.
+Thus PSP will measure solar-wind acceleration processes \citep{McComas2008}, maybe even still at \SI{30}{\Rs} as the study by \citet{Sheeley1997} suggests.
+        The proton density increases from about \SI{84}{\per\cm\cubed} at \SI{0.25}{\au} to about \SI{3018}{\per\cm\cubed} at \SI{0.046}{\au} 6~years after a SSN of zero occurred.
+Being almost independent of the SSN, the values for a SSN of 200 are only \SI{17}{\%} larger.
 The results are in good agreement with those of \citet{Leblanc1998}, who derived an electron density model from type~III radio burst observations.
 Their model shows that the density distance dependency scales with $r^{-2}$ and steepens just below \SI{10}{\Rs} with $r^{-6}$.
-We assumed a solar wind helium abundance of \SI{5}{\%} to convert these electron densities to proton densities.
-	The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} 3~years after a SSN of 0 occurred and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
+We assumed a solar-wind helium abundance of \SI{5}{\%} to convert these electron densities to proton densities.
+        The extrapolated proton temperature increases from about \SI{260000}{\K} at \SI{0.25}{\au} to about \SI{1690000}{\K} at \SI{0.046}{\au} 3~years after a SSN of zero occurred and from \SI{440000}{\K} to \SI{2860000}{\K} for a SSN of 200.
 Knowing that near-Sun coronal temperatures are in the range of \SIrange{2}{3}{\mega\K} \citep{Billings1959,Liebenberg1975}, the model overestimates the extrapolated temperatures at the PSP perihelion distance.
 
-	Aside from the solar distance the derived solar wind parameter models depend on the SSN.
-Short-term predictions of the SSN can be used for the solar wind predictions of PSP's early perihelia and also for refining the solar wind predictions during PSP's mission.
+        Aside from the solar distance, the derived solar-wind parameter models depend on the SSN.
+Short-term predictions of the SSN can be used for the solar-wind predictions of PSP's early perihelia and also for refining the solar-wind predictions during PSP's mission.
 Several sources are available for SSN short-term predictions.
 The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g., Kalman filter Standard Curve method).
-The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) follows for the time period until end of 2019 a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
-	The SSN for PSP's first perihelion will be small -- certainly below 20, whereas the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.
-However \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
+The SSN prediction of NOAA's Space Weather Prediction Center (SWPC) for the time period until the end of 2019 follows  a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://www.swpc.noaa.gov/products/solar-cycle-progression}}.
+        The SSN for PSP's first perihelion will be small -- certainly below 20 -- whereas the SSN during the closest perihelia, which will commence at the end of 2024 at the likely maximum phase of cycle~25, cannot be predicted at this time.
+However, \citet{Hathaway2016} found indications that the next solar cycle will be similar in size to the current cycle~24.
 Therefore we simply assume a pattern similar to the last cycle for the prediction of the next solar cycle and thus shift the last cycle by 11~years.
-Additionally we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
+Additionally, we consider as possible alternatives SSN patterns of half and twice its amplitude as shown in the bottom panel of Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_f_plot}.
 
-	Implementing the SSN predictions for the PSP mission time and the orbital trajectory data, we can infer which solar wind parameter magnitudes can be expected.
-Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the median values (\ref{eq:median_with_ssn}) of the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the first closest perihelion in December 2024.
+        Implementing the SSN predictions for the PSP mission time and the orbital trajectory data, we can infer which solar-wind parameter magnitudes can be expected.
+Figures~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the median values (\ref{eq:median_with_ssn}) of the considered different solar-wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the first closest perihelion in December 2024.
         \begin{figure}
                 \resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
-		\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
+                \caption{Estimated solar-wind parameter medians (black lines) and their error bands (gray) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
 For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
@@
                 \resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
-		\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's 22nd (the first closest) perihelion at \SI{0.0459}{\au}.
+                \caption{Estimated solar-wind parameter medians (black lines) and their error bands (gray) during 12~days in 2024 with PSP's 22nd (the first closest) perihelion at \SI{0.0459}{\au}.
 For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
@@
         In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the first closest approach at \SI{0.046}{\au}.
-Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions.
-These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
-The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.
+Monthly SSNs -- shifted by the time lags specific to the solar-wind parameters -- are used in the calculation of the solar-wind predictions.
+These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges, or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties.
+The error bands given in both Figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.
 
-	Finally the estimated solar wind environment can be derived from the function $W'''(x,ssn,r)$.
-The estimated frequency distributions of the four solar wind parameters at PSP's first and 22nd (first closest) perihelion are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.
+        Finally the estimated solar-wind environment can be derived from the function $W'''(x,ssn,r)$.
+The estimated frequency distributions of the four solar-wind parameters at PSP's 1st and 22nd (first closest) perihelion are plotted in Fig.~\ref{fig:SPP_sw_distributions_b}.
         \begin{figure}
                 \resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions_b.pdf}}
-		\caption{Frequency distributions of the four solar wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar wind model for PSP's first and 22nd (first closest) perihelion.
-In these figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}
+                \caption{Frequency distributions of the four solar-wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar-wind model for PSP's 1st and 22nd (first closest) perihelion.
+In these Figures the frequencies of both extrapolated curves are scaled for visibility to the same height as the \SI{1}{\au} distribution.}
                 \label{fig:SPP_sw_distributions_b}
@@
         \label{sec:discussion_and_summary}
-	The scientific objective of this study, being part of the CGAUSS project -- the German contribution to the WISPR instrument, is to model the solar wind environment for the PSP mission to be launched mid 2018.
-For this purpose we started the development of the empirical solar wind environment model for the near-ecliptic PSP orbit.
-We derived lognormal representations of the in situ near-Earth solar wind data collected in the OMNI database, using the frequency distributions of the key solar wind parameters magnetic field strength, proton velocity, density and temperature.
-Throughout the different analyses in our study the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
+        The scientific objective of this study, being part of the CGAUSS project -- the German contribution to the WISPR instrument -- is to model the solar-wind environment for the PSP mission to be launched mid 2018.
+For this purpose we started the development of the empirical solar-wind environment model for the near-ecliptic PSP orbit.
+We derived lognormal representations of the in situ near-Earth solar-wind data collected in the OMNI database, using the frequency distributions of the key solar-wind parameters, magnetic field strength, proton velocity, density, and temperature.
+Throughout the different analyses in our study, the velocity's frequency distribution is treated as a composition of a slow and a fast wind distribution.
 Each velocity part is fitted with a lognormal function, which allows for the overlap of both velocity ranges.
-The OMNI multi-spacecraft solar wind data is intercalibrated and covers almost five solar cycles.
+The OMNI multi-spacecraft solar-wind data is intercalibrated and covers almost five solar cycles.
 It thus represents solar wind gathered at different phases of solar activity in the ecliptic plane.
-In the next step we investigated the yearly variation of the solar wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar wind parameters with the SSN.
-The radial dependencies of the solar wind distribution functions were then analyzed, using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}, deriving power law fit functions that were used to scale the prior calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, taking into account SSN predictions for the years 2018--2025, encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.
-The reason for performing the analysis this way is based on the fact that the OMNI solar wind database is much larger than the Helios database.
+In the next step we investigated the yearly variation of the solar-wind distribution functions along with the SSN over 53~years and derived linear dependencies of the solar-wind parameters with the SSN.
+The radial dependencies of the solar-wind distribution functions were then analyzed, using Helios~1 and 2 data for the distance range \SIrange{0.29}{0.98}{\au} in bins of \SI{0.01}{\au}, deriving power law fit functions that were used to scale the previously calculated SSN-dependent \SI{1}{\au} distribution fit functions to the PSP orbit, taking into account SSN predictions for the years 2018--2025, encompassing the prime mission up to the closest approach of \SI{9.86}{\Rs}.
+The reason for performing the analysis this way is based on the fact that the OMNI solar-wind database is much larger than the Helios database.
 
-	For determining solar activity and solar distance dependent relations for the median and mean solar wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
+        For determining solar-activity- and solar-distance-dependent relations for the median and mean solar-wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
 It is expected that the results of a simpler analysis would have similar distance scaling results, as can be inferred from the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}.
@@
 
-	It is clear that the calculated distribution functions just represent first order estimates of the real solar wind to be encountered by PSP.
-The solar wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar wind streams and superimposed CMEs and shocks.
-However, the derived results are in good agreement with existing studies about near-Sun solar wind magnetic field strenghts and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
+        It is clear that the calculated distribution functions only represent first-order estimates of the real solar wind to be encountered by PSP.
+The solar-wind environment to be encountered will depend at times of PSP on the structure of the solar corona and underlying photospheric magnetic field and on the evolution and interaction of individual solar-wind streams and superimposed CMEs and shocks.
+However, the derived results are in good agreement with existing studies about near-Sun solar-wind magnetic field strengths and densities as shown in Sect.~\ref{sec:model_extrapolation_to_psp_orbit}.
 The extrapolation results of the velocity and the temperature differ from the direct measurements seen in existing studies.
 This suggests that below about \SI{20}{\Rs} PSP may dive into the region where the acceleration and heating of the solar wind is expected to occur (see Fig.~\ref{fig:sw_extrapolation_ssn_f_plot}).
-The near-Sun solar wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar maximum \citep{Katsikas2010,Goelzer2014}.
+The near-Sun solar-wind velocity at PSP perihelion is also expected to be slower than our model estimates, because the solar wind is assumed to be accelerated up to the height of the Alfvénic critical surface, which is predicted to lie on average around \SI{17}{\Rs} \citep[e.g.,][]{Sittler1999,Exarhos2000}, scaling with solar activity within a range of between \SI{15}{\Rs} at solar minimum and \SI{30}{\Rs} at solar maximum \citep{Katsikas2010,Goelzer2014}.
 
-	We have not specifically investigated the occurrences of extreme solar wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
-The Helios solar wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar wind velocities, which are associated with individual CMEs.
-The results by \citet{Sachdeva2017} indicate that due to solar wind drag, the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
+        We have not specifically investigated the occurrences of extreme solar-wind parameters caused by CMEs or enhanced values due to stream interaction or co-rotating interaction regions.
+The Helios solar-wind measurements plotted over radial distance in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip} show several extreme values far above the usual solar-wind velocities, which are associated with individual CMEs.
+The results by \citet{Sachdeva2017} indicate that due to solar-wind drag, the speeds of fast CMEs will commonly slow down substantially from early distances of a few solar radii.
 Therefore, it is expected that PSP will encounter CMEs with much higher speeds than those observed during the Helios mission.
-Also, the magnetic field, density and temperature values are expected to be much larger than in the average solar wind in individual fast shock associated CME events.
+Also, the magnetic field, density and temperature values are expected to be much larger than in the average solar wind in individual fast-shock-associated CME events.
 PSP will thus also substantially improve our understanding of the near-Sun evolution of CMEs and their expansion with radial distance.
 
-	With the resulting CGAUSS empirical solar wind model for PSP the following main results for the bulk solar wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
+        With the resulting CGAUSS empirical solar-wind model for PSP, the following main results for the bulk solar-wind parameters and estimations for their median values at PSP’s first perihelion in 2018 at a solar distance of \SI{0.16}{\au} and at PSP’s closest perihelia beginning in 2024 at \SI{0.046}{\au} (\SI{9.86}{\Rs}) are obtained:
         \begin{itemize}
-		\item The dependency of the magnetic field strength on solar activity and radial distance appears to be valid above \SI{20}{\Rs}, however near PSP's closest perihelia the actual values might be found to be slightly higher.
-		\item The estimated magnetic field strength median values obtained from relation (\ref{eq:median_B}) for PSP's first and 22nd perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
-		\item The radial dependencies of the proton velocity median values for slow and fast solar wind (\ref{eq:median_v}) appear to be valid above about \SI{20}{\Rs} solar distance, below they overestimate the actual solar wind velocities obtained from remote measurements.
-The share of their frequency distributions to the overall solar wind velocity distribution (\ref{eq:double_lognormal_fit_function}) is depending on solar activity with their balance relation (\ref{eq:balance_v}).
-Thus, at solar minimum with a SSN around 0 the slow wind component contributes about \SI{64}{\%} and drops to \SI{28}{\%} during solar maximum conditions with a SSN around 200.
-		\item The calculated median velocity values for PSP's first and 22nd perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
+                \item The dependency of the magnetic field strength on solar activity and radial distance appears to be valid above \SI{20}{\Rs}, however near PSP's closest perihelia, the actual values might be found to be slightly higher.
+                \item The estimated magnetic field strength median values obtained from relation (\ref{eq:median_B}) for PSP's 1st and 22nd perihelion are \SI{87}{\nT} and \SI{943}{\nT}.
+                \item The radial dependencies of the proton velocity median values for slow and fast solar wind (\ref{eq:median_v}) appear to be valid above about \SI{20}{\Rs} solar distance; below they overestimate the actual solar wind velocities obtained from remote measurements.
+The share of their frequency distributions to the overall solar-wind velocity distribution (\ref{eq:double_lognormal_fit_function}) depends on solar activity with their balance relation (\ref{eq:balance_v}).
+Thus, at solar minimum, with a SSN of around zero, the slow-wind component contributes about \SI{64}{\%} and drops to \SI{28}{\%} during solar maximum conditions with a SSN around 200.
+                \item The calculated median velocity values for PSP's 1st and 22nd perihelion are \SI{340}{\km\per\s} and \SI{290}{\km\per\s}.
                 \item The proton density relation appears to be valid throughout the full PSP orbital distance range, even down to about \SI{8}{\Rs}.
-		\item The estimated density median values obtained from relation (\ref{eq:median_n}) for PSP's first and 22nd perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
-		\item The derived correlation function for the proton temperature appears to provide too high temperature values around PSP’s closest perihelion in comparison to coronal measurements.
-		\item The estimated temperature median values obtained from relation (\ref{eq:median_T}) for PSP's first and 22nd perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
+                \item The estimated density median values obtained from relation (\ref{eq:median_n}) for PSP's 1st and 22nd perihelion are \SI{214}{\per\cm\cubed} and \SI{2951}{\per\cm\cubed}.
+                \item The derived correlation function for the proton temperature appears to provide overly high temperature values around PSP’s closest perihelion in comparison to coronal measurements.
+                \item The estimated temperature median values obtained from relation (\ref{eq:median_T}) for PSP's 1st and 22nd perihelion are \SI{503000}{\K} and \SI{1930000}{\K}.
         \end{itemize}
 
-	The results of the modeled solar wind environment will be useful to help optimize the WISPR and in situ instrument science plannings and PSP mission operations.
+        The results of the modeled solar-wind environment will be useful to help optimize the WISPR and in situ instrument science plannings and PSP mission operations.
 This also applies for the Heliospheric Imager (SoloHI) \citep{Howard2013} and the in situ instruments on board the Solar Orbiter spacecraft.

### 2017-11-17 paperMVVB_language_editor/31831_corr.tex
implemented the *.tex file from the language editor

--- 2017-11-17 paperMVVB_for_aanda/paperMVVB.tex
@@
+%
+
 \documentclass[]{aa}
@@
 \begin{document}
+
         \title{Solar-wind predictions for the Parker Solar Probe orbit}
@@
         The study presented in this paper is undertaken in the Coronagraphic German And US SolarProbePlus Survey (CGAUSS) project, which is the German contribution to the PSP mission as part of the Wide-field Imager for Solar PRobe (WISPR).
-WISPR will contribute to the PSP science goals by deriving the three-dimensional structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
+WISPR will contribute to the PSP science goals by deriving the three-dimaensional (3D) structure of the solar corona through which the in situ measurements are made to determine the sources of the solar wind.
 It will provide density power spectra over a wide range of structures (e.g., streamers, pseudostreamers and equatorial coronal holes) for determining the roles of turbulence, waves, and pressure-balanced structures in the solar wind.
@@
 The data coverage of the different parameters is in the range \SIrange{67}{74}{\percent},  corresponding to a total duration of 36--40~years.
-        We note that a test-comparison of hourly averaged data with higher-time-resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
+        We note that a test-comparison of hourly averaged data points with higher-time-resolution data for the available shorter time span 1981--2016 did not show significant differences in our results.
 According to the OMNI data precision and maximal parameter ranges we specify bin sizes of \SI{0.5}{\nT} for the magnetic field strength, \SI{10}{\km\per\s} for the velocity, \SI{1}{\per\cm\cubed} for the density and \SI{10000}{\K} for the temperature.
@@
                 \resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_f_plot.pdf}}
-                \caption{Ratio of slow to fast solar wind for a SSN lagged by 3~years.
+                \caption{Ratio of slow to fast solar wind for a\LEt{Please insert missing text.} by 3~years lagged SSN.
 The yearly ratios (+) and their weighted linear fit (solid line) are obtained from OMNI data with a threshold velocity of $v_\text{th} = \SI{400}{\km\per\s}$.
@@
         \begin{table*}
-                \caption{Fit coefficients for the distance-dependent single lognormal function, based on Equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}) from the combined Helios data.
-Regarding the velocity, the double lognormal function (\ref{eq:double_lognormal_fit_function}) is used instead.
+                \caption{Fit coefficients for the distance-dependent single lognormal function, based on Equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function}), respectively double lognormal function (\ref{eq:double_lognormal_fit_function}) for the velocity from the combined Helios data\LEt{The meaning of this second part of the sentence is unclear; please rephrase for improved clarity.}.
 The numbers in parentheses are the errors on the corresponding last digits of the quoted value.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}
-                \caption{Helios yearly variation of the solar wind parameter power exponents for the dependence on radial distance together with the SIDC 13-month smoothed monthly SSN.
+                \resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}         \caption{Helios yearly variation of the solar wind parameter power exponents for the dependence on radial distance together with the SIDC 13-month smoothed monthly SSN.
 The weighted standard deviations and average values for all years are indicated by the shaded areas.
@@
         \begin{figure*}
-                \includegraphics[width=18cm]{figures/sw_extrapolation_ssn_f_plot.pdf}
-                \caption{Radial extrapolation of the solar-wind parameters to the PSP orbit region.
+                \includegraphics[width=18cm]{figures/sw_extrapolation_ssn_f_plot.pdf}           \caption{Radial extrapolation of the solar-wind parameters to the PSP orbit region.
 The median values from the models, obtained from Helios and OMNI measurements, are extrapolated to the PSP region for SSN values between solar minimum and maximum, that is, $0 \le ssn \le 200$.
@@
 
-        For determining solar-activity- and solar-distance-dependent relations for the median and mean solar-wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
+        For determining solar-activity- and solar-distance-dependent relations\LEt{Please check that I have retained your intended meaning.} for the median and mean solar-wind values, we could have used the simpler approach of combining the radial dependence of averaged Helios data with averaged \SI{1}{\au} OMNI data scaled with the SSN.
 It is expected that the results of a simpler analysis would have similar distance scaling results, as can be inferred from the exponents in Tables~\ref{tab:mean_median_fit_parameter} and \ref{tab:extrapolation_model_fit_parameters}.

### 2017-11-20 paperMVVB_for_aanda/paperMVVB.tex
for aanda bib modified; for arXiv tex files modified

@@
         \institute{University of Goettingen, Institute for Astrophysics, Friedrich-Hund-Platz~1, 37077~Göttingen, Germany}
-        \date{Received 25 August 2017; accepted date}
+        \date{Received 25 August 2017; accepted 10 November 2017}
 
@@
         \begin{figure*}
-                \includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
+                \includegraphics[width=18cm]{histogram_fits_4_a_zoom_paper_pdfplot.pdf}
                 \caption{Frequency distributions of the four solar-wind parameters and their lognormal fits derived from the hourly OMNI data set.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/histogram_fits_V_a_zoom_dbl_paper_pdfplot.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{histogram_fits_V_a_zoom_dbl_paper_pdfplot.pdf}}
                 \caption{Velocity frequency distribution (same as in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}) and its compositional lognormal fit.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{OMNI_yearly_ssn_correlation_c_plot.pdf}}
                 \caption{Solar-wind parameter yearly frequencies (gray shading) with yearly medians (lines) derived from OMNI data and the yearly SSN from the \citet{sidc} with solar cycle number (top).
@@
         \begin{figure*}
-                \includegraphics[width=18cm]{figures/OMNI_yearly_BVdblNTSSN_fit_e_plot.pdf}
+                \includegraphics[width=18cm]{OMNI_yearly_BVdblNTSSN_fit_e_plot.pdf}
                 \caption{Solar wind parameter yearly data frequencies and lognormal fit models, both with their median values (white lines) over the OMNI time period 1963--2016.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_BVNTvsSSN_a.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{OMNI_yearly_BVNTvsSSN_a.pdf}}
                 \caption{Solar-wind parameter medians with respect to the lagged SSN.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_f_plot.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{Vdbl_SSN_ratio_f_plot.pdf}}
                 \caption{Ratio of slow to fast solar wind for a SSN lagged by 3~years.
@@
         \begin{figure*}
-                \includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_b_skip.pdf}
+                \includegraphics[width=18cm]{radial_fit_4_thesis_light_b_skip.pdf}
                 \caption{Helios hourly data plots of the four solar wind parameters over solar distance.
@@
         \begin{figure*}
-                \includegraphics[width=18cm]{figures/mixed_fit_fixed_4_paper_f_plot.pdf}
+                \includegraphics[width=18cm]{mixed_fit_fixed_4_paper_f_plot.pdf}
                 \caption{Frequency distributions of the four solar wind parameters with respect to solar distance.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/yearly_gradients_c.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{yearly_gradients_c.pdf}}
                 \caption{Helios yearly variation of the solar wind parameter power exponents for the dependence on radial distance together with the SIDC 13-month smoothed monthly SSN.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{SPP_orbit_predicted_SSN_overview_f_plot.pdf}}
                 \caption{PSP's solar distance during its mission time (top).
@@
         \begin{figure*}
-                \includegraphics[width=18cm]{figures/sw_extrapolation_ssn_f_plot.pdf}
+                \includegraphics[width=18cm]{sw_extrapolation_ssn_f_plot.pdf}
                 \caption{Radial extrapolation of the solar-wind parameters to the PSP orbit region.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{SPP_perihelia_prediction_f_plot.pdf}}
                 \caption{Estimated solar-wind parameter medians (black lines) and their error bands (gray) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{SPP_perihelia_prediction_nearest_f_plot.pdf}}
                 \caption{Estimated solar-wind parameter medians (black lines) and their error bands (gray) during 12~days in 2024 with PSP's 22nd (the first closest) perihelion at \SI{0.0459}{\au}.
@@
         \begin{figure}
-                \resizebox{\hsize}{!}{\includegraphics{figures/SPP_sw_distributions_b.pdf}}
+                \resizebox{\hsize}{!}{\includegraphics{SPP_sw_distributions_b.pdf}}
                 \caption{Frequency distributions of the four solar-wind parameters (same as in Figs.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot} and \ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}) and those estimated with the solar-wind model for PSP's 1st and 22nd (first closest) perihelion.
